### 2023-10-27 paper/manuscript.Rmd
initial commit

---
title: "TANGO-CC: An open-source website for researchers to build a culture-sensitive task of gaze understanding"
shorttitle: "measuring gaze understanding across the globe"
author:

  - name          : "Julia Christin Prein"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "julia_prein@eva.mpg.de"
    role          :
      - Conceptualization
      - Methodology
      - Software
      - Investigation
      - Formal Analysis
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

  - name          : "Daniel B. M. Haun"
    affiliation   : "1"
    role          :
      - Supervision
      - Writing - Review & Editing

  - name          : "Manuel Bohn"
    affiliation   : "1,2"
    role          :
      - Conceptualization
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "2"
    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"
abstract: |

keywords          : "cross-cultural psychology, social-cognitive development, gaze following, individual differences, reliability"
wordcount         : "XXX"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : yes 
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes   :
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options    : 
  markdown: 
    wrap: sentence
bibliography      : "../../references.bib"
---

```{r setup, include = FALSE}
library("tidyverse")
library("papaja")
library("kableExtra")
library("brms")
library("janitor")

theme_set(theme_classic())
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction
- increased interest in cc research but not many new methods that enable or ease cross cultural research
- hard to capture ind diff, even harder in cc settings
- goal: comparable data across cultural settings
- approach 1: standardized procedure, as similar as possible. taken here
- approach 2: see in each cultural setting how to translate the psychological construct into experiment
- prein2023tango: works for ind diff. reliable. 
- supplements prein2023variation: differences between animal & human faces

# Methods
- testing setups: rural & urban
- no prior touchscreen experience needed
- how does website work: which variables you can select
- output from website
- shiny app?!
- psychometric properties of tango germany
- describe cc sample

# Results
- splithalf per cultural setting
- effect of age distribution, different for each cultural setting
- in plot: weigh sample size: x: splithalf, y: culture, size geom count: sample size
- visualize ind diff
- plot training trials argument for children understand to touch balloon
- response time?
- droup outs across cultures

# Discussion
- flexibility for researchers
- adjust to each cultural setting: faces, languages, background scene
- easy to add new layers to svg to adjust even further
- minimal language demands
- worked across 16(?) different communities already

# Limitations
- measure same construct across communities?
- technology effects

# Conclusion

\newpage

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```

### 2023-10-27 stats/analysis.Rmd
initial commit

---
title: "Tango-cc analysis"
author: "Julia Prein"
date: "10/27/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
library(janitor) # clean_names
library(ggpubr) # ggarrange
library(ggpubr)
library(prettyR) # for describe()

# load source code for geom_flat_violin()
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)

options(scipen = 999)
theme_set(theme_classic())

# Seed for random number generation
set.seed(42)
```

```{r load_data}
dataFam <- read_csv("../data/gafo-cc-clean-data-incl-fam.csv") %>%
  filter(community != "chimfunshi") %>% 
  mutate(
         trialtype = factor(trialtype, levels = c("touch", "fam", "test")),
         agegroup = floor(ageinyears), 
         click = abs(clickdistfromtargetcenterx)/160, 
         community = factor(community, levels = c("leipzig", "hai||om", "khwe", "windhoek", "akure", "stanford"))
                      %>% recode(.,
                            leipzig = "Leipzig (Germany)",
                            akure = "Akure (Nigeria)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)"
                            )
         ) %>% 
  filter(!is.na(trialtype)) %>% 
  mutate_if(is.character,as.factor)

data <- read_csv("../data/gafo-cc-clean-data.csv") %>%
  filter(community != "chimfunshi" & !voiceover) %>% 
  mutate(
         agegroup = floor(ageinyears), 
         click = abs(clickdistfromtargetcenterx)/160, 
         community = factor(community, levels = c("leipzig", "hai||om", "khwe", "windhoek", "akure", "stanford"))
                      %>% recode(.,
                            leipzig = "Leipzig (Germany)",
                            akure = "Akure (Nigeria)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)"
                            )
         ) %>% 
  mutate_if(is.character,as.factor)

mdata <- data %>%
  mutate(
          # same as: ageinyears-mean(ageinyears)
          ageinyears = scale(ageinyears, center = T, scale = F), 
          targetcentralityx = scale(targetcentralityx),
          trialnr = scale(trialnr),
  ) %>%
  group_by(subjid, community, agegroup, ageinyears, touchscreen, household) %>%
  summarise(mean_click = mean(click)) %>%
  group_by(community) %>%
  mutate(
         household = scale(household), 
         touchscreen = factor(touchscreen),
  ) %>%
  na.omit()
```

```{r sample}
# full sample
data %>%
  group_by(community, agegroup) %>%
  summarise(n= n_distinct(subjid))

data %>%
  group_by(community) %>%
  summarise(n= n_distinct(subjid))

data %>%
  summarise(n= n_distinct(subjid))

# model data
mdata %>%
  group_by(community, agegroup) %>%
  summarise(n= n_distinct(subjid))

mdata %>%
  group_by(community) %>%
  summarise(n= n_distinct(subjid))

mdata %>% ungroup() %>% 
  summarise(n= n_distinct(subjid))
```

```{r samplesize_plot}
ggplot(data = data %>% group_by(subjid) %>% slice(1), 
       mapping = aes(x = community, 
                     y = ageinyears, 
                     fill = community)) + 
  geom_flat_violin(scale = "count", trim = T) + 
  stat_summary(fun.data = mean_sdl,
               fun.args = list(mult = 1),
               geom = "pointrange",
               position = position_nudge(0.5)) +
  geom_dotplot(binaxis = "y",
               dotsize = 1,
               stackdir = "down",
               binwidth = 0.1,
               position = position_nudge(-0.025)) +
  theme_classic() +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) + 
  guides(fill = "none") +
  scale_y_continuous(limits = c(2, 9), breaks = seq(2, 9, 1)) + 
  labs(x = "", y = "Age in years") +
  facet_grid(~ community, scales="free")
```

```{r variation}
cc_variation <- data %>% 
  summarise(
    imprecision_mean = mean(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_sd = sd(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_min = min(click_dist_balloons, na.rm = T),
    imprecision_max = max(click_dist_balloons, na.rm = T),
  )

cc_variation_communities <- data %>% 
  group_by(age_group, community) %>%
  summarise(
    imprecision_mean = mean(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_sd = sd(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_min = min(click_dist_balloons, na.rm = T),
    imprecision_max = max(click_dist_balloons, na.rm = T),
  )

cc_variation
write.csv(cc_variation, "../saves/cc_variation.csv", quote = F, row.names = F)
saveRDS(cc_variation, "../saves/cc_variation.rds")

cc_variation_communities
write.csv(cc_variation_communities, "../saves/cc_variation_communities.csv", quote = F, row.names = F)
saveRDS(cc_variation_communities, "../saves/cc_variation_communities.rds")
```

```{r variation_plot}
ggplot() +
  geom_point(data = mdata %>% filter(community == "Leipzig (Germany)"), aes(x = (ageinyears + mean(data$ageinyears)), y = mean_click, col = community), pch = 19, alpha = 0.5) +
  theme_classic() +
  scale_color_ptol(name = "Community") +
  scale_fill_ptol(name = "Community") +
  scale_x_continuous(limits = c(2, 9), breaks = seq(2, 9, 0.5)) + 
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1)) + 
  labs(x = "Age in years", y = "Average imprecision in target width")

ggplot() +
  geom_point(data = mdata, aes(x = (ageinyears + mean(data$ageinyears)), y = mean_click, col = community), pch = 19, alpha = 0.5) +
  theme_classic() +
  scale_color_ptol(name = "Community") +
  scale_fill_ptol(name = "Community") +
  scale_x_continuous(limits = c(2, 9), breaks = seq(2, 9, 0.5)) + 
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1)) + 
  labs(x = "Age in years", y = "Average imprecision in target width")
```

```{r gazefunnel}
data %>%
  group_by(targetcentralityx) %>%
  mutate(chance_upper = (targetcentralityx + 960)/2,
         chance_lower = -((targetcentralityx + 960)/2),
         center_lower = -targetcentralityx,
         center_upper = targetcentralityx) %>%
  ggplot(aes(x = targetcentralityx, y = clickdistfromtargetcenterx, col = community)) +
  labs(x = "Target centrality", y = "Imprecision") +
  geom_hline(yintercept = 0, lty = 2, size = 1, alpha = 0.75) +
  geom_point(pch = 1, alpha = 0.5) +
  scale_color_colorblind() +
  scale_x_continuous(breaks = seq(0, 960, 120)) +
  scale_y_continuous(breaks = seq(-1920, 1920, 480)) +
  theme_classic()
```

```{r clicks_bin}
clicks_bin <- data %>%
  mutate(targetposition = factor(targetposition, levels = c(1:10))) %>%
  group_by(community, targetposition) %>%
  tidyboot_mean(col = click)

ggplot(clicks_bin, aes(x = targetposition, y = mean, col = community)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), pch = 1, alpha = 1, position = position_dodge(width = .5)) +
  labs(x = "Target position (binned)", y = "Average imprecision in target width") +
  theme_classic() +
  scale_color_ptol(name = "Community") +
  scale_fill_ptol(name = "Community")
```

```{r famtrials_descriptives}
# see which trials were the most "difficult"
dataFam %>% 
  group_by(trialtype, community) %>%
  summarise(mean = mean(abs(clickdistfromtargetcenterx)), sd = sd(abs(clickdistfromtargetcenterx))) %>% 
  arrange(mean)

# identify kids that did clicked more than two balloon widths away from actual target position
dataFam %>% 
  filter(trialtype != "test" & click > 2) %>% 
  select(subjid, trialtype, agegroup, community, click) %>% 
  arrange(abs(click))

dataFam %>% 
  filter(click > 2) %>% 
  select(trialtype, agegroup, community) %>% 
  ftable()
```

```{r famtrials}
# RESOURCES:
# https://orchid00.github.io/tidy_raincloudplot
# https://www.r-bloggers.com/2021/07/ggdist-make-a-raincloud-plot-to-visualize-distribution-in-ggplot2/
# https://twitter.com/rogierk/status/1194591652452675584
# https://gist.github.com/benmarwick/b7dc863d53e0eabc272f4aad909773d2

ggplot(data = dataFam, 
       mapping = aes(x = "", 
                     y = click, 
                     fill = trialtype)) + 
  geom_flat_violin(scale = "count", 
                   trim = FALSE) + 
  stat_summary(fun.data = mean_sdl, 
               fun.args = list(mult = 1), 
               geom = "pointrange", 
               position = position_nudge(0.05)) + 
  geom_dotplot(binaxis = "y", 
               dotsize = 1, 
               stackdir = "down", 
               binwidth = 0.1, 
               position = position_nudge(-0.025)) + 
  theme(legend.position = "none") + guides(fill="none") +
  labs(x = "", 
       y = "Imprecision in balloon widths") +
  facet_grid(trialtype ~ community) + # , scales="free"
  theme_classic()
```

```{r dropouts}
dropouts <- data %>%
  group_by(subjid) %>%
  mutate(
    completedTrials = n(),
    completedStudy = ifelse(completedTrials <= 15, FALSE, TRUE), # depending on voice over included or not..
  ) %>% 
  filter(!completedStudy) %>% 
  group_by(community, agegroup) %>%
  summarise(n = n_distinct(subjid))

ggplot(dropouts, aes(x = community, y = n, fill = agegroup)) +
  geom_bar(stat="identity") + 
  theme_minimal()
```

```{r responsetime}
data %>%
  select(responsetime) %>%
  mutate(responsetime = responsetime / 1000) %>% 
  describe()

data %>% 
  ggplot(., aes((responsetime/1000))) + 
  geom_density(alpha = 0.2, fill = "grey10") + 
  geom_vline(aes(xintercept = median(clientscreenscaling)), color = "#29AF7FFF", size = 1, linetype = "longdash") +
  geom_vline(aes(xintercept = mean(clientscreenscaling, na.rm = TRUE)), color = "#FDE725FF", size = 1, linetype = "longdash")

data %>% 
  ggplot(., aes(x = (responsetime/1000), y = click)) + 
  geom_point() +
  geom_smooth(method = "lm", color = "#7D2636", alpha = 0.8) +
  stat_cor(r.accuracy = 0.01, p.accuracy = 0.01) + 
  scale_x_continuous(limits = c(0, 175), breaks = seq(0, 175, by = 50)) + 
  theme_minimal()

ggplot(data = dataFam, 
       mapping = aes(x = "", 
                     y = responsetime/1000, 
                     fill = trialtype)) + 
  geom_flat_violin(scale = "count", 
                   trim = FALSE) + 
  stat_summary(fun.data = mean_sdl, 
               fun.args = list(mult = 1), 
               geom = "pointrange", 
               position = position_nudge(0.05)) + 
  geom_dotplot(binaxis = "y", 
               dotsize = 1, 
               stackdir = "down", 
               binwidth = 0.1, 
               position = position_nudge(-0.025)) + 
  theme(legend.position = "none") + guides(fill="none") +
  labs(x = "", 
       y = "Response time") +
  facet_grid(trialtype ~ community, scales="free") +
  theme_classic()
```

### 2023-12-08 stats/analysis.Rmd
add data and internal consistency

@@
 library(ggpubr) # ggarrange
-library(ggpubr)
-library(prettyR) # for describe()
-
-# load source code for geom_flat_violin()
-source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
-
-check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)
+library(splithalfr) # split half reliability
+library(ggridges) # for ridge plot
 
@@
 ```{r load_data}
-dataFam <- read_csv("../data/gafo-cc-clean-data-incl-fam.csv") %>%
-  filter(community != "chimfunshi") %>% 
-  mutate(
-         trialtype = factor(trialtype, levels = c("touch", "fam", "test")),
-         agegroup = floor(ageinyears), 
-         click = abs(clickdistfromtargetcenterx)/160, 
-         community = factor(community, levels = c("leipzig", "hai||om", "khwe", "windhoek", "akure", "stanford"))
-                      %>% recode(.,
-                            leipzig = "Leipzig (Germany)",
-                            akure = "Akure (Nigeria)",
-                            `hai||om` = "Hai||om (Namibia)",
-                            khwe = "Khwe (Namibia)",
-                            windhoek = "Windhoek (Namibia)",
-                            stanford = "Stanford (USA)"
-                            )
-         ) %>% 
-  filter(!is.na(trialtype)) %>% 
-  mutate_if(is.character,as.factor)
+data <- read_csv("../data/data.csv")
 
-data <- read_csv("../data/gafo-cc-clean-data.csv") %>%
-  filter(community != "chimfunshi" & !voiceover) %>% 
-  mutate(
-         agegroup = floor(ageinyears), 
-         click = abs(clickdistfromtargetcenterx)/160, 
-         community = factor(community, levels = c("leipzig", "hai||om", "khwe", "windhoek", "akure", "stanford"))
-                      %>% recode(.,
-                            leipzig = "Leipzig (Germany)",
-                            akure = "Akure (Nigeria)",
-                            `hai||om` = "Hai||om (Namibia)",
-                            khwe = "Khwe (Namibia)",
-                            windhoek = "Windhoek (Namibia)",
-                            stanford = "Stanford (USA)"
-                            )
-         ) %>% 
-  mutate_if(is.character,as.factor)
-
-mdata <- data %>%
-  mutate(
-          # same as: ageinyears-mean(ageinyears)
-          ageinyears = scale(ageinyears, center = T, scale = F), 
-          targetcentralityx = scale(targetcentralityx),
-          trialnr = scale(trialnr),
-  ) %>%
-  group_by(subjid, community, agegroup, ageinyears, touchscreen, household) %>%
-  summarise(mean_click = mean(click)) %>%
-  group_by(community) %>%
-  mutate(
-         household = scale(household), 
-         touchscreen = factor(touchscreen),
-  ) %>%
-  na.omit()
+mdata <- read_csv("../data/data.csv")%>%
+  group_by(subjid, community, age_group, ageinyears)%>%
+  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
+  ungroup()%>%
+  mutate(age = scale(ageinyears))
 ```
@@
 data %>%
-  group_by(community, agegroup) %>%
+  group_by(subjid) %>%
+  summarise(n= n())%>%
+  arrange(n)
+
+data %>%
+  group_by(community, age_group) %>%
   summarise(n= n_distinct(subjid))
@@
 mdata %>%
-  group_by(community, agegroup) %>%
+  group_by(community, age_group) %>%
   summarise(n= n_distinct(subjid))
@@
 
-```{r samplesize_plot}
-ggplot(data = data %>% group_by(subjid) %>% slice(1), 
-       mapping = aes(x = community, 
-                     y = ageinyears, 
-                     fill = community)) + 
-  geom_flat_violin(scale = "count", trim = T) + 
-  stat_summary(fun.data = mean_sdl,
-               fun.args = list(mult = 1),
-               geom = "pointrange",
-               position = position_nudge(0.5)) +
-  geom_dotplot(binaxis = "y",
-               dotsize = 1,
-               stackdir = "down",
-               binwidth = 0.1,
-               position = position_nudge(-0.025)) +
-  theme_classic() +
-  theme(axis.ticks.x = element_blank(),
-        axis.text.x = element_blank()) + 
-  guides(fill = "none") +
-  scale_y_continuous(limits = c(2, 9), breaks = seq(2, 9, 1)) + 
-  labs(x = "", y = "Age in years") +
-  facet_grid(~ community, scales="free")
+# Internal consistency
+
+```{r}
+# children who did not finish all trials are removed (only 5 children total)
+
+exclude <- data %>%
+  group_by(subjid) %>%
+  summarise(n= n())%>%
+  filter(n < 15)%>%
+  pull(subjid)
+
+reli_data <- data%>%
+  filter(!subjid %in% exclude)%>%
+  mutate(pos_cent = as.character(abs(5-targetposition)))
 ```
 
-```{r variation}
-cc_variation <- data %>% 
-  summarise(
-    imprecision_mean = mean(click_dist_balloons, na.rm = T) %>% round(2),
-    imprecision_sd = sd(click_dist_balloons, na.rm = T) %>% round(2),
-    imprecision_min = min(click_dist_balloons, na.rm = T),
-    imprecision_max = max(click_dist_balloons, na.rm = T),
-  )
+## Odd-even
 
-cc_variation_communities <- data %>% 
-  group_by(age_group, community) %>%
-  summarise(
-    imprecision_mean = mean(click_dist_balloons, na.rm = T) %>% round(2),
-    imprecision_sd = sd(click_dist_balloons, na.rm = T) %>% round(2),
-    imprecision_min = min(click_dist_balloons, na.rm = T),
-    imprecision_max = max(click_dist_balloons, na.rm = T),
-  )
-
-cc_variation
-write.csv(cc_variation, "../saves/cc_variation.csv", quote = F, row.names = F)
-saveRDS(cc_variation, "../saves/cc_variation.rds")
-
-cc_variation_communities
-write.csv(cc_variation_communities, "../saves/cc_variation_communities.csv", quote = F, row.names = F)
-saveRDS(cc_variation_communities, "../saves/cc_variation_communities.rds")
-```
-
-```{r variation_plot}
-ggplot() +
-  geom_point(data = mdata %>% filter(community == "Leipzig (Germany)"), aes(x = (ageinyears + mean(data$ageinyears)), y = mean_click, col = community), pch = 19, alpha = 0.5) +
-  theme_classic() +
-  scale_color_ptol(name = "Community") +
-  scale_fill_ptol(name = "Community") +
-  scale_x_continuous(limits = c(2, 9), breaks = seq(2, 9, 0.5)) + 
-  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1)) + 
-  labs(x = "Age in years", y = "Average imprecision in target width")
-
-ggplot() +
-  geom_point(data = mdata, aes(x = (ageinyears + mean(data$ageinyears)), y = mean_click, col = community), pch = 19, alpha = 0.5) +
-  theme_classic() +
-  scale_color_ptol(name = "Community") +
-  scale_fill_ptol(name = "Community") +
-  scale_x_continuous(limits = c(2, 9), breaks = seq(2, 9, 0.5)) + 
-  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1)) + 
-  labs(x = "Age in years", y = "Average imprecision in target width")
-```
-
-```{r gazefunnel}
-data %>%
-  group_by(targetcentralityx) %>%
-  mutate(chance_upper = (targetcentralityx + 960)/2,
-         chance_lower = -((targetcentralityx + 960)/2),
-         center_lower = -targetcentralityx,
-         center_upper = targetcentralityx) %>%
-  ggplot(aes(x = targetcentralityx, y = clickdistfromtargetcenterx, col = community)) +
-  labs(x = "Target centrality", y = "Imprecision") +
-  geom_hline(yintercept = 0, lty = 2, size = 1, alpha = 0.75) +
-  geom_point(pch = 1, alpha = 0.5) +
-  scale_color_colorblind() +
-  scale_x_continuous(breaks = seq(0, 960, 120)) +
-  scale_y_continuous(breaks = seq(-1920, 1920, 480)) +
-  theme_classic()
-```
-
-```{r clicks_bin}
-clicks_bin <- data %>%
-  mutate(targetposition = factor(targetposition, levels = c(1:10))) %>%
-  group_by(community, targetposition) %>%
-  tidyboot_mean(col = click)
-
-ggplot(clicks_bin, aes(x = targetposition, y = mean, col = community)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), pch = 1, alpha = 1, position = position_dodge(width = .5)) +
-  labs(x = "Target position (binned)", y = "Average imprecision in target width") +
-  theme_classic() +
-  scale_color_ptol(name = "Community") +
-  scale_fill_ptol(name = "Community")
-```
-
-```{r famtrials_descriptives}
-# see which trials were the most "difficult"
-dataFam %>% 
-  group_by(trialtype, community) %>%
-  summarise(mean = mean(abs(clickdistfromtargetcenterx)), sd = sd(abs(clickdistfromtargetcenterx))) %>% 
-  arrange(mean)
-
-# identify kids that did clicked more than two balloon widths away from actual target position
-dataFam %>% 
-  filter(trialtype != "test" & click > 2) %>% 
-  select(subjid, trialtype, agegroup, community, click) %>% 
-  arrange(abs(click))
-
-dataFam %>% 
-  filter(click > 2) %>% 
-  select(trialtype, agegroup, community) %>% 
-  ftable()
-```
-
-```{r famtrials}
-# RESOURCES:
-# https://orchid00.github.io/tidy_raincloudplot
-# https://www.r-bloggers.com/2021/07/ggdist-make-a-raincloud-plot-to-visualize-distribution-in-ggplot2/
-# https://twitter.com/rogierk/status/1194591652452675584
-# https://gist.github.com/benmarwick/b7dc863d53e0eabc272f4aad909773d2
-
-ggplot(data = dataFam, 
-       mapping = aes(x = "", 
-                     y = click, 
-                     fill = trialtype)) + 
-  geom_flat_violin(scale = "count", 
-                   trim = FALSE) + 
-  stat_summary(fun.data = mean_sdl, 
-               fun.args = list(mult = 1), 
-               geom = "pointrange", 
-               position = position_nudge(0.05)) + 
-  geom_dotplot(binaxis = "y", 
-               dotsize = 1, 
-               stackdir = "down", 
-               binwidth = 0.1, 
-               position = position_nudge(-0.025)) + 
-  theme(legend.position = "none") + guides(fill="none") +
-  labs(x = "", 
-       y = "Imprecision in balloon widths") +
-  facet_grid(trialtype ~ community) + # , scales="free"
-  theme_classic()
-```
-
-```{r dropouts}
-dropouts <- data %>%
-  group_by(subjid) %>%
-  mutate(
-    completedTrials = n(),
-    completedStudy = ifelse(completedTrials <= 15, FALSE, TRUE), # depending on voice over included or not..
-  ) %>% 
-  filter(!completedStudy) %>% 
-  group_by(community, agegroup) %>%
-  summarise(n = n_distinct(subjid))
-
-ggplot(dropouts, aes(x = community, y = n, fill = agegroup)) +
-  geom_bar(stat="identity") + 
+```{r}
+reli_data%>%
+  mutate(half = ifelse(trialnr %% 2 == 0, "half_1", "half_2"))%>%
+  group_by(subjid, community, half)%>%
+  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
+  pivot_wider(names_from = half, values_from = impr)%>%
+  group_by(community)%>%
+  summarise(reli = cor(half_1, half_2))%>%
+  ggplot(aes(x = reli, y = community))+
+  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
+  geom_point(alpha = .5)+
+  #geom_pointrange(aes(xmin = lci, xmax = uci))+
+  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
+  ggtitle("Simple odd-even split")+
   theme_minimal()
@@
 
-```{r responsetime}
-data %>%
-  select(responsetime) %>%
-  mutate(responsetime = responsetime / 1000) %>% 
-  describe()
+## Stratified by target position (categorical target centrality)
 
-data %>% 
-  ggplot(., aes((responsetime/1000))) + 
-  geom_density(alpha = 0.2, fill = "grey10") + 
-  geom_vline(aes(xintercept = median(clientscreenscaling)), color = "#29AF7FFF", size = 1, linetype = "longdash") +
-  geom_vline(aes(xintercept = mean(clientscreenscaling, na.rm = TRUE)), color = "#FDE725FF", size = 1, linetype = "longdash")
+```{r}
+# fn_mean <- function(ds) {
+#   return(mean(abs(ds$clickdistfromtargetcenterx), na.rm = TRUE))
+# }
+# 
+# #rel <- tibble()
+# 
+# communities <- unique(data$community)
+# 
+# for (j in c(21:50)) {
+# 
+# for (i in communities) {
+#   
+# # stratified by target position
+# rel_s <- by_split(
+#   data = reli_data %>% filter(community == i),
+#   participants = reli_data %>% filter(community == i) %>% pull(subjid),
+#   fn_score = fn_mean,
+#   verbose = F,
+#   stratification = paste(reli_data %>% filter(community == i) %>% pull(pos_cent)),
+#   careful = FALSE
+# )
+# 
+# samp <- tibble(
+#   community = i,
+#   iter = j,
+#   reli = split_coefs(rel_s, cor),
+#   lci = split_ci(rel_s, cor)$lims["0.025","bca"],
+#   uci = split_ci(rel_s, cor)$lims["0.975","bca"]
+#   )
+# 
+# rel <- bind_rows(rel, samp)
+# 
+# }
+# 
+# }
+# 
+# saveRDS(rel, "../saves/stratified_internal_consistency.rds")
 
-data %>% 
-  ggplot(., aes(x = (responsetime/1000), y = click)) + 
-  geom_point() +
-  geom_smooth(method = "lm", color = "#7D2636", alpha = 0.8) +
-  stat_cor(r.accuracy = 0.01, p.accuracy = 0.01) + 
-  scale_x_continuous(limits = c(0, 175), breaks = seq(0, 175, by = 50)) + 
+rel <- readRDS("../saves/stratified_internal_consistency.rds")
+
+```
+
+```{r}
+ggplot(rel, aes(x = reli, y = community))+
+  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
+  geom_density_ridges(col = "white", alpha = .5,rel_min_height = 0.01,)+
+  geom_point(alpha = .5)+
+  #geom_pointrange(aes(xmin = lci, xmax = uci))+
+  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
+  ggtitle("Stratified by target position - no age correction")+
+  theme_minimal()
+```
+
+## Stratefied and age-corrected
+
+```{r}
+# # estimate age-corrected reliability
+# # run model first for one community to use update()
+# split <- split_df(
+#   data = reli_data %>% filter(community == "leipzig"),
+#   stratification = reli_data %>% filter(community == "leipzig") %>% pull(pos_cent),
+#   careful = FALSE
+# )
+# 
+# sdata <- bind_rows(
+#   split[[1]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
+#   split[[2]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2"))%>%
+#   mutate(age = scale(ageinyears))
+# 
+# reli_age <- brm(impr ~ age + (0 + half | subjid), 
+#                 data   = sdata, 
+#                 family = lognormal(), 
+#                 warmup = 1000, 
+#                 iter   = 3000,
+#                 control = list(adapt_delta = 0.95),
+#                 chains = 4,
+#                 cores  = 4)
+# 
+# # loop over communities
+# 
+# communities <- unique(data$community)
+# 
+# #model_cor <- tibble()
+# 
+# for (j in c(21:50)) {
+#   
+# for (i in communities) {
+#   
+# com_split <- split_df(
+#   data = reli_data %>% filter(community == i),
+#   stratification = reli_data %>% filter(community == i) %>% pull(pos_cent),
+#   careful = FALSE
+#   )
+# 
+# com_sdata <- bind_rows(
+#   com_split[[1]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
+#   com_split[[2]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2"))%>%
+#   mutate(age = scale(ageinyears))
+#  
+# com_mod <-  update(reli_age,
+#         newdata = com_sdata,
+#         warmup = 1000, 
+#         iter   = 3000,
+#         control = list(adapt_delta = 0.95),
+#         chains = 4,
+#         cores  = 4)
+#   
+#   cor <- summary(com_mod)$random$subjid%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(halfhalf_1,halfhalf_2)")%>%mutate(community = i, iter = j)
+# 
+#   model_cor <- bind_rows(model_cor, cor)
+#   
+#   
+#   }
+#   
+# }
+# 
+# saveRDS(model_cor, "../saves/age_corrected_internal_consistency.rds")
+
+model_cor <- readRDS("../saves/age_corrected_internal_consistency.rds")  
+```
+
+```{r}
+
+ggplot(model_cor, aes(x = Estimate, y = community))+
+  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
+  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01,)+
+  geom_point(alpha = .5)+
+  #geom_pointrange(aes(xmin = `l-95% CI`, xmax = `u-95% CI`), alpha = .5)+
+  ggtitle("Stratified by target position - model-based age correction")+
+  scale_x_continuous(limits = c(-1, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
   theme_minimal()
 
-ggplot(data = dataFam, 
-       mapping = aes(x = "", 
-                     y = responsetime/1000, 
-                     fill = trialtype)) + 
-  geom_flat_violin(scale = "count", 
-                   trim = FALSE) + 
-  stat_summary(fun.data = mean_sdl, 
-               fun.args = list(mult = 1), 
-               geom = "pointrange", 
-               position = position_nudge(0.05)) + 
-  geom_dotplot(binaxis = "y", 
-               dotsize = 1, 
-               stackdir = "down", 
-               binwidth = 0.1, 
-               position = position_nudge(-0.025)) + 
-  theme(legend.position = "none") + guides(fill="none") +
-  labs(x = "", 
-       y = "Response time") +
-  facet_grid(trialtype ~ community, scales="free") +
-  theme_classic()
 ```

### 2024-01-25 stats/analysis.Rmd
add plots

@@
 library(ggridges) # for ridge plot
+library(RColorBrewer) # for color palette
+library(pals) # for color palette
 
-options(scipen = 999)
-theme_set(theme_classic())
+options(scipen = 999) # turn off scientific notation
+theme_set(theme_classic()) # set theme
 
@@
 set.seed(42)
+
+# color palette
+# qual_col_pals = brewer.pal.info[brewer.pal.info$colorblind == TRUE,]
+# col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
+# 
+# # kelly palette of 22 colors maximize the contrast between colors in a set if the colors are chosen in sequential order. Kelly paid attention to the needs of people with color blindness
+# colors=kelly(n=n_distinct(data$community)+1)
+
+# create a custom color pallette with 17 easily distinguishable, different colors
+custom_palette <- c(
+  brewer.pal(11, "RdYlGn"),
+  brewer.pal(6, "BuPu")
+)
 ```
@@
 ```{r load_data}
-data <- read_csv("../data/data.csv")
+data <- read_csv("../data/data.csv") %>% 
+    mutate(continent = ifelse(
+    community %in% c("leipzig", "plymouth"), "Europe", 
+    ifelse(
+      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
+      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
+             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
+    )
+  ))%>%
+  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
+  mutate(community = recode(community,
+                            akure = "Akure (Nigeria)",
+                            leipzig = "Leipzig (Germany)",
+                            `hai||om` = "Hai||om (Namibia)",
+                            khwe = "Khwe (Namibia)",
+                            windhoek = "Windhoek (Namibia)",
+                            stanford = "Stanford (USA)",
+                            chimfunshi = "Chimfunshi (Zambia)",
+                            mexico = "Ocuilan (Mexico)",
+                            plymouth = "Plymouth (UK)",
+                            beijing = "Beijing (China)", 
+                            india = "Pune (India)",
+                            buenos_aires = "Buenos Aires (Argentina)",
+                            auckland = "Auckland (New Zealand)",
+                            turkey = "Malatya (Türkiye)",
+                            bandongo = "Bandongo (Rep. Congo)",
+                            bayaka = "BaYaka (Rep. Congo)", 
+                            uganda = "Nyabyeya (Uganda)")
+  ) %>% 
+  mutate(
+    click = abs(clickdistfromtargetcenterx)/160,
+    mean_click = mean(abs(clickdistfromtargetcenterx) / 160),
+    .by = c(ageinyears, community, subjid)
+  )
 
-mdata <- read_csv("../data/data.csv")%>%
+mdata <- data %>%
+  filter(trialtype == "test",
+         voiceover == F
+         )%>%
+  mutate(trialnr = as.numeric(factor(trialnr)))%>%
   group_by(subjid, community, age_group, ageinyears)%>%
@@
 
-```{r}
+```{r exclude_children}
 # children who did not finish all trials are removed (only 5 children total)
-
 exclude <- data %>%
+  filter(trialtype == "test", voiceover == F) %>%
   group_by(subjid) %>%
@@
 reli_data <- data%>%
+  filter(trialtype == "test", voiceover == F) %>%
   filter(!subjid %in% exclude)%>%
@@
 
-```{r}
+```{r odd_even_plot}
 reli_data%>%
@@
   geom_point(alpha = .5)+
-  #geom_pointrange(aes(xmin = lci, xmax = uci))+
+  # geom_pointrange(aes(xmin = lci, xmax = uci))+
   scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
@@
 
-```{r}
+```{r stratified_targetposition_data}
 # fn_mean <- function(ds) {
@@
 rel <- readRDS("../saves/stratified_internal_consistency.rds")
-
 ```
 
-```{r}
+```{r stratified_targetposition_plot}
 ggplot(rel, aes(x = reli, y = community))+
@@
 
-```{r}
+```{r stratified_agecorrected_data}
 # # estimate age-corrected reliability
@@
 
-```{r}
-
+```{r stratified_agecorrected_plot}
 ggplot(model_cor, aes(x = Estimate, y = community))+
@@
   theme_minimal()
+```
 
+```{r beautified_plot}
+model_cor <- model_cor %>% 
+    mutate(continent = ifelse(
+    community %in% c("leipzig", "plymouth"), "Europe", 
+    ifelse(
+      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
+      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
+             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
+    )
+  ))%>%
+  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
+  mutate(community = recode(community,
+                            akure = "Akure (Nigeria)",
+                            leipzig = "Leipzig (Germany)",
+                            `hai||om` = "Hai||om (Namibia)",
+                            khwe = "Khwe (Namibia)",
+                            windhoek = "Windhoek (Namibia)",
+                            stanford = "Stanford (USA)",
+                            chimfunshi = "Chimfunshi (Zambia)",
+                            mexico = "Ocuilan (Mexico)",
+                            plymouth = "Plymouth (UK)",
+                            beijing = "Beijing (China)", 
+                            india = "Pune (India)",
+                            buenos_aires = "Buenos Aires (Argentina)",
+                            auckland = "Auckland (New Zealand)",
+                            turkey = "Malatya (Türkiye)",
+                            bandongo = "Bandongo (Rep. Congo)",
+                            bayaka = "BaYaka (Rep. Congo)", 
+                            uganda = "Nyabyeya (Uganda)")
+  )
+
+model_cor %>% 
+  ggplot(., aes(x = Estimate, y = community))+
+  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
+  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01, fill="#29485D")+
+  geom_point(alpha = .5)+
+  #geom_pointrange(aes(xmin = `l-95% CI`, xmax = `u-95% CI`), alpha = .5)+
+  # ggtitle("Stratified by target position - model-based age correction")+
+  scale_x_continuous(limits = c(-1, 1), breaks = c(-1, -0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
+  theme_light() +
+  labs(y = "", x = "Splithalf reliability estimate", caption = "(stratified by target position; model-based age correction)")
+
+ggsave("../figures/splithalf_stratified_agecorrected.png", width = 8, height = 5, scale = 1)
 ```
+
+```{r scatterplot}
+reli_data %>% 
+  ggplot() +
+  geom_point(aes(x = ageinyears, y = mean_click, col = community), alpha = 0.9) +
+  scale_color_manual(values = custom_palette) +
+  scale_x_continuous(limits = c(2, 11), breaks = seq(2, 11, 1)) +
+  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
+  labs(x = "Age in years", y = "Average absolute imprecision in target width", col = "")
+
+ggsave("../figures/age_imprecision.png", width = 8, height = 5, scale = 1)
+```
+
+```{r ind_diff}
+data %>% 
+  summarise(mean_click = mean(click), .by = c(community, ageinyears, subjid)) %>%
+  ggplot(aes(x = community, y = mean_click, col = ageinyears)) +
+  geom_jitter(width = 0.2, height = 0.2, size = 0.9, alpha = 0.9) +
+  scale_color_viridis_c(direction = -1) +
+  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
+  theme(
+    axis.text.x = element_text(angle = 30, hjust = 1), 
+    plot.margin = margin(l = 25)
+  ) +
+  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")
+
+ggsave("../figures/ind_diff.png", width = 8, height = 5, scale = 1)
+```
+
+```{r dev_trajectory}
+dev_model <- brm(impr ~ age + (0 + half | subjid),
+                data   = mdata,
+                family = lognormal(),
+                warmup = 1000,
+                iter   = 3000,
+                control = list(adapt_delta = 0.95),
+                chains = 4,
+                cores  = 4)
+
+full_model <- brm(mean_click ~ ageinyears + touchscreen + household + (ageinyears + touchscreen + household | community), 
+                              data   = mdata, 
+                              family = "lognormal",
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4) %>% 
+  add_criterion(., c("waic","loo"))
+```
+
+```{r samplesize_plot}
+# load source code for geom_flat_violin()
+source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
+library(Hmisc)
+
+plot_data %>% 
+  summarise(click = mean(click), .by = c(community, ageinyears)) %>%
+  ggplot(mapping = aes(x = community, 
+                     y = ageinyears, 
+                     fill = community)) + 
+  geom_flat_violin(scale = "count", trim = T) + 
+  geom_dotplot(binaxis = "y",
+               dotsize = 1,
+               stackdir = "down",
+               binwidth = 0.1,
+               position = position_nudge(-0.025)) +
+  guides(fill = "none") +
+  scale_y_continuous(limits = c(2, 11), breaks = seq(2, 11, 1)) + 
+  labs(x = "", y = "Age in years") + 
+  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
+  scale_fill_manual(values = custom_palette)
+
+ggsave("../figures/age_distribution.png", width = 10, height = 5, scale = 1.1)
+```
+
+```{r u_plot}
+clicks_bin <- plot_data %>%
+  mutate(targetposition = factor(targetposition, levels = c(1:10))) %>%
+  group_by(community, targetposition) %>%
+  tidyboot_mean(column = click)
+
+clicks_bin %>% 
+  ggplot(aes(x = targetposition, y = mean, col = community)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), pch = 20, alpha = 1, position = position_dodge(width = .5)) +
+  labs(x = "Target position (binned)", y = "Average absolute imprecision in target width", col = "") +
+  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
+  scale_color_manual(values = custom_palette) +
+  scale_fill_manual(values = custom_palette)
+
+ggsave("../figures/target_position.png", width = 8, height = 4, scale = 1.1)
+```
+
+```{r training_plot}
+data %>% 
+  mutate(trialtype = recode(trialtype, touch = "Training 1", fam = "Training 2", test = "Test") %>% as_factor(.)) %>% 
+  na.omit() %>% 
+  summarise(mean_click = mean(click), .by = c(community, subjid, ageinyears, trialtype)) %>%
+  ggplot(aes(x = community, y = mean_click, col = ageinyears)) +
+  geom_jitter(width = 0.25, size = 0.9, alpha = 0.9) +
+  scale_color_viridis_c(direction = -1) +
+  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
+  theme(
+    axis.text.x = element_text(angle = 30, hjust = 1), 
+    plot.margin = margin(l = 25)
+  ) +
+  facet_wrap(~trialtype, ncol = 1) +
+  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")
+
+ggsave("../figures/training.png", width = 11, height = 5, scale = 1)
+```
+
+```{r per_culture_plot}
+# function to suppress labels
+delete_no_display <- function(v) {
+  if_else(str_detect(v, 'no_display'), '', v)
+}
+
+data %>% 
+  mutate(trialtype = recode(trialtype, touch = "Training 1", fam = "Training 2", test = "Test") %>% as_factor(.)) %>%
+  na.omit() %>%
+  summarise(mean_click = mean(click), .by = c(continent, community, subjid, ageinyears, trialtype)) %>% 
+  mutate(
+    continent = fct_inorder(continent) %>% fct_rev(.), 
+    # so that first facet row doesnt show x axis labels
+    trialtype = if_else(continent == "Africa",
+                              as.character(trialtype),
+                              paste0(as.character(trialtype), 'no_display')) %>% as_factor(.) %>% fct_relevel(., "Training 1", "Training 2", "Test")
+  ) %>%
+  ggplot(aes(x = trialtype, y = mean_click, col = ageinyears)) +
+  geom_jitter(width = 0.2, size = 0.9, alpha = 0.9) +
+  scale_color_viridis_c(direction = -1) +
+  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
+  theme_light() +
+  facet_wrap(~ continent * community, nrow = 2, scales="free_x") +
+    theme(
+    axis.text.x = element_text(angle = 30, hjust = 1), 
+    legend.position = c(0.95, 0.25), 
+    axis.ticks.x = element_blank(),
+  ) +
+  scale_x_discrete(label = delete_no_display) +
+  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")
+
+ggsave("../figures/per_culture.png", width = 11, height = 5, scale = 1.3)
+```
+
+```{r sd_plot}
+sd_df <- data %>% 
+  add_row(community = "OVERALL") %>% 
+  summarise(sd_ind = sd(click), .by = c(community, subjid, ageinyears, mean_click)) %>%
+  mutate(
+    mean_community = mean(mean_click, na.rm = TRUE),
+    sd_community = sd(mean_click, na.rm = TRUE),
+    .by = community
+  ) %>%
+  mutate(sd_overall = sd(mean_community, na.rm = TRUE), facet = ifelse(community == "OVERALL", "OVERALL", "COMMUNITY"))
+
+# plot sd of individual and community means
+sd_df %>% 
+  ggplot() +
+  geom_jitter(data = sd_df %>%  filter(facet == "COMMUNITY"), aes(x = community, y = sd_ind, col = ageinyears), width = 0.1, size = 0.9, alpha = 0.5) +
+  geom_point(data = sd_df %>%  filter(facet == "COMMUNITY"), aes(x = community, y = sd_community), size = 3, pch = 18) +
+  geom_point(data = sd_df %>%  filter(facet == "OVERALL"), aes(x = "OVERALL", y = sd_overall), size = 5, pch = 18, color = "purple") +
+  facet_grid(~ facet, scales = "free", space = "free") +
+  scale_color_viridis_c(direction = -1) +
+  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
+  theme(
+    axis.text.x = element_text(angle = 30, hjust = 1), 
+    plot.margin = margin(l = 25), 
+    strip.text = element_blank()
+  ) +
+  labs(x = "", y = "Standard deviation of clicks", col = "Age in years")
+
+ggsave("../figures/sd_plot.png", width = 10, height = 5, scale = 1)
+```

### 2024-01-31 stats/analysis.Rmd
script for server

@@
 # # kelly palette of 22 colors maximize the contrast between colors in a set if the colors are chosen in sequential order. Kelly paid attention to the needs of people with color blindness
-# colors=kelly(n=n_distinct(data$community)+1)
+# colors=kelly(n=n_distinct(data$community) +1)
 
@@
 ```{r load_data}
-data <- read_csv("../data/data.csv") %>% 
+complete_data <- read_csv("../data/data.csv")
+```
+
+```{r data_preparation}
+# complete dataset, with all trials
+all_trials <- complete_data %>% 
     mutate(continent = ifelse(
@@
       community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
-      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
+      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "Americas",
              ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
     )
-  ))%>%
-  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
+  )) %>%
+  mutate(continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T)) %>%
   mutate(community = recode(community,
@@
   mutate(
-    click = abs(clickdistfromtargetcenterx)/160,
-    mean_click = mean(abs(clickdistfromtargetcenterx) / 160),
-    .by = c(ageinyears, community, subjid)
+    imprecision = abs(clickdistfromtargetcenterx)/160,
+    centrality = as.character(abs(5-targetposition))
   )
 
+# dataset with test trials only 
+data <- all_trials %>%
+  filter(trialtype == "test", voiceover == F) %>%
+  mutate(trialnr = as.numeric(factor(trialnr)))
+
+# dataset with test trials only, with mean imprecision per participant
 mdata <- data %>%
-  filter(trialtype == "test",
-         voiceover == F
-         )%>%
-  mutate(trialnr = as.numeric(factor(trialnr)))%>%
-  group_by(subjid, community, age_group, ageinyears)%>%
-  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
-  ungroup()%>%
+  summarise(mean_imprecision = mean(imprecision), .by = c(subjid, community, age_group, ageinyears)) %>%
   mutate(age = scale(ageinyears))
@@
 # full sample
-data %>%
+all_trials %>%
   group_by(subjid) %>%
-  summarise(n= n())%>%
+  summarise(n= n()) %>%
   arrange(n)
 
-data %>%
+all_trials %>%
   group_by(community, age_group) %>%
@@
 
-data %>%
+all_trials %>%
   group_by(community) %>%
@@
 
-data %>%
+all_trials %>%
   summarise(n= n_distinct(subjid))
@@
 
-# Internal consistency
-
 ```{r exclude_children}
 # children who did not finish all trials are removed (only 5 children total)
-exclude <- data %>%
+exclude <- all_trials %>%
   filter(trialtype == "test", voiceover == F) %>%
   group_by(subjid) %>%
-  summarise(n= n())%>%
-  filter(n < 15)%>%
+  summarise(n= n()) %>%
+  filter(n < 15) %>%
   pull(subjid)
 
-reli_data <- data%>%
-  filter(trialtype == "test", voiceover == F) %>%
-  filter(!subjid %in% exclude)%>%
-  mutate(pos_cent = as.character(abs(5-targetposition)))
+all_trials <- all_trials %>% filter(!subjid %in% exclude)
+data <- data %>% filter(!subjid %in% exclude)
+mdata <- mdata %>% filter(!subjid %in% exclude)
 ```
 
+# Internal Consistency
 ## Odd-even
@@
 ```{r odd_even_plot}
-reli_data%>%
-  mutate(half = ifelse(trialnr %% 2 == 0, "half_1", "half_2"))%>%
-  group_by(subjid, community, half)%>%
-  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
-  pivot_wider(names_from = half, values_from = impr)%>%
-  group_by(community)%>%
-  summarise(reli = cor(half_1, half_2))%>%
-  ggplot(aes(x = reli, y = community))+
-  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
-  geom_point(alpha = .5)+
-  # geom_pointrange(aes(xmin = lci, xmax = uci))+
-  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
-  ggtitle("Simple odd-even split")+
+data %>%
+  mutate(half = ifelse(trialnr %% 2 == 0, "half_1", "half_2")) %>%
+  group_by(subjid, community, half) %>%
+  summarise(mean_imprecision = mean(imprecision)) %>%
+  pivot_wider(names_from = half, values_from = mean_imprecision) %>%
+  group_by(community) %>%
+  summarise(reli = cor(half_1, half_2)) %>%
+  ggplot(aes(x = reli, y = community)) +
+  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
+  geom_point(alpha = .5) +
+  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
+  labs(x = "Simple odd-even split") +
   theme_minimal()
@@
 ```{r stratified_targetposition_data}
-# fn_mean <- function(ds) {
-#   return(mean(abs(ds$clickdistfromtargetcenterx), na.rm = TRUE))
-# }
-# 
-# #rel <- tibble()
-# 
-# communities <- unique(data$community)
-# 
-# for (j in c(21:50)) {
-# 
-# for (i in communities) {
-#   
-# # stratified by target position
-# rel_s <- by_split(
-#   data = reli_data %>% filter(community == i),
-#   participants = reli_data %>% filter(community == i) %>% pull(subjid),
-#   fn_score = fn_mean,
-#   verbose = F,
-#   stratification = paste(reli_data %>% filter(community == i) %>% pull(pos_cent)),
-#   careful = FALSE
-# )
-# 
-# samp <- tibble(
-#   community = i,
-#   iter = j,
-#   reli = split_coefs(rel_s, cor),
-#   lci = split_ci(rel_s, cor)$lims["0.025","bca"],
-#   uci = split_ci(rel_s, cor)$lims["0.975","bca"]
-#   )
-# 
-# rel <- bind_rows(rel, samp)
-# 
-# }
-# 
-# }
-# 
-# saveRDS(rel, "../saves/stratified_internal_consistency.rds")
+fn_mean <- function(ds) {
+  return(mean(abs(ds$clickdistfromtargetcenterx), na.rm = TRUE))
+}
 
-rel <- readRDS("../saves/stratified_internal_consistency.rds")
+rel <- tibble()
+
+communities <- unique(data$community)
+
+for (j in c(1:50)) {
+  for (i in communities) {
+    # stratified by target position
+    rel_s <- by_split(
+      data = data %>% filter(community == i),
+      participants = data %>% filter(community == i) %>% pull(subjid),
+      fn_score = fn_mean,
+      verbose = F,
+      stratification = paste(data %>% filter(community == i) %>% pull(centrality)),
+      careful = FALSE
+      )
+
+    samp <- tibble(
+      community = i,
+      iter = j,
+      reli = split_coefs(rel_s, cor),
+      lci = split_ci(rel_s, cor)$lims["0.025","bca"],
+      uci = split_ci(rel_s, cor)$lims["0.975","bca"]
+      )
+
+    print(i)
+    print(j)
+    print(rel_s)
+    print(samp)
+
+    rel <- bind_rows(rel, samp)
+  }
+}
+
+saveRDS(rel, "../saves/stratified_internal_consistency.rds")
+
+# rel <- readRDS("../saves/stratified_internal_consistency.rds")
 ```
@@
 ```{r stratified_targetposition_plot}
-ggplot(rel, aes(x = reli, y = community))+
-  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
-  geom_density_ridges(col = "white", alpha = .5,rel_min_height = 0.01,)+
-  geom_point(alpha = .5)+
-  #geom_pointrange(aes(xmin = lci, xmax = uci))+
-  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
-  ggtitle("Stratified by target position - no age correction")+
+ggplot(rel, aes(x = reli, y = community)) +
+  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
+  geom_density_ridges(col = "white", alpha = .5,rel_min_height = 0.01,) +
+  geom_point(alpha = .5) +
+  #geom_pointrange(aes(xmin = lci, xmax = uci)) +
+  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
+  ggtitle("Stratified by target position - no age correction") +
   theme_minimal()
@@
 ```{r stratified_agecorrected_data}
-# # estimate age-corrected reliability
-# # run model first for one community to use update()
-# split <- split_df(
-#   data = reli_data %>% filter(community == "leipzig"),
-#   stratification = reli_data %>% filter(community == "leipzig") %>% pull(pos_cent),
-#   careful = FALSE
-# )
-# 
-# sdata <- bind_rows(
-#   split[[1]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
-#   split[[2]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2"))%>%
-#   mutate(age = scale(ageinyears))
-# 
-# reli_age <- brm(impr ~ age + (0 + half | subjid), 
-#                 data   = sdata, 
-#                 family = lognormal(), 
-#                 warmup = 1000, 
-#                 iter   = 3000,
-#                 control = list(adapt_delta = 0.95),
-#                 chains = 4,
-#                 cores  = 4)
-# 
-# # loop over communities
-# 
-# communities <- unique(data$community)
-# 
-# #model_cor <- tibble()
-# 
-# for (j in c(21:50)) {
-#   
-# for (i in communities) {
-#   
-# com_split <- split_df(
-#   data = reli_data %>% filter(community == i),
-#   stratification = reli_data %>% filter(community == i) %>% pull(pos_cent),
-#   careful = FALSE
-#   )
-# 
-# com_sdata <- bind_rows(
-#   com_split[[1]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
-#   com_split[[2]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2"))%>%
-#   mutate(age = scale(ageinyears))
-#  
-# com_mod <-  update(reli_age,
-#         newdata = com_sdata,
-#         warmup = 1000, 
-#         iter   = 3000,
-#         control = list(adapt_delta = 0.95),
-#         chains = 4,
-#         cores  = 4)
-#   
-#   cor <- summary(com_mod)$random$subjid%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(halfhalf_1,halfhalf_2)")%>%mutate(community = i, iter = j)
-# 
-#   model_cor <- bind_rows(model_cor, cor)
-#   
-#   
-#   }
-#   
-# }
-# 
-# saveRDS(model_cor, "../saves/age_corrected_internal_consistency.rds")
+# estimate age-corrected reliability
+# run model first for one community to use update()
+split <- split_df(
+  data = data %>% filter(community == "Leipzig (Germany)"),
+  stratification = data %>% filter(community == "Leipzig (Germany)") %>% pull(centrality),
+  careful = FALSE
+)
 
-model_cor <- readRDS("../saves/age_corrected_internal_consistency.rds")  
+sdata <- bind_rows(
+  split[[1]] %>% 
+    select(subjid, ageinyears, clickdistfromtargetcenterx) %>% 
+    mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
+  split[[2]] %>% 
+    select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
+    mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
+  mutate(age = scale(ageinyears))
+
+reli_age <- brm(impr ~ age + (0 + half | subjid),
+                data   = sdata,
+                family = lognormal(),
+                warmup = 1000,
+                iter   = 3000,
+                control = list(adapt_delta = 0.95),
+                chains = 4,
+                cores  = 4)
+
+# loop over communities
+communities <- unique(data$community)
+
+model_cor <- tibble()
+
+for (j in c(1:50)) {
+  for (i in communities) {
+
+    com_split <- split_df(
+      data = data %>% filter(community == i),
+      stratification = data %>% filter(community == i) %>% pull(centrality),
+      careful = FALSE
+    )
+
+    com_sdata <- bind_rows(
+      com_split[[1]] %>% 
+        select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
+        mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
+      com_split[[2]] %>%
+        select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
+        mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
+      mutate(age = scale(ageinyears))
+
+    com_mod <- update(reli_age,
+        newdata = com_sdata,
+        warmup = 1000,
+        iter   = 3000,
+        control = list(adapt_delta = 0.95),
+        chains = 4,
+        cores  = 4)
+
+    cor <- summary(com_mod)$random$subjid %>%
+      as_tibble(rownames = "parameter") %>%
+      filter(parameter == "cor(halfhalf_1,halfhalf_2)") %>%
+      mutate(community = i, iter = j)
+
+    model_cor <- bind_rows(model_cor, cor)
+  }
+}
+
+saveRDS(model_cor, "../saves/age_corrected_internal_consistency.rds")
+
+# model_cor <- readRDS("../saves/age_corrected_internal_consistency.rds")  
 ```
@@
 ```{r stratified_agecorrected_plot}
-ggplot(model_cor, aes(x = Estimate, y = community))+
-  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
-  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01,)+
-  geom_point(alpha = .5)+
-  #geom_pointrange(aes(xmin = `l-95% CI`, xmax = `u-95% CI`), alpha = .5)+
-  ggtitle("Stratified by target position - model-based age correction")+
-  scale_x_continuous(limits = c(-1, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
+ggplot(model_cor, aes(x = Estimate, y = community)) +
+  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
+  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01,) +
+  geom_point(alpha = .5) +
+  #geom_pointrange(aes(xmin = `l-95% CI`, xmax = `u-95% CI`), alpha = .5) +
+  ggtitle("Stratified by target position - model-based age correction") +
+  scale_x_continuous(limits = c(-1, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
   theme_minimal()
 ```
+
+### run until here
 
@@
 model_cor %>% 
-  ggplot(., aes(x = Estimate, y = community))+
-  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
-  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01, fill="#29485D")+
-  geom_point(alpha = .5)+
-  #geom_pointrange(aes(xmin = `l-95% CI`, xmax = `u-95% CI`), alpha = .5)+
-  # ggtitle("Stratified by target position - model-based age correction")+
-  scale_x_continuous(limits = c(-1, 1), breaks = c(-1, -0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
+  ggplot(., aes(x = Estimate, y = community)) +
+  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
+  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01, fill="#29485D") +
+  geom_point(alpha = .5) +
+  #geom_pointrange(aes(xmin = `l-95% CI`, xmax = `u-95% CI`), alpha = .5) +
+  # ggtitle("Stratified by target position - model-based age correction") +
+  scale_x_continuous(limits = c(-1, 1), breaks = c(-1, -0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
   theme_light() +
@@
 ```{r scatterplot}
-reli_data %>% 
+data %>% 
   ggplot() +

### 2024-02-01 stats/analysis.Rmd
organize plots

--- 2023-12-08 stats/analysis.Rmd
@@
 library(ggridges) # for ridge plot
+library(RColorBrewer) # for color palette
+library(pals) # for color palette
+library(Hmisc) # for kelly color palette
+# load source code for geom_flat_violin()
+source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
 
-options(scipen = 999)
-theme_set(theme_classic())
+options(scipen = 999) # turn off scientific notation
+theme_set(theme_classic()) # set theme
 
@@
 set.seed(42)
+
+# color palette
+# qual_col_pals = brewer.pal.info[brewer.pal.info$colorblind == TRUE,]
+# col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
+# 
+# # kelly palette of 22 colors maximize the contrast between colors in a set if the colors are chosen in sequential order. Kelly paid attention to the needs of people with color blindness
+# colors=kelly(n=n_distinct(data$community) +1)
+
+# create a custom color pallette with 17 easily distinguishable, different colors
+custom_palette <- c(
+  brewer.pal(11, "RdYlGn"),
+  brewer.pal(6, "BuPu")
+)
 ```
@@
 ```{r load_data}
-data <- read_csv("../data/data.csv")
+complete_data <- read_csv("../data/data.csv")
+```
 
-mdata <- read_csv("../data/data.csv")%>%
-  group_by(subjid, community, age_group, ageinyears)%>%
-  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
-  ungroup()%>%
-  mutate(age = scale(ageinyears))
+```{r data_preparation}
+# complete dataset, with all trials
+all_trials <- complete_data %>% 
+    mutate(continent = ifelse(
+    community %in% c("leipzig", "plymouth"), "Europe", 
+    ifelse(
+      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
+      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "Americas",
+             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
+    )
+  )) %>%
+  mutate(continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T)) %>%
+  mutate(community = recode(community,
+                            akure = "Akure (Nigeria)",
+                            leipzig = "Leipzig (Germany)",
+                            `hai||om` = "Hai||om (Namibia)",
+                            khwe = "Khwe (Namibia)",
+                            windhoek = "Windhoek (Namibia)",
+                            stanford = "Stanford (USA)",
+                            chimfunshi = "Chimfunshi (Zambia)",
+                            mexico = "Ocuilan (Mexico)",
+                            plymouth = "Plymouth (UK)",
+                            beijing = "Beijing (China)", 
+                            india = "Pune (India)",
+                            buenos_aires = "Buenos Aires (Argentina)",
+                            auckland = "Auckland (New Zealand)",
+                            turkey = "Malatya (Türkiye)",
+                            bandongo = "Bandongo (Rep. Congo)",
+                            bayaka = "BaYaka (Rep. Congo)", 
+                            uganda = "Nyabyeya (Uganda)")
+  ) %>% 
+  mutate(
+    imprecision = abs(clickdistfromtargetcenterx)/160,
+    centrality = as.character(abs(5-targetposition))
+  )
+
+# dataset with test trials only 
+data <- all_trials %>%
+  filter(trialtype == "test", voiceover == F) %>%
+  mutate(trialnr = as.numeric(factor(trialnr)))
+
+# dataset with test trials only, with mean imprecision per participant
+# scale age across communities; mean_imprecision per subjid; household, touchscreen scaled per community
+mdata <- data %>%
+  mutate(age = scale(ageinyears, center = T, scale = F)) %>%
+  group_by(subjid, community, age_group, ageinyears, age, household, touchscreen) %>%
+  summarise(mean_imprecision = mean(imprecision)) %>%
+  group_by(community) %>%
+  mutate(
+    household = scale(household), 
+    touchscreen = factor(touchscreen),
+  ) %>%
+  na.omit()
 ```
@@
 
-# Internal consistency
-
-```{r}
+```{r exclude_children}
 # children who did not finish all trials are removed (only 5 children total)
-
-exclude <- data %>%
+exclude <- all_trials %>%
+  filter(trialtype == "test", voiceover == F) %>%
   group_by(subjid) %>%
-  summarise(n= n())%>%
-  filter(n < 15)%>%
+  summarise(n= n()) %>%
+  filter(n < 15) %>%
   pull(subjid)
 
-reli_data <- data%>%
-  filter(!subjid %in% exclude)%>%
-  mutate(pos_cent = as.character(abs(5-targetposition)))
+all_trials <- all_trials %>% filter(!subjid %in% exclude)
+data <- data %>% filter(!subjid %in% exclude)
+mdata <- mdata %>% filter(!subjid %in% exclude)
 ```
 
+```{r samplesize_plot}
+data %>% 
+  summarise(click = mean(imprecision), .by = c(community, ageinyears)) %>%
+  ggplot(mapping = aes(x = community, 
+                     y = ageinyears, 
+                     fill = community)) + 
+  geom_flat_violin(scale = "count", trim = T) + 
+  geom_dotplot(binaxis = "y",
+               dotsize = 1,
+               stackdir = "down",
+               binwidth = 0.1,
+               position = position_nudge(-0.025)) +
+  guides(fill = "none") +
+  scale_y_continuous(limits = c(2, 11), breaks = seq(2, 11, 1)) + 
+  labs(x = "", y = "Age in years") + 
+  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
+  scale_fill_manual(values = custom_palette)
+
+ggsave("../figures/age_distribution.png", width = 10, height = 5, scale = 1.1)
+```
+
+# Variation
+
+```{r scatterplot}
+mdata %>% 
+  ggplot() +
+  geom_point(aes(x = ageinyears, y = mean_imprecision, col = community), alpha = 0.9) +
+  scale_color_manual(values = custom_palette) +
+  scale_x_continuous(limits = c(2, 11), breaks = seq(2, 11, 1)) +
+  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
+  labs(x = "Age in years", y = "Average absolute imprecision in target width", col = "")
+
+ggsave("../figures/age_imprecision.png", width = 8, height = 5, scale = 1)
+```
+
+```{r ind_diff}
+mdata %>% 
+  ggplot(aes(x = community, y = mean_imprecision, col = ageinyears)) +
+  geom_jitter(width = 0.2, height = 0.2, size = 0.9, alpha = 0.9) +
+  scale_color_viridis_c(direction = -1) +
+  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
+  theme(
+    axis.text.x = element_text(angle = 30, hjust = 1), 
+    plot.margin = margin(l = 25)
+  ) +
+  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")
+
+ggsave("../figures/ind_diff.png", width = 8, height = 5, scale = 1)
+```
+
+```{r training_trials}
+# function to suppress labels
+delete_no_display <- function(v) {
+  if_else(str_detect(v, 'no_display'), '', v)
+}
+
+all_trials %>% 
+  mutate(trialtype = recode(trialtype, touch = "Training 1", fam = "Training 2", test = "Test") %>% as_factor(.)) %>%
+  na.omit() %>%
+  summarise(mean_click = mean(imprecision), .by = c(continent, community, subjid, ageinyears, trialtype)) %>% 
+  mutate(
+    continent = fct_inorder(continent) %>% fct_rev(.), 
+    # so that first facet row doesnt show x axis labels
+    trialtype = if_else(continent == "Africa",
+                              as.character(trialtype),
+                              paste0(as.character(trialtype), 'no_display')) %>% as_factor(.) %>% fct_relevel(., "Training 1", "Training 2", "Test")
+  ) %>%
+  ggplot(aes(x = trialtype, y = mean_click, col = ageinyears)) +
+  geom_jitter(width = 0.2, size = 0.9, alpha = 0.9) +
+  scale_color_viridis_c(direction = -1) +
+  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
+  theme_light() +
+  facet_wrap(~ continent * community, nrow = 2, scales="free_x") +
+    theme(
+    axis.text.x = element_text(angle = 30, hjust = 1), 
+    legend.position = c(0.95, 0.25), 
+    axis.ticks.x = element_blank(),
+  ) +
+  scale_x_discrete(label = delete_no_display) +
+  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")
+
+ggsave("../figures/training_trials.png", width = 11, height = 5, scale = 1.3)
+```
+
+```{r sd_plot}
+sd_df <- data %>% 
+  add_row(community = "OVERALL") %>% 
+  summarise(
+    mean_ind = mean(imprecision),
+    sd_ind = sd(imprecision), 
+    .by = c(community, subjid, ageinyears)
+  ) %>%
+  mutate(
+    mean_community = mean(mean_ind, na.rm = TRUE),
+    sd_community = sd(mean_ind, na.rm = TRUE),
+    .by = community
+  ) %>%
+  mutate(sd_overall = sd(mean_community, na.rm = TRUE), facet = ifelse(community == "OVERALL", "OVERALL", "COMMUNITY"))
+
+# plot sd of individual and community means
+sd_df %>% 
+  ggplot() +
+  geom_jitter(data = sd_df %>%  filter(facet == "COMMUNITY"), aes(x = community, y = sd_ind, col = ageinyears), width = 0.1, size = 0.9, alpha = 0.5) +
+  geom_point(data = sd_df %>%  filter(facet == "COMMUNITY"), aes(x = community, y = sd_community), size = 3, pch = 18) +
+  geom_point(data = sd_df %>%  filter(facet == "OVERALL"), aes(x = "OVERALL", y = sd_overall), size = 5, pch = 18, color = "purple") +
+  facet_grid(~ facet, scales = "free", space = "free") +
+  scale_color_viridis_c(direction = -1) +
+  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
+  theme(
+    axis.text.x = element_text(angle = 30, hjust = 1), 
+    plot.margin = margin(l = 25), 
+    strip.text = element_blank()
+  ) +
+  labs(x = "", y = "Standard deviation of clicks", col = "Age in years")
+
+ggsave("../figures/sd_plot.png", width = 10, height = 5, scale = 1)
+```
+
+# Dev Model
+
+```{r models}
+# age scaled across communities; touchscreen factor, household scaled per community
+# full_model <- brm(mean_imprecision ~ age + touchscreen + household + (age + touchscreen + household | community),
+#                 data   = mdata,
+#                 family = lognormal(),
+#                 warmup = 1000,
+#                 iter   = 3000,
+#                 control = list(adapt_delta = 0.95),
+#                 chains = 4,
+#                 cores  = 4) %>% 
+#   add_criterion(., c("waic","loo"))
+# 
+# saveRDS(full_model, "../saves/full_model.rds")
+
+full_model <- readRDS("../saves/full_model.rds")
+
+# only age
+# age_model <- brm(mean_imprecision ~ age + (age | community),
+#                 data   = mdata,
+#                 family = lognormal(),
+#                 warmup = 1000,
+#                 iter   = 3000,
+#                 control = list(adapt_delta = 0.95),
+#                 chains = 4,
+#                 cores  = 4) %>% 
+#   add_criterion(., c("waic","loo"))
+# 
+# saveRDS(age_model, "../saves/age_model.rds")
+
+age_model <- readRDS("../saves/age_model.rds")
+```
+
+```{r model_comparison}
+```
+
+```{r age_model_plot}
+ndata <- mdata %>%
+  distinct(community) %>%
+  expand_grid(age = unique(mdata$age))
+
+post <- fitted(age_model, newdata = ndata, re_formula = ~ (age | community)) %>%
+  as_tibble() %>%
+  bind_cols(ndata) %>%
+  # because we scaled age beforehand, we need to add the mean age back in
+  mutate(age = age + mean(mdata$ageinyears))
+
+ggplot() +
+  geom_smooth(data = post, aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill = community, col = community), alpha = .25, stat = "identity") +
+  geom_point(data = mdata, aes(x = (age + mean(mdata$ageinyears)), y = mean_imprecision, col = community), pch = 19, alpha = 0.5) +
+  scale_x_continuous(limits = c(2, 11), breaks = seq(2, 11, 1)) +
+  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
+  scale_color_manual(values = custom_palette) +
+  scale_fill_manual(values = custom_palette) +
+  labs(x = "Age in years", y = "Average imprecision in target width", fill = "", col = "")
+
+ggsave("../figures/age_model.png", width = 8, height = 5, scale = 1)
+```
+
+```{r posterior_samples}
+ps <- full_model %>% posterior_samples() %>%
+  select("b_Intercept", "b_age", "b_household", "b_touchscreen1", starts_with("r_community")) %>% 
+  pivot_longer(cols = c(5:72), names_to = "community", values_to = "value") %>%
+  mutate(
+         community = str_remove(community, "r_community"),
+         community = str_remove(community, "\\]"), 
+         community = str_remove(community, "\\["), 
+         ) %>%
+  separate(col = community, into = c("community", "parameter"), sep = ",") %>% 
+  pivot_longer(cols = c(b_Intercept, b_household, b_age, b_touchscreen1), names_to = "fix_param", values_to = "fix_value") %>%
+  mutate(fix_param = tolower(str_remove(fix_param,"b_")), 
+         parameter = tolower(parameter), 
+         fix_param = str_remove(fix_param, "1"), 
+         parameter = str_remove(parameter, "1"), 
+         community = str_replace(community, "\\.", " "), 
+         community = factor(community) %>% 
+           recode(., 
+                  `Auckland (New.Zealand)` = "Auckland (New Zealand)", 
+                  `Bandongo (Rep..Congo)` = "Bandongo (Rep. Congo)",
+                  `BaYaka (Rep..Congo)` = "BaYaka (Rep. Congo)"
+                  )
+  ) %>%
+  filter(parameter == fix_param) %>%
+  mutate(est = value + fix_value)
+```
+
+```{r age_estimates}
+ps %>% 
+  filter(parameter == "age") %>%
+  ggplot(aes(y = fct_rev(community), x = est, fill = stat(x) > 0)) +
+  tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80), scale = 1) +
+    labs(x = "Age - posterior estimate", y ="") +
+  guides(fill = "none") +
+  geom_vline(xintercept = fixef(full_model) %>% as_tibble(rownames = "param") %>% filter(param == "age") %>% pull(Estimate), linetype = "dashed") +
+  geom_vline(xintercept = 0, linetype = "solid") +
+  scale_fill_manual(values = c("#29485D", "grey")) +
+  theme_minimal()
+```
+
+# Demographics
+
+```{r demographics_descriptives}
+demographics <- data %>%
+  mutate(older_children = children - 1 - younger_children) %>%
+  group_by(community)%>%
+  summarise(screen = mean(screen, na.rm = T),
+            touchscreen = mean(touchscreen, na.rm = T), 
+            older_children = mean(older_children, na.rm = T), 
+            household = mean(household, na.rm = T))%>%
+  pivot_longer(names_to = "predictor", values_to = "value", cols = c(screen, touchscreen, older_children, household))
+
+demographics
+
+```
+
+```{r touchscreen}
+touchscreen_model <- ps %>% 
+  filter(parameter == "touchscreen") %>%
+  ggplot(., aes(x = est, y = fct_rev(community))) +
+  geom_vline(xintercept = 0, lty = "solid", color = "black", size = 0.5) +
+  geom_point(size = 0.5, alpha = .5) +
+  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01, fill="#29485D") +
+  scale_x_continuous(limits = c(-1, 0.5), breaks = seq(-1, 0.5, 0.25)) +
+  theme_light() + 
+  labs(x = "Posterior estimate", y = "")
+
+touchscreen_model
+
+ggsave("../figures/touchscreen_model.png", width = 5, height = 5, scale = 0.9, bg = "white")
+
+touchscreen_descr <- demographics %>% 
+  filter(predictor == "touchscreen") %>%
+  ggplot(aes(x = predictor, y = fct_rev(community), fill = value)) +
+  geom_point(pch = 22, size = 5, stroke = 0) +
+  scale_fill_viridis_c() +
+  labs(x = "", y = "", fill = "Proportion") +
+  theme(axis.line = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks = element_blank(),
+  )
+
+touchscreen_descr
+
+ggsave("../figures/touchscreen_descr.png", width = 3.5, height = 5, scale = 0.9, bg = "white")
+```
+
+```{r household}
+household_model <- ps %>% 
+  filter(parameter == "household") %>%
+  ggplot(., aes(x = est, y = fct_rev(community))) +
+  geom_vline(xintercept = 0, lty = "solid", color = "black", size = 0.5) +
+  geom_point(size = 0.5, alpha = .5) +
+  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01, fill="#29485D") +
+  scale_x_continuous(limits = c(-0.25, 0.25), breaks = seq(-0.25, 0.25, 0.125)) +
+  theme_light() + 
+  labs(x = "Posterior estimate", y = "")
+
+household_model
+
+ggsave("../figures/household_model.png", width = 5, height = 5, scale = 0.9, bg = "white")
+
+household_descr <- demographics %>% 
+  filter(predictor == "household") %>%
+  ggplot(aes(x = predictor, y = fct_rev(community), fill = value)) +
+  geom_point(pch = 22, size = 5, stroke = 0) +
+  scale_fill_viridis_c() +
+  labs(x = "", y = "", fill = "# Members") +
+  theme(axis.line = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks = element_blank(),
+  )
+
+household_descr
+
+ggsave("../figures/household_descr.png", width = 3.5, height = 5, scale = 0.9, bg = "white")
+```
+
+# Gaze model U
+
+```{r u_plot}
+clicks_bin <- data %>%
+  mutate(targetposition = factor(targetposition, levels = c(1:10))) %>%
+  group_by(community, targetposition) %>%
+  tidyboot_mean(column = imprecision)
+
+clicks_bin %>% 
+  ggplot(aes(x = targetposition, y = mean, col = community)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), pch = 20, alpha = 1, position = position_dodge(width = .5)) +
+  labs(x = "Target position (binned)", y = "Average absolute imprecision in target width", col = "") +
+  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
+  scale_color_manual(values = custom_palette) +
+  scale_fill_manual(values = custom_palette)
+
+ggsave("../figures/target_position.png", width = 8, height = 4, scale = 1.1)
+```
+
+# Internal Consistency
 ## Odd-even
 
-```{r}
-reli_data%>%
-  mutate(half = ifelse(trialnr %% 2 == 0, "half_1", "half_2"))%>%
-  group_by(subjid, community, half)%>%
-  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
-  pivot_wider(names_from = half, values_from = impr)%>%
-  group_by(community)%>%
-  summarise(reli = cor(half_1, half_2))%>%
-  ggplot(aes(x = reli, y = community))+
-  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
-  geom_point(alpha = .5)+
-  #geom_pointrange(aes(xmin = lci, xmax = uci))+
-  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
-  ggtitle("Simple odd-even split")+
-  theme_minimal()
+```{r odd_even_plot}
+odd_even <- data %>%
+  mutate(half = ifelse(trialnr %% 2 == 0, "half_1", "half_2")) %>%
+  group_by(subjid, community, half) %>%
+  summarise(mean_imprecision = mean(imprecision)) %>%
+  pivot_wider(names_from = half, values_from = mean_imprecision) %>%
+  group_by(community) %>%
+  summarise(reli = cor(half_1, half_2)) %>%
+  ggplot(aes(x = reli, y = fct_rev(community))) +
+  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
+  geom_point(alpha = .5) +
+  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
+  labs(x = "Simple odd-even split", y = "") +
+  theme_light() +
+  theme(axis.title.x = element_text(size = 10))
+
+odd_even
 ```
@@
 
-```{r}
+```{r stratified_data}
 # fn_mean <- function(ds) {
@@
 # 
-# #rel <- tibble()
+# rel <- tibble()
 # 
@@
 # 
-# for (j in c(21:50)) {
-# 
+# for (j in c(1:50)) {
 #   for (i in communities) {
-#   
 #     # stratified by target position
 #     rel_s <- by_split(
-#   data = reli_data %>% filter(community == i),
-#   participants = reli_data %>% filter(community == i) %>% pull(subjid),
+#       data = data %>% filter(community == i),
+#       participants = data %>% filter(community == i) %>% pull(subjid),
 #       fn_score = fn_mean,
 #       verbose = F,
-#   stratification = paste(reli_data %>% filter(community == i) %>% pull(pos_cent)),
+#       stratification = paste(data %>% filter(community == i) %>% pull(centrality)),
 #       careful = FALSE
@@
 #     
+#     print(i)
+#     print(j)
+#     print(rel_s)
+#     print(samp)
+#     
 #     rel <- bind_rows(rel, samp)
-# 
 #   }
-# 
 # }
-# 
+
 # saveRDS(rel, "../saves/stratified_internal_consistency.rds")
@@
 rel <- readRDS("../saves/stratified_internal_consistency.rds")
-
 ```
 
-```{r}
-ggplot(rel, aes(x = reli, y = community))+
-  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
-  geom_density_ridges(col = "white", alpha = .5,rel_min_height = 0.01,)+
-  geom_point(alpha = .5)+
-  #geom_pointrange(aes(xmin = lci, xmax = uci))+
-  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
-  ggtitle("Stratified by target position - no age correction")+
-  theme_minimal()
+```{r stratified_plot}
+stratified_plot <- rel %>%   
+  ggplot(., aes(x = reli, y = fct_rev(community))) +
+  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
+  geom_point(alpha = .5) +
+  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01, fill="#29485D") +
+  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
+  theme_light() +
+  labs(y = "", x = "Stratified by target centrality") +
+  theme(axis.title.x = element_text(size = 10))
+
+stratified_plot
+
+ggsave("../figures/splithalf_stratified.png", width = 8, height = 5, scale = 1, bg = "white")
 ```
 
-## Stratefied and age-corrected
+## Stratified and age-corrected
 
-```{r}
-# # estimate age-corrected reliability
-# # run model first for one community to use update()
+```{r stratified_agecorrected_data}
+# estimate age-corrected reliability
+# run model first for one community to use update()
 # split <- split_df(
-#   data = reli_data %>% filter(community == "leipzig"),
-#   stratification = reli_data %>% filter(community == "leipzig") %>% pull(pos_cent),
+#   data = data %>% filter(community == "Leipzig (Germany)"),
+#   stratification = data %>% filter(community == "Leipzig (Germany)") %>% pull(centrality),
 #   careful = FALSE
@@
 # sdata <- bind_rows(
-#   split[[1]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
-#   split[[2]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2"))%>%
+#   split[[1]] %>% 
+#     select(subjid, ageinyears, clickdistfromtargetcenterx) %>% 
+#     mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
+#   split[[2]] %>% 
+#     select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
+#     mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
 #   mutate(age = scale(ageinyears))
@@
 # # loop over communities
-# 
 # communities <- unique(data$community)
 # 
-# #model_cor <- tibble()
+# model_cor <- tibble()
 # 
-# for (j in c(21:50)) {
-#   
+# for (j in c(1:50)) {
 #   for (i in communities) {
@@
 #     com_split <- split_df(
-#   data = reli_data %>% filter(community == i),
-#   stratification = reli_data %>% filter(community == i) %>% pull(pos_cent),
+#       data = data %>% filter(community == i),
+#       stratification = data %>% filter(community == i) %>% pull(centrality),
 #       careful = FALSE
@@
 #     com_sdata <- bind_rows(
-#   com_split[[1]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
-#   com_split[[2]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2"))%>%
+#       com_split[[1]] %>% 
+#         select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
+#         mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
+#       com_split[[2]] %>%
+#         select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
+#         mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
 #       mutate(age = scale(ageinyears))
@@
 #     
-#   cor <- summary(com_mod)$random$subjid%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(halfhalf_1,halfhalf_2)")%>%mutate(community = i, iter = j)
+#     cor <- summary(com_mod)$random$subjid %>%
+#       as_tibble(rownames = "parameter") %>%
+#       filter(parameter == "cor(halfhalf_1, halfhalf_2)") %>%
+#       mutate(community = i, iter = j)
 #     
 #     model_cor <- bind_rows(model_cor, cor)
-#   
-#   
 #   }
-#   
 # }
@@
 
-```{r}
+```{r stratified_agecorrected_plot}
+stratified_agecorrected_plot <- model_cor %>% 
+  ggplot(., aes(x = Estimate, y = fct_rev(community))) +
+  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
+  geom_point(alpha = .5) +
+  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01, fill="#29485D") +
+  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
+  theme_light() +
+  labs(y = "", x = "Stratified by target centrality, model-based age correction") +
+  theme(axis.title.x = element_text(size = 10))
 
-ggplot(model_cor, aes(x = Estimate, y = community))+
-  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
-  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01,)+
-  geom_point(alpha = .5)+
-  #geom_pointrange(aes(xmin = `l-95% CI`, xmax = `u-95% CI`), alpha = .5)+
-  ggtitle("Stratified by target position - model-based age correction")+
-  scale_x_continuous(limits = c(-1, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
-  theme_minimal()
+stratified_agecorrected_plot
 
+ggsave("../figures/splithalf_stratified_agecorrected.png", width = 8, height = 5, scale = 1, bg = "white")
 ```
+
+```{r consistency_plots}
+ggarrange(
+  odd_even,
+  stratified_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
+  stratified_agecorrected_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
+  widths = c(2, 1.5, 1.5), 
+  nrow = 1,
+  labels = "AUTO" 
+)
+
+ggsave("../figures/splithalf.png", width = 14, height = 5, scale = 0.9, bg = "white")
+```

### 2024-04-04 stats/analysis.Rmd
work on analyses & plots

--- 2024-01-31 stats/analysis.Rmd
@@
 library(pals) # for color palette
+library(Hmisc) # for kelly color palette
+library(ggrepel) # for geom_text_repel
+# load source code for geom_flat_violin()
+source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
 
 options(scipen = 999) # turn off scientific notation
-theme_set(theme_classic()) # set theme
+theme_set(theme_light()) # set theme
 
@@
 ```{r load_data}
-complete_data <- read_csv("../data/data.csv")
+complete_data <- read_csv("../data/data.csv") %>% 
+  mutate(age_group = floor(ageinyears))
 ```
@@
 # dataset with test trials only, with mean imprecision per participant
+# scale age across communities; mean_imprecision per subjid; household, touchscreen scaled per community
 mdata <- data %>%
-  summarise(mean_imprecision = mean(imprecision), .by = c(subjid, community, age_group, ageinyears)) %>%
-  mutate(age = scale(ageinyears))
+  mutate(age = scale(ageinyears, center = T, scale = F)) %>%
+  group_by(subjid, community, age_group, ageinyears, age, household, touchscreen) %>%
+  summarise(mean_imprecision = mean(imprecision)) %>%
+  group_by(community) %>%
+  mutate(
+    household = scale(household), 
+    touchscreen = factor(touchscreen),
+  ) %>%
+  na.omit()
 ```
+
+# Sample
 
@@
 
+```{r samplesize_table}
+# sample size table
+sample_table <- data %>%
+  group_by(community, age_group) %>%
+  summarise(n = n_distinct(subjid)) %>%
+  arrange(age_group) %>% 
+  pivot_wider(names_from = age_group, values_from = n) %>% 
+  arrange(community) %>%
+  rename(Community = community) %>% 
+  replace(is.na(.), 0) %>% 
+  # total per community added as column
+  mutate(Total = sum(across(where(is.numeric)))) %>% 
+  ungroup() %>% 
+  # total per age added as row
+  bind_rows(summarise(.,
+                      across(where(is.numeric), sum),
+                      across(where(is.character), ~"Total")))
+
+saveRDS(sample_table, "../saves/sample_table.rds")
+```
+
+```{r samplesize_plot}
+data %>% 
+  summarise(click = mean(imprecision), .by = c(community, ageinyears)) %>%
+  ggplot(mapping = aes(x = community, y = ageinyears)) + 
+  geom_flat_violin(scale = "count", trim = T, fill = "#29485D", alpha = 0.75) + 
+  geom_dotplot(binaxis = "y",
+               dotsize = 1,
+               stackdir = "down",
+               binwidth = 0.1,
+               position = position_nudge(-0.025), 
+               fill = "#ffffff"
+               ) +
+  scale_y_continuous(limits = c(2, 11), breaks = seq(2, 11, 1)) + 
+  labs(x = "", y = "Age in years") + 
+  theme(axis.text.x = element_text(angle = 30, hjust = 1))
+
+ggsave("../figures/age_distribution.png", width = 10, height = 5, scale = 1.1)
+```
+
+# Variation
+
+```{r model_density}
+age_model <- brm(mean_imprecision ~ age + (1 | subjid),
+                data   = mdata,
+                family = lognormal(),
+                warmup = 2000,
+                iter   = 6000,
+                control = list(adapt_delta = 0.95),
+                chains = 4,
+                cores  = 4)
+
+age_model
+
+nd <- mdata %>% 
+  select(-c(mean_imprecision))
+
+# extract model predictions for mock data
+pred_agecorrected <- fitted(age_model, newdata = nd, re_formula = NA) %>% as_tibble() %>% bind_cols(mdata)
+
+density_plot <- pred_agecorrected %>% 
+  ggplot(aes(x = Estimate, y = fct_rev(community))) +
+  geom_density_ridges(
+    jittered_points = TRUE,
+    position = position_points_jitter(width = 0.05, height = 0),
+    point_shape = '|', point_size = 2, point_alpha = 1, point_color = "#ffffff",
+    alpha = 1,
+    fill = "#29485D", 
+    col = "#ffffff", 
+    scale = 1.5
+  ) +
+  labs(x = "Absolute imprecision in target width", y = "", fill = "Community") +
+  expand_limits(y = c(1, 18.5)) + 
+  scale_x_continuous(limits = c(0.5, 4), breaks = seq(0, 4, 0.5)) +
+  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
+
+density_plot
+```
+
+```{r training_trials}
+# function to suppress labels
+delete_no_display <- function(v) {
+  if_else(str_detect(v, 'no_display'), '', v)
+}
+
+training_trials_plot <- all_trials %>% 
+  mutate(trialtype = recode(trialtype, touch = "Training 1", fam = "Training 2", test = "Test") %>% as_factor(.)) %>%
+  na.omit() %>%
+  summarise(mean_click = mean(imprecision), .by = c(community, subjid, ageinyears, trialtype)) %>% 
+  mutate(
+    # so that first facet row doesnt show x axis labels
+    trialtype = if_else(community %in% c("Leipzig (Germany)", "Malatya (Türkiye)", "Nyabyeya (Uganda)", "Ocuilan (Mexico)", "Plymouth (UK)", "Pune (India)", "Stanford (USA)", "Windhoek (Namibia)"),
+                              as.character(trialtype),
+                              paste0(as.character(trialtype), 'no_display')) %>% as_factor(.) %>% fct_relevel(., "Training 1", "Training 2", "Test")
+  ) %>%
+  ggplot(aes(x = trialtype, y = mean_click, col = ageinyears)) +
+  geom_jitter(width = 0.2, size = 0.7, alpha = 0.7) +
+  scale_color_viridis_c(direction = -1) +
+  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
+  facet_wrap(~ community, nrow = 2, scales="free_x") +
+  theme(
+    axis.text.x = element_text(angle = 30, hjust = 1), 
+    legend.position = c(0.96, 0.25), 
+    axis.ticks.x = element_blank(),
+    strip.text.x = element_text(size = 7.5), 
+    legend.title = element_text(size = 8),
+  ) +
+  scale_x_discrete(label = delete_no_display) +
+  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")
+
+training_trials_plot
+```
+
+```{r icc}
+within_person <- data %>%
+  group_by(subjid) %>%
+  summarise(
+    mean = mean(imprecision, na.rm = TRUE),
+    sd = sd(imprecision, na.rm = TRUE),
+    var = var(imprecision, na.rm =TRUE),
+  )
+
+within_person
+saveRDS(within_person, "../saves/within_person.rds")
+
+# proportion of between-community variance relative to the sum of within-community and between-community variance
+# generally: ICC = (variance of interest) / (total variance) = (variance of interest) / (variance of interest + unwanted variance)
+var_df <- data %>%
+  group_by(subjid, community) %>%
+  summarise(
+    person_mean = mean(imprecision, na.rm = TRUE),
+  ) %>% 
+  group_by(community) %>%
+  summarise(
+    community_mean = mean(person_mean),
+    community_sd = sd(person_mean),
+    within_community_var = var(person_mean)
+  ) %>% 
+  mutate(
+    between_community_var= var(community_mean),
+    total_var = between_community_var + sum(within_community_var),
+    ICC_b= between_community_var / total_var, 
+    ICC_w = sum(within_community_var) / total_var
+  ) %>% 
+  mutate(across(where(is.numeric), ~round(., 2)))
+
+var_df
+saveRDS(var_df, "../saves/var_df.rds")
+```
+
 # Internal Consistency
@@
 ```{r odd_even_plot}
-data %>%
+int_con <- data %>%
   mutate(half = ifelse(trialnr %% 2 == 0, "half_1", "half_2")) %>%
@@
   group_by(community) %>%
-  summarise(reli = cor(half_1, half_2)) %>%
-  ggplot(aes(x = reli, y = community)) +
-  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
-  geom_point(alpha = .5) +
-  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
-  labs(x = "Simple odd-even split") +
-  theme_minimal()
+  summarise(odd_even = cor(half_1, half_2))
+
+odd_even_plot <- int_con %>% 
+  left_join(data %>% group_by(community) %>% summarise(n= n_distinct(subjid))) %>% 
+  ggplot(aes(x = odd_even, y = fct_rev(community))) + 
+  geom_point(aes(size = n), col = "#29485D", alpha = 1) + 
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
+  scale_size(limits = c(20, 160), breaks = seq(25, 150, 50)) + 
+  labs(y = "", x = "Odd-even split") +
+  theme(
+    legend.position = c(0.2, 0.2),
+    strip.text = element_text(face = "bold", size = 10), 
+    legend.title = element_text(size = 8),
+    legend.text = element_text(size = 8), 
+    legend.box.background = element_rect(), 
+    legend.key.height = unit(0.4, "cm"),
+    legend.key.width = unit(-1.2, "cm"),
+  ) +
+  expand_limits(y = c(1, 18.5))
+
+odd_even_plot
 ```
@@
 
-```{r stratified_targetposition_data}
-fn_mean <- function(ds) {
-  return(mean(abs(ds$clickdistfromtargetcenterx), na.rm = TRUE))
-}
+```{r stratified_data}
+# fn_mean <- function(ds) {
+#   return(mean(abs(ds$clickdistfromtargetcenterx), na.rm = TRUE))
+# }
+# 
+# strat <- tibble()
+# 
+# communities <- unique(data$community)
+# 
+# for (j in c(1:50)) {
+#   for (i in communities) {
+#     # stratified by target position
+#     strat_s <- by_split(
+#       data = data %>% filter(community == i),
+#       participants = data %>% filter(community == i) %>% pull(subjid),
+#       fn_score = fn_mean,
+#       verbose = F,
+#       stratification = paste(data %>% filter(community == i) %>% pull(centrality)),
+#       careful = FALSE
+#       )
+#     
+#     samp <- tibble(
+#       community = i,
+#       iter = j,
+#       reli = split_coefs(strat_s, cor),
+#       lci = split_ci(strat_s, cor)$lims["0.025","bca"],
+#       uci = split_ci(strat_s, cor)$lims["0.975","bca"]
+#       )
+#     
+#     print(i)
+#     print(j)
+#     print(strat_s)
+#     print(samp)
+#     
+#     strat <- bind_rows(strat, samp)
+#   }
+# }
 
-rel <- tibble()
+# saveRDS(strat, "../saves/stratified_internal_consistency.rds")
 
-communities <- unique(data$community)
-
-for (j in c(1:50)) {
-  for (i in communities) {
-    # stratified by target position
-    rel_s <- by_split(
-      data = data %>% filter(community == i),
-      participants = data %>% filter(community == i) %>% pull(subjid),
-      fn_score = fn_mean,
-      verbose = F,
-      stratification = paste(data %>% filter(community == i) %>% pull(centrality)),
-      careful = FALSE
-      )
-
-    samp <- tibble(
-      community = i,
-      iter = j,
-      reli = split_coefs(rel_s, cor),
-      lci = split_ci(rel_s, cor)$lims["0.025","bca"],
-      uci = split_ci(rel_s, cor)$lims["0.975","bca"]
-      )
-
-    print(i)
-    print(j)
-    print(rel_s)
-    print(samp)
-
-    rel <- bind_rows(rel, samp)
-  }
-}
-
-saveRDS(rel, "../saves/stratified_internal_consistency.rds")
-
-# rel <- readRDS("../saves/stratified_internal_consistency.rds")
+strat <- readRDS("../saves/stratified_internal_consistency.rds")
 ```
 
-```{r stratified_targetposition_plot}
-ggplot(rel, aes(x = reli, y = community)) +
-  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
-  geom_density_ridges(col = "white", alpha = .5,rel_min_height = 0.01,) +
-  geom_point(alpha = .5) +
-  #geom_pointrange(aes(xmin = lci, xmax = uci)) +
-  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
-  ggtitle("Stratified by target position - no age correction") +
-  theme_minimal()
+```{r stratified_plot}
+stratified_plot <- strat %>%   
+  ggplot(., aes(x = reli, y = fct_rev(community))) +
+  geom_density_ridges(col = "white", alpha = 1, rel_min_height = 0.01, fill="#29485D") +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
+  labs(y = "", x = "Stratified by target centrality") +
+  theme(axis.title.x = element_text(size = 10)) +
+  expand_limits(y = c(1, 18.5))
+
+stratified_plot
 ```
 
-## Stratefied and age-corrected
+## Stratified and age-corrected
 
@@
 # run model first for one community to use update()
-split <- split_df(
-  data = data %>% filter(community == "Leipzig (Germany)"),
-  stratification = data %>% filter(community == "Leipzig (Germany)") %>% pull(centrality),
-  careful = FALSE
-)
+# split <- split_df(
+#   data = data %>% filter(community == "Leipzig (Germany)"),
+#   stratification = data %>% filter(community == "Leipzig (Germany)") %>% pull(centrality),
+#   careful = FALSE
+# )
+# 
+# sdata <- bind_rows(
+#   split[[1]] %>% 
+#     select(subjid, ageinyears, clickdistfromtargetcenterx) %>% 
+#     mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
+#   split[[2]] %>% 
+#     select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
+#     mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
+#   mutate(age = scale(ageinyears))
+# 
+# strat_age_model <- brm(impr ~ age + (0 + half | subjid),
+#                 data   = sdata,
+#                 family = lognormal(),
+#                 warmup = 1000,
+#                 iter   = 3000,
+#                 control = list(adapt_delta = 0.95),
+#                 chains = 4,
+#                 cores  = 4)
+# 
+# # loop over communities
+# communities <- unique(data$community)
+# 
+# strat_age <- tibble()
+# 
+# for (j in c(1:50)) {
+#   for (i in communities) {
+#     
+#     com_split <- split_df(
+#       data = data %>% filter(community == i),
+#       stratification = data %>% filter(community == i) %>% pull(centrality),
+#       careful = FALSE
+#     )
+#     
+#     com_sdata <- bind_rows(
+#       com_split[[1]] %>% 
+#         select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
+#         mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
+#       com_split[[2]] %>%
+#         select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
+#         mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
+#       mutate(age = scale(ageinyears))
+#     
+#     com_mod <- update(strat_split_model,
+#         newdata = com_sdata,
+#         warmup = 1000,
+#         iter   = 3000,
+#         control = list(adapt_delta = 0.95),
+#         chains = 4,
+#         cores  = 4)
+#     
+#     cor <- summary(com_mod)$random$subjid %>%
+#       as_tibble(rownames = "parameter") %>%
+#       filter(parameter == "cor(halfhalf_1, halfhalf_2)") %>%
+#       mutate(community = i, iter = j)
+#     
+#     strat_age <- bind_rows(strat_age, cor)
+#   }
+# }
+# 
+# saveRDS(strat_age, "../saves/age_corrected_internal_consistency.rds")
 
-sdata <- bind_rows(
-  split[[1]] %>% 
-    select(subjid, ageinyears, clickdistfromtargetcenterx) %>% 
-    mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
-  split[[2]] %>% 
-    select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
-    mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
-  mutate(age = scale(ageinyears))
-
-reli_age <- brm(impr ~ age + (0 + half | subjid),
-                data   = sdata,
-                family = lognormal(),
-                warmup = 1000,
-                iter   = 3000,
-                control = list(adapt_delta = 0.95),
-                chains = 4,
-                cores  = 4)
-
-# loop over communities
-communities <- unique(data$community)
-
-model_cor <- tibble()
-
-for (j in c(1:50)) {
-  for (i in communities) {
-
-    com_split <- split_df(
-      data = data %>% filter(community == i),
-      stratification = data %>% filter(community == i) %>% pull(centrality),
-      careful = FALSE
-    )
-
-    com_sdata <- bind_rows(
-      com_split[[1]] %>% 
-        select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
-        mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
-      com_split[[2]] %>%
-        select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
-        mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
-      mutate(age = scale(ageinyears))
-
-    com_mod <- update(reli_age,
-        newdata = com_sdata,
-        warmup = 1000,
-        iter   = 3000,
-        control = list(adapt_delta = 0.95),
-        chains = 4,
-        cores  = 4)
-
-    cor <- summary(com_mod)$random$subjid %>%
-      as_tibble(rownames = "parameter") %>%
-      filter(parameter == "cor(halfhalf_1,halfhalf_2)") %>%
-      mutate(community = i, iter = j)
-
-    model_cor <- bind_rows(model_cor, cor)
-  }
-}
-
-saveRDS(model_cor, "../saves/age_corrected_internal_consistency.rds")
-
-# model_cor <- readRDS("../saves/age_corrected_internal_consistency.rds")  
+strat_age <- readRDS("../saves/age_corrected_internal_consistency.rds")
 ```
@@
 ```{r stratified_agecorrected_plot}
-ggplot(model_cor, aes(x = Estimate, y = community)) +
-  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
-  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01,) +
-  geom_point(alpha = .5) +
-  #geom_pointrange(aes(xmin = `l-95% CI`, xmax = `u-95% CI`), alpha = .5) +
-  ggtitle("Stratified by target position - model-based age correction") +
-  scale_x_continuous(limits = c(-1, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
-  theme_minimal()
+stratified_agecorrected_plot <- strat_age %>% 
+  ggplot(., aes(x = Estimate, y = fct_rev(community))) +
+  geom_density_ridges(col = "white", alpha = 1, rel_min_height = 0.01, fill="#29485D") +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
+  labs(y = "", x = "Stratified & age-corrected") +
+  theme(axis.title.x = element_text(size = 10)) +
+  expand_limits(y = c(1, 18.5))
+
+stratified_agecorrected_plot
 ```
 
-### run until here
-
-```{r beautified_plot}
-model_cor <- model_cor %>% 
-    mutate(continent = ifelse(
-    community %in% c("leipzig", "plymouth"), "Europe", 
-    ifelse(
-      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
-      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "Americas",
-             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
-    )
-  )) %>%
-  mutate(continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T)) %>%
-  mutate(community = recode(community,
-                            akure = "Akure (Nigeria)",
-                            leipzig = "Leipzig (Germany)",
-                            `hai||om` = "Hai||om (Namibia)",
-                            khwe = "Khwe (Namibia)",
-                            windhoek = "Windhoek (Namibia)",
-                            stanford = "Stanford (USA)",
-                            chimfunshi = "Chimfunshi (Zambia)",
-                            mexico = "Ocuilan (Mexico)",
-                            plymouth = "Plymouth (UK)",
-                            beijing = "Beijing (China)", 
-                            india = "Pune (India)",
-                            buenos_aires = "Buenos Aires (Argentina)",
-                            auckland = "Auckland (New Zealand)",
-                            turkey = "Malatya (Türkiye)",
-                            bandongo = "Bandongo (Rep. Congo)",
-                            bayaka = "BaYaka (Rep. Congo)", 
-                            uganda = "Nyabyeya (Uganda)")
+```{r combine_data}
+int_con <- full_join(
+  int_con, 
+  strat %>% 
+    group_by(community) %>%
+    summarise(stratified = mean(reli, na.rm = T))
+) %>% 
+  full_join(
+    strat_age %>% 
+      group_by(community) %>%
+      summarise(stratified_agecorrected = mean(Estimate, na.rm = T))
   )
 
-model_cor %>% 
-  ggplot(., aes(x = Estimate, y = community)) +
-  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
-  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01, fill="#29485D") +
-  geom_point(alpha = .5) +
-  #geom_pointrange(aes(xmin = `l-95% CI`, xmax = `u-95% CI`), alpha = .5) +
-  # ggtitle("Stratified by target position - model-based age correction") +
-  scale_x_continuous(limits = c(-1, 1), breaks = c(-1, -0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
-  theme_light() +
-  labs(y = "", x = "Splithalf reliability estimate", caption = "(stratified by target position; model-based age correction)")
-
-ggsave("../figures/splithalf_stratified_agecorrected.png", width = 8, height = 5, scale = 1)
+int_con
+saveRDS(int_con, "../saves/internal_consistency.rds")
 ```
 
-```{r scatterplot}
-data %>% 
-  ggplot() +
-  geom_point(aes(x = ageinyears, y = mean_click, col = community), alpha = 0.9) +
-  scale_color_manual(values = custom_palette) +
-  scale_x_continuous(limits = c(2, 11), breaks = seq(2, 11, 1)) +
-  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
-  labs(x = "Age in years", y = "Average absolute imprecision in target width", col = "")
+# Combine plots
 
-ggsave("../figures/age_imprecision.png", width = 8, height = 5, scale = 1)
+```{r combine_plot}
+top_row <- ggarrange(
+  density_plot,
+  odd_even_plot,
+  stratified_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
+  stratified_agecorrected_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
+  widths = c(1.5, 2.1, 1.4, 1.4), 
+  nrow = 1,
+  labels = c("B", "C", "D", "E") 
+)
+
+ggarrange(
+  training_trials_plot,
+  top_row,
+  nrow = 2,
+  heights = c(2.2, 1.4),
+  labels = c("A", "") 
+)
+
+ggsave("../figures/tango-cc.png", width = 12, height = 8, scale = 1, bg = "white")
 ```
 
-```{r ind_diff}
-data %>% 
-  summarise(mean_click = mean(click), .by = c(community, ageinyears, subjid)) %>%
-  ggplot(aes(x = community, y = mean_click, col = ageinyears)) +
-  geom_jitter(width = 0.2, height = 0.2, size = 0.9, alpha = 0.9) +
-  scale_color_viridis_c(direction = -1) +
-  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
-  theme(
-    axis.text.x = element_text(angle = 30, hjust = 1), 
-    plot.margin = margin(l = 25)
-  ) +
-  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")
+# Exploratory: Correlation SD and internal consistency
 
-ggsave("../figures/ind_diff.png", width = 8, height = 5, scale = 1)
+```{r sd_int_plot}
+sd_int_plot <- var_df %>%  
+  select(community, community_sd) %>% 
+  full_join(int_con) %>% 
+  ggplot(aes(x = community_sd, y = stratified_agecorrected)) +
+  geom_point(shape = 4, size = 2) +
+  geom_smooth(method = "lm", se = FALSE, col = "#29485D") +
+  stat_cor(aes(label = paste(..r.label..)), method = "pearson", size = 4, r.accuracy = 0.01, cor.coef.name = "r", label.x = 0.25, label.y = 0.95) +
+  scale_x_continuous(limits = c(0.25, 2), breaks = seq(0, 2, 0.5)) +
+  scale_y_continuous(limits = c(0.25, 1), breaks = seq(0, 1, 0.2)) +
+  labs(x = "Community SD", y = "Internal consistency")
+
+sd_int_plot
 ```
-
-```{r dev_trajectory}
-dev_model <- brm(impr ~ age + (0 + half | subjid),
-                data   = mdata,
-                family = lognormal(),
-                warmup = 1000,
-                iter   = 3000,
-                control = list(adapt_delta = 0.95),
-                chains = 4,
-                cores  = 4)
-
-full_model <- brm(mean_click ~ ageinyears + touchscreen + household + (ageinyears + touchscreen + household | community), 
-                              data   = mdata, 
-                              family = "lognormal",
-                              warmup = 2000, 
-                              iter   = 4000, 
-                              chains = 4, 
-                              cores  = 4) %>% 
-  add_criterion(., c("waic","loo"))
-```
-
-```{r samplesize_plot}
-# load source code for geom_flat_violin()
-source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
-library(Hmisc)
-
-plot_data %>% 
-  summarise(click = mean(click), .by = c(community, ageinyears)) %>%
-  ggplot(mapping = aes(x = community, 
-                     y = ageinyears, 
-                     fill = community)) + 
-  geom_flat_violin(scale = "count", trim = T) + 
-  geom_dotplot(binaxis = "y",
-               dotsize = 1,
-               stackdir = "down",
-               binwidth = 0.1,
-               position = position_nudge(-0.025)) +
-  guides(fill = "none") +
-  scale_y_continuous(limits = c(2, 11), breaks = seq(2, 11, 1)) + 
-  labs(x = "", y = "Age in years") + 
-  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
-  scale_fill_manual(values = custom_palette)
-
-ggsave("../figures/age_distribution.png", width = 10, height = 5, scale = 1.1)
-```
-
-```{r u_plot}
-clicks_bin <- plot_data %>%
-  mutate(targetposition = factor(targetposition, levels = c(1:10))) %>%
-  group_by(community, targetposition) %>%
-  tidyboot_mean(column = click)
-
-clicks_bin %>% 
-  ggplot(aes(x = targetposition, y = mean, col = community)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), pch = 20, alpha = 1, position = position_dodge(width = .5)) +
-  labs(x = "Target position (binned)", y = "Average absolute imprecision in target width", col = "") +
-  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
-  scale_color_manual(values = custom_palette) +
-  scale_fill_manual(values = custom_palette)
-
-ggsave("../figures/target_position.png", width = 8, height = 4, scale = 1.1)
-```
-
-```{r training_plot}
-data %>% 
-  mutate(trialtype = recode(trialtype, touch = "Training 1", fam = "Training 2", test = "Test") %>% as_factor(.)) %>% 
-  na.omit() %>% 
-  summarise(mean_click = mean(click), .by = c(community, subjid, ageinyears, trialtype)) %>%
-  ggplot(aes(x = community, y = mean_click, col = ageinyears)) +
-  geom_jitter(width = 0.25, size = 0.9, alpha = 0.9) +
-  scale_color_viridis_c(direction = -1) +
-  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
-  theme(
-    axis.text.x = element_text(angle = 30, hjust = 1), 
-    plot.margin = margin(l = 25)
-  ) +
-  facet_wrap(~trialtype, ncol = 1) +
-  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")
-
-ggsave("../figures/training.png", width = 11, height = 5, scale = 1)
-```
-
-```{r per_culture_plot}
-# function to suppress labels
-delete_no_display <- function(v) {
-  if_else(str_detect(v, 'no_display'), '', v)
-}
-
-data %>% 
-  mutate(trialtype = recode(trialtype, touch = "Training 1", fam = "Training 2", test = "Test") %>% as_factor(.)) %>%
-  na.omit() %>%
-  summarise(mean_click = mean(click), .by = c(continent, community, subjid, ageinyears, trialtype)) %>% 
-  mutate(
-    continent = fct_inorder(continent) %>% fct_rev(.), 
-    # so that first facet row doesnt show x axis labels
-    trialtype = if_else(continent == "Africa",
-                              as.character(trialtype),
-                              paste0(as.character(trialtype), 'no_display')) %>% as_factor(.) %>% fct_relevel(., "Training 1", "Training 2", "Test")
-  ) %>%
-  ggplot(aes(x = trialtype, y = mean_click, col = ageinyears)) +
-  geom_jitter(width = 0.2, size = 0.9, alpha = 0.9) +
-  scale_color_viridis_c(direction = -1) +
-  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
-  theme_light() +
-  facet_wrap(~ continent * community, nrow = 2, scales="free_x") +
-    theme(
-    axis.text.x = element_text(angle = 30, hjust = 1), 
-    legend.position = c(0.95, 0.25), 
-    axis.ticks.x = element_blank(),
-  ) +
-  scale_x_discrete(label = delete_no_display) +
-  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")
-
-ggsave("../figures/per_culture.png", width = 11, height = 5, scale = 1.3)
-```
-
-```{r sd_plot}
-sd_df <- data %>% 
-  add_row(community = "OVERALL") %>% 
-  summarise(sd_ind = sd(click), .by = c(community, subjid, ageinyears, mean_click)) %>%
-  mutate(
-    mean_community = mean(mean_click, na.rm = TRUE),
-    sd_community = sd(mean_click, na.rm = TRUE),
-    .by = community
-  ) %>%
-  mutate(sd_overall = sd(mean_community, na.rm = TRUE), facet = ifelse(community == "OVERALL", "OVERALL", "COMMUNITY"))
-
-# plot sd of individual and community means
-sd_df %>% 
-  ggplot() +
-  geom_jitter(data = sd_df %>%  filter(facet == "COMMUNITY"), aes(x = community, y = sd_ind, col = ageinyears), width = 0.1, size = 0.9, alpha = 0.5) +
-  geom_point(data = sd_df %>%  filter(facet == "COMMUNITY"), aes(x = community, y = sd_community), size = 3, pch = 18) +
-  geom_point(data = sd_df %>%  filter(facet == "OVERALL"), aes(x = "OVERALL", y = sd_overall), size = 5, pch = 18, color = "purple") +
-  facet_grid(~ facet, scales = "free", space = "free") +
-  scale_color_viridis_c(direction = -1) +
-  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
-  theme(
-    axis.text.x = element_text(angle = 30, hjust = 1), 
-    plot.margin = margin(l = 25), 
-    strip.text = element_blank()
-  ) +
-  labs(x = "", y = "Standard deviation of clicks", col = "Age in years")
-
-ggsave("../figures/sd_plot.png", width = 10, height = 5, scale = 1)
-```

### 2024-04-15 paper/manuscript.Rmd
create rough first draft

@@
 ---
-title: "TANGO-CC: An open-source website for researchers to build a culture-sensitive task of gaze understanding"
-shorttitle: "measuring gaze understanding across the globe"
+title: "Measuring variation in gaze-following across cultures, individuals, and age — a showcase of the TANGO-CC"
+shorttitle: "measuring gaze following across cultures"
+
 author: 
-
-  - name          : "Julia Christin Prein"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
-    email         : "julia_prein@eva.mpg.de"
-    role          :
-      - Conceptualization
-      - Methodology
-      - Software
-      - Investigation
-      - Formal Analysis
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-
-  - name          : "Daniel B. M. Haun"
-    affiliation   : "1"
-    role          :
-      - Supervision
-      - Writing - Review & Editing
-
-  - name          : "Manuel Bohn"
+  - name          : "Julia Prein (ORCID: 0000-0002-3154-6167)"
     affiliation   : "1,2"
-    role          :
-      - Conceptualization
-      - Writing - Review & Editing
+    corresponding : yes
+    address       : "Universitätsallee 1, 21335 Lüneburg, Germany"
+    email         : "manuel.bohn@leuphana.de"
+    role:
+      - "Conceptualization"
+      - "Methodology"
+      - "Software"
+      - "Investigation"
+      - "Writing - Original Draft Preparation"
+      - "Writing - Review & Editing"
+  - name          : "Florian M. Bednarski (ORCID: 0000-0003-4384-4791)"
+    affiliation   : "4"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Ardain Dzabatou"
+    affiliation   : "5"
+    role:
+      - "Investigation"
+  - name          : "Michael C. Frank (ORCID: 0000-0002-7551-4378)"
+    affiliation   : "6"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"
+  - name          : "Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)"
+    affiliation   : "4"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"      
+  - name          : "Josefine Kalbitz"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"
+  - name          : "Patricia Kanngiesser (ORCID:0000-0003-1068-3725)"
+    affiliation   : "7"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)"
+    affiliation   : "8"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Bahar Köymen (ORCID: 0000-0001-5126-8240)"
+    affiliation   : "9"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"  
+  - name          : "Maira V. Manrique-Hernandez"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+  - name          : "Shirley Magazi (ORCID: 0009-0006-0479-9800)"
+    affiliation   : "10"
+    role:
+      - "Investigation"
+  - name          : "Lizbeth Mújica-Manrique"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Julia Ohlendorf"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+  - name          : "Damilola Olaoba"
+    affiliation   : "2"
+    role:
+     - "Investigation"
+  - name          : "Wesley R. Pieters (ORCID:0000-0002-6152-249X)"
+    affiliation   : "10"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Sarah Pope-Caldwell"
+    affiliation   : "2"
+    role:
+     - "Investigation"
+  - name          : "Roman Stengelin (ORCID: 0000-0003-2212-4613)"
+    affiliation   : "2,10"
+    role:
+      - "Conceptualization"
+      - "Methodology"
+      - "Investigation"
+      - "Writing - Review & Editing"     
+  - name          : "Katie Slocombe (ORCID: 0000-0002-7310-1887)"
+    affiliation   : "11"
+    role:
+     - "Investigation"
+     - "Writing - Review & Editing"
+  - name          : "Robert Z. Sparks (ORCID: 0000-0001-7545-0522)"
+    affiliation   : "6"
+    role:
+      - "Investigation"
+  - name          : "Jahnavi Sunderarajan"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+  - name          : "Florence Tusiime"
+    affiliation   : "3"
+    role:
+      - "Investigation"
+  - name          : "Wilson Vieira (ORCID: 0009-0001-9400-6328)"
+    affiliation   : "2"
+    role:
+     - "Investigation"
+  - name          : "Zhen Zhang (ORCID: 0000-0001-9300-0920)"
+    affiliation   : "12"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"   
+  - name          : "Yufei Zong (ORCID: 0009-0000-5012-0244)"
+    affiliation   : "12"
+    role:
+      - "Investigation"
+  - name          : "Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)"
+    affiliation   : "2,+"
+    role:
+      - "Conceptualization"
+      - "Funding acquisition"
+      - "Writing - Review & Editing"
+  - name          : "Manuel Bohn (ORCID: 0000-0001-6006-1348)"
+    affiliation   : "1,2,+"
+    role:
+      - "Conceptualization"
+      - "Methodology"
+      - "Writing - Review & Editing"
 
@@
   - id            : "1"
-    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
+    institution   : "Institute of Psychology in Education, Leuphana University Lüneburg"
   - id            : "2"
-    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"
+    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
+  - id            : "3"
+    institution   : "Budongo Conservation Field Station"
+  - id            : "4"
+    institution   : "School of Psychology, University of Auckland"
+  - id            : "5"
+    institution   : "Université Marien Ngouabi"
+  - id            : "6"
+    institution   : "Department of Psychology, Stanford University"
+  - id            : "7"
+    institution   : "School of Psychology, University of Plymouth"
+  - id            : "8"
+    institution   : "Department of Psychology, Koç University"
+  - id            : "9"
+    institution   : "Division of Psychology, Communication, and Human Neuroscience, University of Manchester"
+  - id            : "10"
+    institution   : "Department of Psychology and Social Work, University of Namibia"
+  - id            : "11"
+    institution   : "Department of Psychology, University of York"
+  - id            : "12"
+    institution   : "CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences"
+  - id            : "+"
+    institution   : "joint last author"
+
 abstract: | 
+            Cross-cultural studies are crucial for establishing the universality and robustness of developmental milestones.
+Yet, suitable methods to measure variability in social cognition across linguistic and cultural settings are lacking.
+This paper describes the TANGO-CC (Task for Assessing Individual Differences in Gaze Understanding - Cross Cultural), a gaze-following task designed to measure imprecision in gaze following across individuals, ages, and communities.
+The development of the TANGO-CC involved two main phases: initial implementation and validation in Leipzig, Germany, followed by collaboration with cross-cultural researchers to expand the stimulus pool and collect data from 2.5- to 11-year-old children (N = 1372) from 17 diverse communities worldwide.
+The TANGO-CC captured individual differences and showed high internal consistency in each community.
+Within-community variation outweighed between-community variation.
+Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each cultural setting.
+We provide an open-source website for researchers to customize the task to their needs.
+Overall, the TANGO-CC represents a valuable contribution to the assessment of social-cognitive development in diverse social-cultural environments, facilitating future cross-cultural studies.
 
-keywords          : "cross-cultural psychology, social-cognitive development, gaze following, individual differences, reliability"
+keywords          : "cross-cultural psychology, social cognition, gaze following, individual differences, reliability"
 wordcount         : "XXX"
@@
 draft             : no
-documentclass     : "apa6"
 classoption       : "man"
-output            : papaja::apa6_pdf
-header-includes   :
+header-includes:
   - \usepackage{setspace}
+  - \usepackage{libertine}
   - \captionsetup[figure]{font={stretch=1}}
+  - |
+    \makeatletter
+    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-1em}%
+      {\normalfont\normalsize\bfseries\typesectitle}}
+
+    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-\z@\relax}%
+      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+    \makeatother
+
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+documentclass     : "apa7"
+output            : papaja::apa6_word
 editor_options    : 
@@
 # Introduction
-- increased interest in cc research but not many new methods that enable or ease cross cultural research
-- hard to capture ind diff, even harder in cc settings
-- goal: comparable data across cultural settings
-- approach 1: standardized procedure, as similar as possible. taken here
-- approach 2: see in each cultural setting how to translate the psychological construct into experiment
-- prein2023tango: works for ind diff. reliable. 
-- supplements prein2023variation: differences between animal & human faces
 
-# Methods
-- testing setups: rural & urban
-- no prior touchscreen experience needed
-- how does website work: which variables you can select
-- output from website
-- shiny app?!
-- psychometric properties of tango germany
-- describe cc sample
+More than a decade ago, @henrich2010weirdesta advocated for more diverse samples in psychological research and cautioned against relying solely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) backgrounds.
+Despite numerous calls for change, the subject pools reported in high-impact journals still lack diversity [@nielsen2017persistent].
+This lack of representation creates inequities and hampers progress in theory building: If we want to draw inferences about the unique characteristics of human behavior and "human nature", we need to study it in many humans from many different backgrounds [@krys2024weirda].
+
+The present sampling bias might be especially problematic in research concerning the development of social cognition.
+Social cognition concerns the processes by which individuals encode and decode social information [@glynn2016social], which allows them to successfully participate in joint activities and communication.
+Many developmental theories emphasize the role of social interaction in the development of social cognition (e.g., reinforcement learning in gaze following; [@jasso2006using]).
+However, social interactions differ substantially in their characteristics across communities and even across families and individuals.
+Cultural and social experiences influence the beliefs, values, norms and expectations of an individual, which, in turn, determines how they interpret other's actions.
+Consequently, @selcuk2023development have urged for studying how social-cultural factors on a macro-, community-level as well as a micro-, family-level influence the social cognition development.
+
+Why are there not more social-cognitive studies focusing on the variation between diverse communities and individuals?
+A potential reason for the under-representation of these studies may be the scarcity of suitable tools [@bourdage2023evaluation].
+A suitable tool for studying individual- and community-level variation needs to address its (1) psychometric properties and (2) cross-cultural adaptations.
+
+First, studies investigating variation between communities and/or individuals need to ensure that the captured variation is systematic and not just random noise.
+This requires measurement reliability and validity.
+Yet, social cognition studies based on US-American and European samples rarely report psychometric information [for a review, see @beaudoin2020systematic].
+This picture further deteriorates when we pay attention to the reliability and validity of cross-cultural social cognition tasks [@hajduk2020how; @bourdage2023evaluation].
+It remains challenging to find reliable and valid tasks that can capture individual differences within one community, let alone finding tasks that can be applied across different cultural settings.
+
+Second, adapting tasks to diverse cultural settings and re-assessing their validity and reliability might be especially important in the social-cognitive domain.
+If, in theory, stimuli used in social cognition tasks should depict people's everyday experiences, the tasks need to represent different social and cultural environments.
+Indeed, task performance can be diminished when stimuli are not adjusted [@pena2007lost].
+For example, @elfenbein2002universality found better emotion recognition for members of the same national, ethnic, or regional group.
+@selcuk2023development concluded that children often attribute mental states more accurately and more frequently to individuals from the same cultural group.
+This underlines the importance of adapting tasks to each specific cultural context.
+
+Broadly speaking, there are two different approaches that researchers can take to collect data that is comparable across cultural settings.
+One approach would be to translate the psychological construct into an individually designed study for each cultural setting.
+While this approach is most flexible and sensitive to cultural differences, it might be most feasible for studying up to a handful communities.
+Examples for studies that followed this approach are @mehta2011validation, @stengelin2020cultural, @chasiotis2006theory.
+However, recent articles call for the inclusion of more field sites in cross-cultural studies [e.g., @krys2024weirda].
+The approach of individually re-designing a study for each community might then become too demanding and time-consuming.
+Another approach would be to use the same standardized procedure across diverse cultural settings.
+This approach is less sensitive to each community's unique characteristics but allows for a direct comparison of data across cultural settings.
+Examples following this approach include @callaghan2011early, @taumoepeau2019crosscultural, @hughes2018does, @hughes2014lost, @fujita2022theory.
+This paper aims to describe the development and psychometric properties of a standardized task that can be adapted to different social and linguistic settings.
+
+The task presented in this manuscript focuses on gaze following, the ability to identify the attentional focus of another agent.
+Gaze following develops early in infancy [@delbianco2019developmental; @tang2024slow] and contributes to social learning, communication and collaboration [@shepherd2010following; @tomasello2007reliance; @bohn2018common; @hernik2019infant].
+While gaze following acts as one of the most fundamental social-cognitive abilities, studies focusing on cultural variations are rare.
+The few existing results are mixed whether gaze following is influenced by cultural factors or not [@hernik2019infant; @callaghan2011early].
+
+The task presented here builds upon the TANGO (Task for Assessing iNdividual differences in gaze understanding - Open) by @prein2023tango.
+The TANGO measures participants' imprecision of locating an agent's attentional focus.
+It has been shown to reliably capture individual differences in a German child sample and an international remote adult sample.
+The task was sensitive to developmental changes and linked to children's receptive vocabulary.
+Furthermore, an exploratory analysis showed that children performed equally well in a study version with animal faces compared to cartoon human faces [@prein2023variation].
+Therefore, superficial variations in the stimulus design do not seem to influence children's performance in the task.
+
+This paper showcases the TANGO-CC (TANGO - Cross Cultural), a standardized gaze-following task that can be adapted to several languages and cultural settings.
+We describe our reasoning behind the task's development and provide a tutorial for the open-source website (<https://ccp-odc.eva.mpg.de/tango-cc/>).
+We present results from a large cross-cultural sample of 2.5- to 11-year-olds from 17 different urban/rural communities across the world and discuss the task's psychometrics.
+The task and all its adaptations have been initially designed for a paper by @bohn2024universal, and we re-use the data set in this paper.
+
+# Task development
+
+## Approach
+
+In a perfect world, developing a cross-cultural task would include international collaboration and diverse samples from the beginning, already during piloting and item selection.
+As this seems hardly feasible, we present an alternative, pragmatic approach to developing a task that can be applied across different communities.
+This approach has its faults.
+However, we later present results that show that our task adaptation yielded stable, clear results across a wide range of communities.
+
+Our general approach to developing the TANGO-CC consisted of two main parts.
+First, the task was implemented in one context, in our case with a German sample (the TANGO; [@prein2023tango]).
+In this context, we assessed the task's reliability and validity in detail.
+Even though this does not guarantee that the task will work in another context, we believe it increases the chances.
+Second, we collaborated with cross-cultural researchers and expanded the stimulus pool to diverse cultural and linguistic settings.
+@bohn2024universal collected data in 17 communities worldwide.
+We assessed performance across trial types and checked for individual differences.
+If we found individual differences in other communities to a similar degree to the German sample, it was likely that these individual differences were also systematic.
+This would be, for example, less likely if we saw floor- or ceiling effects.
+Reliability was estimated using internal consistency measures.
+Therefore, our procedure tried to maintain a balance between a detailed analysis of the task's psychometric properties across communities and a swift and feasible task adaptation.
+In the following, we describe the different steps in further detail.
+Even though we focus on the cross-cultural adaptation of the TANGO, we believe the general approach might be helpful for other researchers who aim to design cross-culturally adaptable tasks.
+
+In the first step, we designed the task's underlying functionality.
+We aimed for a measure that maps directly onto the task's underlying psychological construct: in our case, the imprecision with which participants can locate an agent's attentional focus.
+We were motivated to create a continuous outcome measure since this allows for more room to capture individual differences.
+The core of the task was calculating where the agent's eyes must move to follow the target's movement.
+In the next step, this structure was filled with the task's superficial appearance and audio instructions.
+Notably, the task's presentation can be adjusted without changing its underlying structure.
+For example, we can change the background scene, the faces of the agent, and the target without changing the logic of where the agent looks or the participants' task to identify an agent's attentional focus.
+We realized that as soon as the task's underlying structure was implemented, adaptations of the task and data collection efforts were greatly simplified.
+
+After implementing the task, we assessed the psychometric properties of the TANGO in a WEIRD sample.
+We collected data of a German child sample and an international remote adult sample [@prein2023tango].
+The adult sample worked as a proof-of-concept and showed that remote data collection worked very well.
+We reasoned that if we find individual differences in an adult sample, chances are high that we also find them in a child sample, as adults usually exhibit less variation in abilities than children.
+The task captured a developmental change and showed neither floor nor ceiling effects.
+
+Most importantly, we found individual differences across all age groups.
+By evaluating split half- and retest reliability estimates, we could show that the individual variation was systematic and not just random noise.
+Additionally, we assessed the task's validity by examining the relationship with theoretically related concepts.
+Performance in the TANGO was linked to children's receptive vocabulary and weakly related to factors of children's daily social environment [@prein2023tango].
+In another study, we proposed a computational cognitive model that described gaze following as a social form of vector following.
+Gaze following, as measured by the TANGO, was related to children's vector following and visual perspective-taking abilities [@prein2023variation].
+These connections to related constructs speak toward the task's validity in the German setting.
+An exploratory analysis showed that performance in the TANGO was similar when presenting animal vs.
+human faces [@prein2023variation supplements].
+This demonstrates that the participants' performance did not depend on superficial features of the task's appearance.
+
+As a next step, we contacted cross-cultural researchers and field assistants interested in using the TANGO.
+We asked local people to give input as to how we could adapt the task to their local needs.
+Together with their help, we generated a set of 50 diverse human faces that were aimed to be representative of each local population.
+Similarly, different backgrounds were created that roughly represented a typical accommodation in each community.
+Research assistants translated the audio instructions into the corresponding local language.
+By back-translating these instructions, we ensured the original meaning did not change.
+Sometimes, specific words were linguistically slightly modified, although functionally equivalent (e.g., "bush" instead of "hedge") to ensure that all participants understood the instructions.
+Before collecting data in each community, we piloted with a small sample.
+This procedure slightly varied between communities; see supplements for further details.
+In the following, we describe the design features of the TANGO-CC in greater detail.
+
+## Features of the TANGO
+
+The task presented in this manuscript is the cross-cultural adaptation of the TANGO [@prein2023tango].
+We quickly recap the TANGO's most characteristic features: Participants are asked to locate a balloon with the help of a gaze cue.
+The outcome variable is the distance between the participant's touch and the balloon's center.
+Trials can be completed in a fast and efficient way, so that children can easily complete 15 trials within 10 min.
+This drastically reduced drop-out rates.
+By using essentially self-explanatory animations, language demands are kept to a minimum.
+To keep trials comparable and avoid learning effects, no differential feedback is given.
+
+### Task implementation
+
+The task was implemented in `JavaScript`, `HTML`, and `CSS`, and is presented as a web app.
+It can be accessed on any web browser and does not require prior installation.
+The online version of the task has been proven convenient for unsupervised data collection (for example, using participant recruitment services like *Prolific*, see @prein2023tango), and sharing the task across big international collaborations.
+Importantly, the web app implementation does not necessarily need a working WIFI connection: An offline, local version of the task can be quickly set up for devices that support Node.js (<https://nodejs.org/en>).
+This is an especially useful feature for researchers working in remote areas with limited internet access.
+
+The stimuli are embedded as Scalable Vector Graphics (SVG).
+The setup allows for an easy adaptation of study elements and ensures that picture quality, aspect ratio and relative object positioning are constant.
+We implemented some features designed to ensure meaningful clicking responses.
+The study is programmed so that responses are only registered when the participant touches the relevant part of the screen (i.e., in test trials the hedge).
+Furthermore, clicks are only registered after the voice recordings stopped playing.
+If no click is registered within 5 seconds, an audio reminder is played again.
+
+The website does not use cookies, nor does it upload any data to servers; that is, the data is only stored locally on the device.
+The output of the study is a CSV file that contains the participants' responses and can be easily imported into statistical software for further analysis.
+The saved variables are: id, language, background, trial_number, study_phase, audio_instructions, keep_trial, agent, balloon_color, balloon_bin, balloon_center, click, absolute_click_distance, timestamp, responsetime_ms.
+In case a webcam recording was selected, a second file is saved that contains the webcam recording (WEBM file).
+The files will be stored in the device's downloads folder and is named after the following pattern: "tangoCC-participantID-YYYY-MM-DD_hh_mm_ss".
+
+### Trial types
+
+The task consists of three different trial types.
+In every trial, participants see an agent (boy or girl) looking out of house, with a balloon (red, blue, green or yellow) in front of them.
+The balloon falls down to the ground, while the eyes of the agent follow the movement of the balloon in a way that their centers always align.
+Depending on the trial type, participants have different visual access to the balloon's position.
+In training 1, participants see the full trajectory of the balloon and directly have to touch the balloon itself.
+In training 2, participants see most of the balloon's movement but the final location is covered by a hedge.
+In test trials, a hedge grows in the beginning of the trial and participants see neither the movement nor the final position of the balloon.
+The first trial of each type contains an audio description of the presented events (see Supplements).
+Importantly, the instructions explicitly state that the agent is looking at the balloon.
+
+### Randomization
+
+The order of the agents, balloon colors (red, yellow, green, blue), and balloon positions are each randomized independently.
+For the balloon positions, the full width of the screen (1920 in "SVG unit") is divided into ten bins.
+Exact coordinates (value between 0 far left and 1920 far right) within each bin are then randomly generated.
+The number of repetitions for each agent, balloon color, and balloon bin is calculated based on the total number of trials and the number of unique agents, balloon colors, and bins, respectively.
+All agents, balloon colors, and bins appear equally often and are not repeated in more than two consecutive trials.
+If the total number of trials is not divisible by the number of unique elements, additional elements are randomly selected to make up for the remainder.
+
+## Cross-cultural customization
+
+The TANGO-CC expands the stimulus pool of the TANGO by depicting human faces and different languages for the audio instructions.
+The TANGO-CC can be accessed here: (<https://ccp-odc.eva.mpg.de/tango-cc/>).
+Researchers can customize the following parts of the task.
+In the first step, researchers can enter an alphanumeric participant identifier (1 - 8 characters).
+Audio instructions are currently available in 13 different languages (and even more dialects): Bayaka (Rep.
+Congo), Bemba (Zambia), Chinese (China), English (India), English (New Zealand), English (Nigeria), English (UK), English (USA), German (Germany), Hai||om (Namibia), Khewdam (Namibia), Lingala (Rep.
+Congo), Marathi (India), Shona (Zimbabwe), Spanish (Argentina), Spanish (Mexico), Swahili (Uganda), Turkish (Türkiye).
+Please note that the written instructions are always in English, however, children are not required to understand them (directed to the research assistants).
+A webcam recording of the participant can be enabled to record the participant's behavior during the task.
+Please ensure appropriate data protection measures are in place before enabling this feature.
+The study can either be started with default settings (depending on the chosen language: the stimuli which have been used by our reported samples here will be shown), or further customized.
+
+If researchers choose to further customize, the number of trials can be chosen for each trial type.
+No trial type can be skipped, so the minimum number of trials per type equals 1, the maximum equals 100.
+As the trial types build up on each other, each trial type is necessary to understand the structure of the task and needs to be completed before the next trial type starts.
+One out of four different backgrounds can be picked.
+Finally, there are 50 diverse human faces (50% female, 50% male) from which researchers can choose.
+There is no constraint on how many faces are allowed (min 1, max 50).
+Once all the settings are adjusted, the task can be started.
+
+We have compiled an instruction manual with the most frequently asked questions (<https://ccp-odc.eva.mpg.de/tango-cc/manual.html>).
+The source-code of the task is available on GitHub (<https://github.com/ccp-eva/tango-cc>).
+By edited the `HTML` and `JavaScript` code directly, researchers gain even more flexibility in adjusting the task to their needs.
+
+(ref:figlab1) **Customizable components of the TANGO-CC.** Researchers can select the language of the audio instructions, the number of trials per trial type, the background, and the agent's face.
+Screenshots of the trial show the proceeding events: in Training 1, an agent looks at a balloon that falls to the ground and participants have to respond by touching the balloon.
+In Training 2, the balloon falls behind the hedge, while its flight is still visible.
+Participants respond by touching the hedge where they think the balloon is.
+In Test trials, the balloon's movement and final position are covered by a hedge and participants respond by touching the hedge.
+In the task, all movements are smoothly animated (no still pictures).
+Yellow frames indicate the timepoint when participants respond (only illustrative, not shown during the task).
+
+```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
+knitr::include_graphics("../figures/tango-cc-procedure.png")
+```
+
+# Data collection
+
+## Participants
+
+```{r sample_table}
+sample_table <- readRDS("../saves/sample_table.rds")
+```
+
+The here used data set has been published by @bohn2024universal.
+The sample includes *N* = `r sample_table[sample_table$Community == "Total",]$Total` children between 2.5 to 11 years of age.
+Participants come from 17 communities in rural and urban settings on five continents with varying degrees of market integration and technology exposure.
+
+## Procedure
+
+We collected data using offline and online versions of the TANGO-CC on a Windows tablet.
+A local research assistant guided the children through the study.
+We instructed the research assistants to motivate the children and guide their attention to the screen, while explicit feedback (e.g., praise for a precise click) and hints (e.g., "look at the eyes") were not allowed.
+
+## Analysis
+
+As a first feasibility check, we inspected the mean and standard deviations by community and compared performance in each trial type (training 1, training 2, test trials).
+Since the age distribution across communities varied slightly, test trials were further analysed by performing a model-based age correction.
+A Generalized Linear Mixed Model (GLMM) was fitted with the mean imprecision as the outcome, age as a predictor and participant id as random effects: `imprecision ~ age + (1 | subjid)`.
+Furthermore, the within- and between-community variance and the intraclass correlation (ICC) were calculated.
+
+To assess reliability, we estimated internal consistency in each community in three different ways.
+First, data of each participant was split into odd and even trials and a Pearson correlation was calculated between the aggregated scores of the two halves.
+Second, using the function `by_split` from the `splithalfr` package [@pronk2022methods], data was stratified by target centrality, and a Pearson correlation was calculated between the matched halves.
+Third, an age correction was performed for the stratified approach by fitting a GLMM with the mean imprecision as the outcome, age as a predictor, and test half and participant id as random effects: `imprecision ~ age + (0 + half | subjid)`.
+This process was repeated 50 times for each community.
+The posterior estimate of the correlation between the two person-specific estimates is taken as the age-independent estimate for internal consistency.
 
 # Results
-- splithalf per cultural setting
-- effect of age distribution, different for each cultural setting
-- in plot: weigh sample size: x: splithalf, y: culture, size geom count: sample size
-- visualize ind diff
-- plot training trials argument for children understand to touch balloon
-- response time?
-- droup outs across cultures
+
+```{r read_results}
+var_df <- readRDS("../saves/var_df.rds")
+within_person <- readRDS("../saves/within_person.rds")
+# range(var_df$within_community_variance)
+# var_df$community[which.min(var_df$within_community_variance)]
+# var_df$community[which.max(var_df$within_community_variance)]
+```
+
+(ref:figlab2) **Measurement of the TANGO-CC by community and trial type.** (A) Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type.
+Imprecision is defined as the distance between the participant's touch and the balloon's center, in units of balloon width.
+For a depiction of each trial's procedure, see Figure 1.
+(B) Age-corrected imprecision in test trials by community.
+White lines (|) show the person-specific model predictions.
+(C) Internal consistency estimates by community, following three different approaches.
+In the odd-even split, the size of points reflects the sample size in each community.
+
+```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
+knitr::include_graphics("../figures/tango-cc-results.png")
+```
+
+Across communities, children performed best in training 1, followed by training 2 and test trials (see Figure \@ref(fig:fig2)A).
+The almost perfect performance in training trials indicated that children understood the task and were able to locate the balloon.
+In test trials, children's imprecision was higher, indicating that the task was more challenging.
+The TANGO-CC captured individual differences across ages and communities.
+A model-based age correction (see Figure \@ref(fig:fig2)B) provided evidence that the variation between individuals existed beyond the effect of age.
+All communities showed great individual variation and overlapped massively in their imprecision levels.
+
+The variation of children within one community was greater than the variation between the communities.
+The mean within-community variance was `r mean(var_df$within_community_var)`, ranging from `r min(var_df$within_community_var)` (in Pune, India) to `r max(var_df$within_community_var)` (in Chimfunshi, Zambia).
+Between-community variance was `r var_df$between_community_var[1]`.
+The intraclass correlation (ICC), representing the proportion of between-community variance relative to the total variance (sum of within- and between-community variance) was `r var_df$ICC_b[1]`.
+
+To see whether these differences were reliable, we assessed the task's internal consistency.
+The results from a simple odd-even split and the split half-reliability stratified by target centrality with and without model-based age correction yielded comparable results and are shown in Figure \@ref(fig:fig2)C.
+Across all communities, the task showed satisfactory to high reliability, with estimates ranging roughly between 0.5 and 0.9 (Plymouth, UK, being an outlier in the stratified, age-corrected internal consistency).
+In an exploratory analysis, we found that communities with larger individual variation showed higher internal consistency estimates.
+Please note that this could be influenced by outliers and that the sample size here (*N* = 17 communities) is too small to make substantial claims.
+
+As data collection across communities was organized slightly differently, we cannot report drop-out rates by community.
 
 # Discussion
-- flexibility for researchers
-- adjust to each cultural setting: faces, languages, background scene
-- easy to add new layers to svg to adjust even further
-- minimal language demands
-- worked across 16(?) different communities already
+
+We have presented a new task, the TANGO-CC, that measures imprecision in gaze following across individuals, ages, and communities.
+The task development took place in two main phases.
+First, we implemented the task's underlying functionality in one community and established validity and reliability in this setting (Leipzig, Germany).
+In the next step, we collaborated with cross-cultural researchers to create a larger stimulus pool.
+In this paper, we presented data from 17 different communities across the world and discussed the TANGO-CC's psychometrics.
+Children's imprecision in gaze-following highly overlapped between communities: children performed similarly in training and test trials, and within-community variation greatly exceeded between-community variation.
+The task showed satisfactory to high reliability across all communities.
+Therefore, we believe the TANGO-CC is a promising tool to capture individual differences in social-cognitive development in diverse social-cultural environments.
+
+A similar approach to task development was followed by @mehta2011validation.
+The researchers (1) selected social cognition measures that have been established in other settings, (2) adapted the agent's names, appearance, backgrounds, and languages to the local context, and (3) assessed the task's validity and internal consistency in the new setting.
+Their approach yielded a successful adaptation of social cognition measures for Indian (Hindi/Kannada) communities.
+Yet, @bourdage2023evaluation have argued that adapting social cognition tasks to each individual community is infeasible: the number of world cultures is vast, and communities are constantly changing.
+A promising approach, as taken by the TANGO-CC, might be to provide tasks with a modular building block system where components can be exchanged according to the local context.
+
+The biggest strength of the TANGO-CC is its flexibility: researchers can choose from different agents, languages, trial numbers and background scenes (see Figure \@ref(fig:fig1)).
+The task is presented as a web app, which can also run offline to enable remote data collection.
+Minimal language demands and an engaging, playful design increase the task's comprehensibility.
+Together with a short study duration, this reduces drop-out rates and enables efficient data collection with large sample sizes.
+The TANGO-CC follows a standardized procedure and uses a continuous, objective outcome measure (leaving no room for rater errors).
+An online manual with the most frequently asked questions is available at https://ccp-odc.eva.mpg.de/tango-cc/manual.html.
+Even more customization can be achieved by adding new stimuli to the open-source code available on GitHub (https://github.com/ccp-eva/tango-cc).
+
+Since years, researchers haved called for more diverse sampling and culturally valid social cognition measures [e.g., @mehta2011validation; @nielsen2017persistent; @matsumoto2006new].
+As @hajduk2020how put it, "using large samples and multisite approaches will align with efforts to improve reproducibility and will clarify both the type and extent of cultural influences on social cognition" (p.
+463).
+The TANGO-CC takes a valuable step in this direction by including large sample sizes from diverse communities and sharing both the data set and the task itself with other researchers.
+In this manuscript, we could show that data collection with the TANGO-CC was feasible in 17 diverse communities in rural and urban settings with varying degrees of market integration and technology exposure.
+While we cannot generalize our findings to all communities worldwide, we found that it worked well in the 17 communities that took part in this study.
+However, we do not want to signal that cross-cultural research is easy or that data can be collected remotely without a lot of effort.
+We want to emphasize that using the TANGO-CC in a new community, of course, needs sensitivity to the specific context, piloting, and, most importantly, input from local collaborators.
+We hope that the TANGO-CC will facilitate future cross-cultural studies to assess social-cognitive development in a wide range of communities.
+
+A valid question is whether the TANGO-CC measures the same construct across different groups.
+This so-called measurement invariance is often seen as a requirement for a "fair" cross-cultural comparison and relies on minimizing group differences, while individual differences are magnified.
+As @kusano2024mismeasure put it: "The research challenge is to achieve a balance between ensuring methodological “fairness” at the individual level while also recognizing and capturing genuine sociocultural variability" (p.
+34).
+We argue that the TANGO-CC measures a fundamental social-cognitive ability that is likely similar across cultural groups.
+This is also represented in our results, as we found that the within-group variability was greater than the between-group variability.
+Similarly, @selcuk2023development pointed out that researchers should study both the within- and the between-culture variability in the development of social cognition since sometimes within-culture differences are more influential.
+While we do believe that the TANGO-CC can be used to compare mean differences across cultural settings, we would recommend focusing on linking individual differences to social-cognitive or environmental factors.
 
 # Limitations
-- measure same construct across communities?
-- technology effects
+
+The TANGO-CC and its psychometric properties need to be considered against some limitations.
+Reliability for each community was assessed by calculating the internal consistency.
+Ideally, we would have additionally assessed the task's retest reliability by cultural setting and checked for relationships with theoretically related constructs.
+
+@schilbach2013secondperson pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions.
+This argument touches on two different points: (1) the mode of stimulus presentation (i.e., online vs.
+offline/real-life) and (2) the role of the participant (i.e., active vs.
+passive).
+First, potentially, not all children perceive the tablet-based presentation of the TANGO-CC as depicting a social interaction.
+In a German sample, we found that performance in the TANGO was linked to children's visual perspective-taking abilities in real-life social interaction [@prein2023variation].
+Arguably, children in this sample recognized the social context of the task.
+However, this could vary between communities: Children with prior TV or computer game exposure might be more inclined to interpret the cartoon-like faces as social stimuli.
+Indeed, @bohn2024universal have shown that children with no prior touchscreen exposure were slightly less precise in the TANGO-CC than children with prior experience.
+Notably, while this caused absolute differences in task performance, all communities showed the same processing signature: more precise responses for more central target locations.
+Furthermore, individual differences were also found in communities with 100% touch screen exposure, showing that this factor alone could not explain children's performance in the task [@bohn2024universal].
+In this manuscript, we could additionally show that internal consistency was high across all communities.
+Nevertheless, the mode of stimulus presentation surely needs to be kept in mind when administering the TANGO-CC, especially in communities with little technology exposure.
+Additional touch screen training (e.g., more trials of training 1) might prove helpful in these cases.
+
+Second, participants in the TANGO-CC observe another agent's gaze.
+While we employ an active choice measure and ask participants to use the agent's gaze to guide their behavior, children do not take part in a turn-taking social interaction.
+Future research could investigate whether a prior social interaction, for example, trials in which the child determines where the agent should look, could increase children's performance in the task.
+
+The target object presented in the TANGO-CC might be more common in some communities than in others.
+While we cannot rule out that this influenced children's performance, the huge overlap in performance across communities speaks for a generalizable underlying construct.
+In test trials, the target object is only visible for a very short amount of time, and the identity of the object is not relevant for succeeding in the task.
+Nevertheless, future research could investigate the effects of presenting different target objects.
+For example, @pena2007lost has proposed a decentering approach, where items are individually adapted to be culturally familiar in each setting.
+The same applies to the agent's face: while we tried to create a diverse set of faces, the faces might be more representative of some communities than others.
+The component-like structure and the open-source implementation with SVGs allow researchers to exchange stimuli according to their needs.
+
+@krys2024weirda have recently categorized countries into "macrocultural groupings: (1) WEIRD, (2) Confucian-influenced, (3) Latin America and Caribbean, (4) Middle East and North Africa (excluding Israel), (5) non-Confucian Asia and Oceania, (6) sub-Saharan Africa, and (7) non-EU postcommunist states" (p.
+5) and proposed that cross-cultural studies should aim to include at least one country from each macrocultural grouping.
+Although we included communities from five continents, we did not follow this categorization and indeed did not collect data in "non-EU postcommunist states" (e.g., Russia, Georgia, Serbia; even though it might be questioned whether this label is well-chosen).
+While the results from the TANGO-CC seem promising, we cannot generalize them to all communities worldwide.
 
 # Conclusion
+
+The TANGO-CC is a promising tool to capture individual differences in social-cognitive development across diverse social-cultural environments.
+Task development occurred in two phases: (1) establishing the task's underlying functionality and detailed psychometrics in one community, and (2) expanding the stimulus pool and collecting data from diverse communities world-wide.
+The task's flexibility, minimal language demands, and engaging design make it a valuable tool for cross-cultural research.
+We successfully collected data with the TANGO-CC from 2.5- to 11-year-olds in 17 communities, with children showing similar performance across communities.
+The task showed satisfactory to high reliability across all communities as measured by internal consistency.
+We hope that the TANGO-CC will facilitate future cross-cultural studies to assess social-cognitive development in a wide range of communities.
 

### 2024-04-15 paper/manuscript.tex
create rough first draft

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,mask,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{cross-cultural psychology, social cognition, gaze following, individual differences, reliability\newline\indent Word count: XXX}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{setspace}
\usepackage{libertine}
\captionsetup[figure]{font={stretch=1}}
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Measuring variation in gaze-following across cultures, individuals, and age --- a showcase of the TANGO-CC},
  pdflang={en-EN},
  pdfkeywords={cross-cultural psychology, social cognition, gaze following, individual differences, reliability},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Measuring variation in gaze-following across cultures, individuals, and age --- a showcase of the TANGO-CC}
\author{Julia Prein (ORCID: 0000-0002-3154-6167)\textsuperscript{1,2}, Florian M. Bednarski (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Ardain Dzabatou\textsuperscript{5}, Michael C. Frank (ORCID: 0000-0002-7551-4378)\textsuperscript{6}, Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Josefine Kalbitz\textsuperscript{2}, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)\textsuperscript{7}, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)\textsuperscript{8}, Bahar Köymen (ORCID: 0000-0001-5126-8240)\textsuperscript{9}, Maira V. Manrique-Hernandez\textsuperscript{2}, Shirley Magazi (ORCID: 0009-0006-0479-9800)\textsuperscript{10}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R. Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{10}, Sarah Pope-Caldwell\textsuperscript{2}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,10}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{11}, Robert Z. Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{6}, Jahnavi Sunderarajan\textsuperscript{2}, Florence Tusiime\textsuperscript{3}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{12}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{12}, Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)\textsuperscript{2,+}, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)\textsuperscript{1,2,+}}
\date{}

\shorttitle{measuring gaze following across cultures}

\authornote{

The authors made the following contributions. Julia Prein (ORCID: 0000-0002-3154-6167): Conceptualization, Methodology, Software, Investigation, Writing - Original Draft Preparation, Writing - Review \& Editing; Florian M. Bednarski (ORCID: 0000-0003-4384-4791): Investigation, Writing - Review \& Editing; Ardain Dzabatou: Investigation; Michael C. Frank (ORCID: 0000-0002-7551-4378): Investigation, Writing - Review \& Editing; Annette M. E. Henderson (ORCID: 0000-0003-4384-4791): Investigation, Writing - Review \& Editing; Josefine Kalbitz: Investigation, Writing - Review \& Editing; Patricia Kanngiesser (ORCID:0000-0003-1068-3725): Investigation, Writing - Review \& Editing; Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733): Investigation, Writing - Review \& Editing; Bahar Köymen (ORCID: 0000-0001-5126-8240): Investigation, Writing - Review \& Editing; Maira V. Manrique-Hernandez: Investigation; Shirley Magazi (ORCID: 0009-0006-0479-9800): Investigation; Lizbeth Mújica-Manrique: Investigation, Writing - Review \& Editing; Julia Ohlendorf: Investigation; Damilola Olaoba: Investigation; Wesley R. Pieters (ORCID:0000-0002-6152-249X): Investigation, Writing - Review \& Editing; Sarah Pope-Caldwell: Investigation; Roman Stengelin (ORCID: 0000-0003-2212-4613): Conceptualization, Methodology, Investigation, Writing - Review \& Editing; Katie Slocombe (ORCID: 0000-0002-7310-1887): Investigation, Writing - Review \& Editing; Robert Z. Sparks (ORCID: 0000-0001-7545-0522): Investigation; Jahnavi Sunderarajan: Investigation; Florence Tusiime: Investigation; Wilson Vieira (ORCID: 0009-0001-9400-6328): Investigation; Zhen Zhang (ORCID: 0000-0001-9300-0920): Investigation, Writing - Review \& Editing; Yufei Zong (ORCID: 0009-0000-5012-0244): Investigation; Daniel B. M. Haun (ORCID: 0000-0002-3262-645X): Conceptualization, Funding acquisition, Writing - Review \& Editing; Manuel Bohn (ORCID: 0000-0001-6006-1348): Conceptualization, Methodology, Writing - Review \& Editing.

Correspondence concerning this article should be addressed to Julia Prein (ORCID: 0000-0002-3154-6167), Universitätsallee 1, 21335 Lüneburg, Germany. E-mail: \href{mailto:manuel.bohn@leuphana.de}{\nolinkurl{manuel.bohn@leuphana.de}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology\\\textsuperscript{3} Budongo Conservation Field Station\\\textsuperscript{4} School of Psychology, University of Auckland\\\textsuperscript{5} Université Marien Ngouabi\\\textsuperscript{6} Department of Psychology, Stanford University\\\textsuperscript{7} School of Psychology, University of Plymouth\\\textsuperscript{8} Department of Psychology, Koç University\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia\\\textsuperscript{11} Department of Psychology, University of York\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences\\\textsuperscript{+} joint last author}

\abstract{%
Cross-cultural studies are crucial for establishing the universality and robustness of developmental milestones. Yet, suitable methods to measure variability in social cognition across linguistic and cultural settings are lacking. This paper describes the TANGO-CC (Task for Assessing Individual Differences in Gaze Understanding - Cross Cultural), a gaze-following task designed to measure imprecision in gaze following across individuals, ages, and communities. The development of the TANGO-CC involved two main phases: initial implementation and validation in Leipzig, Germany, followed by collaboration with cross-cultural researchers to expand the stimulus pool and collect data from 2.5- to 11-year-old children (N = 1377) from 17 diverse communities worldwide. The TANGO-CC captured individual differences and high internal consistency in each community. Within-community variation outweighed between-community variation. Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each cultural setting. We provide an open-source website for researchers to customize the task to their needs. Overall, the TANGO-CC represents a valuable contribution to the assessment of social-cognitive development in diverse social-cultural environments, facilitating future cross-cultural studies.
}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

More than a decade ago, Henrich et al. (2010) advocated for more diverse samples in psychological research and cautioned against relying solely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) backgrounds. Despite numerous calls for change, the subject pools reported in high-impact journals still lack diversity (Nielsen et al., 2017). This lack of representation creates inequities and hampers progress in theory building: If we want to draw inferences about the unique characteristics of human behavior and ``human nature'', we need to study it in many humans from many different backgrounds (Krys et al., 2024).

The present sampling bias might be especially problematic in research concerning the development of social cognition. Social cognition concerns the processes by which individuals encode and decode social information (Glynn \& Watkiss, 2016), which allows them to successfully participate in joint activities and communication. Many developmental theories emphasize the role of social interaction in the development of social cognition (e.g., reinforcement learning in gaze following; (Jasso \& Triesch, 2006)). However, social interactions differ substantially in their characteristics across communities and even across families and individuals. Cultural and social experiences influence the beliefs, values, norms and expectations of an individual, which, in turn, determines how they interpret other's actions. Consequently, Selcuk et al. (2023) have urged for studying how social-cultural factors on a macro-, community-level as well as a micro-, family-level influence the social cognition development.

Why are there not more social-cognitive studies focusing on the variation between diverse communities and individuals? A potential reason for the under-representation of these studies may be the scarcity of suitable tools (Bourdage et al., 2023). A suitable tool for studying individual- and community-level variation needs to address its (1) psychometric properties and (2) cross-cultural adaptations.

First, studies investigating variation between communities and/or individuals need to ensure that the captured variation is systematic and not just random noise. This requires measurement reliability and validity. Yet, social cognition studies based on US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020). This picture further deteriorates when we pay attention to the reliability and validity of cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020). It remains challenging to find reliable and valid tasks that can capture individual differences within one community, let alone finding tasks that can be applied across different cultural settings.

Second, adapting tasks to diverse cultural settings and re-assessing their validity and reliability might be especially important in the social-cognitive domain. If, in theory, stimuli used in social cognition tasks should depict people's everyday experiences, the tasks need to represent different social and cultural environments. Indeed, task performance can be diminished when stimuli are not adjusted (Peña, 2007). For example, Elfenbein and Ambady (2002) found better emotion recognition for members of the same national, ethnic, or regional group. Selcuk et al. (2023) concluded that children often attribute mental states more accurately and more frequently to individuals from the same cultural group. This underlines the importance of adapting tasks to each specific cultural context.

Broadly speaking, there are two different approaches that researchers can take to collect data that is comparable across cultural settings. One approach would be to translate the psychological construct into an individually designed study for each cultural setting. While this approach is most flexible and sensitive to cultural differences, it might be most feasible for studying up to a handful communities. Examples for studies that followed this approach are Mehta et al. (2011), Stengelin et al. (2020), Chasiotis et al. (2006). However, recent articles call for the inclusion of more field sites in cross-cultural studies (e.g., Krys et al., 2024). The approach of individually re-designing a study for each community might then become too demanding and time-consuming. Another approach would be to use the same standardized procedure across diverse cultural settings. This approach is less sensitive to each community's unique characteristics but allows for a direct comparison of data across cultural settings. Examples following this approach include Callaghan et al. (2011), Taumoepeau et al. (2019), Hughes et al. (2018), Hughes et al. (2014), Fujita et al. (2022). This paper aims to describe the development and psychometric properties of a standardized task that can be adapted to different social and linguistic settings.

The task presented in this manuscript focuses on gaze following, the ability to identify the attentional focus of another agent. Gaze following develops early in infancy (Del Bianco et al., 2019; Tang et al., 2024) and contributes to social learning, communication and collaboration (Bohn \& Köymen, 2018; Hernik \& Broesch, 2019; Shepherd, 2010; Tomasello et al., 2007). While gaze following acts as one of the most fundamental social-cognitive abilities, studies focusing on cultural variations are rare. The few existing results are mixed whether gaze following is influenced by cultural factors or not (Callaghan et al., 2011; Hernik \& Broesch, 2019).

The task presented here builds upon the TANGO (Task for Assessing iNdividual differences in gaze understanding - Open) by Prein, Kalinke, et al. (2023). The TANGO measures participants' imprecision of locating an agent's attentional focus. It has been shown to reliably capture individual differences in a German child sample and an international remote adult sample. The task was sensitive to developmental changes and linked to children's receptive vocabulary. Furthermore, an exploratory analysis showed that children performed equally well in a study version with animal faces compared to cartoon human faces (Prein, Maurits, et al., 2023). Therefore, superficial variations in the stimulus design do not seem to influence children's performance in the task.

This paper showcases the TANGO-CC (TANGO - Cross Cultural), a standardized gaze-following task that can be adapted to several languages and cultural settings. We describe our reasoning behind the task's development and provide a tutorial for the open-source website (\url{https://ccp-odc.eva.mpg.de/tango-cc/}). We present results from a large cross-cultural sample of 2.5- to 11-year-olds from 17 different urban/rural communities across the world and discuss the task's psychometrics. The task and all its adaptations have been initially designed for a paper by Bohn et al. (2024), and we re-use the data set in this paper.

\hypertarget{task-development}{%
\section{Task development}\label{task-development}}

\hypertarget{approach}{%
\subsection{Approach}\label{approach}}

In a perfect world, developing a cross-cultural task would include international collaboration and diverse samples from the beginning, already during piloting and item selection. As this seems hardly feasible, we present an alternative, pragmatic approach to developing a task that can be applied across different communities. This approach has its faults. However, we later present results that show that our task adaptation yielded stable, clear results across a wide range of communities.

Our general approach to developing the TANGO-CC consisted of two main parts. First, the task was implemented in one context, in our case with a German sample (the TANGO; (Prein, Kalinke, et al., 2023)). In this context, we assessed the task's reliability and validity in detail. Even though this does not guarantee that the task will work in another context, we believe it increases the chances. Second, we collaborated with cross-cultural researchers and expanded the stimulus pool to diverse cultural and linguistic settings. Bohn et al. (2024) collected data in 17 communities worldwide. We assessed performance across trial types and checked for individual differences. If we found individual differences in other communities to a similar degree to the German sample, it was likely that these individual differences were also systematic. This would be, for example, less likely if we saw floor- or ceiling effects. Reliability was estimated using internal consistency measures. Therefore, our procedure tried to maintain a balance between a detailed analysis of the task's psychometric properties across communities and a swift and feasible task adaptation. In the following, we describe the different steps in further detail. Even though we focus on the cross-cultural adaptation of the TANGO, we believe the general approach might be helpful for other researchers who aim to design cross-culturally adaptable tasks.

In the first step, we designed the task's underlying functionality. We aimed for a measure that maps directly onto the task's underlying psychological construct: in our case, the imprecision with which participants can locate an agent's attentional focus. We were motivated to create a continuous outcome measure since this allows for more room to capture individual differences. The core of the task was calculating where the agent's eyes must move to follow the target's movement. In the next step, this structure was filled with the task's superficial appearance and audio instructions. Notably, the task's presentation can be adjusted without changing its underlying structure. For example, we can change the background scene, the faces of the agent, and the target without changing the logic of where the agent looks or the participants' task to identify an agent's attentional focus. We realized that as soon as the task's underlying structure was implemented, adaptations of the task and data collection efforts were greatly simplified.

After implementing the task, we assessed the psychometric properties of the TANGO in a WEIRD sample. We collected data of a German child sample and an international remote adult sample (Prein, Kalinke, et al., 2023). The adult sample worked as a proof-of-concept and showed that remote data collection worked very well. We reasoned that if we find individual differences in an adult sample, chances are high that we also find them in a child sample, as adults usually exhibit less variation in abilities than children. The task captured a developmental change and showed neither floor nor ceiling effects.

Most importantly, we found individual differences across all age groups. By evaluating split half- and retest reliability estimates, we could show that the individual variation was systematic and not just random noise. Additionally, we assessed the task's validity by examining the relationship with theoretically related concepts. Performance in the TANGO was linked to children's receptive vocabulary and weakly related to factors of children's daily social environment (Prein, Kalinke, et al., 2023). In another study, we proposed a computational cognitive model that described gaze following as a social form of vector following. Gaze following, as measured by the TANGO, was related to children's vector following and visual perspective-taking abilities (Prein, Maurits, et al., 2023). These connections to related constructs speak toward the task's validity in the German setting. An exploratory analysis showed that performance in the TANGO was similar when presenting animal vs.~human faces (Prein, Maurits, et al., 2023 supplements). This demonstrates that the participants' performance did not depend on superficial features of the task's appearance.

As a next step, we contacted cross-cultural researchers and field assistants interested in using the TANGO. We asked local people to give input as to how we could adapt the task to their local needs. Together with their help, we generated a set of 50 diverse human faces that were aimed to be representative of each local population. Similarly, different backgrounds were created that roughly represented a typical accommodation in each community. Research assistants translated the audio instructions into the corresponding local language. By back-translating these instructions, we ensured the original meaning did not change. Sometimes, specific words were linguistically slightly modified, although functionally equivalent (e.g., ``bush'' instead of ``hedge'') to ensure that all participants understood the instructions. Before collecting data in each community, we piloted with a small sample. This procedure slightly varied between communities; see supplements for further details. In the following, we describe the design features of the TANGO-CC in greater detail.

\hypertarget{features-of-the-tango}{%
\subsection{Features of the TANGO}\label{features-of-the-tango}}

The task presented in this manuscript is the cross-cultural adaptation of the TANGO (Prein, Kalinke, et al., 2023). We quickly recap the TANGO's most characteristic features: Participants are asked to locate a balloon with the help of a gaze cue. The outcome variable is the distance between the participant's touch and the balloon's center. Trials can be completed in a fast and efficient way, so that children can easily complete 15 trials within 10 min. This drastically reduced drop-out rates. By using essentially self-explanatory animations, language demands are kept to a minimum. To keep trials comparable and avoid learning effects, no differential feedback is given.

\hypertarget{task-implementation}{%
\subsubsection{Task implementation}\label{task-implementation}}

The task was implemented in \texttt{JavaScript}, \texttt{HTML}, and \texttt{CSS}, and is presented as a web app. It can be accessed on any web browser and does not require prior installation. The online version of the task has been proven convenient for unsupervised data collection (for example, using participant recruitment services like \emph{Prolific}, see Prein, Kalinke, et al. (2023)), and sharing the task across big international collaborations. Importantly, the web app implementation does not necessarily need a working WIFI connection: An offline, local version of the task can be quickly set up for devices that support Node.js (\url{https://nodejs.org/en}). This is an especially useful feature for researchers working in remote areas with limited internet access.

The stimuli are embedded as Scalable Vector Graphics (SVG). The setup allows for an easy adaptation of study elements and ensures that picture quality, aspect ratio and relative object positioning are constant. We implemented some features designed to ensure meaningful clicking responses. The study is programmed so that responses are only registered when the participant touches the relevant part of the screen (i.e., in test trials the hedge). Furthermore, clicks are only registered after the voice recordings stopped playing. If no click is registered within 5 seconds, an audio reminder is played again.

The website does not use cookies, nor does it upload any data to servers; that is, the data is only stored locally on the device. The output of the study is a CSV file that contains the participants' responses and can be easily imported into statistical software for further analysis. The saved variables are: id, language, background, trial\_number, study\_phase, audio\_instructions, keep\_trial, agent, balloon\_color, balloon\_bin, balloon\_center, click, absolute\_click\_distance, timestamp, responsetime\_ms. In case a webcam recording was selected, a second file is saved that contains the webcam recording (WEBM file). The files will be stored in the device's downloads folder and is named after the following pattern: ``tangoCC-participantID-YYYY-MM-DD\_hh\_mm\_ss''.

\hypertarget{trial-types}{%
\subsubsection{Trial types}\label{trial-types}}

The task consists of three different trial types. In every trial, participants see an agent (boy or girl) looking out of house, with a balloon (red, blue, green or yellow) in front of them. The balloon falls down to the ground, while the eyes of the agent follow the movement of the balloon in a way that their centers always align. Depending on the trial type, participants have different visual access to the balloon's position.
In training 1, participants see the full trajectory of the balloon and directly have to touch the balloon itself. In training 2, participants see most of the balloon's movement but the final location is covered by a hedge. In test trials, a hedge grows in the beginning of the trial and participants see neither the movement nor the final position of the balloon. The first trial of each type contains an audio description of the presented events (see Supplements). Importantly, the instructions explicitly state that the agent is looking at the balloon.

\hypertarget{randomization}{%
\subsubsection{Randomization}\label{randomization}}

The order of the agents, balloon colors (red, yellow, green, blue), and balloon positions are each randomized independently. For the balloon positions, the full width of the screen (1920 in ``SVG unit'') is divided into ten bins. Exact coordinates (value between 0 far left and 1920 far right) within each bin are then randomly generated. The number of repetitions for each agent, balloon color, and balloon bin is calculated based on the total number of trials and the number of unique agents, balloon colors, and bins, respectively. All agents, balloon colors, and bins appear equally often and are not repeated in more than two consecutive trials. If the total number of trials is not divisible by the number of unique elements, additional elements are randomly selected to make up for the remainder.

\hypertarget{cross-cultural-customization}{%
\subsection{Cross-cultural customization}\label{cross-cultural-customization}}

The TANGO-CC expands the stimulus pool of the TANGO by depicting human faces and different languages for the audio instructions. The TANGO-CC can be accessed here: (\url{https://ccp-odc.eva.mpg.de/tango-cc/}). Researchers can customize the following parts of the task. In the first step, researchers can enter an alphanumeric participant identifier (1 - 8 characters). Audio instructions are currently available in 13 different languages (and even more dialects): Bayaka (Rep.~Congo), Bemba (Zambia), Chinese (China), English (India), English (New Zealand), English (Nigeria), English (UK), English (USA), German (Germany), Hai\textbar\textbar om (Namibia), Khewdam (Namibia), Lingala (Rep.~Congo), Marathi (India), Shona (Zimbabwe), Spanish (Argentina), Spanish (Mexico), Swahili (Uganda), Turkish (Türkiye). Please note that the written instructions are always in English, however, children are not required to understand them (directed to the research assistants). A webcam recording of the participant can be enabled to record the participant's behavior during the task. Please ensure appropriate data protection measures are in place before enabling this feature. The study can either be started with default settings (depending on the chosen language: the stimuli which have been used by our reported samples here will be shown), or further customized.

If researchers choose to further customize, the number of trials can be chosen for each trial type. No trial type can be skipped, so the minimum number of trials per type equals 1, the maximum equals 100. As the trial types build up on each other, each trial type is necessary to understand the structure of the task and needs to be completed before the next trial type starts. One out of four different backgrounds can be picked. Finally, there are 50 diverse human faces (50\% female, 50\% male) from which researchers can choose. There is no constraint on how many faces are allowed (min 1, max 50). Once all the settings are adjusted, the task can be started.

We have compiled an instruction manual with the most frequently asked questions (\url{https://ccp-odc.eva.mpg.de/tango-cc/manual.html}). The source-code of the task is available on GitHub (\url{https://github.com/ccp-eva/tango-cc}). By edited the \texttt{HTML} and \texttt{JavaScript} code directly, researchers gain even more flexibility in adjusting the task to their needs.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango-cc-procedure}

}

\caption{\textbf{Customizable components of the TANGO-CC.} Researchers can select the language of the audio instructions, the number of trials per trial type, the background, and the agent's face. Screenshots of the trial show the proceeding events: in Training 1, an agent looks at a balloon that falls to the ground and participants have to respond by touching the balloon. In Training 2, the balloon falls behind the hedge, while its flight is still visible. Participants respond by touching the hedge where they think the balloon is. In Test trials, the balloon's movement and final position are covered by a hedge and participants respond by touching the hedge. In the task, all movements are smoothly animated (no still pictures). Yellow frames indicate the timepoint when participants respond (only illustrative, not shown during the task).}\label{fig:fig1}
\end{figure}

\hypertarget{data-collection}{%
\section{Data collection}\label{data-collection}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

The here used data set has been published by (Bohn et al., 2024). The sample includes \emph{N} = 1372 children between 2.5 to 11 years of age. Participants come from 17 communities in rural and urban settings on five continents with varying degrees of market integration and technology exposure.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

We collected data using offline and online versions of the TANGO-CC on a Windows tablet. A local research assistant guided the children through the study. We instructed the research assistants to motivate the children and guide their attention to the screen, while explicit feedback (e.g., praise for a precise click) and hints (e.g., ``look at the eyes'') were not allowed.

\hypertarget{analysis}{%
\subsection{Analysis}\label{analysis}}

As a first feasibility check, we inspected the mean and standard deviations by community and compared performance in each trial type (training 1, training 2, test trials). Since the age distribution across communities varied slightly, test trials were further analysed by performing a model-based age correction. A Generalized Linear Mixed Model (GLMM) was fitted with the mean imprecision as the outcome, age as a predictor and participant id as random effects: \texttt{imprecision\ \textasciitilde{}\ age\ +\ (1\ \textbar{}\ subjid)}. Furthermore, the within- an between-community variance and the intraclass correlation (ICC) were calculated.

To assess reliability, we estimated internal consistency in each community in three different ways. First, data of each participant was split into odd and even trials and a Pearson correlation was calculated between the aggregated scores of the two halves. Second, using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2022), data was stratified by target centrality and a Pearson correlation was calculated between the matched halves. Third, an age correction was performed for the stratified approach by fitting a GLMM with the mean imprecision as the outcome, age as a predictor and test half and participant id as random effects: \texttt{imprecision\ \textasciitilde{}\ age\ +\ (0\ +\ half\ \textbar{}\ subjid)}. This process was repeated 50 times for each community. The posterior estimate of the correlation between the two person-specific estimates is taken as the age-independent estimate for internal consistency.

\hypertarget{results}{%
\section{Results}\label{results}}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango-cc-results}

}

\caption{\textbf{Measurement of the TANGO-CC by community and trial type.} (A) Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type. Imprecision is defined as the distance between the participant's touch and the balloon's center, in units of balloon width. For a depiction each trial's procedure, see Figure 1. (B) Age-corrected imprecision in test trials by community. White lines (\textbar) show the person-specific model predictions. (C) Internal consistency estimates by community, following three different approaches. In the odd-even split, the size of points reflects the sample size in each community.}\label{fig:fig2}
\end{figure}

Across communities, children performed best in training 1, followed by training 2 and test trials (see Figure \ref{fig:fig2}A). The almost perfect performance in training trials indicated that children understood the task and were able to locate the balloon. In test trials, children's imprecision was higher, indicating that the task was more challenging. The TANGO-CC captured individual differences across ages and communities. A model-based age correction (see Figure \ref{fig:fig2}B) provided evidence that the variation between individuals existed beyond the effect of age. All communities showed great individual variation and overlapped massively in their imprecision levels.

Variation of children within one community was greater than the variation between the communities. The mean within-community variance was 1.28, ranging from 0.24 (in Pune, India) to 3.46 (in Chimfunshi, Zambia). Between-community variance was 0.34. The intraclass correlation (ICC), representing the proportion of between-community variance relative to the total variance (sum of within- and between-community variance) was 0.02.

To see whether these differences were reliable, we assessed the task's internal consistency. The results from a simple odd-even split and the splithalf-reliability stratified by target centrality with and without model-based age correction yielded comparable results and are shown in Figure \ref{fig:fig2}C. Across all communities, the task showed satisfactory to high reliability, with estimates ranging roughly between 0.5 and 0.9 (Plymouth, UK, being an outlier in the stratified, age-corrected internal consistency). In an exploratory analysis, we found that communities with larger individual variation showed higher internal consistency estimates. Please note that this could be influenced by outliers and that the sample size here (\emph{N} = 17 communities) is very small to make substantial claims.

As data collection across communities was organized slightly differently, we cannot report drop-out rates by community.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

We have presented a new task, the TANGO-CC, that measures imprecision in gaze following across individuals, ages, and communities. The task development took place in two main phases. First, we implemented the task's underlying functionality in one community and established validity and reliability in this setting (Leipzig, Germany). In the next step, we collaborated with cross-cultural researchers to create a larger stimulus pool. In this paper, we presented data from 17 different communities across the world and discussed the TANGO-CC's psychometrics. Children's imprecision in gaze-following highly overlapped between communities: children performed similarly in training and test trials, and within-community variation greatly exceeded between-community variation. The task showed satisfactory to high reliability across all communities. Therefore, we believe the TANGO-CC is a promising tool to capture individual differences in social-cognitive development in diverse social-cultural environments.

A similar approach to task development was followed by Mehta et al. (2011). The researchers (1) selected social cognition measures that have been established in other settings, (2) adapted the agent's names, appearance, backgrounds, and languages to the the local context, and (3) assessed the task's validity and internal consistency in the new setting. Their approach yielded a successful adaptation of social cognition measures for Indian (Hindi/Kannada) communities. Yet, Bourdage et al. (2023) have argued that adapting social cognition tasks to each individual community is infeasible: the number of world cultures is vast and communities are constantly changing. A promising approach, as taken by the TANGO-CC, might be to provide tasks with a modular building block system, where components can be exchanged according to the local context.

The biggest strength of the TANGO-CC is its flexibility: researchers can can choose from different agents, languages, trial numbers and background scenes (see Figure \ref{fig:fig1}). The task is presented as a web-app, which can also run offline to enable remote data collection. Minimal language demands and an engaging, playful design increase the task's comprehensibility. Together with a short study duration, this reduces drop-out rates and enables efficient data collection with large sample sizes. The TANGO-CC follows a standardized procedure and uses a continuous, objective outcome measure (leaving no room for rater errors). An online manual with the most frequently asked questions is available at \url{https://ccp-odc.eva.mpg.de/tango-cc/manual.html}. Even more customization can be achieved by adding new stimuli to the open-source code available on GitHub (\url{https://github.com/ccp-eva/tango-cc}).

Since years, researchers haved called for more diverse sampling and culturally valid social cognition measures (Matsumoto \& Yoo, 2006; e.g., Mehta et al., 2011; Nielsen et al., 2017). As Hajdúk et al. (2020) put it, ``using large samples and multisite approaches will align with efforts to improve reproducibility and will clarify both the type and extent of cultural influences on social cognition'' (p.~463). The TANGO-CC takes a valuable step in this direction by including large sample sizes from diverse communities and sharing both the data set and the task itself to other researchers. In this manuscript, we could show that data collection with the TANGO-CC was feasible in 17 diverse communities, in rural and urban settings with varying degrees of market integration and technology exposure. While we cannot generalize our findings to all communities world-wide, we found that it worked well in the 17 communities that took part in this study. However, we do not want to signal that cross-cultural research is easy or that data can be collected remotely without a lot of effort. We want to emphasize that using the TANGO-CC in a new community of course needs sensitivity to the specific context, piloting and, most importantly, input from local collaborators. We hope that the TANGO-CC will facilitate future cross-cultural studies to assess social-cognitive development in a wide range of communities.

A valid question is whether the TANGO-CC measures the same construct across different groups. This so-called measurement invariance is often seen as a requirement for a ``fair'' cross-cultural comparison and relies on minimizing group differences, while individual differences are magnified. As Kusano et al. (2024) put it: ``The research challenge is to achieve a balance between ensuring methodological ``fairness'' at the individual level while also recognizing and capturing genuine sociocultural variability'' (p.~34). We argue that the TANGO-CC measures a fundamental social-cognitive ability that is likely similar across cultural groups. This is also represented in our results, as we found that the within-group variability was greater than the between-group variability. Similarly, Selcuk et al. (2023) pointed out that researchers should study both the within- and the between-culture variability in the development of social cognition, since sometimes within-culture differences are more influential. While we do believe that the TANGO-CC can be used to compare mean differences across cultural settings, we would recommend focusing on linking individual differences to social-cognitive or environmental factors.

\hypertarget{limitations}{%
\section{Limitations}\label{limitations}}

The TANGO-CC and its psychometric properties need to be considered against some limitations. Reliability for each community was assessed by calculating the internal consistency. Ideally, we would have additionally assessed the task's retest reliability by cultural setting and checked for relationships with theoretically related constructs.

Schilbach et al. (2013) pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions. This argument touches on two different points: (1) the mode of stimulus presentation (i.e., online vs.~offline/real-life) and (2) the role of the participant (i.e., active vs.~passive). First, potentially, not all children perceive the tablet-based presentation of the TANGO-CC as depicting a social interaction. In a German sample, we found that performance in the TANGO was linked to children's visual perspective-taking abilities in real-life social interaction (Prein, Maurits, et al., 2023). Arguably, children in this sample recognized the social context of the task. However, this could vary between communities: Children with prior TV or computer game exposure might be more inclined to interpret the cartoon-like faces as social stimuli. Indeed, Bohn et al. (2024) have shown that children with no touchscreen exposure were slightly less precise in the TANGO-CC than children with prior experience. Notably, while this caused absolute differences in task performance, all communities showed the same processing signature: more precise responses for more central target locations. Furthermore, individual differences were also found in communities with 100\% touch screen exposure, showing that this factor alone could not explain children's performance in the task (Bohn et al., 2024). In this manuscript, we could additionally show that internal consistency was high across all communities. Nevertheless, the mode of stimulus presentation surely needs to be kept in mind when administering the TANGO-CC, especially in communities with little technology exposure. Additional touch screen training (e.g., more trials of training 1) might prove helpful in these cases.

Second, participants in the TANGO-CC observe another agent's gaze. While we employ an active choice measure and ask participants to use the agent's gaze to guide their behavior, children do not take part in a turn-taking social interaction. Future research could investigate whether a prior social interaction, for example, trials in which the child determines where the agent should look, could increase children's performance in the task.

The target object presented in the TANGO-CC might be more common in some communities than in others. While we cannot rule out that this influenced children's performance, the huge overlap in performance across communities speaks for a generalizable underlying construct. In test trials, the target object is only visible for a very short amount of time, and the identity of the object is not relevant for succeeding in the task. Nevertheless, future research could investigate the effects of presenting different target objects. For exanple, Peña (2007) have proposed a decentering approach, where items are individually adapted to be culturally familiar in each setting. The same applies to the agent's face: while we tried to create a diverse set of faces, the faces might be more representative of some communities than others. The component-like structure and the open-source implementation with SVGs allows researchers to exchange stimuli according to their needs.

Krys et al. (2024) have recently categorized countries into ``macrocultural groupings: (1) WEIRD, (2) Confucian-influenced, (3) Latin America and Caribbean, (4) Middle East and North Africa (excluding Israel), (5) non-Confucian Asia and Oceania, (6) sub-Saharan Africa, and (7) non-EU postcommunist states'' (p.~5) and proposed that cross-cultural studies should aim to include at least one country from each macrocultural grouping. While we included communities from five continents, we did not follow this categorization and indeed did not collect data in ``non-EU postcommunist states'' (e.g., Russia, Georgia, Serbia; even though it might be questioned whether this label is well-chosen). While the results from the TANGO-CC seem promising, we cannot generalize them to all communities world-wide.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

The TANGO-CC is a promising tool to capture individual differences in social-cognitive development across diverse social-cultural environments. Task development occurred in two phases: (1) establishing the task's underlying functionality and detailed psychometrics in one community, and (2) expanding the stimulus pool and collecting data from diverse communities world-wide. The task's flexibility, minimal language demands, and engaging design make it a valuable tool for cross-cultural research. The TANGO-CC was successfully implemented in 17 communities, with children showing similar performance across communities. The task showed satisfactory to high reliability across all communities. We hope that the TANGO-CC will facilitate future cross-cultural studies to assess social-cognitive development in a wide range of communities.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-beaudoin2020systematic}{}}%
Beaudoin, C., Leblanc, É., Gagner, C., \& Beauchamp, M. H. (2020). Systematic {Review} and {Inventory} of {Theory} of {Mind Measures} for {Young Children}. \emph{Frontiers in Psychology}, \emph{10}, 2905. \url{https://doi.org/10.3389/fpsyg.2019.02905}

\leavevmode\vadjust pre{\hypertarget{ref-bohn2018common}{}}%
Bohn, M., \& Köymen, B. (2018). Common {Ground} and {Development}. \emph{Child Development Perspectives}, \emph{12}(2), 104--108. \url{https://doi.org/10.1111/cdep.12269}

\leavevmode\vadjust pre{\hypertarget{ref-bohn2024universal}{}}%
Bohn, M., Prein, J. C., Ayikoru, A., Bednarski, F. M., Dzabatou, A., Frank, M. C., Henderson, A. M. E., Isabella, J., Kalbitz, J., Kanngiesser, P., Keşşafoğlu, D., Koymen, B., Manrique-Hernandez, M., Magazi, S., Mújica-Manrique, L., Ohlendorf, J., Olaoba, D., Pieters, W., Pope-Caldwell, S., \ldots{} Haun, D. (2024). \emph{A universal of human social cognition: {Children} from 17 communities process gaze in similar ways}. OSF. \url{https://doi.org/10.31234/osf.io/z3ahv}

\leavevmode\vadjust pre{\hypertarget{ref-bourdage2023evaluation}{}}%
Bourdage, R., Narme, P., Neeskens, R., Papma, J., \& Franzen, S. (2023). An {Evaluation} of {Cross-Cultural Adaptations} of {Social Cognition Testing}: {A Systematic Review}. \emph{Neuropsychology Review}. \url{https://doi.org/10.1007/s11065-023-09616-0}

\leavevmode\vadjust pre{\hypertarget{ref-callaghan2011early}{}}%
Callaghan, T., Moll, H., Rakoczy, H., Warneken, F., Liszkowski, U., Behne, T., \& Tomasello, M. (2011). Early social cognition in three cultural contexts. \emph{Monographs of the Society for Research in Child Development}, \emph{76}(2), vii--viii, 1--142. \url{https://doi.org/10.1111/j.1540-5834.2011.00603.x}

\leavevmode\vadjust pre{\hypertarget{ref-chasiotis2006theory}{}}%
Chasiotis, A., Kiessling, F., Hofer, J., \& Campos, D. (2006). Theory of mind and inhibitory control in three cultures: {Conflict} inhibition predicts false belief understanding in {Germany}, {Costa Rica} and {Cameroon}. \emph{International Journal of Behavioral Development}, \emph{30}(3), 249--260. \url{https://doi.org/10.1177/0165025406066759}

\leavevmode\vadjust pre{\hypertarget{ref-delbianco2019developmental}{}}%
Del Bianco, T., Falck-Ytter, T., Thorup, E., \& Gredebäck, G. (2019). The {Developmental Origins} of {Gaze-Following} in {Human Infants}. \emph{Infancy}, \emph{24}(3), 433--454. \url{https://doi.org/10.1111/infa.12276}

\leavevmode\vadjust pre{\hypertarget{ref-elfenbein2002universality}{}}%
Elfenbein, H. A., \& Ambady, N. (2002). On the universality and cultural specificity of emotion recognition: {A} meta-analysis. \emph{Psychological Bulletin}, \emph{128}(2), 203--235. \url{https://doi.org/10.1037/0033-2909.128.2.203}

\leavevmode\vadjust pre{\hypertarget{ref-fujita2022theory}{}}%
Fujita, N., Devine, R. T., \& Hughes, C. (2022). Theory of mind and executive function in early childhood: {A} cross-cultural investigation. \emph{Cognitive Development}, \emph{61}, 101150. \url{https://doi.org/10.1016/j.cogdev.2021.101150}

\leavevmode\vadjust pre{\hypertarget{ref-glynn2016social}{}}%
Glynn, M. A., \& Watkiss, L. (2016). Social {Cognition}. In M. Augier \& D. J. Teece (Eds.), \emph{The {Palgrave Encyclopedia} of {Strategic Management}} (pp. 1--4). Palgrave Macmillan UK. \url{https://doi.org/10.1057/978-1-349-94848-2_614-1}

\leavevmode\vadjust pre{\hypertarget{ref-hajduk2020how}{}}%
Hajdúk, M., Achim, A. M., Brunet -- Gouet, E., Mehta, U. M., \& Pinkham, A. E. (2020). How to move forward in social cognition research? {Put} it into an international perspective. \emph{Schizophrenia Research}, \emph{215}, 463--464. \url{https://doi.org/10.1016/j.schres.2019.10.001}

\leavevmode\vadjust pre{\hypertarget{ref-henrich2010weirdesta}{}}%
Henrich, J., Heine, S. J., \& Norenzayan, A. (2010). The weirdest people in the world? \emph{The Behavioral and Brain Sciences}, \emph{33}(2-3), 61-83; discussion 83-135. \url{https://doi.org/10.1017/S0140525X0999152X}

\leavevmode\vadjust pre{\hypertarget{ref-hernik2019infant}{}}%
Hernik, M., \& Broesch, T. (2019). Infant gaze following depends on communicative signals: {An} eye-tracking study of 5- to 7-month-olds in {Vanuatu}. \emph{Developmental Science}, \emph{22}(4), e12779. \url{https://doi.org/10.1111/desc.12779}

\leavevmode\vadjust pre{\hypertarget{ref-hughes2014lost}{}}%
Hughes, C., Devine, R. T., Ensor, R., Koyasu, M., Mizokawa, A., \& Lecce, S. (2014). Lost in {Translation}? {Comparing British}, {Japanese}, and {Italian Children}'s {Theory-of-Mind Performance}. \emph{Child Development Research}, \emph{2014}, e893492. \url{https://doi.org/10.1155/2014/893492}

\leavevmode\vadjust pre{\hypertarget{ref-hughes2018does}{}}%
Hughes, C., Devine, R. T., \& Wang, Z. (2018). Does {Parental Mind-Mindedness Account} for {Cross-Cultural Differences} in {Preschoolers}' {Theory} of {Mind}? \emph{Child Development}, \emph{89}(4), 1296--1310. \url{https://doi.org/10.1111/cdev.12746}

\leavevmode\vadjust pre{\hypertarget{ref-jasso2006using}{}}%
Jasso, H., \& Triesch, J. (2006). Using eye direction cues for gaze following -- {A} developmental model. \emph{In}.

\leavevmode\vadjust pre{\hypertarget{ref-krys2024weirda}{}}%
Krys, K., De Almeida, I., Wasiel, A., \& Vignoles, V. L. (2024). {WEIRD}--{Confucian} comparisons: {Ongoing} cultural biases in psychology's evidence base and some recommendations for improving global representation. \emph{American Psychologist}. \url{https://doi.org/10.1037/amp0001298}

\leavevmode\vadjust pre{\hypertarget{ref-kusano2024mismeasure}{}}%
Kusano, K., Napier, J., \& Jost, J. (2024). \emph{The {Mismeasure} of {Culture}: {When Measurement Invariance Requirements Hinder Cross-Cultural Research} in {Psychology}}. OSF. \url{https://doi.org/10.31234/osf.io/9qe2k}

\leavevmode\vadjust pre{\hypertarget{ref-matsumoto2006new}{}}%
Matsumoto, D., \& Yoo, S. H. (2006). Toward a {New Generation} of {Cross-Cultural Research}. \emph{Perspectives on Psychological Science}, \emph{1}(3), 234--250. \url{https://doi.org/10.1111/j.1745-6916.2006.00014.x}

\leavevmode\vadjust pre{\hypertarget{ref-mehta2011validation}{}}%
Mehta, U. M., Thirthalli, J., Naveen Kumar, C., Mahadevaiah, M., Rao, K., Subbakrishna, D. K., Gangadhar, B. N., \& Keshavan, M. S. (2011). Validation of {Social Cognition Rating Tools} in {Indian Setting} ({SOCRATIS}): {A} new test-battery to assess social cognition. \emph{Asian Journal of Psychiatry}, \emph{4}(3), 203--209. \url{https://doi.org/10.1016/j.ajp.2011.05.014}

\leavevmode\vadjust pre{\hypertarget{ref-nielsen2017persistent}{}}%
Nielsen, M., Haun, D., Kärtner, J., \& Legare, C. H. (2017). The persistent sampling bias in developmental psychology: {A} call to action. \emph{Journal of Experimental Child Psychology}, \emph{162}, 31--38. \url{https://doi.org/10.1016/j.jecp.2017.04.017}

\leavevmode\vadjust pre{\hypertarget{ref-pena2007lost}{}}%
Peña, E. D. (2007). Lost in {Translation}: {Methodological Considerations} in {Cross-Cultural Research}. \emph{Child Development}, \emph{78}(4), 1255--1264. \url{https://www.jstor.org/stable/4620701}

\leavevmode\vadjust pre{\hypertarget{ref-prein2023tango}{}}%
Prein, J. C., Kalinke, S., Haun, D. B. M., \& Bohn, M. (2023). {TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults. \emph{Behavior Research Methods}. \url{https://doi.org/10.3758/s13428-023-02159-5}

\leavevmode\vadjust pre{\hypertarget{ref-prein2023variation}{}}%
Prein, J. C., Maurits, L., Werwach, A., Haun, D. B. M., \& Bohn, M. (2023). \emph{Variation in gaze understanding across the life span: {A} process-level perspective}. PsyArXiv. \url{https://doi.org/10.31234/osf.io/dy73a}

\leavevmode\vadjust pre{\hypertarget{ref-pronk2022methods}{}}%
Pronk, T., Molenaar, D., Wiers, R. W., \& Murre, J. (2022). Methods to split cognitive task data for estimating split-half reliability: {A} comprehensive review and systematic assessment. \emph{Psychonomic Bulletin \& Review}, \emph{29}(1), 44--54. \url{https://doi.org/10.3758/s13423-021-01948-3}

\leavevmode\vadjust pre{\hypertarget{ref-schilbach2013secondperson}{}}%
Schilbach, L., Timmermans, B., Reddy, V., Costall, A., Bente, G., Schlicht, T., \& Vogeley, K. (2013). Toward a second-person neuroscience. \emph{The Behavioral and Brain Sciences}, \emph{36}(4), 393--414. \url{https://doi.org/10.1017/S0140525X12000660}

\leavevmode\vadjust pre{\hypertarget{ref-selcuk2023development}{}}%
Selcuk, B., Gonultas, S., \& Ekerim-Akbulut, M. (2023). Development and use of theory of mind in social and cultural context. \emph{Child Development Perspectives}, \emph{17}(1), 39--45. \url{https://doi.org/10.1111/cdep.12473}

\leavevmode\vadjust pre{\hypertarget{ref-shepherd2010following}{}}%
Shepherd, S. (2010). Following {Gaze}: {Gaze-Following Behavior} as a {Window} into {Social Cognition}. \emph{Frontiers in Integrative Neuroscience}, \emph{4}(5). \url{https://doi.org/10.3389/fnint.2010.00005}

\leavevmode\vadjust pre{\hypertarget{ref-stengelin2020cultural}{}}%
Stengelin, R., Hepach, R., \& Haun, D. B. M. (2020). Cultural variation in young children's social motivation for peer collaboration and its relation to the ontogeny of {Theory} of {Mind}. \emph{PLOS ONE}, \emph{15}(11), e0242071. \url{https://doi.org/10.1371/journal.pone.0242071}

\leavevmode\vadjust pre{\hypertarget{ref-tang2024slow}{}}%
Tang, Y., Gonzalez, M. R., \& Deák, G. O. (2024). The slow emergence of gaze- and point-following: {A} longitudinal study of infants from 4 to 12 months. \emph{Developmental Science}, \emph{27}(3), e13457. \url{https://doi.org/10.1111/desc.13457}

\leavevmode\vadjust pre{\hypertarget{ref-taumoepeau2019crosscultural}{}}%
Taumoepeau, M., Sadeghi, S., \& Nobilo, A. (2019). Cross-cultural differences in children's theory of mind in {Iran} and {New Zealand}: {The} role of caregiver mental state talk. \emph{Cognitive Development}, \emph{51}, 32--45. \url{https://doi.org/10.1016/j.cogdev.2019.05.004}

\leavevmode\vadjust pre{\hypertarget{ref-tomasello2007reliance}{}}%
Tomasello, M., Hare, B., Lehmann, H., \& Call, J. (2007). Reliance on head versus eyes in the gaze following of great apes and human infants: The cooperative eye hypothesis. \emph{Journal of Human Evolution}, \emph{52}(3), 314--320. \url{https://doi.org/10.1016/j.jhevol.2006.10.001}

\end{CSLReferences}

\endgroup

\end{document}

### 2024-04-15 stats/analysis.Rmd
create rough first draft

@@
 ```{r load_data}
-complete_data <- read_csv("../data/data.csv") %>% 
-  mutate(age_group = floor(ageinyears))
+complete_data <- read_csv("../data/data.csv")
 ```
@@
 all_trials <- complete_data %>% 
-    mutate(continent = ifelse(
-    community %in% c("leipzig", "plymouth"), "Europe", 
-    ifelse(
-      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
-      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "Americas",
-             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
-    )
-  )) %>%
-  mutate(continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T)) %>%
-  mutate(community = recode(community,
+    mutate(
+      continent = case_when(community %in% c("leipzig", "plymouth") ~ "Europe", 
+                            community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda") ~ "Africa",
+                            community %in% c("stanford", "mexico", "buenos_aires") ~ "Americas",
+                            community %in% c("india", "beijing", "turkey") ~ "Asia", 
+                            community == "auckland" ~ "Oceania"), 
+      continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T), 
+      community = recode(community,
                             akure = "Akure (Nigeria)",
@@
                             bayaka = "BaYaka (Rep. Congo)", 
-                            uganda = "Nyabyeya (Uganda)")
-  ) %>% 
-  mutate(
+                            uganda = "Nyabyeya (Uganda)"), 
       imprecision = abs(clickdistfromtargetcenterx)/160,
-    centrality = as.character(abs(5-targetposition))
+      centrality = as.character(abs(5-targetposition)), 
+      age_group = floor(ageinyears)
   )
@@
 ```{r sample}
+range(all_trials$ageinyears)
+
 # full sample
@@
 ```{r model_density}
-age_model <- brm(mean_imprecision ~ age + (1 | subjid),
-                data   = mdata,
-                family = lognormal(),
-                warmup = 2000,
-                iter   = 6000,
-                control = list(adapt_delta = 0.95),
-                chains = 4,
-                cores  = 4)
+# age_model <- brm(mean_imprecision ~ age + (1 | subjid),
+#                 data   = mdata,
+#                 family = lognormal(),
+#                 warmup = 2000,
+#                 iter   = 6000,
+#                 control = list(adapt_delta = 0.95),
+#                 chains = 4,
+#                 cores  = 4)
 
-age_model
+# saveRDS(age_model, "../saves/age_model.rds")
+
+age_model <- readRDS("../saves/age_model.rds")
 
@@
 density_plot
+saveRDS(density_plot, "../saves/density_plot.rds")
 ```
@@
     # so that first facet row doesnt show x axis labels
-    trialtype = if_else(community %in% c("Leipzig (Germany)", "Malatya (Türkiye)", "Nyabyeya (Uganda)", "Ocuilan (Mexico)", "Plymouth (UK)", "Pune (India)", "Stanford (USA)", "Windhoek (Namibia)"),
+    trialtype = if_else(community %in% c("Ocuilan (Mexico)", "Plymouth (UK)", "Pune (India)", "Stanford (USA)", "Windhoek (Namibia)"),
                               as.character(trialtype),
@@
   scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
-  facet_wrap(~ community, nrow = 2, scales="free_x") +
+  facet_wrap(~ community, nrow = 3, scales="free_x") +
   theme(
     axis.text.x = element_text(angle = 30, hjust = 1), 
-    legend.position = c(0.96, 0.25), 
+    legend.position = c(0.93, 0.14), 
     axis.ticks.x = element_blank(),
-    strip.text.x = element_text(size = 7.5), 
-    legend.title = element_text(size = 8),
+    strip.text.x = element_text(size = 10), 
+    legend.title = element_text(size = 10),
   ) +
@@
 training_trials_plot
+saveRDS(training_trials_plot, "../saves/training_trials_plot.rds")
 ```
@@
   scale_size(limits = c(20, 160), breaks = seq(25, 150, 50)) + 
-  labs(y = "", x = "Odd-even split") +
+  labs(x = expression(paste("Pearson's ", italic("r"))), y = "", title = "Odd-even split") +
   theme(
     legend.position = c(0.2, 0.2),
-    strip.text = element_text(face = "bold", size = 10), 
     legend.title = element_text(size = 8),
@@
     legend.key.width = unit(-1.2, "cm"),
+    title = element_text(size = 8),
+    axis.title.x = element_text(size = 8)
   ) +
@@
 odd_even_plot
+saveRDS(odd_even_plot, "../saves/odd_even_plot.rds")
 ```
@@
   scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
-  labs(y = "", x = "Stratified by target centrality") +
-  theme(axis.title.x = element_text(size = 10)) +
+  labs(x = expression(paste("Pearson's ", italic("r"))), y = "", title = "Stratified by target centrality") +
+  theme(axis.title.x = element_text(size = 8), title = element_text(size = 8),) +
   expand_limits(y = c(1, 18.5))
@@
 stratified_plot
+saveRDS(stratified_plot, "../saves/stratified_plot.rds")
 ```
@@
   scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
-  labs(y = "", x = "Stratified & age-corrected") +
-  theme(axis.title.x = element_text(size = 10)) +
+    labs(x = expression(paste("Pearson's ", italic("r"))), y = "", title = "Stratified, age-corrected") +
+  theme(axis.title.x = element_text(size = 8), title = element_text(size = 8)) +
   expand_limits(y = c(1, 18.5))
@@
 stratified_agecorrected_plot
+saveRDS(stratified_agecorrected_plot, "../saves/stratified_agecorrected_plot.rds")
 ```
@@
 ```{r combine_plot}
+# density_plot <- readRDS("../saves/density_plot.rds")
+# odd_even_plot <- readRDS("../saves/odd_even_plot.rds")
+# stratified_plot <- readRDS("../saves/stratified_plot.rds")
+# stratified_agecorrected_plot <- readRDS("../saves/stratified_agecorrected_plot.rds")
+# training_trials_plot <- readRDS("../saves/training_trials_plot.rds")
+
 top_row <- ggarrange(
@@
   nrow = 1,
-  labels = c("B", "C", "D", "E") 
+  labels = c("B", "C", "", "") 
 )
@@
   nrow = 2,
-  heights = c(2.2, 1.4),
+  heights = c(2.9, 1.4),
   labels = c("A", "") 
@@
 
-ggsave("../figures/tango-cc.png", width = 12, height = 8, scale = 1, bg = "white")
+ggsave("../figures/tango-cc-results.png", width = 12, height = 12, scale = 1, bg = "white")
 ```

### 2024-05-08 paper/manuscript.Rmd
incorporate Manuel's feedback; adjust intro; add trial type model

--- 2023-10-27 paper/manuscript.Rmd
@@
 ---
-title: "TANGO-CC: An open-source website for researchers to build a culture-sensitive task of gaze understanding"
-shorttitle: "measuring gaze understanding across the globe"
+title: "Measuring variation in gaze following across communities, ages, and individuals — a showcase of the TANGO--CC"
+shorttitle: "measuring gaze following across communities"
+
 author: 
-
-  - name          : "Julia Christin Prein"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
-    email         : "julia_prein@eva.mpg.de"
-    role          :
-      - Conceptualization
-      - Methodology
-      - Software
-      - Investigation
-      - Formal Analysis
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-
-  - name          : "Daniel B. M. Haun"
-    affiliation   : "1"
-    role          :
-      - Supervision
-      - Writing - Review & Editing
-
-  - name          : "Manuel Bohn"
+  - name          : "Julia Prein (ORCID: 0000-0002-3154-6167)"
     affiliation   : "1,2"
-    role          :
-      - Conceptualization
-      - Writing - Review & Editing
+    corresponding : yes
+    address       : "Universitätsallee 1, 21335 Lüneburg, Germany"
+    email         : "manuel.bohn@leuphana.de"
+    role:
+      - "Conceptualization"
+      - "Methodology"
+      - "Software"
+      - "Investigation"
+      - "Writing - Original Draft Preparation"
+      - "Writing - Review & Editing"
+  - name          : "Florian M. Bednarski (ORCID: 0000-0003-4384-4791)"
+    affiliation   : "4"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Ardain Dzabatou"
+    affiliation   : "5"
+    role:
+      - "Investigation"
+  - name          : "Michael C. Frank (ORCID: 0000-0002-7551-4378)"
+    affiliation   : "6"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"
+  - name          : "Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)"
+    affiliation   : "4"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"      
+  - name          : "Josefine Kalbitz"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"
+  - name          : "Patricia Kanngiesser (ORCID:0000-0003-1068-3725)"
+    affiliation   : "7"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)"
+    affiliation   : "8"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Bahar Köymen (ORCID: 0000-0001-5126-8240)"
+    affiliation   : "9"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"  
+  - name          : "Maira V. Manrique-Hernandez"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+  - name          : "Shirley Magazi (ORCID: 0009-0006-0479-9800)"
+    affiliation   : "10"
+    role:
+      - "Investigation"
+  - name          : "Lizbeth Mújica-Manrique"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Julia Ohlendorf"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+  - name          : "Damilola Olaoba"
+    affiliation   : "2"
+    role:
+     - "Investigation"
+  - name          : "Wesley R. Pieters (ORCID:0000-0002-6152-249X)"
+    affiliation   : "10"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Sarah Pope-Caldwell"
+    affiliation   : "2"
+    role:
+     - "Investigation"
+  - name          : "Roman Stengelin (ORCID: 0000-0003-2212-4613)"
+    affiliation   : "2,10"
+    role:
+      - "Conceptualization"
+      - "Methodology"
+      - "Investigation"
+      - "Writing - Review & Editing"     
+  - name          : "Katie Slocombe (ORCID: 0000-0002-7310-1887)"
+    affiliation   : "11"
+    role:
+     - "Investigation"
+     - "Writing - Review & Editing"
+  - name          : "Robert Z. Sparks (ORCID: 0000-0001-7545-0522)"
+    affiliation   : "6"
+    role:
+      - "Investigation"
+  - name          : "Jahnavi Sunderarajan"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+  - name          : "Florence Tusiime"
+    affiliation   : "3"
+    role:
+      - "Investigation"
+  - name          : "Wilson Vieira (ORCID: 0009-0001-9400-6328)"
+    affiliation   : "2"
+    role:
+     - "Investigation"
+  - name          : "Zhen Zhang (ORCID: 0000-0001-9300-0920)"
+    affiliation   : "12"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"   
+  - name          : "Yufei Zong (ORCID: 0009-0000-5012-0244)"
+    affiliation   : "12"
+    role:
+      - "Investigation"
+  - name          : "Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)"
+    affiliation   : "2,+"
+    role:
+      - "Conceptualization"
+      - "Funding acquisition"
+      - "Writing - Review & Editing"
+  - name          : "Manuel Bohn (ORCID: 0000-0001-6006-1348)"
+    affiliation   : "1,2,+"
+    role:
+      - "Conceptualization"
+      - "Methodology"
+      - "Writing - Review & Editing"
 
@@
   - id            : "1"
-    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
+    institution   : "Institute of Psychology in Education, Leuphana University Lüneburg"
   - id            : "2"
-    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"
+    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
+  - id            : "3"
+    institution   : "Budongo Conservation Field Station"
+  - id            : "4"
+    institution   : "School of Psychology, University of Auckland"
+  - id            : "5"
+    institution   : "Université Marien Ngouabi"
+  - id            : "6"
+    institution   : "Department of Psychology, Stanford University"
+  - id            : "7"
+    institution   : "School of Psychology, University of Plymouth"
+  - id            : "8"
+    institution   : "Department of Psychology, Koç University"
+  - id            : "9"
+    institution   : "Division of Psychology, Communication, and Human Neuroscience, University of Manchester"
+  - id            : "10"
+    institution   : "Department of Psychology and Social Work, University of Namibia"
+  - id            : "11"
+    institution   : "Department of Psychology, University of York"
+  - id            : "12"
+    institution   : "CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences"
+  - id            : "+"
+    institution   : "joint last author"
+
 abstract: | 
+            Cross-cultural studies are crucial for investigating the universality and robustness of cognitive developmental processes.
+Yet, suitable methods to measure variability in cognition across languages and communities are lacking.
+This paper describes the TANGO--CC (Task for Assessing Individual Differences in Gaze Understanding -- Cross-Cultural), a gaze following task designed to measure basic social cognition across individuals, ages, and communities.
+The TANGO--CC was developed and psychometrically assessed in one setting and subsequently adapted for cross-cultural data collection.
+Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community.
+The TANGO--CC captured individual differences and showed good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities.
+Within-community variation outweighed between-community variation.
+We provide an open-source website for researchers to customize and use the task.
+The TANGO--CC represents a valuable contribution to assessing basic social cognition in diverse communities, establishing a roadmap for researching cross-cultural individual differences.
 
-keywords          : "cross-cultural psychology, social-cognitive development, gaze following, individual differences, reliability"
+keywords          : "cross-cultural psychology, social cognition, gaze following, individual differences, reliability"
 wordcount         : "XXX"
@@
 # Introduction
-- increased interest in cc research but not many new methods that enable or ease cross cultural research
-- hard to capture ind diff, even harder in cc settings
-- goal: comparable data across cultural settings
-- approach 1: standardized procedure, as similar as possible. taken here
-- approach 2: see in each cultural setting how to translate the psychological construct into experiment
-- prein2023tango: works for ind diff. reliable. 
-- supplements prein2023variation: differences between animal & human faces
 
-# Methods
-- testing setups: rural & urban
-- no prior touchscreen experience needed
-- how does website work: which variables you can select
-- output from website
-- shiny app?!
-- psychometric properties of tango germany
-- describe cc sample
+For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) backgrounds [@henrich2010weirdesta; @lillard1998ethnopsychologies].
+Despite numerous calls for change, the subject pools reported in high-impact journals still lack diversity [@nielsen2017persistent; @gutchess2023considerationa].
+This lack of representation hinders progress in theory building: inferences about the unique characteristics of human behavior and "human nature" cannot be drawn from humans from only one community [@krys2024weirda].
 
-# Results
-- splithalf per cultural setting
-- effect of age distribution, different for each cultural setting
-- in plot: weigh sample size: x: splithalf, y: culture, size geom count: sample size
-- visualize ind diff
-- plot training trials argument for children understand to touch balloon
-- response time?
-- droup outs across cultures
+To do justice to the diversity in experiences, we must study cognition and its development in diverse communities and even across families and individuals [@selcuk2023development; @gutchess2023considerationa].
+So why are not more social-cognitive studies focusing on the variation between individuals living in diverse communities?
+A potential reason for the under-representation of these studies may be the scarcity of suitable tasks [@bourdage2023evaluation].
+
+Studies investigating variation between communities and/or individuals need to ensure that the captured variation is systematic and not just random noise.
+This requires measurement reliability and validity.
+Yet, social cognition studies based on US-American and European samples rarely report psychometric information [for a review, see @beaudoin2020systematic].
+This picture further deteriorates when we pay attention to the reliability and validity of cross-cultural social cognition tasks [@hajduk2020how; @bourdage2023evaluation; @waschl2022crosscultural].
+It remains challenging to find reliable and valid tasks that can capture individual differences within one community, let alone tasks that do so across different communities.
+
+Adapting tasks to diverse communities and re-assessing their validity and reliability might be especially important in the social-cognitive domain.
+If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, the tasks need to represent different communities.
+Indeed, task performance can be diminished when stimuli are not adjusted [@pena2007lost].
+For example, @elfenbein2002universality found better emotion recognition for members of the same national, ethnic, or regional group.
+@selcuk2023development concluded that children often attribute mental states more accurately and more frequently to individuals from the same community.
+This underlines the importance of adapting tasks to each specific cultural context.
+
+Broadly speaking, there are two different approaches that researchers can take to collect cross-cultural data.
+One approach would be to translate the psychological construct into an individually designed study for each community (termed "assembly"; @he2012bias, @waschl2022crosscultural).
+While this approach is most flexible and sensitive to cultural differences, it might be most feasible for studying up to a handful of communities as it becomes too demanding and time-consuming.
+Most importantly, this approach assumes that the measured underlying concept is the same, while absolute task scores are not comparable across the communities.
+Another approach would be to use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of culturally inappropriate stimuli (termed "adoption" and "adaptation", respectively; @he2012bias, @waschl2022crosscultural).
+This approach is less sensitive to each community's unique characteristics but allows for a direct comparison of the data across communities.
+Examples following this approach include @callaghan2011early, @taumoepeau2019crosscultural, @hughes2018does, @hughes2014lost, @fujita2022theory, @mehta2011validation, @stengelin2020cultural, and @chasiotis2006theory.
+The present paper aims to describe the development and psychometric properties of a standardized task that can be adapted to diverse communities.
+
+The task presented here focuses on gaze following, that is, the ability to identify the attentional focus of another agent.
+Gaze following develops early in infancy [@delbianco2019developmental; @tang2024slow] and contributes to social learning, communication, and collaboration [@shepherd2010following; @tomasello2007reliance; @bohn2018common; @hernik2019infant].
+While gaze following is one of the most fundamental social-cognitive abilities, studies focusing on cultural variations are rare.
+The few existing results are mixed on whether gaze following is influenced by cultural factors or not [@hernik2019infant; @callaghan2011early].
+
+The task presented here builds upon the TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open) by @prein2023tango.
+The TANGO measures participants' imprecision in locating an agent's attentional focus.
+It has been shown to reliably capture individual differences in a German child sample and an English-speaking remote adult sample.
+The task was sensitive to developmental changes and linked to children's receptive vocabulary.
+Furthermore, an exploratory analysis showed that children performed equally well in a task version with animal faces compared to cartoon human faces [@prein2024variation].
+This suggests that superficial variations in the stimulus design do not influence children's performance in the task.
+
+This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that can be -- and has been -- adapted to several languages and communities.
+We describe the task's development and provide a tutorial for the open-source website (<https://ccp-odc.eva.mpg.de/TANGO--CC/>).
+We assess its cross-cultural applicability based on data from a large cross-cultural sample of 2.5- to 11-year-olds from 17 different urban/rural communities across the world and discuss the task's psychometrics.
+The task and all its adaptations have been initially designed for a paper by @bohn2024universal, and we re-use the data set in this paper.
+
+# Task development
+
+## Approach
+
+In a perfect world, developing a cross-cultural task would include international collaboration and diverse samples from the beginning, already during study design, piloting and item selection.
+As this seems hardly feasible, we present an alternative, pragmatic approach.
+First, the task was implemented in one context, in our case with a German sample [@prein2023tango].
+In this context, the task's reliability and validity were assessed in detail.
+Even though this does not guarantee that the task will be valid and reliable in another context, it substantially increases the likelihood.
+Second, we reassessed the TANGO--CC's measurement quality (i.e., variability and reliability) across diverse communities by analyzing the data from @bohn2024universal, who used the task to collect data in 17 communities.
+Therefore, our procedure maintains a balance between a detailed analysis of the task's psychometric properties and a swift and feasible task adaptation.
+In the following, we describe the different steps in further detail.
+We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful for other researchers.
+
+In the first step, the task's underlying structure was designed.
+The TANGO--CC measures the precision with which participants locate an agent’s attentional focus.
+The participant's task is to locate a target by following the agent's gaze (see Figure \@ref(fig:fig1)).
+Precision was measured in a continuous way as the distance between the participant's click on the screen and the target position.
+The task's core functionality is to animate the agent's eyes so that they follow the target's movement.
+This basic structure was then embedded in the task's superficial appearance (e.g., background scene) and audio instructions.
+Once this structure was implemented, adaptations of the task were greatly simplified.
+For example, we can change the background scene, the faces of the agent, and the target without changing how and what the task measures.
+
+This basic version of the TANGO was psychometrically evaluated in a prototypical WEIRD sample (German child sample; English-speaking remote adult sample) and was found to be highly reliable and valid [@prein2023tango].
+While participants got more and more precise in locating the attentional focus of the agent the older they were, individuals differed across all age groups and showed no floor- or ceiling effects.
+Performance in the TANGO was linked to children's receptive vocabulary and weakly related to factors of children's daily social environment.
+In another study, @prein2024variation proposed a computational cognitive model that described gaze following as a social form of vector following.
+Gaze following, as measured by the TANGO, was related to children's non-social vector following and visual perspective-taking abilities.
+These connections to related constructs indicate the task's validity in the tested WEIRD setting.
+
+To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces that were judged by researchers and research assistants from each target community to be representative of the local population (see Figure \@ref(fig:fig1)).
+Similarly, different backgrounds were created that roughly represented a typical accommodation in each community.
+Audio instructions were translated into the corresponding local language.
+By back-translating these instructions, we ensured the original meaning did not change.
+Sometimes, specific words were linguistically slightly modified, although functionally equivalent (e.g., "bush" instead of "hedge"), to ensure that all participants understood the instructions.
+In the following, we describe how researchers can use and customize the TANGO--CC in more detail.
+
+## Features of the TANGO--CC
+
+### Trials
+
+We quickly recap the TANGO's [@prein2023tango] most characteristic features: Participants are asked to locate a balloon with the help of a gaze cue.
+The task consists of three different trial types (see Figure \@ref(fig:fig1)).
+In every trial, participants see an agent (boy or girl) looking out of a house with a balloon (red, blue, green, or yellow) in front of them.
+The balloon falls down to the ground, while the eyes of the agent follow the movement of the balloon in a way that their centers always align.
+Depending on the trial type, participants have different visual access to the balloon's position.
+In training 1, participants see the full trajectory of the balloon and directly have to touch the balloon itself.
+In training 2, participants see most of the balloon's movement, but a hedge covers the final location.
+In test trials, a hedge grows at the beginning of the trial and participants see neither the movement nor the final position of the balloon.
+The first trial of each type contains an audio description of the presented events (see supplements of @bohn2024universal).
+Notably, the instructions explicitly state that the agent is looking at the balloon.
+
+The outcome variable is the distance between the participant's touch and the balloon's center.
+Trials can be completed quickly and efficiently so that children can easily complete 15 trials within 10 minutes.
+This drastically reduces drop-out rates.
+By using essentially self-explanatory animations, language demands are kept to a minimum.
+No differential feedback is given to keep trials comparable and avoid learning effects.
+
+### Randomization
+
+The order of the agents, balloon colors (red, yellow, green, blue), and balloon positions are each randomized independently.
+For the balloon positions, the entire width of the screen (1920 in "SVG units") is divided into ten bins.
+Exact coordinates (value between 0 far left and 1920 far right) within each bin are then randomly generated.
+The number of repetitions for each agent, balloon color, and balloon bin is calculated based on the total number of trials and the number of unique agents, balloon colors, and bins, respectively.
+All agents, balloon colors, and bins appear equally often and are not repeated in more than two consecutive trials.
+If the total number of trials is not divisible by the number of unique elements, additional elements are randomly selected to make up for the remainder.
+
+### Cross-cultural customization
+
+The TANGO--CC can be accessed via the following link: (<https://ccp-odc.eva.mpg.de/TANGO--CC/>).
+In the first step, researchers can select the language for audio instructions, currently available for 13 different languages and even more dialects (see Table 1).
+All written instructions are presented in English because they are not directed to the participant but to the research assistant who guides the participant through the task.
+The task can either be started with the default settings or further customized.
+The default settings use the version applied in @bohn2024universal based on the selected language.
+
+If researchers choose to customize the task (see Figure \@ref(fig:fig1)), the number of trials can be chosen for each trial type.
+As the trial types build up on each other, each trial type is necessary to understand the structure of the task and needs to be completed before the next trial type starts.
+Therefore, no trial type can be skipped.
+The minimum number of trials per type is 1; the maximum is 100.
+One out of four different backgrounds can be selected.
+Finally, there are 50 diverse human faces (50% female, 50% male) from which researchers can choose.
+No constraint exists on how many faces are allowed (min 1, max 50).
+Once all the settings are adjusted, the customized task is compiled.
+
+In the last step, researchers can enter an alphanumeric participant identifier (1 - 8 characters) and enable a webcam recording of the participant, if needed.
+To save the selected settings, researchers can bookmark the URL so that the customized task can be easily accessed, and only the participant ID and choice of webcam recording need to be entered again.
+The task can then be started.
+
+The source code of the task is available on GitHub (<https://github.com/ccp-eva/TANGO--CC>).
+By directly editing the `HTML` and `JavaScript` code, researchers gain even more flexibility in adjusting the task to their needs.
+
+```{r langtab}
+lang <- tibble(
+            Languages = c(
+              "Bemba", 
+              "Chinese",
+              "English", 
+              "German", 
+              "Hai||om", 
+              "Khewdam",
+              "Lingala",
+              "Marathi",
+              "Shona",
+              "Spanish",
+              "Swahili",
+              "Turkish", 
+              "Yaka"
+            ), 
+            `Language family` = c(
+              "Bantu",
+              "Sino-Tibetan",
+              "Indo-European",
+              "Indo-European",
+              "Khoesan",
+              "Khoesan",
+              "Bantu",
+              "Indo-European",
+              "Bantu",
+              "Indo-European",
+              "Bantu",
+              "Turkic",
+              "Bantu"
+            ), 
+            `Speaker's country of origin` = c(
+              "Zambia", 
+              "China", 
+              "USA / UK / India / Nigeria / New Zealand", 
+              "Germany", 
+              "Namibia", 
+              "Namibia", 
+              "Rep. Congo", 
+              "India", 
+              "Zimbabwe", 
+              "Argentina / Mexico", 
+              "Uganda", 
+              "Türkiye", 
+              "Rep. Congo"
+            ), 
+          )
+
+apa_table(
+  lang,
+  caption = "Languages available for the audio instructions in the TANGO--CC"
+)
+```
+
+(ref:figlab1) **Customizable components of the TANGO--CC.** Researchers can select the language of the audio instructions, the number of trials per trial type, the background, and the agent's face.
+Screenshots of the trials show the proceeding events: In training 1, an agent looks at a balloon that falls to the ground, and participants have to respond by touching the balloon.
+In training 2, the balloon falls behind the hedge while its flight is still visible.
+Participants respond by touching the hedge where they think the balloon is.
+In test trials, the balloon's movement and final position are covered by a hedge, and participants respond by touching the hedge.
+In the task, all movements are smoothly animated (no still pictures).
+Yellow frames indicate the time point when participants respond (only illustrative, not shown during the task).
+
+```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
+knitr::include_graphics("../figures/TANGO-CC-procedure.png")
+```
+
+### Task implementation
+
+The task was implemented in `JavaScript`, `HTML`, and `CSS` and is presented as a web app.
+It can be accessed on any web browser and does not require prior installation.
+The online version of the task has been proven convenient for unsupervised data collection (for example, using participant recruitment services like *Prolific*; see @prein2023tango) and sharing the task internationally.
+Importantly, the web app implementation does not necessarily need a working WIFI connection: An offline, local version of the task can be quickly set up for devices that support Node.js (<https://nodejs.org/en>).
+This is an especially useful feature for researchers working in remote areas with limited internet access.
+
+The stimuli are embedded as Scalable Vector Graphics (SVG).
+The setup allows for an easy adaptation of task elements and ensures that picture quality, aspect ratio, and relative object positioning are constant.
+The task is programmed so that responses are only registered when the participant touches the relevant part of the screen (i.e., in test trials, the hedge).
+Furthermore, clicks are only registered after the voice recordings stop playing.
+An audio reminder is played again if no click is registered within 5 seconds.
+
+The website does not use cookies, nor does it upload any data to servers; that is, the data is only stored locally on the device.
+The output of the task is a CSV file (and WEBM file if a webcam recording was selected) that contains the participants' responses and can be easily imported into statistical software for further analysis.
+The file will be stored in the device's downloads folder and is named after the following pattern: "tangoCC-participantID-YYYY-MM-DD_hh_mm_ss".
+
+# Psychometric evaluation
+
+```{r sample_table}
+sample_table <- readRDS("../saves/sample_table.rds")
+```
+
+## Data set
+
+We used the data set from @bohn2024universal for the psychometric evaluation of the TANGO--CC.
+They collected data using the TANGO--CC in a sample of *N* = `r sample_table[sample_table$Community == "Total",]$Total` children between 2.5 to 11 years of age.
+Participants came from 17 communities on five continents, in rural and urban settings, with varying degrees of market integration and technology exposure.
+@bohn2024universal carried out 19 trials (1 training 1, 2 training 2, and 16 test trials, of which the first of each type had audio instructions).
+Faces, backgrounds, and languages were chosen by researchers and assistants with experience in the specific community.
+For further details on the communities and data collection procedures, see the supplements of @bohn2024universal.
+
+## Individual differences
+
+(ref:figlab2) **Measurement of the TANGO--CC by community.** (A) Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type.
+Imprecision is defined as the distance between the participant's touch and the balloon's center in units of balloon width.
+For a depiction of each trial's procedure, see Figure \@ref(fig:fig1).
+(B) Internal consistency estimates by community, following three different approaches.
+In the odd-even split, the size of points reflects the sample size in each community.
+In the stratified approach with and without age correction, density curves show the posterior distributions of the GLMM.
+
+```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
+knitr::include_graphics("../figures/TANGO-CC-results.png")
+```
+
+```{r read_results}
+var_df <- readRDS("../saves/var_df.rds")
+within_person <- readRDS("../saves/within_person.rds")
+sd_int_cor <- readRDS("../saves/sd_int_cor.rds")
+descr_trialtypes <- readRDS("../saves/descr_trialtypes.rds")
+int_con <- readRDS("../saves/internal_consistency.rds")
+mtrialtypes <- readRDS("../saves/mtrialtypes.rds")
+trialtypes_est <- readRDS("../saves/trialtypes_est")
+
+int_con_wo_uk <- int_con %>% filter(community != "Plymouth (UK)") %>% summarise(min = min(stratified_agecorrected))
+```
+
+As a first feasibility check, we inspected the mean and standard deviations by community and compared performance in each trial type (training 1, training 2, test trials).
+Performance was defined as the absolute click distance between the target center and the click x coordinate, scaled according to balloon widths.
+Across communities, children performed best in training 1 (mean = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 1",]$mean_click`, sd = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 1",]$sd_click`), followed by training 2 (mean = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 2",]$mean_click`, sd = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 2",]$sd_click`) and test trials (mean = `r descr_trialtypes[descr_trialtypes$trialtype== "Test",]$mean_click`, sd = `r descr_trialtypes[descr_trialtypes$trialtype== "Test",]$sd_click`; see Figure \@ref(fig:fig2)A).
+
+To formally estimate the effect of trial type on performance in the TANGO--CC, we fit a generalized linear mixed model (GLMM) predicting the task performance by trial type (reference category: test trials).
+All analyses were run in `r R.version$version.string` [@rcoreteam2024language].
+GLMMs were fit with default priors using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].
+The model included random effects for trial type by community (model notation in `R: imprecision ~ trialtype + (trialtype | community)`), and imprecision was modeled by a `lognormal` distribution.
+We inspected the posterior distribution (mean and 95% Credible Interval (CrI)) for the trial type estimates.
+
+Our GLMM analysis supported the visual inspection of the data: the estimates for training 1 ($\beta$ = `r fixef(mtrialtypes)["trialtypeTraining1", "Estimate"]`; 95% CrI [`r fixef(mtrialtypes)["trialtypeTraining1", "Q2.5"]`; `r fixef(mtrialtypes)["trialtypeTraining1", "Q97.5"]`]) and training 2 ($\beta$ = `r fixef(mtrialtypes)["trialtypeTraining2", "Estimate"]`; 95% CrI [`r fixef(mtrialtypes)["trialtypeTraining2", "Q2.5"]`; `r fixef(mtrialtypes)["trialtypeTraining2", "Q97.5"]`]) were negative and reliably different from zero.
+Please note that the TANGO--CC measures imprecision in gaze following.
+Therefore, a negative sign shows that children showed less imprecision (i.e., were more precise) in the training trials than in the test trials.
+This effect was found across all communities (minimum estimate for training 1 = `r max(trialtypes_est$Training1)`; minimum estimate for training 2 = `r max(trialtypes_est$Training2)`).
+The almost perfect performance in training trials indicated that children understood the task and were able to locate the balloon.
+In test trials, children's imprecision was higher, indicating that the task was more challenging.
+All communities showed great individual variation and overlapped in their imprecision levels (see Figure \@ref(fig:fig2)A).
+
+To identify the sources of variation, we computed intraclass correlations (ICC).
+The variation of children within communities was substantially larger than the variation between the communities.
+The mean within-community variance was `r mean(var_df$within_community_var)`, ranging from `r min(var_df$within_community_var)` (in Pune, India) to `r max(var_df$within_community_var)` (in Chimfunshi, Zambia).
+Between-community variance was `r var_df$between_community_var[1]`.
+The ICC, representing the proportion of between-community variance relative to the total variance (sum of within- and between-community variance), was `r var_df$ICC_b[1]`.
+This indicates that only `r var_df$ICC_b[1] * 100`% of the total variability in the data can be attributed to differences between communities, while the remaining `r (1 - var_df$ICC_b[1]) * 100`% are attributed to differences within communities [@kusano2024mismeasure].
+
+## Reliability
+
+To assess reliability, we estimated internal consistency in each community in three different ways.
+First, data of each participant was split into odd and even trials and a Pearson correlation was calculated between the aggregated scores of the two halves.
+Second, using the function `by_split` from the `splithalfr` package [@pronk2022methods], data was stratified by target centrality (capturing trial difficulty), and a Pearson correlation was calculated between the matched halves.
+Third, a data set was generated with stratified test halves by target centrality.
+Then, we followed the Generalized Linear Mixed Model (GLMM) approach introduced by @rouder2019psychometrics.
+A GLMM was fitted with the mean imprecision as the outcome, age as the predictor, and test half and participant id as random effects (model notation: `imprecision ~ age + (0 + half | subjid)`).
+The model estimates correlations between participant-specific estimates for each test half.
+The hierarchical shrinkage of the model enables accurate person-specific estimates.
+By incorporating age as a fixed effect, the correlation between the two person-specific estimates represents the age-independent estimate for internal consistency.
+This eliminates the chance that a good internal consistency estimate results from general cognitive development rather than task-specific inter-individual differences.
+Because the process of generating stratified data sets is partly random, the model was fit 50 times for each community.
+The posterior estimate of the correlation between the two person-specific estimates was taken as the age-independent estimate for internal consistency.
+
+The results are shown in Figure \@ref(fig:fig2)C. 
+Across communities, internal consistency estimates ranged from `r min(int_con$odd_even)` to `r max(int_con$odd_even)` for the odd-even split, `r min(int_con$stratified)` to `r max(int_con$stratified)` for the stratified internal consistency, and `r int_con_wo_uk$min` to `r max(int_con$stratified_agecorrected)` for the age-corrected approach (Plymouth, UK, being an outlier with `r int_con$stratified_agecorrected[int_con$community == "Plymouth (UK)"]`).
+Following Cohen's suggestions [@cohen1988statistical; @cohen1992power], these correlations constitute large effects (*r* >.50), and indicated good internal consistency.[^1] 
+The results are comparable to the internal consistency estimates found in the original TANGO study [@prein2023tango], and also resemble reliability estimates of classical false belief tasks [@hughes2000good].
+
+[^1]: Note that for scale reliability and Cronbach's $\alpha$, values of .7 to .8 have been suggested to be acceptable [@kline1999handbook; @field2012discovering].
+However, @kline1999handbook suggested that values below .7 could be realistic for psychological constructs due to their variable nature.
+
+In an exploratory analysis, we found that communities with larger individual variation showed higher internal consistency estimates (Pearson's *r* = `r sd_int_cor$r`, 95%CI [`r sd_int_cor$lower`; `r sd_int_cor$upper`]).
+Please note that this could be influenced by outliers and that the sample size here (*N* = 17 communities) is too small to make substantial claims.
 
 # Discussion
-- flexibility for researchers
-- adjust to each cultural setting: faces, languages, background scene
-- easy to add new layers to svg to adjust even further
-- minimal language demands
-- worked across 16(?) different communities already
+
+The TANGO--CC measures imprecision in gaze following across individuals, ages, and communities.
+The task was developed in two phases.
+First, the task's underlying functionality was designed in one community.
+Next, we adapted the superficial features of the task to be used in 17 diverse communities and assessed the task's psychometric properties.
+Children’s imprecision in gaze following highly overlapped between communities: children performed similarly in the communities depending on the trial type, and within-community variation greatly exceeded between-community variation.
+The task showed satisfactory to high reliability across all communities.
+Therefore, we believe the TANGO--CC is a promising task to capture individual differences in social-cognitive development in diverse communities.
+Its design process lays out a much-needed pragmatic approach to conducting cross-cultural individual differences research.
+
+A similar approach to task development was taken by @mehta2011validation.
+The researchers (1) selected social cognition measures that have been established in WEIRD settings, (2) adapted the agent's names, appearance, backgrounds, and languages to the local context, and (3) assessed the task's validity and internal consistency in the new setting.
+Participants were adults with and without schizophrenia from India. Theory of Mind tasks included Sally-Anne, Smarties, Ice cream van and Missing cookies stories.
+For this specific context, the authors' approach yielded a successful adaptation of social cognition measures for the tested Indian (Hindi/Kannada) communities.
+
+@bourdage2023evaluation pointed out a major challenge with adapting social cognition tasks to diverse communities: the number of world cultures is vast, and communities are constantly changing.
+Therefore, a promising approach might be to provide tasks with a modular system where components can be exchanged according to the local context.
+In the case of the TANGO--CC, the task can not only be adapted to different languages, cartoon faces, and backgrounds (see Figure \@ref(fig:fig1)) but also updated with new stimuli.
+Unlike studies that present sequential, hand-painted pictures that are difficult to adapt [@mehta2011validation], the TANGO--CC uses SVGs that can be easily exchanged.
+
+The biggest strength of the TANGO--CC is its flexibility.
+The task is presented as a web app that can also run offline to enable remote data collection.
+Minimal language demands and an engaging, playful design increase the task's usability.
+Together with a short task duration, this reduces drop-out rates and enables efficient data collection with large sample sizes.
+The TANGO--CC follows a standardized procedure and uses a continuous, objective outcome measure (leaving no room for rater errors).
+An online manual with the most frequently asked questions is available at <https://ccp-odc.eva.mpg.de/TANGO--CC/manual.html>.
+Additional customization can be achieved by adding new stimuli to the open-source code available on GitHub (<https://github.com/ccp-eva/TANGO--CC>).
+
+For years, researchers have called for more diverse sampling and culturally valid measures of cognitive development [e.g., @mehta2011validation; @nielsen2017persistent; @matsumoto2006new].
+As @hajduk2020how put it, "using large samples and multisite approaches will align with efforts to improve reproducibility and will clarify both the type and extent of cultural influences on social cognition" (p.
+463).
+The TANGO--CC takes a valuable step in this direction by sharing the task and its source code with other researchers.
+@bohn2024universal showed that data collection with the TANGO--CC was feasible in 17 diverse communities in rural and urban settings with varying degrees of market integration and technology exposure.
+While we cannot generalize our findings to all communities worldwide, we found that it induced reliable individual variation in the 17 communities studied by @bohn2024universal.
+Using the TANGO--CC in a new community nevertheless requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
+We hope that the TANGO--CC will facilitate future cross-cultural studies to assess social-cognitive development in a wide range of communities.
+
+A valid question is whether the TANGO--CC measures the same construct across different groups.
+This so-called measurement invariance is often seen as a requirement for a "fair" cross-cultural comparison and relies on minimizing group differences while individual differences are magnified.
+As @kusano2024mismeasure put it: "The research challenge is to achieve a balance between ensuring methodological “fairness” at the individual level while also recognizing and capturing genuine sociocultural variability" (p.
+34).
+We argue that the TANGO--CC measures a fundamental social-cognitive ability that is likely similar across communities.
+@bohn2024universal have shown that children with no prior touchscreen exposure were less precise in the TANGO--CC than children with prior experience.
+However, individual differences were also found in communities with 100% touch screen exposure, showing that this factor alone could not explain children's performance in the task [@bohn2024universal].
+Notably, even though the touchscreen experience caused absolute differences in task performance, all communities showed the same processing signature.
+A recent computational cognitive model described gaze following as a process of estimating pupil angles and the corresponding gaze vectors [@prein2024variation].
+The model predicted that all individuals use the same process to locate an attentional focus but differ in their uncertainty around the estimated pupil angles, which results in less precision.
+@bohn2024universal found clear support for this model in every community they studied, suggesting that children all over the world process gaze in a similar way.
+In this manuscript, we could also show that internal consistency was high across all communities, meaning that the task captured individual differences in a similar way.
+Consequently, the TANGO--CC seems to measure systematic individual differences across diverse communities.
+
+@selcuk2023development pointed out that researchers should study both within- and between-culture variability in the development of social cognition since sometimes within-culture differences exceed between-culture differences.
+Indeed, we found that within-group variability was greater than between-group variability.
+While we believe that the TANGO--CC can be used to compare mean differences across communities, we would recommend using it to study individual differences within communities.
 
 # Limitations
-- measure same construct across communities?
-- technology effects
+
+The TANGO--CC and its psychometric properties need to be considered against some limitations.
+Reliability for each community was assessed by calculating the internal consistency.
+Ideally, we would have additionally assessed the task's retest reliability in each community and checked for relationships with theoretically related constructs to assess validity.
+
+@schilbach2013secondperson pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions.
+Of course, the TANGO--CC does not depict a real-life social interaction, and future research should investigate how task performance relates to the real world.
+Suggestive evidence comes from a study by @prein2024variation, who found that children's performance in the TANGO was linked to children's visual perspective-taking abilities in real-life social interaction.
+The mode of stimulus presentation surely needs to be kept in mind when administering the TANGO--CC, especially in communities with little technology exposure.
+Additional touch screen training (e.g., more trials of training 1) might prove helpful in these cases.
 
 # Conclusion
+
+The TANGO--CC is a promising task to capture individual differences in social-cognitive development across diverse communities.
+The task was developed in two phases: (1) implementing the task’s underlying functionality and estimating detailed psychometrics in one community, and (2) expanding the stimulus pool to accommodate diverse communities worldwide.
+The task’s flexibility, minimal language demands, and engaging design make it a valuable task for cross-cultural research.
+The task showed satisfactory to high reliability (internal consistency) in a large dataset including 17 diverse communities.
+We hope that the TANGO--CC – and its pragmatic construction process – will inspire future cross-cultural studies to assess cognitive development in a wide range of communities.
 

### 2024-05-08 stats/analysis.Rmd
incorporate Manuel's feedback; adjust intro; add trial type model

@@
 library(cmdstanr) # modeling
-library(janitor) # clean_names
 library(ggpubr) # ggarrange
@@
 library(ggridges) # for ridge plot
-library(RColorBrewer) # for color palette
-library(pals) # for color palette
-library(Hmisc) # for kelly color palette
-library(ggrepel) # for geom_text_repel
 # load source code for geom_flat_violin()
@@
 set.seed(42)
-
-# color palette
-# qual_col_pals = brewer.pal.info[brewer.pal.info$colorblind == TRUE,]
-# col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
-# 
-# # kelly palette of 22 colors maximize the contrast between colors in a set if the colors are chosen in sequential order. Kelly paid attention to the needs of people with color blindness
-# colors=kelly(n=n_distinct(data$community) +1)
-
-# create a custom color pallette with 17 easily distinguishable, different colors
-custom_palette <- c(
-  brewer.pal(11, "RdYlGn"),
-  brewer.pal(6, "BuPu")
-)
 ```
@@
   mutate(trialnr = as.numeric(factor(trialnr))) 
-
-# dataset with test trials only, with mean imprecision per participant
-# scale age across communities; mean_imprecision per subjid; household, touchscreen scaled per community
-mdata <- data %>%
-  mutate(age = scale(ageinyears, center = T, scale = F)) %>%
-  group_by(subjid, community, age_group, ageinyears, age, household, touchscreen) %>%
-  summarise(mean_imprecision = mean(imprecision)) %>%
-  group_by(community) %>%
-  mutate(
-    household = scale(household), 
-    touchscreen = factor(touchscreen),
-  ) %>%
-  na.omit()
 ```
@@
 ```{r sample}
-range(all_trials$ageinyears)
-
-# full sample
+# full sample, check for less than 4 test trials
 all_trials %>%
@@
 
-all_trials %>%
-  group_by(community, age_group) %>%
-  summarise(n= n_distinct(subjid))
-
-all_trials %>%
-  group_by(community) %>%
-  summarise(n= n_distinct(subjid))
-
-all_trials %>%
-  summarise(n= n_distinct(subjid))
-
-# model data
-mdata %>%
-  group_by(community, age_group) %>%
-  summarise(n= n_distinct(subjid))
-
-mdata %>%
-  group_by(community) %>%
-  summarise(n= n_distinct(subjid))
-
-mdata %>% ungroup() %>% 
-  summarise(n= n_distinct(subjid))
-```
-
-```{r exclude_children}
-# children who did not finish all trials are removed (only 5 children total)
+# exclude children with less than 4 test trials (1 training 1, 2 training 2, 1 test with audio instructions + 4 test trials = 8 min)
 exclude <- all_trials %>%
-  filter(trialtype == "test", voiceover == F) %>%
   group_by(subjid) %>%
-  summarise(n= n()) %>%
-  filter(n < 15) %>%
+  summarise(n = n()) %>%
+  filter(n < 8) %>%
   pull(subjid)
@@
 data <- data %>% filter(!subjid %in% exclude)
-mdata <- mdata %>% filter(!subjid %in% exclude)
 ```
@@
 
-```{r samplesize_plot}
-data %>% 
-  summarise(click = mean(imprecision), .by = c(community, ageinyears)) %>%
-  ggplot(mapping = aes(x = community, y = ageinyears)) + 
-  geom_flat_violin(scale = "count", trim = T, fill = "#29485D", alpha = 0.75) + 
-  geom_dotplot(binaxis = "y",
-               dotsize = 1,
-               stackdir = "down",
-               binwidth = 0.1,
-               position = position_nudge(-0.025), 
-               fill = "#ffffff"
-               ) +
-  scale_y_continuous(limits = c(2, 11), breaks = seq(2, 11, 1)) + 
-  labs(x = "", y = "Age in years") + 
-  theme(axis.text.x = element_text(angle = 30, hjust = 1))
+# Variation
 
-ggsave("../figures/age_distribution.png", width = 10, height = 5, scale = 1.1)
+```{r trialtypes_model}
+mdata <- all_trials %>% 
+  summarise(
+    imprecision = mean(imprecision), 
+    .by = c(trialtype, subjid, community)
+  ) %>% 
+  mutate(
+    trialtype = recode(trialtype, touch = "Training 1", fam = "Training 2", test = "Test") %>% as_factor(.) %>% relevel("Test"),
+    community = as.factor(community),
+  )
+
+mtrialtypes <- brm(imprecision ~ trialtype + (trialtype | community),
+                    data = mdata,
+                    family = lognormal(),
+                    warmup = 1000, 
+                    iter   = 3000, 
+                    chains = 4, 
+                    inits  = "random",
+                    cores  = 4) %>%
+  add_criterion(c("loo","waic"))
+
+summary(mtrialtypes)
+
+# ranef(mtrialtypes)
+mestimates <- coef(mtrialtypes)
+
+trialtypes_est <- tibble(
+  community = rownames(mestimates$community[,,1]),
+  Intercept = mestimates$community[, , "Intercept"][1:17],
+  Training1 = mestimates$community[, , "trialtypeTraining1"][1:17],
+  Training2 = mestimates$community[, , "trialtypeTraining2"][1:17]
+)
+
+saveRDS(mtrialtypes, "../saves/mtrialtypes.rds")
+saveRDS(trialtypes_est, "../saves/trialtypes_est")
 ```
 
-# Variation
-
-```{r model_density}
-# age_model <- brm(mean_imprecision ~ age + (1 | subjid),
-#                 data   = mdata,
-#                 family = lognormal(),
-#                 warmup = 2000,
-#                 iter   = 6000,
-#                 control = list(adapt_delta = 0.95),
-#                 chains = 4,
-#                 cores  = 4)
-
-# saveRDS(age_model, "../saves/age_model.rds")
-
-age_model <- readRDS("../saves/age_model.rds")
-
-nd <- mdata %>% 
-  select(-c(mean_imprecision))
-
-# extract model predictions for mock data
-pred_agecorrected <- fitted(age_model, newdata = nd, re_formula = NA) %>% as_tibble() %>% bind_cols(mdata)
-
-density_plot <- pred_agecorrected %>% 
-  ggplot(aes(x = Estimate, y = fct_rev(community))) +
-  geom_density_ridges(
-    jittered_points = TRUE,
-    position = position_points_jitter(width = 0.05, height = 0),
-    point_shape = '|', point_size = 2, point_alpha = 1, point_color = "#ffffff",
-    alpha = 1,
-    fill = "#29485D", 
-    col = "#ffffff", 
-    scale = 1.5
-  ) +
-  labs(x = "Absolute imprecision in target width", y = "", fill = "Community") +
-  expand_limits(y = c(1, 18.5)) + 
-  scale_x_continuous(limits = c(0.5, 4), breaks = seq(0, 4, 0.5)) +
-  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
-
-density_plot
-saveRDS(density_plot, "../saves/density_plot.rds")
+```{r model_draws}
+# newdata <- mdata %>% 
+#   select(-imprecision)
+# 
+# post <- fitted(mtrialtypes, newdata = newdata, re_formula = ~ (trialtype | community)) %>%
+#   as_tibble() %>%
+#   bind_cols(newdata)
+# 
+# post_sum <- post %>% 
+#   summarise(
+#     estimate = mean(Estimate), 
+#     .by = c(community, trialtype)
+#   ) %>% 
+#   pivot_wider(names_from = trialtype, values_from = estimate)
+# 
+# min(post_sum$`Training 1`)
+# min(post_sum$`Training 2`)
 ```
@@
 }
+
+descr_trialtypes <- all_trials %>% 
+  mutate(trialtype = recode(trialtype, touch = "Training 1", fam = "Training 2", test = "Test") %>% as_factor(.)) %>%
+  na.omit() %>%
+  summarise(
+    mean_click = mean(imprecision), 
+    sd_click = sd(imprecision), 
+    .by = trialtype
+  )
+
+saveRDS(descr_trialtypes, "../saves/descr_trialtypes.rds")
 
@@
   ) %>%
-  ggplot(aes(x = trialtype, y = mean_click, col = ageinyears)) +
-  geom_jitter(width = 0.2, size = 0.7, alpha = 0.7) +
+  ggplot(aes(x = as.factor(trialtype), y = mean_click)) +
+  geom_jitter(aes(col = ageinyears), height = 0, width = 0.2, size = 1, alpha = 1) + 
+  geom_violin(alpha = 0.25, fill = "darkgrey", scale = "width", draw_quantiles = c(0.5)) +
   scale_color_viridis_c(direction = -1) +
-  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
+  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, 2)) +
   facet_wrap(~ community, nrow = 3, scales="free_x") +
@@
 ```{r stratified_data}
-# fn_mean <- function(ds) {
-#   return(mean(abs(ds$clickdistfromtargetcenterx), na.rm = TRUE))
-# }
-# 
-# strat <- tibble()
-# 
-# communities <- unique(data$community)
-# 
-# for (j in c(1:50)) {
-#   for (i in communities) {
-#     # stratified by target position
-#     strat_s <- by_split(
-#       data = data %>% filter(community == i),
-#       participants = data %>% filter(community == i) %>% pull(subjid),
-#       fn_score = fn_mean,
-#       verbose = F,
-#       stratification = paste(data %>% filter(community == i) %>% pull(centrality)),
-#       careful = FALSE
-#       )
-#     
-#     samp <- tibble(
-#       community = i,
-#       iter = j,
-#       reli = split_coefs(strat_s, cor),
-#       lci = split_ci(strat_s, cor)$lims["0.025","bca"],
-#       uci = split_ci(strat_s, cor)$lims["0.975","bca"]
-#       )
-#     
-#     print(i)
-#     print(j)
-#     print(strat_s)
-#     print(samp)
-#     
-#     strat <- bind_rows(strat, samp)
-#   }
-# }
+fn_mean <- function(ds) {
+  return(mean(abs(ds$clickdistfromtargetcenterx), na.rm = TRUE))
+}
 
-# saveRDS(strat, "../saves/stratified_internal_consistency.rds")
+strat <- tibble()
 
-strat <- readRDS("../saves/stratified_internal_consistency.rds")
+communities <- unique(data$community)
+for (j in c(1:50)) {
+  for (i in communities) {
+    # stratified by target position
+    strat_s <- by_split(
+      data = data %>% filter(community == i),
+      participants = data %>% filter(community == i) %>% pull(subjid),
+      fn_score = fn_mean,
+      verbose = F,
+      stratification = paste(data %>% filter(community == i) %>% pull(centrality)),
+      careful = FALSE
+      )
+
+    samp <- tibble(
+      community = i,
+      iter = j,
+      reli = split_coefs(strat_s, cor),
+      lci = split_ci(strat_s, cor)$lims["0.025","bca"],
+      uci = split_ci(strat_s, cor)$lims["0.975","bca"]
+      )
+
+    print(i)
+    print(j)
+    print(strat_s)
+    print(samp)
+
+    strat <- bind_rows(strat, samp)
+  }
+}
+
+saveRDS(strat, "../saves/stratified_internal_consistency.rds")
+# strat <- readRDS("../saves/stratified_internal_consistency.rds")
 ```
@@
 # run model first for one community to use update()
-# split <- split_df(
-#   data = data %>% filter(community == "Leipzig (Germany)"),
-#   stratification = data %>% filter(community == "Leipzig (Germany)") %>% pull(centrality),
-#   careful = FALSE
-# )
-# 
-# sdata <- bind_rows(
-#   split[[1]] %>% 
-#     select(subjid, ageinyears, clickdistfromtargetcenterx) %>% 
-#     mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
-#   split[[2]] %>% 
-#     select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
-#     mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
-#   mutate(age = scale(ageinyears))
-# 
-# strat_age_model <- brm(impr ~ age + (0 + half | subjid),
-#                 data   = sdata,
-#                 family = lognormal(),
-#                 warmup = 1000,
-#                 iter   = 3000,
-#                 control = list(adapt_delta = 0.95),
-#                 chains = 4,
-#                 cores  = 4)
-# 
-# # loop over communities
-# communities <- unique(data$community)
-# 
-# strat_age <- tibble()
-# 
-# for (j in c(1:50)) {
-#   for (i in communities) {
-#     
-#     com_split <- split_df(
-#       data = data %>% filter(community == i),
-#       stratification = data %>% filter(community == i) %>% pull(centrality),
-#       careful = FALSE
-#     )
-#     
-#     com_sdata <- bind_rows(
-#       com_split[[1]] %>% 
-#         select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
-#         mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
-#       com_split[[2]] %>%
-#         select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
-#         mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
-#       mutate(age = scale(ageinyears))
-#     
-#     com_mod <- update(strat_split_model,
-#         newdata = com_sdata,
-#         warmup = 1000,
-#         iter   = 3000,
-#         control = list(adapt_delta = 0.95),
-#         chains = 4,
-#         cores  = 4)
-#     
-#     cor <- summary(com_mod)$random$subjid %>%
-#       as_tibble(rownames = "parameter") %>%
-#       filter(parameter == "cor(halfhalf_1, halfhalf_2)") %>%
-#       mutate(community = i, iter = j)
-#     
-#     strat_age <- bind_rows(strat_age, cor)
-#   }
-# }
-# 
-# saveRDS(strat_age, "../saves/age_corrected_internal_consistency.rds")
+split <- split_df(
+  data = data %>% filter(community == "Leipzig (Germany)"),
+  stratification = data %>% filter(community == "Leipzig (Germany)") %>% pull(centrality),
+  careful = FALSE
+)
 
-strat_age <- readRDS("../saves/age_corrected_internal_consistency.rds")
+sdata <- bind_rows(
+  split[[1]] %>%
+    select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
+    mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
+  split[[2]] %>%
+    select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
+    mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
+  mutate(age = scale(ageinyears))
+
+strat_age_model <- brm(impr ~ age + (0 + half | subjid),
+                data   = sdata,
+                family = lognormal(),
+                warmup = 1000,
+                iter   = 3000,
+                control = list(adapt_delta = 0.95),
+                chains = 4,
+                cores  = 4)
+
+# loop over communities
+communities <- unique(data$community)
+
+strat_age <- tibble()
+
+for (j in c(1:50)) {
+  for (i in communities) {
+
+    com_split <- split_df(
+      data = data %>% filter(community == i),
+      stratification = data %>% filter(community == i) %>% pull(centrality),
+      careful = FALSE
+    )
+
+    com_sdata <- bind_rows(
+      com_split[[1]] %>%
+        select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
+        mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
+      com_split[[2]] %>%
+        select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
+        mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
+      mutate(age = scale(ageinyears))
+
+    com_mod <- update(strat_split_model,
+        newdata = com_sdata,
+        warmup = 1000,
+        iter   = 3000,
+        control = list(adapt_delta = 0.95),
+        chains = 4,
+        cores  = 4)
+
+    cor <- summary(com_mod)$random$subjid %>%
+      as_tibble(rownames = "parameter") %>%
+      filter(parameter == "cor(halfhalf_1, halfhalf_2)") %>%
+      mutate(community = i, iter = j)
+
+    strat_age <- bind_rows(strat_age, cor)
+  }
+}
+
+saveRDS(strat_age, "../saves/age_corrected_internal_consistency.rds")
+
+# strat_age <- readRDS("../saves/age_corrected_internal_consistency.rds")
 ```
@@
       summarise(stratified_agecorrected = mean(Estimate, na.rm = T))
-  )
+  ) %>%
+  mutate(across(where(is.numeric), ~round(., 2)))
 
@@
 ```{r combine_plot}
-# density_plot <- readRDS("../saves/density_plot.rds")
 # odd_even_plot <- readRDS("../saves/odd_even_plot.rds")
@@
 top_row <- ggarrange(
-  density_plot,
   odd_even_plot,
@@
   stratified_agecorrected_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
-  widths = c(1.5, 2.1, 1.4, 1.4), 
+  widths = c(1.7, 1.2, 1.2), 
   nrow = 1,
@@
   nrow = 2,
-  heights = c(2.9, 1.4),
+  heights = c(3, 1.5),
   labels = c("A", "") 
@@
 
-ggsave("../figures/tango-cc-results.png", width = 12, height = 12, scale = 1, bg = "white")
+ggsave("../figures/tango-cc-results.png", width = 12, height = 11, scale = 0.9, bg = "white")
 ```
@@
 ```{r sd_int_plot}
+# var_df <- readRDS("../saves/var_df.rds")
+# int_con <- readRDS("../saves/internal_consistency.rds")
+
 sd_int_plot <- var_df %>%  
@@
 sd_int_plot
+
+sd_int_cor <- var_df %>%  
+  select(community, community_sd) %>% 
+  full_join(int_con) %>% 
+  select(c(community_sd, stratified_agecorrected)) %>%
+  corr.test()
+
+sd_int_cor$ci %>% round(2) %>% 
+  saveRDS("../saves/sd_int_cor.rds")
 ```

### 2024-05-15 paper/manuscript.Rmd
correct small errors (esp. authors)

@@
 author: 
-  - name          : "Julia Prein (ORCID: 0000-0002-3154-6167)"
+  - name          : "Julia Christin Prein (ORCID: 0000-0002-3154-6167)"
     affiliation   : "1,2"
@@
     address       : "Universitätsallee 1, 21335 Lüneburg, Germany"
-    email         : "manuel.bohn@leuphana.de"
+    email         : "julia.prein@leuphana.de"
     role:
@@
       - "Software"
-      - "Investigation"
+      - "Formal Analysis"
+      - "Resources"
       - "Writing - Original Draft Preparation"
@@
     role:
-      - "Investigation"
+      - "Resources"
       - "Writing - Review & Editing" 
@@
     role:
-      - "Investigation"
+      - "Resources"
+      - "Writing - Review & Editing" 
   - name          : "Michael C. Frank (ORCID: 0000-0002-7551-4378)"
@@
     role:
-      - "Investigation"
+      - "Resources"
       - "Writing - Review & Editing"     
@@
     role:
-      - "Investigation"
+      - "Resources"
+      - "Writing - Review & Editing" 
   - name          : "Shirley Magazi (ORCID: 0009-0006-0479-9800)"
@@
     role:
-      - "Investigation"
+      - "Resources"
+      - "Writing - Review & Editing" 
   - name          : "Lizbeth Mújica-Manrique"
@@
     role:
-      - "Investigation"
+      - "Resources"
+      - "Writing - Review & Editing" 
   - name          : "Damilola Olaoba"
@@
     role:
-     - "Investigation"
+      - "Resources"
+      - "Writing - Review & Editing" 
   - name          : "Wesley R. Pieters (ORCID:0000-0002-6152-249X)"
@@
     role:
-     - "Investigation"
-  - name          : "Roman Stengelin (ORCID: 0000-0003-2212-4613)"
-    affiliation   : "2,10"
+      - "Resources"
+      - "Writing - Review & Editing" 
+  - name          : "Umay Sen (ORCID: 0000-0001-9488-0851)"
+    affiliation   : "13"
     role:
-      - "Conceptualization"
-      - "Methodology"
-      - "Investigation"
+      - "Resources"
       - "Writing - Review & Editing" 
@@
     role:
-     - "Investigation"
+      - "Resources"
       - "Writing - Review & Editing" 
@@
     role:
-      - "Investigation"
+      - "Resources"
+      - "Writing - Review & Editing" 
+  - name          : "Roman Stengelin (ORCID: 0000-0003-2212-4613)"
+    affiliation   : "2,10"
+    role:
+      - "Resources"
+      - "Writing - Review & Editing"     
   - name          : "Jahnavi Sunderarajan"
@@
     role:
-      - "Investigation"
+      - "Resources"
+      - "Writing - Review & Editing" 
+  - name          : "Kirsten Sutherland"
+    affiliation   : "2"
+    role:
+      - "Resources"
+      - "Writing - Review & Editing" 
   - name          : "Florence Tusiime"
@@
     role:
-      - "Investigation"
+      - "Resources"
+      - "Writing - Review & Editing" 
   - name          : "Wilson Vieira (ORCID: 0009-0001-9400-6328)"
@@
     role:
-     - "Investigation"
+      - "Resources"
+      - "Writing - Review & Editing" 
   - name          : "Zhen Zhang (ORCID: 0000-0001-9300-0920)"
@@
     role:
-      - "Investigation"
+      - "Resources"
       - "Writing - Review & Editing"   
@@
     role:
-      - "Investigation"
+      - "Resources"
+      - "Writing - Review & Editing" 
   - name          : "Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)"
@@
     role:
-      - "Conceptualization"
       - "Funding acquisition"
@@
     institution   : "CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences"
+  - id            : "13"
+    institution   : "Department of Psychology, Developmental Psychology, Uppsala University"
   - id            : "+"
@@
 keywords          : "cross-cultural psychology, social cognition, gaze following, individual differences, reliability"
-wordcount         : "XXX"
+wordcount         : "5457"
 floatsintext      : yes
@@
 linenumbers       : yes
-mask              : yes 
+mask              : no 
 draft             : no
@@
 documentclass     : "apa7"
-output            : papaja::apa6_word
+output            : papaja::apa6_pdf
 editor_options    : 
@@
 library("brms")
-library("janitor")
+# library("janitor")
 
@@
 
-For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) backgrounds [@henrich2010weirdesta; @lillard1998ethnopsychologies].
+For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) communities [@henrich2010weirdesta; @lillard1998ethnopsychologies].
 Despite numerous calls for change, the subject pools reported in high-impact journals still lack diversity [@nielsen2017persistent; @gutchess2023considerationa].
-This lack of representation hinders progress in theory building: inferences about the unique characteristics of human behavior and "human nature" cannot be drawn from humans from only one community [@krys2024weirda].
+This lack of representation hinders progress in theory building: inferences about the universal and variable aspects of the human cognitive system cannot be drawn from data collected in single communities [@krys2024weirda].
 
-To do justice to the diversity in experiences, we must study cognition and its development in diverse communities and even across families and individuals [@selcuk2023development; @gutchess2023considerationa].
-So why are not more social-cognitive studies focusing on the variation between individuals living in diverse communities?
-A potential reason for the under-representation of these studies may be the scarcity of suitable tasks [@bourdage2023evaluation].
+One reason for the lack of diversity in psychological studies is the scarcity of suitable methods to collect comparable psychological data in different communities [@bourdage2023evaluation].
+This shortage of suitable measures is even more prevalent in developmental psychology.
+In this paper, we describe the construction and psychometric evaluation of a measure of basic social cognition (gaze following) in children as a concrete example for how to overcome this problem.
 
-Studies investigating variation between communities and/or individuals need to ensure that the captured variation is systematic and not just random noise.
-This requires measurement reliability and validity.
-Yet, social cognition studies based on US-American and European samples rarely report psychometric information [for a review, see @beaudoin2020systematic].
-This picture further deteriorates when we pay attention to the reliability and validity of cross-cultural social cognition tasks [@hajduk2020how; @bourdage2023evaluation; @waschl2022crosscultural].
-It remains challenging to find reliable and valid tasks that can capture individual differences within one community, let alone tasks that do so across different communities.
+Studies investigating variation between communities and/or individuals need to ensure that the captured variation is systematic and not just random noise: measures need to be reliable and valid.
+This, of course, applies to all fields of psychology.
+Given the topic of this paper, we will focus on measures of social cognition for children.
+Studies on social cognition based on US-American and European samples rarely report psychometric information [for a review, see @beaudoin2020systematic].
+This picture further deteriorates when we look at cross-cultural social cognition tasks [@hajduk2020how; @bourdage2023evaluation; @waschl2022crosscultural].
+Thus, it is already challenging to find reliable and valid tasks that can capture individual differences within one community, let alone tasks that do so across different communities.
 
@@
 This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that can be -- and has been -- adapted to several languages and communities.
-We describe the task's development and provide a tutorial for the open-source website (<https://ccp-odc.eva.mpg.de/TANGO--CC/>).
+We describe the task's development and provide a tutorial for the open-source website (<https://ccp-odc.eva.mpg.de/tango-cc/>).
 We assess its cross-cultural applicability based on data from a large cross-cultural sample of 2.5- to 11-year-olds from 17 different urban/rural communities across the world and discuss the task's psychometrics.
@@
 In a perfect world, developing a cross-cultural task would include international collaboration and diverse samples from the beginning, already during study design, piloting and item selection.
-As this seems hardly feasible, we present an alternative, pragmatic approach.
-First, the task was implemented in one context, in our case with a German sample [@prein2023tango].
-In this context, the task's reliability and validity were assessed in detail.
+As this seems hardly feasible, we present a pragmatic approach.
+The TANGO-CC was first implemented in one context, in our case Leipzig, Germany [@prein2023tango].
+Here, the task's reliability and validity were assessed in detail.
 Even though this does not guarantee that the task will be valid and reliable in another context, it substantially increases the likelihood.
@@
 The participant's task is to locate a target by following the agent's gaze (see Figure \@ref(fig:fig1)).
-Precision was measured in a continuous way as the distance between the participant's click on the screen and the target position.
+Precision was measured in a continuous way as the distance between the participant’s click on the screen (*i.e.*, where the participant thinks the target is) and the target’s real position.
 The task's core functionality is to animate the agent's eyes so that they follow the target's movement.
@@
 
-The TANGO--CC can be accessed via the following link: (<https://ccp-odc.eva.mpg.de/TANGO--CC/>).
+The TANGO--CC can be accessed via the following link: (<https://ccp-odc.eva.mpg.de/tango-cc/>).
 In the first step, researchers can select the language for audio instructions, currently available for 13 different languages and even more dialects (see Table 1).
@@
 
-The source code of the task is available on GitHub (<https://github.com/ccp-eva/TANGO--CC>).
+The source code of the task is available on GitHub (<https://github.com/ccp-eva/tango-cc>).
 By directly editing the `HTML` and `JavaScript` code, researchers gain even more flexibility in adjusting the task to their needs.
@@
 
-As a first feasibility check, we inspected the mean and standard deviations by community and compared performance in each trial type (training 1, training 2, test trials).
-Performance was defined as the absolute click distance between the target center and the click x coordinate, scaled according to balloon widths.
+First, we inspected the mean and standard deviations by community and compared performance in each trial type (training 1, training 2, test trials).
+Performance was defined as the absolute click distance between the target center and the click x coordinate (measured in balloon widths).
 Across communities, children performed best in training 1 (mean = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 1",]$mean_click`, sd = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 1",]$sd_click`), followed by training 2 (mean = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 2",]$mean_click`, sd = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 2",]$sd_click`) and test trials (mean = `r descr_trialtypes[descr_trialtypes$trialtype== "Test",]$mean_click`, sd = `r descr_trialtypes[descr_trialtypes$trialtype== "Test",]$sd_click`; see Figure \@ref(fig:fig2)A).
@@
 All analyses were run in `r R.version$version.string` [@rcoreteam2024language].
-GLMMs were fit with default priors using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].
+GLMMs were fitted with default priors using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].
 The model included random effects for trial type by community (model notation in `R: imprecision ~ trialtype + (trialtype | community)`), and imprecision was modeled by a `lognormal` distribution.
@@
 
-Our GLMM analysis supported the visual inspection of the data: the estimates for training 1 ($\beta$ = `r fixef(mtrialtypes)["trialtypeTraining1", "Estimate"]`; 95% CrI [`r fixef(mtrialtypes)["trialtypeTraining1", "Q2.5"]`; `r fixef(mtrialtypes)["trialtypeTraining1", "Q97.5"]`]) and training 2 ($\beta$ = `r fixef(mtrialtypes)["trialtypeTraining2", "Estimate"]`; 95% CrI [`r fixef(mtrialtypes)["trialtypeTraining2", "Q2.5"]`; `r fixef(mtrialtypes)["trialtypeTraining2", "Q97.5"]`]) were negative and reliably different from zero.
+Our GLMM analysis supported the visual inspection of the data: the fixed-effect estimates for training 1 ($\beta$ = `r fixef(mtrialtypes)["trialtypeTraining1", "Estimate"]`; 95% CrI [`r fixef(mtrialtypes)["trialtypeTraining1", "Q2.5"]`; `r fixef(mtrialtypes)["trialtypeTraining1", "Q97.5"]`]) and training 2 ($\beta$ = `r fixef(mtrialtypes)["trialtypeTraining2", "Estimate"]`; 95% CrI [`r fixef(mtrialtypes)["trialtypeTraining2", "Q2.5"]`; `r fixef(mtrialtypes)["trialtypeTraining2", "Q97.5"]`]) were negative and reliably different from zero.
 Please note that the TANGO--CC measures imprecision in gaze following.
 Therefore, a negative sign shows that children showed less imprecision (i.e., were more precise) in the training trials than in the test trials.
-This effect was found across all communities (minimum estimate for training 1 = `r max(trialtypes_est$Training1)`; minimum estimate for training 2 = `r max(trialtypes_est$Training2)`).
+This effect was found across all communities (random effects of trial type within community: minimum estimate for training 1 = `r max(trialtypes_est$Training1)`; 95%CrI [`r trialtypes_est$Training1_q25[which.max(trialtypes_est$Training1)]`; `r trialtypes_est$Training1_q975[which.max(trialtypes_est$Training1)]`]; minimum estimate for training 2 = `r max(trialtypes_est$Training2)`; 95%CrI [`r trialtypes_est$Training2_q25[which.max(trialtypes_est$Training2)]`; `r trialtypes_est$Training2_q975[which.max(trialtypes_est$Training2)]`]).
 The almost perfect performance in training trials indicated that children understood the task and were able to locate the balloon.
 In test trials, children's imprecision was higher, indicating that the task was more challenging.
-All communities showed great individual variation and overlapped in their imprecision levels (see Figure \@ref(fig:fig2)A).
+All communities showed substantial individual variation and overlapped in their imprecision levels (see Figure \@ref(fig:fig2)A).
 
@@
 This eliminates the chance that a good internal consistency estimate results from general cognitive development rather than task-specific inter-individual differences.
-Because the process of generating stratified data sets is partly random, the model was fit 50 times for each community.
+Because the process of generating stratified data sets is partly random, the model was fitted 50 times for each community.
 The posterior estimate of the correlation between the two person-specific estimates was taken as the age-independent estimate for internal consistency.
@@
 Across communities, internal consistency estimates ranged from `r min(int_con$odd_even)` to `r max(int_con$odd_even)` for the odd-even split, `r min(int_con$stratified)` to `r max(int_con$stratified)` for the stratified internal consistency, and `r int_con_wo_uk$min` to `r max(int_con$stratified_agecorrected)` for the age-corrected approach (Plymouth, UK, being an outlier with `r int_con$stratified_agecorrected[int_con$community == "Plymouth (UK)"]`).
-Following Cohen's suggestions [@cohen1988statistical; @cohen1992power], these correlations constitute large effects (*r* >.50), and indicated good internal consistency.[^1] 
+Following Cohen's suggestions [@cohen1988statistical; @cohen1992power], these correlations constitute large effects (*r* > .50), and indicate good internal consistency.[^1] 
 The results are comparable to the internal consistency estimates found in the original TANGO study [@prein2023tango], and also resemble reliability estimates of classical false belief tasks [@hughes2000good].
@@
 Next, we adapted the superficial features of the task to be used in 17 diverse communities and assessed the task's psychometric properties.
-Children’s imprecision in gaze following highly overlapped between communities: children performed similarly in the communities depending on the trial type, and within-community variation greatly exceeded between-community variation.
+Children’s imprecision in gaze following highly overlapped between communities: children performed better in the training than the test trials, and within-community variation greatly exceeded between-community variation.
 The task showed satisfactory to high reliability across all communities.
@@
 The TANGO--CC follows a standardized procedure and uses a continuous, objective outcome measure (leaving no room for rater errors).
-An online manual with the most frequently asked questions is available at <https://ccp-odc.eva.mpg.de/TANGO--CC/manual.html>.
-Additional customization can be achieved by adding new stimuli to the open-source code available on GitHub (<https://github.com/ccp-eva/TANGO--CC>).
+An online manual with the most frequently asked questions is available at <https://ccp-odc.eva.mpg.de/tango-cc/manual.html>.
+Additional customization can be achieved by adding new stimuli to the open-source code available on GitHub (<https://github.com/ccp-eva/tango-cc>).
 
@@
 @bohn2024universal showed that data collection with the TANGO--CC was feasible in 17 diverse communities in rural and urban settings with varying degrees of market integration and technology exposure.
-While we cannot generalize our findings to all communities worldwide, we found that it induced reliable individual variation in the 17 communities studied by @bohn2024universal.
+While we cannot generalize our findings to all communities worldwide, we found that it captured reliable individual variation in the 17 communities studied by @bohn2024universal.
 Using the TANGO--CC in a new community nevertheless requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
@@
 @schilbach2013secondperson pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions.
-Of course, the TANGO--CC does not depict a real-life social interaction, and future research should investigate how task performance relates to the real world.
+Of course, the TANGO--CC does not depict real-life social interaction, and future research should investigate how task performance relates to the real world.
 Suggestive evidence comes from a study by @prein2024variation, who found that children's performance in the TANGO was linked to children's visual perspective-taking abilities in real-life social interaction.

### 2024-05-15 paper/manuscript.tex
correct small errors (esp. authors)

@@
 \documentclass[
-  man,mask,floatsintext]{apa7}
+  man,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
 \fi
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 
-% \usepackage{etoolbox}
 \makeatletter
-\patchcmd{\HyOrg@maketitle}
+\usepackage{etoolbox}
+\patchcmd{\maketitle}
   {\section{\normalfont\normalsize\abstractname}}
@@
   {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
+\patchcmd{\maketitle}
   {\section{\protect\normalfont{\@title}}}
@@
 {}{\PatchFailed}
-\keywords{cross-cultural psychology, social cognition, gaze following, individual differences, reliability\newline\indent Word count: XXX}
+\keywords{cross-cultural psychology, social cognition, gaze following, individual differences, reliability\newline\indent Word count: 5457}
 \usepackage{lineno}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 \hypersetup{
-  pdftitle={Measuring variation in gaze-following across cultures, individuals, and age --- a showcase of the TANGO-CC},
+  pdftitle={Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC},
+  pdfauthor={Julia Christin Prein (ORCID: 0000-0002-3154-6167)1,2, Florian M.
+Bednarski (ORCID: 0000-0003-4384-4791)4, Ardain Dzabatou5, Michael C.
+Frank (ORCID: 0000-0002-7551-4378)6, Annette M.
+E.
+Henderson (ORCID: 0000-0003-4384-4791)4, Josefine Kalbitz2, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)7, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)8, Bahar Köymen (ORCID: 0000-0001-5126-8240)9, Maira V.
+Manrique-Hernandez2, Shirley Magazi (ORCID: 0009-0006-0479-9800)10, Lizbeth Mújica-Manrique2, Julia Ohlendorf2, Damilola Olaoba2, Wesley R.
+Pieters (ORCID:0000-0002-6152-249X)10, Sarah Pope-Caldwell2, Umay Sen (ORCID: 0000-0001-9488-0851)13, Katie Slocombe (ORCID: 0000-0002-7310-1887)11, Robert Z.
+Sparks (ORCID: 0000-0001-7545-0522)6, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,10, Jahnavi Sunderarajan2, Kirsten Sutherland2, Florence Tusiime3, Wilson Vieira (ORCID: 0009-0001-9400-6328)2, Zhen Zhang (ORCID: 0000-0001-9300-0920)12, Yufei Zong (ORCID: 0009-0000-5012-0244)12, Daniel B.
+M.
+Haun (ORCID: 0000-0002-3262-645X)2,+, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)1,2,+},
   pdflang={en-EN},
@@
 
-\title{Measuring variation in gaze-following across cultures, individuals, and age --- a showcase of the TANGO-CC}
-\author{Julia Prein (ORCID: 0000-0002-3154-6167)\textsuperscript{1,2}, Florian M.
+\title{Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC}
+\author{Julia Christin Prein (ORCID: 0000-0002-3154-6167)\textsuperscript{1,2}, Florian M.
 Bednarski (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Ardain Dzabatou\textsuperscript{5}, Michael C.
@@
 Manrique-Hernandez\textsuperscript{2}, Shirley Magazi (ORCID: 0009-0006-0479-9800)\textsuperscript{10}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R.
-Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{10}, Sarah Pope-Caldwell\textsuperscript{2}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,10}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{11}, Robert Z.
-Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{6}, Jahnavi Sunderarajan\textsuperscript{2}, Florence Tusiime\textsuperscript{3}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{12}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{12}, Daniel B.
+Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{10}, Sarah Pope-Caldwell\textsuperscript{2}, Umay Sen (ORCID: 0000-0001-9488-0851)\textsuperscript{13}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{11}, Robert Z.
+Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{6}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,10}, Jahnavi Sunderarajan\textsuperscript{2}, Kirsten Sutherland\textsuperscript{2}, Florence Tusiime\textsuperscript{3}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{12}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{12}, Daniel B.
 M.
@@
 
-\shorttitle{measuring gaze following across cultures}
+\shorttitle{measuring gaze following across communities}
 
@@
 The authors made the following contributions.
-Julia Prein (ORCID: 0000-0002-3154-6167): Conceptualization, Methodology, Software, Investigation, Writing - Original Draft Preparation, Writing - Review \& Editing; Florian M.
-Bednarski (ORCID: 0000-0003-4384-4791): Investigation, Writing - Review \& Editing; Ardain Dzabatou: Investigation; Michael C.
-Frank (ORCID: 0000-0002-7551-4378): Investigation, Writing - Review \& Editing; Annette M.
+Julia Christin Prein (ORCID: 0000-0002-3154-6167): Conceptualization, Methodology, Software, Formal Analysis, Resources, Writing - Original Draft Preparation, Writing - Review \& Editing; Florian M.
+Bednarski (ORCID: 0000-0003-4384-4791): Resources, Writing - Review \& Editing; Ardain Dzabatou: Resources, Writing - Review \& Editing; Michael C.
+Frank (ORCID: 0000-0002-7551-4378): Resources, Writing - Review \& Editing; Annette M.
 E.
-Henderson (ORCID: 0000-0003-4384-4791): Investigation, Writing - Review \& Editing; Josefine Kalbitz: Investigation, Writing - Review \& Editing; Patricia Kanngiesser (ORCID:0000-0003-1068-3725): Investigation, Writing - Review \& Editing; Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733): Investigation, Writing - Review \& Editing; Bahar Köymen (ORCID: 0000-0001-5126-8240): Investigation, Writing - Review \& Editing; Maira V.
-Manrique-Hernandez: Investigation; Shirley Magazi (ORCID: 0009-0006-0479-9800): Investigation; Lizbeth Mújica-Manrique: Investigation, Writing - Review \& Editing; Julia Ohlendorf: Investigation; Damilola Olaoba: Investigation; Wesley R.
-Pieters (ORCID:0000-0002-6152-249X): Investigation, Writing - Review \& Editing; Sarah Pope-Caldwell: Investigation; Roman Stengelin (ORCID: 0000-0003-2212-4613): Conceptualization, Methodology, Investigation, Writing - Review \& Editing; Katie Slocombe (ORCID: 0000-0002-7310-1887): Investigation, Writing - Review \& Editing; Robert Z.
-Sparks (ORCID: 0000-0001-7545-0522): Investigation; Jahnavi Sunderarajan: Investigation; Florence Tusiime: Investigation; Wilson Vieira (ORCID: 0009-0001-9400-6328): Investigation; Zhen Zhang (ORCID: 0000-0001-9300-0920): Investigation, Writing - Review \& Editing; Yufei Zong (ORCID: 0009-0000-5012-0244): Investigation; Daniel B.
+Henderson (ORCID: 0000-0003-4384-4791): Resources, Writing - Review \& Editing; Josefine Kalbitz: Resources, Writing - Review \& Editing; Patricia Kanngiesser (ORCID:0000-0003-1068-3725): Resources, Writing - Review \& Editing; Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733): Resources, Writing - Review \& Editing; Bahar Köymen (ORCID: 0000-0001-5126-8240): Resources, Writing - Review \& Editing; Maira V.
+Manrique-Hernandez: Resources, Writing - Review \& Editing; Shirley Magazi (ORCID: 0009-0006-0479-9800): Resources, Writing - Review \& Editing; Lizbeth Mújica-Manrique: Resources, Writing - Review \& Editing; Julia Ohlendorf: Resources, Writing - Review \& Editing; Damilola Olaoba: Resources, Writing - Review \& Editing; Wesley R.
+Pieters (ORCID:0000-0002-6152-249X): Resources, Writing - Review \& Editing; Sarah Pope-Caldwell: Resources, Writing - Review \& Editing; Umay Sen (ORCID: 0000-0001-9488-0851): Resources, Writing - Review \& Editing; Katie Slocombe (ORCID: 0000-0002-7310-1887): Resources, Writing - Review \& Editing; Robert Z.
+Sparks (ORCID: 0000-0001-7545-0522): Resources, Writing - Review \& Editing; Roman Stengelin (ORCID: 0000-0003-2212-4613): Resources, Writing - Review \& Editing; Jahnavi Sunderarajan: Resources, Writing - Review \& Editing; Kirsten Sutherland: Resources, Writing - Review \& Editing; Florence Tusiime: Resources, Writing - Review \& Editing; Wilson Vieira (ORCID: 0009-0001-9400-6328): Resources, Writing - Review \& Editing; Zhen Zhang (ORCID: 0000-0001-9300-0920): Resources, Writing - Review \& Editing; Yufei Zong (ORCID: 0009-0000-5012-0244): Resources, Writing - Review \& Editing; Daniel B.
 M.
-Haun (ORCID: 0000-0002-3262-645X): Conceptualization, Funding acquisition, Writing - Review \& Editing; Manuel Bohn (ORCID: 0000-0001-6006-1348): Conceptualization, Methodology, Writing - Review \& Editing.
+Haun (ORCID: 0000-0002-3262-645X): Funding acquisition, Writing - Review \& Editing; Manuel Bohn (ORCID: 0000-0001-6006-1348): Conceptualization, Methodology, Writing - Review \& Editing.
 
-Correspondence concerning this article should be addressed to Julia Prein (ORCID: 0000-0002-3154-6167), Universitätsallee 1, 21335 Lüneburg, Germany.
-E-mail: \href{mailto:manuel.bohn@leuphana.de}{\nolinkurl{manuel.bohn@leuphana.de}}
+Correspondence concerning this article should be addressed to Julia Christin Prein (ORCID: 0000-0002-3154-6167), Universitätsallee 1, 21335 Lüneburg, Germany.
+E-mail: \href{mailto:julia.prein@leuphana.de}{\nolinkurl{julia.prein@leuphana.de}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology\\\textsuperscript{3} Budongo Conservation Field Station\\\textsuperscript{4} School of Psychology, University of Auckland\\\textsuperscript{5} Université Marien Ngouabi\\\textsuperscript{6} Department of Psychology, Stanford University\\\textsuperscript{7} School of Psychology, University of Plymouth\\\textsuperscript{8} Department of Psychology, Koç University\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia\\\textsuperscript{11} Department of Psychology, University of York\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences\\\textsuperscript{+} joint last author}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology\\\textsuperscript{3} Budongo Conservation Field Station\\\textsuperscript{4} School of Psychology, University of Auckland\\\textsuperscript{5} Université Marien Ngouabi\\\textsuperscript{6} Department of Psychology, Stanford University\\\textsuperscript{7} School of Psychology, University of Plymouth\\\textsuperscript{8} Department of Psychology, Koç University\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia\\\textsuperscript{11} Department of Psychology, University of York\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences\\\textsuperscript{13} Department of Psychology, Developmental Psychology, Uppsala University\\\textsuperscript{+} joint last author}
 
 \abstract{%
-Cross-cultural studies are crucial for establishing the universality and robustness of developmental milestones.
-Yet, suitable methods to measure variability in social cognition across linguistic and cultural settings are lacking.
-This paper describes the TANGO-CC (Task for Assessing Individual Differences in Gaze Understanding - Cross Cultural), a gaze-following task designed to measure imprecision in gaze following across individuals, ages, and communities.
-The development of the TANGO-CC involved two main phases: initial implementation and validation in Leipzig, Germany, followed by collaboration with cross-cultural researchers to expand the stimulus pool and collect data from 2.5- to 11-year-old children (N = 1377) from 17 diverse communities worldwide.
-The TANGO-CC captured individual differences and high internal consistency in each community.
+Cross-cultural studies are crucial for investigating the universality and robustness of cognitive developmental processes.
+Yet, suitable methods to measure variability in cognition across languages and communities are lacking.
+This paper describes the TANGO--CC (Task for Assessing Individual Differences in Gaze Understanding -- Cross-Cultural), a gaze following task designed to measure basic social cognition across individuals, ages, and communities.
+The TANGO--CC was developed and psychometrically assessed in one setting and subsequently adapted for cross-cultural data collection.
+Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community.
+The TANGO--CC captured individual differences and showed good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities.
 Within-community variation outweighed between-community variation.
-Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each cultural setting.
-We provide an open-source website for researchers to customize the task to their needs.
-Overall, the TANGO-CC represents a valuable contribution to the assessment of social-cognitive development in diverse social-cultural environments, facilitating future cross-cultural studies.
+We provide an open-source website for researchers to customize and use the task.
+The TANGO--CC represents a valuable contribution to assessing basic social cognition in diverse communities, establishing a roadmap for researching cross-cultural individual differences.
 }
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}
 
-More than a decade ago, Henrich et al.
-(2010) advocated for more diverse samples in psychological research and cautioned against relying solely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) backgrounds.
-Despite numerous calls for change, the subject pools reported in high-impact journals still lack diversity (Nielsen et al., 2017).
-This lack of representation creates inequities and hampers progress in theory building: If we want to draw inferences about the unique characteristics of human behavior and ``human nature'', we need to study it in many humans from many different backgrounds (Krys et al., 2024).
+For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) communities (Henrich et al., 2010; Lillard, 1998).
+Despite numerous calls for change, the subject pools reported in high-impact journals still lack diversity (Gutchess \& Rajaram, 2023; Nielsen et al., 2017).
+This lack of representation hinders progress in theory building: inferences about the universal and variable aspects of the human cognitive system cannot be drawn from data collected in single communities (Krys et al., 2024).
 
-The present sampling bias might be especially problematic in research concerning the development of social cognition.
-Social cognition concerns the processes by which individuals encode and decode social information (Glynn \& Watkiss, 2016), which allows them to successfully participate in joint activities and communication.
-Many developmental theories emphasize the role of social interaction in the development of social cognition (e.g., reinforcement learning in gaze following; (Jasso \& Triesch, 2006)).
-However, social interactions differ substantially in their characteristics across communities and even across families and individuals.
-Cultural and social experiences influence the beliefs, values, norms and expectations of an individual, which, in turn, determines how they interpret other's actions.
-Consequently, Selcuk et al.
-(2023) have urged for studying how social-cultural factors on a macro-, community-level as well as a micro-, family-level influence the social cognition development.
+One reason for the lack of diversity in psychological studies is the scarcity of suitable methods to collect comparable psychological data in different communities (Bourdage et al., 2023).
+This shortage of suitable measures is even more prevalent in developmental psychology.
+In this paper, we describe the construction and psychometric evaluation of a measure of basic social cognition (gaze following) in children as a concrete example for how to overcome this problem.
 
-Why are there not more social-cognitive studies focusing on the variation between diverse communities and individuals?
-A potential reason for the under-representation of these studies may be the scarcity of suitable tools (Bourdage et al., 2023).
-A suitable tool for studying individual- and community-level variation needs to address its (1) psychometric properties and (2) cross-cultural adaptations.
+Studies investigating variation between communities and/or individuals need to ensure that the captured variation is systematic and not just random noise: measures need to be reliable and valid.
+This, of course, applies to all fields of psychology.
+Given the topic of this paper, we will focus on measures of social cognition for children.
+Studies on social cognition based on US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020).
+This picture further deteriorates when we look at cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020; Waschl \& Chen, 2022).
+Thus, it is already challenging to find reliable and valid tasks that can capture individual differences within one community, let alone tasks that do so across different communities.
 
-First, studies investigating variation between communities and/or individuals need to ensure that the captured variation is systematic and not just random noise.
-This requires measurement reliability and validity.
-Yet, social cognition studies based on US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020).
-This picture further deteriorates when we pay attention to the reliability and validity of cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020).
-It remains challenging to find reliable and valid tasks that can capture individual differences within one community, let alone finding tasks that can be applied across different cultural settings.
-
-Second, adapting tasks to diverse cultural settings and re-assessing their validity and reliability might be especially important in the social-cognitive domain.
-If, in theory, stimuli used in social cognition tasks should depict people's everyday experiences, the tasks need to represent different social and cultural environments.
+Adapting tasks to diverse communities and re-assessing their validity and reliability might be especially important in the social-cognitive domain.
+If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, the tasks need to represent different communities.
 Indeed, task performance can be diminished when stimuli are not adjusted (Peña, 2007).
 For example, Elfenbein and Ambady (2002) found better emotion recognition for members of the same national, ethnic, or regional group.
-Selcuk et al.
-(2023) concluded that children often attribute mental states more accurately and more frequently to individuals from the same cultural group.
+Selcuk et al. (2023) concluded that children often attribute mental states more accurately and more frequently to individuals from the same community.
 This underlines the importance of adapting tasks to each specific cultural context.
 
-Broadly speaking, there are two different approaches that researchers can take to collect data that is comparable across cultural settings.
-One approach would be to translate the psychological construct into an individually designed study for each cultural setting.
-While this approach is most flexible and sensitive to cultural differences, it might be most feasible for studying up to a handful communities.
-Examples for studies that followed this approach are Mehta et al.
-(2011), Stengelin et al.
-(2020), Chasiotis et al.
-(2006).
-However, recent articles call for the inclusion of more field sites in cross-cultural studies (e.g., Krys et al., 2024).
-The approach of individually re-designing a study for each community might then become too demanding and time-consuming.
-Another approach would be to use the same standardized procedure across diverse cultural settings.
-This approach is less sensitive to each community's unique characteristics but allows for a direct comparison of data across cultural settings.
+Broadly speaking, there are two different approaches that researchers can take to collect cross-cultural data.
+One approach would be to translate the psychological construct into an individually designed study for each community (termed ``assembly''; He and Vijver (2012), Waschl and Chen (2022)).
+While this approach is most flexible and sensitive to cultural differences, it might be most feasible for studying up to a handful of communities as it becomes too demanding and time-consuming.
+Most importantly, this approach assumes that the measured underlying concept is the same, while absolute task scores are not comparable across the communities.
+Another approach would be to use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of culturally inappropriate stimuli (termed ``adoption'' and ``adaptation'', respectively; He and Vijver (2012), Waschl and Chen (2022)).
+This approach is less sensitive to each community's unique characteristics but allows for a direct comparison of the data across communities.
 Examples following this approach include Callaghan et al.
@@
 (2014), Fujita et al.
-(2022).
-This paper aims to describe the development and psychometric properties of a standardized task that can be adapted to different social and linguistic settings.
+(2022), Mehta et al.
+(2011), Stengelin et al.
+(2020), and Chasiotis et al.
+(2006).
+The present paper aims to describe the development and psychometric properties of a standardized task that can be adapted to diverse communities.
 
-The task presented in this manuscript focuses on gaze following, the ability to identify the attentional focus of another agent.
-Gaze following develops early in infancy (Del Bianco et al., 2019; Tang et al., 2024) and contributes to social learning, communication and collaboration (Bohn \& Köymen, 2018; Hernik \& Broesch, 2019; Shepherd, 2010; Tomasello et al., 2007).
-While gaze following acts as one of the most fundamental social-cognitive abilities, studies focusing on cultural variations are rare.
-The few existing results are mixed whether gaze following is influenced by cultural factors or not (Callaghan et al., 2011; Hernik \& Broesch, 2019).
+The task presented here focuses on gaze following, that is, the ability to identify the attentional focus of another agent.
+Gaze following develops early in infancy (Del Bianco et al., 2019; Tang et al., 2024) and contributes to social learning, communication, and collaboration (Bohn \& Köymen, 2018; Hernik \& Broesch, 2019; Shepherd, 2010; Tomasello et al., 2007).
+While gaze following is one of the most fundamental social-cognitive abilities, studies focusing on cultural variations are rare.
+The few existing results are mixed on whether gaze following is influenced by cultural factors or not (Callaghan et al., 2011; Hernik \& Broesch, 2019).
 
-The task presented here builds upon the TANGO (Task for Assessing iNdividual differences in gaze understanding - Open) by Prein, Kalinke, et al.
-(2023).
-The TANGO measures participants' imprecision of locating an agent's attentional focus.
-It has been shown to reliably capture individual differences in a German child sample and an international remote adult sample.
+The task presented here builds upon the TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open) by Prein et al. (2023).
+The TANGO measures participants' imprecision in locating an agent's attentional focus.
+It has been shown to reliably capture individual differences in a German child sample and an English-speaking remote adult sample.
 The task was sensitive to developmental changes and linked to children's receptive vocabulary.
-Furthermore, an exploratory analysis showed that children performed equally well in a study version with animal faces compared to cartoon human faces (Prein, Maurits, et al., 2023).
-Therefore, superficial variations in the stimulus design do not seem to influence children's performance in the task.
+Furthermore, an exploratory analysis showed that children performed equally well in a task version with animal faces compared to cartoon human faces (Prein et al., 2024).
+This suggests that superficial variations in the stimulus design do not influence children's performance in the task.
 
-This paper showcases the TANGO-CC (TANGO - Cross Cultural), a standardized gaze-following task that can be adapted to several languages and cultural settings.
-We describe our reasoning behind the task's development and provide a tutorial for the open-source website (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).
-We present results from a large cross-cultural sample of 2.5- to 11-year-olds from 17 different urban/rural communities across the world and discuss the task's psychometrics.
-The task and all its adaptations have been initially designed for a paper by Bohn et al.
-(2024), and we re-use the data set in this paper.
+This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that can be -- and has been -- adapted to several languages and communities.
+We describe the task's development and provide a tutorial for the open-source website (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).
+We assess its cross-cultural applicability based on data from a large cross-cultural sample of 2.5- to 11-year-olds from 17 different urban/rural communities across the world and discuss the task's psychometrics.
+The task and all its adaptations have been initially designed for a paper by Bohn et al. (2024), and we re-use the data set in this paper.
 
-\hypertarget{task-development}{%
-\section{Task development}\label{task-development}}
+\section{Task development}\label{task-development}
 
-\hypertarget{approach}{%
-\subsection{Approach}\label{approach}}
+\subsection{Approach}\label{approach}
 
-In a perfect world, developing a cross-cultural task would include international collaboration and diverse samples from the beginning, already during piloting and item selection.
-As this seems hardly feasible, we present an alternative, pragmatic approach to developing a task that can be applied across different communities.
-This approach has its faults.
-However, we later present results that show that our task adaptation yielded stable, clear results across a wide range of communities.
+In a perfect world, developing a cross-cultural task would include international collaboration and diverse samples from the beginning, already during study design, piloting and item selection.
+As this seems hardly feasible, we present a pragmatic approach.
+The TANGO-CC was first implemented in one context, in our case Leipzig, Germany (Prein et al., 2023).
+Here, the task's reliability and validity were assessed in detail.
+Even though this does not guarantee that the task will be valid and reliable in another context, it substantially increases the likelihood.
+Second, we reassessed the TANGO--CC's measurement quality (i.e., variability and reliability) across diverse communities by analyzing the data from Bohn et al.
+(2024), who used the task to collect data in 17 communities.
+Therefore, our procedure maintains a balance between a detailed analysis of the task's psychometric properties and a swift and feasible task adaptation.
+In the following, we describe the different steps in further detail.
+We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful for other researchers.
 
-Our general approach to developing the TANGO-CC consisted of two main parts.
-First, the task was implemented in one context, in our case with a German sample (the TANGO; (Prein, Kalinke, et al., 2023)).
-In this context, we assessed the task's reliability and validity in detail.
-Even though this does not guarantee that the task will work in another context, we believe it increases the chances.
-Second, we collaborated with cross-cultural researchers and expanded the stimulus pool to diverse cultural and linguistic settings.
-Bohn et al.
-(2024) collected data in 17 communities worldwide.
-We assessed performance across trial types and checked for individual differences.
-If we found individual differences in other communities to a similar degree to the German sample, it was likely that these individual differences were also systematic.
-This would be, for example, less likely if we saw floor- or ceiling effects.
-Reliability was estimated using internal consistency measures.
-Therefore, our procedure tried to maintain a balance between a detailed analysis of the task's psychometric properties across communities and a swift and feasible task adaptation.
-In the following, we describe the different steps in further detail.
-Even though we focus on the cross-cultural adaptation of the TANGO, we believe the general approach might be helpful for other researchers who aim to design cross-culturally adaptable tasks.
+In the first step, the task's underlying structure was designed.
+The TANGO--CC measures the precision with which participants locate an agent's attentional focus.
+The participant's task is to locate a target by following the agent's gaze (see Figure \ref{fig:fig1}).
+Precision was measured in a continuous way as the distance between the participant's click on the screen (\emph{i.e.}, where the participant thinks the target is) and the target's real position.
+The task's core functionality is to animate the agent's eyes so that they follow the target's movement.
+This basic structure was then embedded in the task's superficial appearance (e.g., background scene) and audio instructions.
+Once this structure was implemented, adaptations of the task were greatly simplified.
+For example, we can change the background scene, the faces of the agent, and the target without changing how and what the task measures.
 
-In the first step, we designed the task's underlying functionality.
-We aimed for a measure that maps directly onto the task's underlying psychological construct: in our case, the imprecision with which participants can locate an agent's attentional focus.
-We were motivated to create a continuous outcome measure since this allows for more room to capture individual differences.
-The core of the task was calculating where the agent's eyes must move to follow the target's movement.
-In the next step, this structure was filled with the task's superficial appearance and audio instructions.
-Notably, the task's presentation can be adjusted without changing its underlying structure.
-For example, we can change the background scene, the faces of the agent, and the target without changing the logic of where the agent looks or the participants' task to identify an agent's attentional focus.
-We realized that as soon as the task's underlying structure was implemented, adaptations of the task and data collection efforts were greatly simplified.
+This basic version of the TANGO was psychometrically evaluated in a prototypical WEIRD sample (German child sample; English-speaking remote adult sample) and was found to be highly reliable and valid (Prein et al., 2023).
+While participants got more and more precise in locating the attentional focus of the agent the older they were, individuals differed across all age groups and showed no floor- or ceiling effects.
+Performance in the TANGO was linked to children's receptive vocabulary and weakly related to factors of children's daily social environment.
+In another study, Prein et al. (2024) proposed a computational cognitive model that described gaze following as a social form of vector following.
+Gaze following, as measured by the TANGO, was related to children's non-social vector following and visual perspective-taking abilities.
+These connections to related constructs indicate the task's validity in the tested WEIRD setting.
 
-After implementing the task, we assessed the psychometric properties of the TANGO in a WEIRD sample.
-We collected data of a German child sample and an international remote adult sample (Prein, Kalinke, et al., 2023).
-The adult sample worked as a proof-of-concept and showed that remote data collection worked very well.
-We reasoned that if we find individual differences in an adult sample, chances are high that we also find them in a child sample, as adults usually exhibit less variation in abilities than children.
-The task captured a developmental change and showed neither floor nor ceiling effects.
+To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces that were judged by researchers and research assistants from each target community to be representative of the local population (see Figure \ref{fig:fig1}).
+Similarly, different backgrounds were created that roughly represented a typical accommodation in each community.
+Audio instructions were translated into the corresponding local language.
+By back-translating these instructions, we ensured the original meaning did not change.
+Sometimes, specific words were linguistically slightly modified, although functionally equivalent (e.g., ``bush'' instead of ``hedge''), to ensure that all participants understood the instructions.
+In the following, we describe how researchers can use and customize the TANGO--CC in more detail.
 
-Most importantly, we found individual differences across all age groups.
-By evaluating split half- and retest reliability estimates, we could show that the individual variation was systematic and not just random noise.
-Additionally, we assessed the task's validity by examining the relationship with theoretically related concepts.
-Performance in the TANGO was linked to children's receptive vocabulary and weakly related to factors of children's daily social environment (Prein, Kalinke, et al., 2023).
-In another study, we proposed a computational cognitive model that described gaze following as a social form of vector following.
-Gaze following, as measured by the TANGO, was related to children's vector following and visual perspective-taking abilities (Prein, Maurits, et al., 2023).
-These connections to related constructs speak toward the task's validity in the German setting.
-An exploratory analysis showed that performance in the TANGO was similar when presenting animal vs.~human faces (Prein, Maurits, et al., 2023 supplements).
-This demonstrates that the participants' performance did not depend on superficial features of the task's appearance.
+\subsection{Features of the TANGO--CC}\label{features-of-the-tangocc}
 
-As a next step, we contacted cross-cultural researchers and field assistants interested in using the TANGO.
-We asked local people to give input as to how we could adapt the task to their local needs.
-Together with their help, we generated a set of 50 diverse human faces that were aimed to be representative of each local population.
-Similarly, different backgrounds were created that roughly represented a typical accommodation in each community.
-Research assistants translated the audio instructions into the corresponding local language.
-By back-translating these instructions, we ensured the original meaning did not change.
-Sometimes, specific words were linguistically slightly modified, although functionally equivalent (e.g., ``bush'' instead of ``hedge'') to ensure that all participants understood the instructions.
-Before collecting data in each community, we piloted with a small sample.
-This procedure slightly varied between communities; see supplements for further details.
-In the following, we describe the design features of the TANGO-CC in greater detail.
+\subsubsection{Trials}\label{trials}
 
-\hypertarget{features-of-the-tango}{%
-\subsection{Features of the TANGO}\label{features-of-the-tango}}
-
-The task presented in this manuscript is the cross-cultural adaptation of the TANGO (Prein, Kalinke, et al., 2023).
-We quickly recap the TANGO's most characteristic features: Participants are asked to locate a balloon with the help of a gaze cue.
-The outcome variable is the distance between the participant's touch and the balloon's center.
-Trials can be completed in a fast and efficient way, so that children can easily complete 15 trials within 10 min.
-This drastically reduced drop-out rates.
-By using essentially self-explanatory animations, language demands are kept to a minimum.
-To keep trials comparable and avoid learning effects, no differential feedback is given.
-
-\hypertarget{task-implementation}{%
-\subsubsection{Task implementation}\label{task-implementation}}
-
-The task was implemented in \texttt{JavaScript}, \texttt{HTML}, and \texttt{CSS}, and is presented as a web app.
-It can be accessed on any web browser and does not require prior installation.
-The online version of the task has been proven convenient for unsupervised data collection (for example, using participant recruitment services like \emph{Prolific}, see Prein, Kalinke, et al.
-(2023)), and sharing the task across big international collaborations.
-Importantly, the web app implementation does not necessarily need a working WIFI connection: An offline, local version of the task can be quickly set up for devices that support Node.js (\url{https://nodejs.org/en}).
-This is an especially useful feature for researchers working in remote areas with limited internet access.
-
-The stimuli are embedded as Scalable Vector Graphics (SVG).
-The setup allows for an easy adaptation of study elements and ensures that picture quality, aspect ratio and relative object positioning are constant.
-We implemented some features designed to ensure meaningful clicking responses.
-The study is programmed so that responses are only registered when the participant touches the relevant part of the screen (i.e., in test trials the hedge).
-Furthermore, clicks are only registered after the voice recordings stopped playing.
-If no click is registered within 5 seconds, an audio reminder is played again.
-
-The website does not use cookies, nor does it upload any data to servers; that is, the data is only stored locally on the device.
-The output of the study is a CSV file that contains the participants' responses and can be easily imported into statistical software for further analysis.
-The saved variables are: id, language, background, trial\_number, study\_phase, audio\_instructions, keep\_trial, agent, balloon\_color, balloon\_bin, balloon\_center, click, absolute\_click\_distance, timestamp, responsetime\_ms.
-In case a webcam recording was selected, a second file is saved that contains the webcam recording (WEBM file).
-The files will be stored in the device's downloads folder and is named after the following pattern: ``tangoCC-participantID-YYYY-MM-DD\_hh\_mm\_ss''.
-
-\hypertarget{trial-types}{%
-\subsubsection{Trial types}\label{trial-types}}
-
-The task consists of three different trial types.
-In every trial, participants see an agent (boy or girl) looking out of house, with a balloon (red, blue, green or yellow) in front of them.
+We quickly recap the TANGO's (Prein et al., 2023) most characteristic features: Participants are asked to locate a balloon with the help of a gaze cue.
+The task consists of three different trial types (see Figure \ref{fig:fig1}).
+In every trial, participants see an agent (boy or girl) looking out of a house with a balloon (red, blue, green, or yellow) in front of them.
 The balloon falls down to the ground, while the eyes of the agent follow the movement of the balloon in a way that their centers always align.
@@
 In training 1, participants see the full trajectory of the balloon and directly have to touch the balloon itself.
-In training 2, participants see most of the balloon's movement but the final location is covered by a hedge.
-In test trials, a hedge grows in the beginning of the trial and participants see neither the movement nor the final position of the balloon.
-The first trial of each type contains an audio description of the presented events (see Supplements).
-Importantly, the instructions explicitly state that the agent is looking at the balloon.
+In training 2, participants see most of the balloon's movement, but a hedge covers the final location.
+In test trials, a hedge grows at the beginning of the trial and participants see neither the movement nor the final position of the balloon.
+The first trial of each type contains an audio description of the presented events (see supplements of Bohn et al. (2024)).
+Notably, the instructions explicitly state that the agent is looking at the balloon.
 
-\hypertarget{randomization}{%
-\subsubsection{Randomization}\label{randomization}}
+The outcome variable is the distance between the participant's touch and the balloon's center.
+Trials can be completed quickly and efficiently so that children can easily complete 15 trials within 10 minutes.
+This drastically reduces drop-out rates.
+By using essentially self-explanatory animations, language demands are kept to a minimum.
+No differential feedback is given to keep trials comparable and avoid learning effects.
+
+\subsubsection{Randomization}\label{randomization}
 
 The order of the agents, balloon colors (red, yellow, green, blue), and balloon positions are each randomized independently.
-For the balloon positions, the full width of the screen (1920 in ``SVG unit'') is divided into ten bins.
+For the balloon positions, the entire width of the screen (1920 in ``SVG units'') is divided into ten bins.
 Exact coordinates (value between 0 far left and 1920 far right) within each bin are then randomly generated.
@@
 
-\hypertarget{cross-cultural-customization}{%
-\subsection{Cross-cultural customization}\label{cross-cultural-customization}}
+\subsubsection{Cross-cultural customization}\label{cross-cultural-customization}
 
-The TANGO-CC expands the stimulus pool of the TANGO by depicting human faces and different languages for the audio instructions.
-The TANGO-CC can be accessed here: (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).
-Researchers can customize the following parts of the task.
-In the first step, researchers can enter an alphanumeric participant identifier (1 - 8 characters).
-Audio instructions are currently available in 13 different languages (and even more dialects): Bayaka (Rep.~Congo), Bemba (Zambia), Chinese (China), English (India), English (New Zealand), English (Nigeria), English (UK), English (USA), German (Germany), Hai\textbar\textbar om (Namibia), Khewdam (Namibia), Lingala (Rep.~Congo), Marathi (India), Shona (Zimbabwe), Spanish (Argentina), Spanish (Mexico), Swahili (Uganda), Turkish (Türkiye).
-Please note that the written instructions are always in English, however, children are not required to understand them (directed to the research assistants).
-A webcam recording of the participant can be enabled to record the participant's behavior during the task.
-Please ensure appropriate data protection measures are in place before enabling this feature.
-The study can either be started with default settings (depending on the chosen language: the stimuli which have been used by our reported samples here will be shown), or further customized.
+The TANGO--CC can be accessed via the following link: (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).
+In the first step, researchers can select the language for audio instructions, currently available for 13 different languages and even more dialects (see Table 1).
+All written instructions are presented in English because they are not directed to the participant but to the research assistant who guides the participant through the task.
+The task can either be started with the default settings or further customized.
+The default settings use the version applied in Bohn et al. (2024) based on the selected language.
 
-If researchers choose to further customize, the number of trials can be chosen for each trial type.
-No trial type can be skipped, so the minimum number of trials per type equals 1, the maximum equals 100.
+If researchers choose to customize the task (see Figure \ref{fig:fig1}), the number of trials can be chosen for each trial type.
 As the trial types build up on each other, each trial type is necessary to understand the structure of the task and needs to be completed before the next trial type starts.
-One out of four different backgrounds can be picked.
+Therefore, no trial type can be skipped.
+The minimum number of trials per type is 1; the maximum is 100.
+One out of four different backgrounds can be selected.
 Finally, there are 50 diverse human faces (50\% female, 50\% male) from which researchers can choose.
-There is no constraint on how many faces are allowed (min 1, max 50).
-Once all the settings are adjusted, the task can be started.
+No constraint exists on how many faces are allowed (min 1, max 50).
+Once all the settings are adjusted, the customized task is compiled.
 
-We have compiled an instruction manual with the most frequently asked questions (\url{https://ccp-odc.eva.mpg.de/tango-cc/manual.html}).
-The source-code of the task is available on GitHub (\url{https://github.com/ccp-eva/tango-cc}).
-By edited the \texttt{HTML} and \texttt{JavaScript} code directly, researchers gain even more flexibility in adjusting the task to their needs.
+In the last step, researchers can enter an alphanumeric participant identifier (1 - 8 characters) and enable a webcam recording of the participant, if needed.
+To save the selected settings, researchers can bookmark the URL so that the customized task can be easily accessed, and only the participant ID and choice of webcam recording need to be entered again.
+The task can then be started.
+
+The source code of the task is available on GitHub (\url{https://github.com/ccp-eva/tango-cc}).
+By directly editing the \texttt{HTML} and \texttt{JavaScript} code, researchers gain even more flexibility in adjusting the task to their needs.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:langtab}Languages available for the audio instructions in the TANGO--CC}
+
+\begin{tabular}{lll}
+\toprule
+Languages & \multicolumn{1}{c}{Language family} & \multicolumn{1}{c}{Speaker's country of origin}\\
+\midrule
+Bemba & Bantu & Zambia\\
+Chinese & Sino-Tibetan & China\\
+English & Indo-European & USA / UK / India / Nigeria / New Zealand\\
+German & Indo-European & Germany\\
+Hai||om & Khoesan & Namibia\\
+Khewdam & Khoesan & Namibia\\
+Lingala & Bantu & Rep. Congo\\
+Marathi & Indo-European & India\\
+Shona & Bantu & Zimbabwe\\
+Spanish & Indo-European & Argentina / Mexico\\
+Swahili & Bantu & Uganda\\
+Turkish & Turkic & Türkiye\\
+Yaka & Bantu & Rep. Congo\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../figures/tango-cc-procedure}
+{\centering \includegraphics[width=1\linewidth]{../figures/TANGO-CC-procedure}
 
@@
 
-\caption{\textbf{Customizable components of the TANGO-CC.} Researchers can select the language of the audio instructions, the number of trials per trial type, the background, and the agent's face.
-Screenshots of the trial show the proceeding events: in Training 1, an agent looks at a balloon that falls to the ground and participants have to respond by touching the balloon.
-In Training 2, the balloon falls behind the hedge, while its flight is still visible.
+\caption{\textbf{Customizable components of the TANGO--CC.} Researchers can select the language of the audio instructions, the number of trials per trial type, the background, and the agent's face.
+Screenshots of the trials show the proceeding events: In training 1, an agent looks at a balloon that falls to the ground, and participants have to respond by touching the balloon.
+In training 2, the balloon falls behind the hedge while its flight is still visible.
 Participants respond by touching the hedge where they think the balloon is.
-In Test trials, the balloon's movement and final position are covered by a hedge and participants respond by touching the hedge.
+In test trials, the balloon's movement and final position are covered by a hedge, and participants respond by touching the hedge.
 In the task, all movements are smoothly animated (no still pictures).
-Yellow frames indicate the timepoint when participants respond (only illustrative, not shown during the task).}\label{fig:fig1}
+Yellow frames indicate the time point when participants respond (only illustrative, not shown during the task).}\label{fig:fig1}
 \end{figure}
 
-\hypertarget{data-collection}{%
-\section{Data collection}\label{data-collection}}
+\subsubsection{Task implementation}\label{task-implementation}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+The task was implemented in \texttt{JavaScript}, \texttt{HTML}, and \texttt{CSS} and is presented as a web app.
+It can be accessed on any web browser and does not require prior installation.
+The online version of the task has been proven convenient for unsupervised data collection (for example, using participant recruitment services like \emph{Prolific}; see Prein et al.
+(2023)) and sharing the task internationally.
+Importantly, the web app implementation does not necessarily need a working WIFI connection: An offline, local version of the task can be quickly set up for devices that support Node.js (\url{https://nodejs.org/en}).
+This is an especially useful feature for researchers working in remote areas with limited internet access.
 
-The here used data set has been published by (Bohn et al., 2024).
-The sample includes \emph{N} = 1372 children between 2.5 to 11 years of age.
-Participants come from 17 communities in rural and urban settings on five continents with varying degrees of market integration and technology exposure.
+The stimuli are embedded as Scalable Vector Graphics (SVG).
+The setup allows for an easy adaptation of task elements and ensures that picture quality, aspect ratio, and relative object positioning are constant.
+The task is programmed so that responses are only registered when the participant touches the relevant part of the screen (i.e., in test trials, the hedge).
+Furthermore, clicks are only registered after the voice recordings stop playing.
+An audio reminder is played again if no click is registered within 5 seconds.
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+The website does not use cookies, nor does it upload any data to servers; that is, the data is only stored locally on the device.
+The output of the task is a CSV file (and WEBM file if a webcam recording was selected) that contains the participants' responses and can be easily imported into statistical software for further analysis.
+The file will be stored in the device's downloads folder and is named after the following pattern: ``tangoCC-participantID-YYYY-MM-DD\_hh\_mm\_ss''.
 
-We collected data using offline and online versions of the TANGO-CC on a Windows tablet.
-A local research assistant guided the children through the study.
-We instructed the research assistants to motivate the children and guide their attention to the screen, while explicit feedback (e.g., praise for a precise click) and hints (e.g., ``look at the eyes'') were not allowed.
+\section{Psychometric evaluation}\label{psychometric-evaluation}
 
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
+\subsection{Data set}\label{data-set}
 
-As a first feasibility check, we inspected the mean and standard deviations by community and compared performance in each trial type (training 1, training 2, test trials).
-Since the age distribution across communities varied slightly, test trials were further analysed by performing a model-based age correction.
-A Generalized Linear Mixed Model (GLMM) was fitted with the mean imprecision as the outcome, age as a predictor and participant id as random effects: \texttt{imprecision\ \textasciitilde{}\ age\ +\ (1\ \textbar{}\ subjid)}.
-Furthermore, the within- an between-community variance and the intraclass correlation (ICC) were calculated.
+We used the data set from Bohn et al. (2024) for the psychometric evaluation of the TANGO--CC.
+They collected data using the TANGO--CC in a sample of \emph{N} = 1377 children between 2.5 to 11 years of age.
+Participants came from 17 communities on five continents, in rural and urban settings, with varying degrees of market integration and technology exposure.
+Bohn et al. (2024) carried out 19 trials (1 training 1, 2 training 2, and 16 test trials, of which the first of each type had audio instructions).
+Faces, backgrounds, and languages were chosen by researchers and assistants with experience in the specific community.
+For further details on the communities and data collection procedures, see the supplements of Bohn et al. (2024).
+
+\subsection{Individual differences}\label{individual-differences}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/TANGO-CC-results}
+
+}
+
+\caption{\textbf{Measurement of the TANGO--CC by community.} (A) Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type.
+Imprecision is defined as the distance between the participant's touch and the balloon's center in units of balloon width.
+For a depiction of each trial's procedure, see Figure \ref{fig:fig1}.
+(B) Internal consistency estimates by community, following three different approaches.
+In the odd-even split, the size of points reflects the sample size in each community.
+In the stratified approach with and without age correction, density curves show the posterior distributions of the GLMM.}\label{fig:fig2}
+\end{figure}
+
+First, we inspected the mean and standard deviations by community and compared performance in each trial type (training 1, training 2, test trials).
+Performance was defined as the absolute click distance between the target center and the click x coordinate (measured in balloon widths).
+Across communities, children performed best in training 1 (mean = 0.19, sd = 0.63), followed by training 2 (mean = 0.79, sd = 1.44) and test trials (mean = 2.21, sd = 2.03; see Figure \ref{fig:fig2}A).
+
+To formally estimate the effect of trial type on performance in the TANGO--CC, we fit a generalized linear mixed model (GLMM) predicting the task performance by trial type (reference category: test trials).
+All analyses were run in R version 4.4.0 (2024-04-24) (R Core Team, 2024).
+GLMMs were fitted with default priors using the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017, 2018).
+The model included random effects for trial type by community (model notation in \texttt{R:\ imprecision\ \textasciitilde{}\ trialtype\ +\ (trialtype\ \textbar{}\ community)}), and imprecision was modeled by a \texttt{lognormal} distribution.
+We inspected the posterior distribution (mean and 95\% Credible Interval (CrI)) for the trial type estimates.
+
+Our GLMM analysis supported the visual inspection of the data: the fixed-effect estimates for training 1 (\(\beta\) = -3.26; 95\% CrI {[}-3.41; -3.10{]}) and training 2 (\(\beta\) = -1.47; 95\% CrI {[}-1.58; -1.35{]}) were negative and reliably different from zero.
+Please note that the TANGO--CC measures imprecision in gaze following.
+Therefore, a negative sign shows that children showed less imprecision (i.e., were more precise) in the training trials than in the test trials.
+This effect was found across all communities (random effects of trial type within community: minimum estimate for training 1 = -2.87; 95\%CrI {[}-3.11; -2.60{]}; minimum estimate for training 2 = -1.27; 95\%CrI {[}-1.51; -0.98{]}).
+The almost perfect performance in training trials indicated that children understood the task and were able to locate the balloon.
+In test trials, children's imprecision was higher, indicating that the task was more challenging.
+All communities showed substantial individual variation and overlapped in their imprecision levels (see Figure \ref{fig:fig2}A).
+
+To identify the sources of variation, we computed intraclass correlations (ICC).
+The variation of children within communities was substantially larger than the variation between the communities.
+The mean within-community variance was 1.28, ranging from 0.24 (in Pune, India) to 3.46 (in Chimfunshi, Zambia).
+Between-community variance was 0.34.
+The ICC, representing the proportion of between-community variance relative to the total variance (sum of within- and between-community variance), was 0.02.
+This indicates that only 2\% of the total variability in the data can be attributed to differences between communities, while the remaining 98\% are attributed to differences within communities (Kusano et al., 2024).
+
+\subsection{Reliability}\label{reliability}
 
@@
 First, data of each participant was split into odd and even trials and a Pearson correlation was calculated between the aggregated scores of the two halves.
-Second, using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2022), data was stratified by target centrality and a Pearson correlation was calculated between the matched halves.
-Third, an age correction was performed for the stratified approach by fitting a GLMM with the mean imprecision as the outcome, age as a predictor and test half and participant id as random effects: \texttt{imprecision\ \textasciitilde{}\ age\ +\ (0\ +\ half\ \textbar{}\ subjid)}.
-This process was repeated 50 times for each community.
-The posterior estimate of the correlation between the two person-specific estimates is taken as the age-independent estimate for internal consistency.
+Second, using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2022), data was stratified by target centrality (capturing trial difficulty), and a Pearson correlation was calculated between the matched halves.
+Third, a data set was generated with stratified test halves by target centrality.
+Then, we followed the Generalized Linear Mixed Model (GLMM) approach introduced by Rouder and Haaf (2019).
+A GLMM was fitted with the mean imprecision as the outcome, age as the predictor, and test half and participant id as random effects (model notation: \texttt{imprecision\ \textasciitilde{}\ age\ +\ (0\ +\ half\ \textbar{}\ subjid)}).
+The model estimates correlations between participant-specific estimates for each test half.
+The hierarchical shrinkage of the model enables accurate person-specific estimates.
+By incorporating age as a fixed effect, the correlation between the two person-specific estimates represents the age-independent estimate for internal consistency.
+This eliminates the chance that a good internal consistency estimate results from general cognitive development rather than task-specific inter-individual differences.
+Because the process of generating stratified data sets is partly random, the model was fitted 50 times for each community.
+The posterior estimate of the correlation between the two person-specific estimates was taken as the age-independent estimate for internal consistency.
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+The results are shown in Figure \ref{fig:fig2}C.
+Across communities, internal consistency estimates ranged from 0.51 to 0.80 for the odd-even split, 0.62 to 0.89 for the stratified internal consistency, and 0.62 to 0.87 for the age-corrected approach (Plymouth, UK, being an outlier with 0.28).
+Following Cohen's suggestions (Cohen, 1988, 1992), these correlations constitute large effects (\emph{r} \textgreater{} .50), and indicate good internal consistency.\footnote{Note that for scale reliability and Cronbach's \(\alpha\), values of .7 to .8 have been suggested to be acceptable (Field et al., 2012; Kline, 1999).
+However, Kline (1999) suggested that values below .7 could be realistic for psychological constructs due to their variable nature.}
+The results are comparable to the internal consistency estimates found in the original TANGO study (Prein et al., 2023), and also resemble reliability estimates of classical false belief tasks (Hughes et al., 2000).
 
-\begin{figure}
+In an exploratory analysis, we found that communities with larger individual variation showed higher internal consistency estimates (Pearson's \emph{r} = 0.46, 95\%CI {[}-0.03; 0.77{]}).
+Please note that this could be influenced by outliers and that the sample size here (\emph{N} = 17 communities) is too small to make substantial claims.
 
-{\centering \includegraphics[width=1\linewidth]{../figures/tango-cc-results}
+\section{Discussion}\label{discussion}
 
-}
+The TANGO--CC measures imprecision in gaze following across individuals, ages, and communities.
+The task was developed in two phases.
+First, the task's underlying functionality was designed in one community.
+Next, we adapted the superficial features of the task to be used in 17 diverse communities and assessed the task's psychometric properties.
+Children's imprecision in gaze following highly overlapped between communities: children performed better in the training than the test trials, and within-community variation greatly exceeded between-community variation.
+The task showed satisfactory to high reliability across all communities.
+Therefore, we believe the TANGO--CC is a promising task to capture individual differences in social-cognitive development in diverse communities.
+Its design process lays out a much-needed pragmatic approach to conducting cross-cultural individual differences research.
 
-\caption{\textbf{Measurement of the TANGO-CC by community and trial type.} (A) Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type.
-Imprecision is defined as the distance between the participant's touch and the balloon's center, in units of balloon width.
-For a depiction each trial's procedure, see Figure 1.
-(B) Age-corrected imprecision in test trials by community.
-White lines (\textbar) show the person-specific model predictions.
-(C) Internal consistency estimates by community, following three different approaches.
-In the odd-even split, the size of points reflects the sample size in each community.}\label{fig:fig2}
-\end{figure}
+A similar approach to task development was taken by Mehta et al. (2011).
+The researchers (1) selected social cognition measures that have been established in WEIRD settings, (2) adapted the agent's names, appearance, backgrounds, and languages to the local context, and (3) assessed the task's validity and internal consistency in the new setting.
+Participants were adults with and without schizophrenia from India. Theory of Mind tasks included Sally-Anne, Smarties, Ice cream van and Missing cookies stories.
+For this specific context, the authors' approach yielded a successful adaptation of social cognition measures for the tested Indian (Hindi/Kannada) communities.
 
-Across communities, children performed best in training 1, followed by training 2 and test trials (see Figure \ref{fig:fig2}A).
-The almost perfect performance in training trials indicated that children understood the task and were able to locate the balloon.
-In test trials, children's imprecision was higher, indicating that the task was more challenging.
-The TANGO-CC captured individual differences across ages and communities.
-A model-based age correction (see Figure \ref{fig:fig2}B) provided evidence that the variation between individuals existed beyond the effect of age.
-All communities showed great individual variation and overlapped massively in their imprecision levels.
+Bourdage et al. (2023) pointed out a major challenge with adapting social cognition tasks to diverse communities: the number of world cultures is vast, and communities are constantly changing.
+Therefore, a promising approach might be to provide tasks with a modular system where components can be exchanged according to the local context.
+In the case of the TANGO--CC, the task can not only be adapted to different languages, cartoon faces, and backgrounds (see Figure \ref{fig:fig1}) but also updated with new stimuli.
+Unlike studies that present sequential, hand-painted pictures that are difficult to adapt (Mehta et al., 2011), the TANGO--CC uses SVGs that can be easily exchanged.
 
-Variation of children within one community was greater than the variation between the communities.
-The mean within-community variance was 1.28, ranging from 0.24 (in Pune, India) to 3.46 (in Chimfunshi, Zambia).
-Between-community variance was 0.34.
-The intraclass correlation (ICC), representing the proportion of between-community variance relative to the total variance (sum of within- and between-community variance) was 0.02.
+The biggest strength of the TANGO--CC is its flexibility.
+The task is presented as a web app that can also run offline to enable remote data collection.
+Minimal language demands and an engaging, playful design increase the task's usability.
+Together with a short task duration, this reduces drop-out rates and enables efficient data collection with large sample sizes.
+The TANGO--CC follows a standardized procedure and uses a continuous, objective outcome measure (leaving no room for rater errors).
+An online manual with the most frequently asked questions is available at \url{https://ccp-odc.eva.mpg.de/tango-cc/manual.html}.
+Additional customization can be achieved by adding new stimuli to the open-source code available on GitHub (\url{https://github.com/ccp-eva/tango-cc}).
 
-To see whether these differences were reliable, we assessed the task's internal consistency.
-The results from a simple odd-even split and the splithalf-reliability stratified by target centrality with and without model-based age correction yielded comparable results and are shown in Figure \ref{fig:fig2}C.
-Across all communities, the task showed satisfactory to high reliability, with estimates ranging roughly between 0.5 and 0.9 (Plymouth, UK, being an outlier in the stratified, age-corrected internal consistency).
-In an exploratory analysis, we found that communities with larger individual variation showed higher internal consistency estimates.
-Please note that this could be influenced by outliers and that the sample size here (\emph{N} = 17 communities) is very small to make substantial claims.
-
-As data collection across communities was organized slightly differently, we cannot report drop-out rates by community.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-We have presented a new task, the TANGO-CC, that measures imprecision in gaze following across individuals, ages, and communities.
-The task development took place in two main phases.
-First, we implemented the task's underlying functionality in one community and established validity and reliability in this setting (Leipzig, Germany).
-In the next step, we collaborated with cross-cultural researchers to create a larger stimulus pool.
-In this paper, we presented data from 17 different communities across the world and discussed the TANGO-CC's psychometrics.
-Children's imprecision in gaze-following highly overlapped between communities: children performed similarly in training and test trials, and within-community variation greatly exceeded between-community variation.
-The task showed satisfactory to high reliability across all communities.
-Therefore, we believe the TANGO-CC is a promising tool to capture individual differences in social-cognitive development in diverse social-cultural environments.
-
-A similar approach to task development was followed by Mehta et al.
-(2011).
-The researchers (1) selected social cognition measures that have been established in other settings, (2) adapted the agent's names, appearance, backgrounds, and languages to the the local context, and (3) assessed the task's validity and internal consistency in the new setting.
-Their approach yielded a successful adaptation of social cognition measures for Indian (Hindi/Kannada) communities.
-Yet, Bourdage et al.
-(2023) have argued that adapting social cognition tasks to each individual community is infeasible: the number of world cultures is vast and communities are constantly changing.
-A promising approach, as taken by the TANGO-CC, might be to provide tasks with a modular building block system, where components can be exchanged according to the local context.
-
-The biggest strength of the TANGO-CC is its flexibility: researchers can can choose from different agents, languages, trial numbers and background scenes (see Figure \ref{fig:fig1}).
-The task is presented as a web-app, which can also run offline to enable remote data collection.
-Minimal language demands and an engaging, playful design increase the task's comprehensibility.
-Together with a short study duration, this reduces drop-out rates and enables efficient data collection with large sample sizes.
-The TANGO-CC follows a standardized procedure and uses a continuous, objective outcome measure (leaving no room for rater errors).
-An online manual with the most frequently asked questions is available at \url{https://ccp-odc.eva.mpg.de/tango-cc/manual.html}.
-Even more customization can be achieved by adding new stimuli to the open-source code available on GitHub (\url{https://github.com/ccp-eva/tango-cc}).
-
-Since years, researchers haved called for more diverse sampling and culturally valid social cognition measures (Matsumoto \& Yoo, 2006; e.g., Mehta et al., 2011; Nielsen et al., 2017).
+For years, researchers have called for more diverse sampling and culturally valid measures of cognitive development (Matsumoto \& Yoo, 2006; e.g., Mehta et al., 2011; Nielsen et al., 2017).
 As Hajdúk et al.
 (2020) put it, ``using large samples and multisite approaches will align with efforts to improve reproducibility and will clarify both the type and extent of cultural influences on social cognition'' (p.~463).
-The TANGO-CC takes a valuable step in this direction by including large sample sizes from diverse communities and sharing both the data set and the task itself to other researchers.
-In this manuscript, we could show that data collection with the TANGO-CC was feasible in 17 diverse communities, in rural and urban settings with varying degrees of market integration and technology exposure.
-While we cannot generalize our findings to all communities world-wide, we found that it worked well in the 17 communities that took part in this study.
-However, we do not want to signal that cross-cultural research is easy or that data can be collected remotely without a lot of effort.
-We want to emphasize that using the TANGO-CC in a new community of course needs sensitivity to the specific context, piloting and, most importantly, input from local collaborators.
-We hope that the TANGO-CC will facilitate future cross-cultural studies to assess social-cognitive development in a wide range of communities.
+The TANGO--CC takes a valuable step in this direction by sharing the task and its source code with other researchers.
+Bohn et al. (2024) showed that data collection with the TANGO--CC was feasible in 17 diverse communities in rural and urban settings with varying degrees of market integration and technology exposure.
+While we cannot generalize our findings to all communities worldwide, we found that it captured reliable individual variation in the 17 communities studied by Bohn et al. (2024).
+Using the TANGO--CC in a new community nevertheless requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
+We hope that the TANGO--CC will facilitate future cross-cultural studies to assess social-cognitive development in a wide range of communities.
 
-A valid question is whether the TANGO-CC measures the same construct across different groups.
-This so-called measurement invariance is often seen as a requirement for a ``fair'' cross-cultural comparison and relies on minimizing group differences, while individual differences are magnified.
+A valid question is whether the TANGO--CC measures the same construct across different groups.
+This so-called measurement invariance is often seen as a requirement for a ``fair'' cross-cultural comparison and relies on minimizing group differences while individual differences are magnified.
 As Kusano et al.
 (2024) put it: ``The research challenge is to achieve a balance between ensuring methodological ``fairness'' at the individual level while also recognizing and capturing genuine sociocultural variability'' (p.~34).
-We argue that the TANGO-CC measures a fundamental social-cognitive ability that is likely similar across cultural groups.
-This is also represented in our results, as we found that the within-group variability was greater than the between-group variability.
-Similarly, Selcuk et al.
-(2023) pointed out that researchers should study both the within- and the between-culture variability in the development of social cognition, since sometimes within-culture differences are more influential.
-While we do believe that the TANGO-CC can be used to compare mean differences across cultural settings, we would recommend focusing on linking individual differences to social-cognitive or environmental factors.
+We argue that the TANGO--CC measures a fundamental social-cognitive ability that is likely similar across communities.
+Bohn et al. (2024) have shown that children with no prior touchscreen exposure were less precise in the TANGO--CC than children with prior experience.
+However, individual differences were also found in communities with 100\% touch screen exposure, showing that this factor alone could not explain children's performance in the task (Bohn et al., 2024).
+Notably, even though the touchscreen experience caused absolute differences in task performance, all communities showed the same processing signature.
+A recent computational cognitive model described gaze following as a process of estimating pupil angles and the corresponding gaze vectors (Prein et al., 2024).
+The model predicted that all individuals use the same process to locate an attentional focus but differ in their uncertainty around the estimated pupil angles, which results in less precision.
+Bohn et al. (2024) found clear support for this model in every community they studied, suggesting that children all over the world process gaze in a similar way.
+In this manuscript, we could also show that internal consistency was high across all communities, meaning that the task captured individual differences in a similar way.
+Consequently, the TANGO--CC seems to measure systematic individual differences across diverse communities.
 
-\hypertarget{limitations}{%
-\section{Limitations}\label{limitations}}
+Selcuk et al.
+(2023) pointed out that researchers should study both within- and between-culture variability in the development of social cognition since sometimes within-culture differences exceed between-culture differences.
+Indeed, we found that within-group variability was greater than between-group variability.
+While we believe that the TANGO--CC can be used to compare mean differences across communities, we would recommend using it to study individual differences within communities.
 
-The TANGO-CC and its psychometric properties need to be considered against some limitations.
+\section{Limitations}\label{limitations}
+
+The TANGO--CC and its psychometric properties need to be considered against some limitations.
 Reliability for each community was assessed by calculating the internal consistency.
-Ideally, we would have additionally assessed the task's retest reliability by cultural setting and checked for relationships with theoretically related constructs.
+Ideally, we would have additionally assessed the task's retest reliability in each community and checked for relationships with theoretically related constructs to assess validity.
 
-Schilbach et al.
-(2013) pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions.
-This argument touches on two different points: (1) the mode of stimulus presentation (i.e., online vs.~offline/real-life) and (2) the role of the participant (i.e., active vs.~passive).
-First, potentially, not all children perceive the tablet-based presentation of the TANGO-CC as depicting a social interaction.
-In a German sample, we found that performance in the TANGO was linked to children's visual perspective-taking abilities in real-life social interaction (Prein, Maurits, et al., 2023).
-Arguably, children in this sample recognized the social context of the task.
-However, this could vary between communities: Children with prior TV or computer game exposure might be more inclined to interpret the cartoon-like faces as social stimuli.
-Indeed, Bohn et al.
-(2024) have shown that children with no touchscreen exposure were slightly less precise in the TANGO-CC than children with prior experience.
-Notably, while this caused absolute differences in task performance, all communities showed the same processing signature: more precise responses for more central target locations.
-Furthermore, individual differences were also found in communities with 100\% touch screen exposure, showing that this factor alone could not explain children's performance in the task (Bohn et al., 2024).
-In this manuscript, we could additionally show that internal consistency was high across all communities.
-Nevertheless, the mode of stimulus presentation surely needs to be kept in mind when administering the TANGO-CC, especially in communities with little technology exposure.
+Schilbach et al. (2013) pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions.
+Of course, the TANGO--CC does not depict real-life social interaction, and future research should investigate how task performance relates to the real world.
+Suggestive evidence comes from a study by Prein et al.
+(2024), who found that children's performance in the TANGO was linked to children's visual perspective-taking abilities in real-life social interaction.
+The mode of stimulus presentation surely needs to be kept in mind when administering the TANGO--CC, especially in communities with little technology exposure.
 Additional touch screen training (e.g., more trials of training 1) might prove helpful in these cases.
 
-Second, participants in the TANGO-CC observe another agent's gaze.
-While we employ an active choice measure and ask participants to use the agent's gaze to guide their behavior, children do not take part in a turn-taking social interaction.
-Future research could investigate whether a prior social interaction, for example, trials in which the child determines where the agent should look, could increase children's performance in the task.
+\section{Conclusion}\label{conclusion}
 
-The target object presented in the TANGO-CC might be more common in some communities than in others.
-While we cannot rule out that this influenced children's performance, the huge overlap in performance across communities speaks for a generalizable underlying construct.
-In test trials, the target object is only visible for a very short amount of time, and the identity of the object is not relevant for succeeding in the task.
-Nevertheless, future research could investigate the effects of presenting different target objects.
-For exanple, Peña (2007) have proposed a decentering approach, where items are individually adapted to be culturally familiar in each setting.
-The same applies to the agent's face: while we tried to create a diverse set of faces, the faces might be more representative of some communities than others.
-The component-like structure and the open-source implementation with SVGs allows researchers to exchange stimuli according to their needs.
-
-Krys et al.
-(2024) have recently categorized countries into ``macrocultural groupings: (1) WEIRD, (2) Confucian-influenced, (3) Latin America and Caribbean, (4) Middle East and North Africa (excluding Israel), (5) non-Confucian Asia and Oceania, (6) sub-Saharan Africa, and (7) non-EU postcommunist states'' (p.~5) and proposed that cross-cultural studies should aim to include at least one country from each macrocultural grouping.
-While we included communities from five continents, we did not follow this categorization and indeed did not collect data in ``non-EU postcommunist states'' (e.g., Russia, Georgia, Serbia; even though it might be questioned whether this label is well-chosen).
-While the results from the TANGO-CC seem promising, we cannot generalize them to all communities world-wide.
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-The TANGO-CC is a promising tool to capture individual differences in social-cognitive development across diverse social-cultural environments.
-Task development occurred in two phases: (1) establishing the task's underlying functionality and detailed psychometrics in one community, and (2) expanding the stimulus pool and collecting data from diverse communities world-wide.
-The task's flexibility, minimal language demands, and engaging design make it a valuable tool for cross-cultural research.
-The TANGO-CC was successfully implemented in 17 communities, with children showing similar performance across communities.
-The task showed satisfactory to high reliability across all communities.
-We hope that the TANGO-CC will facilitate future cross-cultural studies to assess social-cognitive development in a wide range of communities.
+The TANGO--CC is a promising task to capture individual differences in social-cognitive development across diverse communities.
+The task was developed in two phases: (1) implementing the task's underlying functionality and estimating detailed psychometrics in one community, and (2) expanding the stimulus pool to accommodate diverse communities worldwide.
+The task's flexibility, minimal language demands, and engaging design make it a valuable task for cross-cultural research.
+The task showed satisfactory to high reliability (internal consistency) in a large dataset including 17 diverse communities.
+We hope that the TANGO--CC -- and its pragmatic construction process -- will inspire future cross-cultural studies to assess cognitive development in a wide range of communities.
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{References}\label{references}
 
@@
 
-\hypertarget{refs}{}
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-beaudoin2020systematic}{}}%
+\bibitem[\citeproctext]{ref-beaudoin2020systematic}
 Beaudoin, C., Leblanc, É., Gagner, C., \& Beauchamp, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bohn2018common}{}}%
+\bibitem[\citeproctext]{ref-bohn2018common}
 Bohn, M., \& Köymen, B. (2018). Common {Ground} and {Development}. \emph{Child Development Perspectives}, \emph{12}(2), 104--108. \url{https://doi.org/10.1111/cdep.12269}
 
-\leavevmode\vadjust pre{\hypertarget{ref-bohn2024universal}{}}%
+\bibitem[\citeproctext]{ref-bohn2024universal}
 Bohn, M., Prein, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bourdage2023evaluation}{}}%
+\bibitem[\citeproctext]{ref-bourdage2023evaluation}
 Bourdage, R., Narme, P., Neeskens, R., Papma, J., \& Franzen, S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-callaghan2011early}{}}%
+\bibitem[\citeproctext]{ref-burkner2017brms}
+Bürkner, P.-C. (2017). Brms: {An R Package} for {Bayesian Multilevel Models Using Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
+
+\bibitem[\citeproctext]{ref-burkner2018advanced}
+Bürkner, P.-C. (2018). Advanced {Bayesian Multilevel Modeling} with the {R Package} brms. \emph{The R Journal}, \emph{10}(1), 395. \url{https://doi.org/10.32614/RJ-2018-017}
+
+\bibitem[\citeproctext]{ref-callaghan2011early}
 Callaghan, T., Moll, H., Rakoczy, H., Warneken, F., Liszkowski, U., Behne, T., \& Tomasello, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chasiotis2006theory}{}}%
+\bibitem[\citeproctext]{ref-chasiotis2006theory}
 Chasiotis, A., Kiessling, F., Hofer, J., \& Campos, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-delbianco2019developmental}{}}%
+\bibitem[\citeproctext]{ref-cohen1988statistical}
+Cohen, J. (1988). \emph{Statistical power analysis for the behavioral sciences} (2nd ed). L. Erlbaum Associates.
+
+\bibitem[\citeproctext]{ref-cohen1992power}
+Cohen, J. (1992). A power primer. \emph{Psychological Bulletin}, \emph{112}(1), 155--159. \url{https://doi.org/10.1037/0033-2909.112.1.155}
+
+\bibitem[\citeproctext]{ref-delbianco2019developmental}
 Del Bianco, T., Falck-Ytter, T., Thorup, E., \& Gredebäck, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-elfenbein2002universality}{}}%
+\bibitem[\citeproctext]{ref-elfenbein2002universality}
 Elfenbein, H.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-fujita2022theory}{}}%
+\bibitem[\citeproctext]{ref-field2012discovering}
+Field, A., Miles, J., \& Field, Z. (2012). \emph{Discovering statistics using {R}}. Sage.
+
+\bibitem[\citeproctext]{ref-fujita2022theory}
 Fujita, N., Devine, R.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-glynn2016social}{}}%
-Glynn, M.
-A., \& Watkiss, L.
-(2016).
-Social {Cognition}.
-In M.
-Augier \& D.
-J.
-Teece (Eds.), \emph{The {Palgrave Encyclopedia} of {Strategic Management}} (pp.
-1--4).
-Palgrave Macmillan UK.
-\url{https://doi.org/10.1057/978-1-349-94848-2_614-1}
+\bibitem[\citeproctext]{ref-gutchess2023considerationa}
+Gutchess, A., \& Rajaram, S.
+(2023).
+Consideration of culture in cognition: {How} we can enrich methodology and theory.
+\emph{Psychonomic Bulletin \& Review}, \emph{30}(3), 914--931.
+\url{https://doi.org/10.3758/s13423-022-02227-5}
 
-\leavevmode\vadjust pre{\hypertarget{ref-hajduk2020how}{}}%
+\bibitem[\citeproctext]{ref-hajduk2020how}
 Hajdúk, M., Achim, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-henrich2010weirdesta}{}}%
+\bibitem[\citeproctext]{ref-he2012bias}
+He, J., \& Vijver, F. van de. (2012). Bias and {Equivalence} in {Cross-Cultural Research}. \emph{Online Readings in Psychology and Culture}, \emph{2}(2). \url{https://doi.org/10.9707/2307-0919.1111}
+
+\bibitem[\citeproctext]{ref-henrich2010weirdesta}
 Henrich, J., Heine, S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-hernik2019infant}{}}%
+\bibitem[\citeproctext]{ref-hernik2019infant}
 Hernik, M., \& Broesch, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-hughes2014lost}{}}%
+\bibitem[\citeproctext]{ref-hughes2000good}
+Hughes, C., Adlam, A., Happé, F., Jackson, J., Taylor, A., \& Caspi, A.
+(2000).
+Good {Test}-{Retest Reliability} for {Standard} and {Advanced False}-{Belief Tasks} across a {Wide Range} of {Abilities}.
+\emph{Journal of Child Psychology and Psychiatry}, \emph{41}(4), 483--490.
+\url{https://doi.org/10.1111/1469-7610.00633}
+
+\bibitem[\citeproctext]{ref-hughes2014lost}
 Hughes, C., Devine, R.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-hughes2018does}{}}%
+\bibitem[\citeproctext]{ref-hughes2018does}
 Hughes, C., Devine, R.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-jasso2006using}{}}%
-Jasso, H., \& Triesch, J. (2006). Using eye direction cues for gaze following -- {A} developmental model. \emph{In}.
+\bibitem[\citeproctext]{ref-kline1999handbook}
+Kline, P. (1999). \emph{The {Handbook} of {Psychological Testing}} (2nd ed.). Routledge.
 
-\leavevmode\vadjust pre{\hypertarget{ref-krys2024weirda}{}}%
+\bibitem[\citeproctext]{ref-krys2024weirda}
 Krys, K., De Almeida, I., Wasiel, A., \& Vignoles, V.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kusano2024mismeasure}{}}%
+\bibitem[\citeproctext]{ref-kusano2024mismeasure}
 Kusano, K., Napier, J., \& Jost, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-matsumoto2006new}{}}%
+\bibitem[\citeproctext]{ref-lillard1998ethnopsychologies}
+Lillard, A. (1998). Ethnopsychologies: {Cultural} variations in theories of mind. \emph{Psychological Bulletin}, \emph{123}(1), 3--32. \url{https://doi.org/10.1037/0033-2909.123.1.3}
+
+\bibitem[\citeproctext]{ref-matsumoto2006new}
 Matsumoto, D., \& Yoo, S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-mehta2011validation}{}}%
+\bibitem[\citeproctext]{ref-mehta2011validation}
 Mehta, U.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-nielsen2017persistent}{}}%
+\bibitem[\citeproctext]{ref-nielsen2017persistent}
 Nielsen, M., Haun, D., Kärtner, J., \& Legare, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-pena2007lost}{}}%
+\bibitem[\citeproctext]{ref-pena2007lost}
 Peña, E. D. (2007). Lost in {Translation}: {Methodological Considerations} in {Cross-Cultural Research}. \emph{Child Development}, \emph{78}(4), 1255--1264. \url{https://www.jstor.org/stable/4620701}
 
-\leavevmode\vadjust pre{\hypertarget{ref-prein2023tango}{}}%
+\bibitem[\citeproctext]{ref-prein2023tango}
 Prein, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-prein2023variation}{}}%
+\bibitem[\citeproctext]{ref-prein2024variation}
 Prein, J.
@@
 M., \& Bohn, M.
-(2023).
-\emph{Variation in gaze understanding across the life span: {A} process-level perspective}.
+(2024).
+\emph{Variation in gaze following across the life span: {A} process-level perspective}.
 PsyArXiv.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-pronk2022methods}{}}%
+\bibitem[\citeproctext]{ref-pronk2022methods}
 Pronk, T., Molenaar, D., Wiers, R.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-schilbach2013secondperson}{}}%
+\bibitem[\citeproctext]{ref-rcoreteam2024language}
+R Core Team. (2024). \emph{R: {A} language and environment for statistical computing} {[}Manual{]}. R Foundation for Statistical Computing.
+
+\bibitem[\citeproctext]{ref-rouder2019psychometrics}
+Rouder, J.
+N., \& Haaf, J.
+M.
+(2019).
+A psychometrics of individual differences in experimental tasks.
+\emph{Psychonomic Bulletin \& Review}, \emph{26}(2), 452--467.
+\url{https://doi.org/10.3758/s13423-018-1558-y}
+
+\bibitem[\citeproctext]{ref-schilbach2013secondperson}
 Schilbach, L., Timmermans, B., Reddy, V., Costall, A., Bente, G., Schlicht, T., \& Vogeley, K.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-selcuk2023development}{}}%
+\bibitem[\citeproctext]{ref-selcuk2023development}
 Selcuk, B., Gonultas, S., \& Ekerim-Akbulut, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-shepherd2010following}{}}%
+\bibitem[\citeproctext]{ref-shepherd2010following}
 Shepherd, S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-stengelin2020cultural}{}}%
+\bibitem[\citeproctext]{ref-stengelin2020cultural}
 Stengelin, R., Hepach, R., \& Haun, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-tang2024slow}{}}%
+\bibitem[\citeproctext]{ref-tang2024slow}
 Tang, Y., Gonzalez, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-taumoepeau2019crosscultural}{}}%
+\bibitem[\citeproctext]{ref-taumoepeau2019crosscultural}
 Taumoepeau, M., Sadeghi, S., \& Nobilo, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-tomasello2007reliance}{}}%
+\bibitem[\citeproctext]{ref-tomasello2007reliance}
 Tomasello, M., Hare, B., Lehmann, H., \& Call, J.
@@
 
+\bibitem[\citeproctext]{ref-waschl2022crosscultural}
+Waschl, N., \& Chen, M.
+(2022).
+Cross-{Cultural Considerations} for {Adapting Valid Psychoeducational Assessments}.
+In O.
+S.
+Tan, K.
+K.
+Poon, B.
+A.
+O'Brien, \& A.
+Rifkin-Graboi (Eds.), \emph{Early {Childhood Development} and {Education} in {Singapore}} (pp.
+113--140).
+Springer.
+\url{https://doi.org/10.1007/978-981-16-7405-1_7}
+
 \end{CSLReferences}

### 2024-05-15 stats/analysis.Rmd
correct small errors (esp. authors)

@@
 library(brms) # modeling
-library(cmdstanr) # modeling
+# library(cmdstanr) # modeling
 library(ggpubr) # ggarrange
@@
   Intercept = mestimates$community[, , "Intercept"][1:17],
+  Intercept_q25 = mestimates$community[, , "Intercept"][35:51],
+  Intercept_q975 = mestimates$community[, , "Intercept"][52:68],
   Training1 = mestimates$community[, , "trialtypeTraining1"][1:17],
-  Training2 = mestimates$community[, , "trialtypeTraining2"][1:17]
-)
+  Training1_q25 = mestimates$community[, , "trialtypeTraining1"][35:51],
+  Training1_q975 = mestimates$community[, , "trialtypeTraining1"][52:68],
+  Training2 = mestimates$community[, , "trialtypeTraining2"][1:17],
+  Training2_q25 = mestimates$community[, , "trialtypeTraining2"][35:51],
+  Training2_q975 = mestimates$community[, , "trialtypeTraining2"][52:68]
+) %>% 
+  mutate(across(where(is.numeric), ~round(., 2)))
+trialtypes_est
 
 saveRDS(mtrialtypes, "../saves/mtrialtypes.rds")
+# mtrialtypes <- readRDS("../saves/mtrialtypes.rds")
 saveRDS(trialtypes_est, "../saves/trialtypes_est")

### 2024-06-12 paper/manuscript.Rmd
incorporate co-author feedback

@@
   - id            : "1"
-    institution   : "Institute of Psychology in Education, Leuphana University Lüneburg"
+    institution   : "Institute of Psychology in Education, Leuphana University Lüneburg, Germany"
   - id            : "2"
-    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
+    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany"
   - id            : "3"
-    institution   : "Budongo Conservation Field Station"
+    institution   : "Budongo Conservation Field Station, Uganda"
   - id            : "4"
-    institution   : "School of Psychology, University of Auckland"
+    institution   : "School of Psychology, University of Auckland, New Zealand"
   - id            : "5"
-    institution   : "Université Marien Ngouabi"
+    institution   : "Université Marien Ngouabi, Republic of the Congo"
   - id            : "6"
-    institution   : "Department of Psychology, Stanford University"
+    institution   : "Department of Psychology, Stanford University, USA"
   - id            : "7"
-    institution   : "School of Psychology, University of Plymouth"
+    institution   : "School of Psychology, University of Plymouth, UK"
   - id            : "8"
-    institution   : "Department of Psychology, Koç University"
+    institution   : "Department of Psychology, Koç University, Türkiye"
   - id            : "9"
-    institution   : "Division of Psychology, Communication, and Human Neuroscience, University of Manchester"
+    institution   : "Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK"
   - id            : "10"
-    institution   : "Department of Psychology and Social Work, University of Namibia"
+    institution   : "Department of Psychology and Social Work, University of Namibia, Namibia"
   - id            : "11"
-    institution   : "Department of Psychology, University of York"
+    institution   : "Department of Psychology, University of York, UK"
   - id            : "12"
-    institution   : "CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences"
+    institution   : "CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China"
   - id            : "13"
-    institution   : "Department of Psychology, Developmental Psychology, Uppsala University"
+    institution   : "Department of Psychology, Developmental Psychology, Uppsala University, Sweden"
   - id            : "+"
@@
 abstract: | 
-            Cross-cultural studies are crucial for investigating the universality and robustness of cognitive developmental processes.
-Yet, suitable methods to measure variability in cognition across languages and communities are lacking.
-This paper describes the TANGO--CC (Task for Assessing Individual Differences in Gaze Understanding -- Cross-Cultural), a gaze following task designed to measure basic social cognition across individuals, ages, and communities.
-The TANGO--CC was developed and psychometrically assessed in one setting and subsequently adapted for cross-cultural data collection.
+            Cross-cultural studies are crucial for investigating cultural variability and universality of cognitive developmental processes.
+However, cross-cultural assessment tools in cognition across languages and communities are limited.
+This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (Task for Assessing iNdividual Differences in Gaze understanding Open -- Cross-Cultural or TANGO--CC).
+The TANGO--CC was developed and psychometrically assessed in one cultural setting and, with the input of local collaborators, adapted for cross-cultural data collection.
 Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community.
-The TANGO--CC captured individual differences and showed good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities.
+The TANGO--CC captures individual- and community-level variation and shows good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities.
 Within-community variation outweighed between-community variation.
 We provide an open-source website for researchers to customize and use the task.
-The TANGO--CC represents a valuable contribution to assessing basic social cognition in diverse communities, establishing a roadmap for researching cross-cultural individual differences.
+The TANGO--CC can be used to assess basic social cognition in diverse communities and provides a roadmap for researching community-level and individual-level differences across cultures.
 
@@
 header-includes:
+  - \usepackage{amsmath}
+  - \usepackage{amssymb}
+  - \usepackage{unicode-math}
   - \usepackage{setspace}
@@
 documentclass     : "apa7"
-output            : papaja::apa6_pdf
+output            :   
+  papaja::apa6_pdf:
+    latex_engine: xelatex
+    keep_tex: true
 editor_options    : 
@@
 
-For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) communities [@henrich2010weirdesta; @lillard1998ethnopsychologies].
-Despite numerous calls for change, the subject pools reported in high-impact journals still lack diversity [@nielsen2017persistent; @gutchess2023considerationa].
-This lack of representation hinders progress in theory building: inferences about the universal and variable aspects of the human cognitive system cannot be drawn from data collected in single communities [@krys2024weirda].
+For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on convenience samples from the Global North [@henrich2010weirdesta; @lillard1998ethnopsychologies; @arnett2008neglecteda].
+Despite numerous calls for change, the samples reported in major psychology journals still lack diversity [@gutchess2023considerationa; @thalmayer2021neglecteda; @apicella2020weird].
+This hinders progress in theory building and testing: we cannot draw inferences about universal and variable aspects of the human cognitive system from data collected exclusively in one single communities [@krys2024weirda].
+While this sampling bias is often discussed within adult psychology, it is equally relevant for developmental psychology [@nielsen2017persistent]. 
+Early experiences shape the way children think about and interact with the world and an ontogenetic perspective is needed to explore the foundational aspects of human behavioral diversity [@torrens2023einfluss; @amir2020crosscultural; @broesch2023roadmap; @liebal2018crosscultural].
 
-One reason for the lack of diversity in psychological studies is the scarcity of suitable methods to collect comparable psychological data in different communities [@bourdage2023evaluation].
-This shortage of suitable measures is even more prevalent in developmental psychology.
-In this paper, we describe the construction and psychometric evaluation of a measure of basic social cognition (gaze following) in children as a concrete example for how to overcome this problem.
+There are numerous challenges with collecting cross-cultural, developmental data [@amir2020crosscultural; @broesch2023roadmap].
+Cross-cultural studies need reliable and valid measures to systematically capture variation between communities and/or individuals.
+However, studies on social cognition with US-American and European samples rarely report psychometric information [for a review, see @beaudoin2020systematic], and the picture further deteriorates when we look at cross-cultural social cognition tasks [@hajduk2020how; @bourdage2023evaluation; @waschl2022crosscultural].
+Thus, it is already challenging to find reliable and valid tasks that have measurement sensitivity to detect individual differences within one community, let alone tasks that do so across different communities.
+In this paper, we describe the construction and psychometric evaluation of a cross-cultural measure of basic social cognition (gaze following) in children as a concrete example for how to address this problem.
 
-Studies investigating variation between communities and/or individuals need to ensure that the captured variation is systematic and not just random noise: measures need to be reliable and valid.
-This, of course, applies to all fields of psychology.
-Given the topic of this paper, we will focus on measures of social cognition for children.
-Studies on social cognition based on US-American and European samples rarely report psychometric information [for a review, see @beaudoin2020systematic].
-This picture further deteriorates when we look at cross-cultural social cognition tasks [@hajduk2020how; @bourdage2023evaluation; @waschl2022crosscultural].
-Thus, it is already challenging to find reliable and valid tasks that can capture individual differences within one community, let alone tasks that do so across different communities.
-
-Adapting tasks to diverse communities and re-assessing their validity and reliability might be especially important in the social-cognitive domain.
-If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, the tasks need to represent different communities.
-Indeed, task performance can be diminished when stimuli are not adjusted [@pena2007lost].
+Adapting tasks to diverse communities and assessing their validity and reliability might be especially important in the social-cognitive domain.
+Social cognition refers to how an individual processes information in social situations which allows them to understand and predict others' behavior [@decety2020social; @zeigler-hill2015how; @adolphs1999social; @frith2007social].
+If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, then tasks themselves should be tuned to the features of specific communities.
+Indeed, task performance can be diminished when stimuli do not reflect characteristics of the participants' communities [@pena2007lost].
 For example, @elfenbein2002universality found better emotion recognition for members of the same national, ethnic, or regional group.
 @selcuk2023development concluded that children often attribute mental states more accurately and more frequently to individuals from the same community.
-This underlines the importance of adapting tasks to each specific cultural context.
 
-Broadly speaking, there are two different approaches that researchers can take to collect cross-cultural data.
-One approach would be to translate the psychological construct into an individually designed study for each community (termed "assembly"; @he2012bias, @waschl2022crosscultural).
-While this approach is most flexible and sensitive to cultural differences, it might be most feasible for studying up to a handful of communities as it becomes too demanding and time-consuming.
-Most importantly, this approach assumes that the measured underlying concept is the same, while absolute task scores are not comparable across the communities.
-Another approach would be to use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of culturally inappropriate stimuli (termed "adoption" and "adaptation", respectively; @he2012bias, @waschl2022crosscultural).
-This approach is less sensitive to each community's unique characteristics but allows for a direct comparison of the data across communities.
-Examples following this approach include @callaghan2011early, @taumoepeau2019crosscultural, @hughes2018does, @hughes2014lost, @fujita2022theory, @mehta2011validation, @stengelin2020cultural, and @chasiotis2006theory.
-The present paper aims to describe the development and psychometric properties of a standardized task that can be adapted to diverse communities.
+There exists a continuum of approaches that researchers can take to collect cross-cultural data, and the decision for a specific method partly depends on whether researchers aim to increasing the *depth* (culture specificity) or *breadth* (standardization across multiple communities) of our psychological knowledge [@amir2020crosscultural].
+At one extreme, researchers translate the psychological construct into an individually designed study for each community (termed "assembly"; @he2012bias, @waschl2022crosscultural).
+While this approach allows greater flexibility and sensitivity to cultural differences, it might not be feasible for studying a multitude of communities as it becomes too demanding and time-consuming.
+Due to its specificity, observations are limited to each community and absolute task scores might not be comparable across communities.
+A study following this approach is @wefers2023universality who investigated how cultural variations in parenting styles modulated infants' responses to disruptions in social interactions. 
+While studies in the Global North often apply the Still-Face Paradigm to assess infants' reactions to unresponsive partners, @wefers2023universality reasoned that this paradigm might not capture infants' everyday interaction routines in communities with proximal (*i.e.,* emphasis on body stimulation) parenting styles.
+By developing the novel No-Touch Paradigm, they found that indeed infants' responses to unresponsive partners were modulated by the cultural context in which they grew up: Kichwa infants from rural Ecuador showed stronger reactions to unresponsive partners in the No-Touch Paradigm compared to the Still-Face Paradigm, while reactions of urban German infants differed less in both paradigms.
 
-The task presented here focuses on gaze following, that is, the ability to identify the attentional focus of another agent.
+At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed "adoption" and "adaptation", respectively [@he2012bias, @waschl2022crosscultural]).
+This approach is less sensitive to each community's unique characteristics but renders quantitative comparisons of data more feasible.
+An example following this approach is the Multilingual Assessment Instrument for Narratives [MAIN; @gagarina2012main], which assesses narrative abilities in mono- and multilingual children. 
+Extensive piloting and adaptation of MAIN materials ensured that the instrument is culturally appropriate, robust and suitable for cross-linguistic comparisons [@gagarina2012main], and new and revised language versions are continuously added to the MAIN database [@gagarina2020new].
+
+The present paper aims to describe the development and psychometric properties of a standardized social cognition task that can be adapted to diverse communities.
+Our task focuses on one of the most fundamental social-cognitive abilities: gaze following, that is, the ability to identify the attentional focus of another agent.
 Gaze following develops early in infancy [@delbianco2019developmental; @tang2024slow] and contributes to social learning, communication, and collaboration [@shepherd2010following; @tomasello2007reliance; @bohn2018common; @hernik2019infant].
-While gaze following is one of the most fundamental social-cognitive abilities, studies focusing on cultural variations are rare.
-The few existing results are mixed on whether gaze following is influenced by cultural factors or not [@hernik2019infant; @callaghan2011early].
+While the question how social-environmental and cultural factors impact gaze following was recently posed as one of the big open questions in gaze following research [@astor2022gaze], studies focusing on cultural variations of gaze following are rare.
+@callaghan2011early investigated gaze following behind barriers in 12- and 17-month-olds from rural Canada (n = 35), Peru (n = 38) and India (n = 65).
+In their setup, an agent sat next to a wall or container and looked at a toy behind this barrier (experimental condition) or a sticker in front of it (control condition).
+The researchers then assessed whether and in which conditions the children crawled towards/around the barriers to follow the agent's gaze.
+While the absolute crawling rates differed across communities, children in all three communities crawled more often to gain visual access when the agent looked at an object behind the barrier compared to in front of it.
+@hernik2019infant studied 22 infants between 5 to 7 months of age from Vanuatu and used an eye-tracking procedure displaying a local actor looking at one of two objects.
+Even though face-to-face interactions are less common in interactions between caregivers and children in Vanuatu than in Western communities, the result patterns of gaze following in Ni-Vanuatu infants resembled those of their Western counterparts: infants from Vanuatu followed the agent's gaze to the target object only when preceded by infant-directed, and not adult-directed, speech.
+While these two studies point towards a potential cross-cultural stability of gaze following, 
+the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings.
 
-The task presented here builds upon the TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open) by @prein2023tango.
-The TANGO measures participants' imprecision in locating an agent's attentional focus.
-It has been shown to reliably capture individual differences in a German child sample and an English-speaking remote adult sample.
-The task was sensitive to developmental changes and linked to children's receptive vocabulary.
-Furthermore, an exploratory analysis showed that children performed equally well in a task version with animal faces compared to cartoon human faces [@prein2024variation].
-This suggests that superficial variations in the stimulus design do not influence children's performance in the task.
-
-This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that can be -- and has been -- adapted to several languages and communities.
+The task presented here aims to tackle these issues and builds upon a previously established gaze-following task called 'TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by @prein2023tango.
+The TANGO measures how precisely participants locate an agent's attentional focus.
+It reliably measured individual differences in a German child sample and an English-speaking remote adult sample [@prein2023tango].
+As we cannot claim a task's generalizability and reliability based on mono-cultural samples, we need to assess the TANGO's psychometric properties in a larger cross-cultural sample. 
+This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 different communities on five continents [@bohn2024universal].
 We describe the task's development and provide a tutorial for the open-source website (<https://ccp-odc.eva.mpg.de/tango-cc/>).
-We assess its cross-cultural applicability based on data from a large cross-cultural sample of 2.5- to 11-year-olds from 17 different urban/rural communities across the world and discuss the task's psychometrics.
-The task and all its adaptations have been initially designed for a paper by @bohn2024universal, and we re-use the data set in this paper.
 
@@
 
-In a perfect world, developing a cross-cultural task would include international collaboration and diverse samples from the beginning, already during study design, piloting and item selection.
-As this seems hardly feasible, we present a pragmatic approach.
-The TANGO-CC was first implemented in one context, in our case Leipzig, Germany [@prein2023tango].
-Here, the task's reliability and validity were assessed in detail.
-Even though this does not guarantee that the task will be valid and reliable in another context, it substantially increases the likelihood.
-Second, we reassessed the TANGO--CC's measurement quality (i.e., variability and reliability) across diverse communities by analyzing the data from @bohn2024universal, who used the task to collect data in 17 communities.
-Therefore, our procedure maintains a balance between a detailed analysis of the task's psychometric properties and a swift and feasible task adaptation.
-In the following, we describe the different steps in further detail.
-We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful for other researchers.
+The TANGO-CC was implemented in Leipzig, Germany, and thoroughly assessed in terms of reliability and validity [@prein2023tango].
+During this process, the cross-cultural adaptation of the task was prepared within a team of cross-cultural psychologists and cognitive scientists. 
+In this paper, we assess the TANGO--CC's measurement quality (i.e., variability and reliability) across 17 diverse communities by analyzing the data set from @bohn2024universal.
+In the following, we describe the different steps in detail.
 
-In the first step, the task's underlying structure was designed.
-The TANGO--CC measures the precision with which participants locate an agent’s attentional focus.
-The participant's task is to locate a target by following the agent's gaze (see Figure \@ref(fig:fig1)).
-Precision was measured in a continuous way as the distance between the participant’s click on the screen (*i.e.*, where the participant thinks the target is) and the target’s real position.
-The task's core functionality is to animate the agent's eyes so that they follow the target's movement.
-This basic structure was then embedded in the task's superficial appearance (e.g., background scene) and audio instructions.
-Once this structure was implemented, adaptations of the task were greatly simplified.
-For example, we can change the background scene, the faces of the agent, and the target without changing how and what the task measures.
+The TANGO--CC is a screen-based task that measures the imprecision with which participants locate a balloon by following an agent’s gaze (see Figure \@ref(fig:fig1)). 
+Participants click or touch the location on the screen where they believe the balloon to be.
+Precision is measured as the distance between the participant’s click on the screen and the balloon’s real position.
 
-This basic version of the TANGO was psychometrically evaluated in a prototypical WEIRD sample (German child sample; English-speaking remote adult sample) and was found to be highly reliable and valid [@prein2023tango].
-While participants got more and more precise in locating the attentional focus of the agent the older they were, individuals differed across all age groups and showed no floor- or ceiling effects.
-Performance in the TANGO was linked to children's receptive vocabulary and weakly related to factors of children's daily social environment.
-In another study, @prein2024variation proposed a computational cognitive model that described gaze following as a social form of vector following.
-Gaze following, as measured by the TANGO, was related to children's non-social vector following and visual perspective-taking abilities.
-These connections to related constructs indicate the task's validity in the tested WEIRD setting.
+During the task development, we decided to implement the task's main functionality independently of the task's appearance.
+We programmed a function that calculates the x and y coordinates of where the agent's pupil and iris should move to follow the balloon, given the eyes' and balloon's original positions and measures.
+As the measures of the eyes and balloon are read out dynamically from the image on screen, stimuli can be easily adapted and exchanged.
+No coordination values for animation are hard-coded into the task's source code.
+After having programmed this "backbone" functionality of the task (*i.e.*, animate the eyes so that they follow the balloon), we added the task's audio instructions and superficial appearance (e.g., background scene, hedge, more agent faces).
 
-To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces that were judged by researchers and research assistants from each target community to be representative of the local population (see Figure \@ref(fig:fig1)).
-Similarly, different backgrounds were created that roughly represented a typical accommodation in each community.
-Audio instructions were translated into the corresponding local language.
+This basic version of the TANGO was psychometrically evaluated in a German child sample and an English-speaking remote adult sample and was found to be highly reliable and valid [@prein2023tango].
+While children became more precise in locating the attentional focus of the agent with age, individuals differed across all age groups and showed no floor- or ceiling effects.
+In the Leipzig sample, performance in the TANGO was weakly related to factors of children's daily social environment and could predict children's receptive vocabulary 6 months later.
+In a computational cognitive model, @prein2024variation described gaze following as form of social vector following and empirically found that performance in the TANGO was related to children's non-social vector following and visual perspective-taking abilities.
+These connections to related constructs indicate the task's convergent validity in the German child sample.
+
+To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces and background scenes with the feedback from local researchers and research assistants. 
+The stimulus pool was adjusted and expanded until the researchers and research assistants from each target community judged the selected stimuli to be representative of the local population and typical accommodation (see Figure \@ref(fig:fig2)).
+Audio instructions were translated from English into the corresponding local language(s).
 By back-translating these instructions, we ensured the original meaning did not change.
-Sometimes, specific words were linguistically slightly modified, although functionally equivalent (e.g., "bush" instead of "hedge"), to ensure that all participants understood the instructions.
+Sometimes, specific words were slightly modified in the target language (e.g., "bush" instead of "hedge") to ensure that all participants understood the instructions well. 
+Based on these adaptations, the TANGO--CC could be applied in 17 communities and 13 different languages [@bohn2024universal].
 In the following, we describe how researchers can use and customize the TANGO--CC in more detail.
@@
 
-We quickly recap the TANGO's [@prein2023tango] most characteristic features: Participants are asked to locate a balloon with the help of a gaze cue.
-The task consists of three different trial types (see Figure \@ref(fig:fig1)).
+(ref:figlab1) **Screenshots of the trials.** In training 1, an agent looks at a balloon that falls to the ground, and participants have to respond by clicking/touching the balloon.
+In training 2, the balloon falls behind the hedge while its flight is still visible.
+Participants respond by clicking the hedge where they think the balloon is.
+In test trials, the balloon's movement and final position are covered by a hedge, and participants respond by clicking the hedge.
+In the task, all movements are smoothly animated (no still pictures).
+Yellow frames indicate the time point when participants respond (only illustrative, not shown during the task).
+
+```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
+knitr::include_graphics("../figures/tango-cc-procedure.png")
+```
+
+The task consists of three different trial types: training 1, training 2, and test trials (see Figure \@ref(fig:fig1)).
 In every trial, participants see an agent (boy or girl) looking out of a house with a balloon (red, blue, green, or yellow) in front of them.
-The balloon falls down to the ground, while the eyes of the agent follow the movement of the balloon in a way that their centers always align.
+The balloon falls down to the ground. The eyes of the agent follow the movement of the balloon in a way that the balloon center and the pupil center always align.
 Depending on the trial type, participants have different visual access to the balloon's position.
-In training 1, participants see the full trajectory of the balloon and directly have to touch the balloon itself.
+In training 1, participants see the full trajectory of the balloon and directly have to click the balloon itself.
 In training 2, participants see most of the balloon's movement, but a hedge covers the final location.
@@
 
-The outcome variable is the distance between the participant's touch and the balloon's center.
-Trials can be completed quickly and efficiently so that children can easily complete 15 trials within 10 minutes.
-This drastically reduces drop-out rates.
-By using essentially self-explanatory animations, language demands are kept to a minimum.
-No differential feedback is given to keep trials comparable and avoid learning effects.
+The outcome variable is the distance between the participant's click and the balloon's center.
+Trials can be completed quickly and efficiently so that children can complete 15 trials within 10 minutes, and few children fail to complete the task.
+By using self-explanatory animations, language demands are kept to a minimum.
+The task uses simple audio instructions, which makes the task accessible to children from different age groups, and no reading skills are needed. 
+There is no feedback during the task to prevent learning effects across trials.
 
@@
 All agents, balloon colors, and bins appear equally often and are not repeated in more than two consecutive trials.
-If the total number of trials is not divisible by the number of unique elements, additional elements are randomly selected to make up for the remainder.
+If the total number of trials is not divisible by the number of unique elements, some elements (*i.e.,* some agents, balloon colors, bins) are randomly repeated to make up for the remainder.
 
@@
 
-The TANGO--CC can be accessed via the following link: (<https://ccp-odc.eva.mpg.de/tango-cc/>).
-In the first step, researchers can select the language for audio instructions, currently available for 13 different languages and even more dialects (see Table 1).
-All written instructions are presented in English because they are not directed to the participant but to the research assistant who guides the participant through the task.
-The task can either be started with the default settings or further customized.
+When reseachers visit the TANGO--CC's website 
+(<https://ccp-odc.eva.mpg.de/tango-cc/>), they can select the language for audio instructions which are currently available for 13 different languages and five more dialects (see Table 1).
+To add a new language, researchers have two options:
+(1) for using their own audio instructions in the offline version of the task, researchers can download the task, exchange the audio instructions in the dist folder (in the folder sounds > custom) and select "Custom" in the language drop down menu.
+For detailed instructions, see the TANGO--CC's manual (<https://ccp-odc.eva.mpg.de/tango-cc/manual.html>). 
+(2) For adding a new language in the online version of the task, researchers can contact the first author of this paper.
+Please note that this option requires new audio recordings by the interested reseachers, which will then be openly available for all users of the task.
+All written instructions in the task are solely for the research assistant to help them guide participants through the task; these instructions are solely available in English. 
+The task can either be started with the default settings or further customized by adapting the numbers of trials, agents, and background scenes.
 The default settings use the version applied in @bohn2024universal based on the selected language.
 
-If researchers choose to customize the task (see Figure \@ref(fig:fig1)), the number of trials can be chosen for each trial type.
-As the trial types build up on each other, each trial type is necessary to understand the structure of the task and needs to be completed before the next trial type starts.
-Therefore, no trial type can be skipped.
+If researchers choose to customize the task (see Figure \@ref(fig:fig2)), they can adjust the number of trials for each trial type, but not their sequence.
+Specifically, trial types build on each other and participants need to complete each trial type (without skipping any) to understand the structure of the task. 
 The minimum number of trials per type is 1; the maximum is 100. 
-One out of four different backgrounds can be selected.
-Finally, there are 50 diverse human faces (50% female, 50% male) from which researchers can choose.
-No constraint exists on how many faces are allowed (min 1, max 50).
-Once all the settings are adjusted, the customized task is compiled.
+Furthermore, researchers can customize backgrounds by selecting one of four different backgrounds. 
+Finally, researchers can choose from 50 diverse cartoon-like human faces (50% female, 50% male) and freely select how many different faces to include (min 1, max 50). 
+Once all the settings are selected, the customized task is compiled. 
+To save the selected settings, researchers can bookmark the URL to easily access the customized task.
 
 In the last step, researchers can enter an alphanumeric participant identifier (1 - 8 characters) and enable a webcam recording of the participant, if needed.
-To save the selected settings, researchers can bookmark the URL so that the customized task can be easily accessed, and only the participant ID and choice of webcam recording need to be entered again.
-The task can then be started.
+A webcam recording might prove especially helpful for unsupervised online data collection to ensure that the participant is alone during the task and no help is provided.
+The participant identifier and webcam choice has to be provided every time the task is run.
 
-The source code of the task is available on GitHub (<https://github.com/ccp-eva/tango-cc>).
-By directly editing the `HTML` and `JavaScript` code, researchers gain even more flexibility in adjusting the task to their needs.
+The source code of the task is openly available on GitHub (<https://github.com/ccp-eva/tango-cc>). 
+By directly editing the `HTML` and `JavaScript` code, researchers can further modify the task as needed.
+
+We created a public OSF page (https://doi.org/10.17605/OSF.IO/P2EGU) where we plan to collect data sets that used the TANGO-CC.
+Researchers who have collected data using the TANGO--CC can share their data with the community by contacting the first author of this paper or visiting this OSF repository.
 
@@
               "German", 
-              "Hai||om", 
-              "Khewdam",
+              "(≠Akhoe) Hai||om", 
+              "Khwedam",
               "Lingala",
@@
               "Spanish",
-              "Swahili",
+              "Kiswahili",
               "Turkish", 
@@
               "Indo-European",
-              "Khoesan",
-              "Khoesan",
+              "Khoe-Kwadi",
+              "Khoe-Kwadi",
               "Bantu",
@@
               "Zimbabwe", 
-              "Argentina / Mexico", 
+              "Argentina (Rioplatense Spanish) / Mexico (Mexiquense Spanish)", 
               "Uganda", 
@@
   lang,
-  caption = "Languages available for the audio instructions in the TANGO--CC"
+  caption = "Current language options available for the audio instructions in the TANGO--CC", 
+  note = "In those cases where more than one speaker's country of origin is listed, the audio instructions were recorded multiple times by different speakers.
+For example, the English instructions are available in five different versions."
 )
@@
 
-(ref:figlab1) **Customizable components of the TANGO--CC.** Researchers can select the language of the audio instructions, the number of trials per trial type, the background, and the agent's face.
-Screenshots of the trials show the proceeding events: In training 1, an agent looks at a balloon that falls to the ground, and participants have to respond by touching the balloon.
-In training 2, the balloon falls behind the hedge while its flight is still visible.
-Participants respond by touching the hedge where they think the balloon is.
-In test trials, the balloon's movement and final position are covered by a hedge, and participants respond by touching the hedge.
-In the task, all movements are smoothly animated (no still pictures).
-Yellow frames indicate the time point when participants respond (only illustrative, not shown during the task).
+(ref:figlab2) **Customizable components of the TANGO--CC.** Researchers can select the language of the audio instructions (see Table 1), the number of trials per trial type, the background, and the agent's face.
 
-```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
-knitr::include_graphics("../figures/TANGO-CC-procedure.png")
+```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
+knitr::include_graphics("../figures/tango-cc-screenshot.png")
 ```
@@
 The task was implemented in `JavaScript`, `HTML`, and `CSS` and is presented as a web app.
-It can be accessed on any web browser and does not require prior installation.
-The online version of the task has been proven convenient for unsupervised data collection (for example, using participant recruitment services like *Prolific*; see @prein2023tango) and sharing the task internationally.
-Importantly, the web app implementation does not necessarily need a working WIFI connection: An offline, local version of the task can be quickly set up for devices that support Node.js (<https://nodejs.org/en>).
-This is an especially useful feature for researchers working in remote areas with limited internet access.
+It can be accessed on any modern web browser on any device (e.g., computer or tablet) and does not require prior installation (please note that configurations of browsers and JavaScript may change in the future).
+Participant's responses can be recorded on a touchscreen or with a mouse or track pad.
+The online version of the task can be used for unsupervised data collection (for example, using online platforms like *Prolific*; see @prein2023tango).
+The task can be shared easily internationally by providing the URL.
+Importantly, the web app implementation does not require a working WIFI connection: An offline version of the task can be downloaded and quickly set up for devices that support Node.js (<https://nodejs.org/en>).
+This is an especially useful feature for researchers working in locations with limited internet access.
 
-The stimuli are embedded as Scalable Vector Graphics (SVG).
-The setup allows for an easy adaptation of task elements and ensures that picture quality, aspect ratio, and relative object positioning are constant.
-The task is programmed so that responses are only registered when the participant touches the relevant part of the screen (i.e., in test trials, the hedge).
+The stimuli are embedded as Scalable Vector Graphics (SVG; an image format that stores image elements via mathematical formulas based on points and lines on a grid).
+SVGs ensure that the picture quality, aspect ratio, and relative object positioning are constant.
+Furthermore, stimuli are added as individual components to the image scene which allows for an easy adaptation of task's elements (in contrast to other image formats that consist of only one combined layer that would need entire replacement).
+The task is programmed so that responses are only registered when the participant clicks the relevant part of the screen (i.e., in test trials, when they click the hedge).
 Furthermore, clicks are only registered after the voice recordings stop playing.
@@
 The file will be stored in the device's downloads folder and is named after the following pattern: "tangoCC-participantID-YYYY-MM-DD_hh_mm_ss".
+To modify the storage location on the device, researchers can change the designated downloads folder in the browser settings.
 
@@
 
-We used the data set from @bohn2024universal for the psychometric evaluation of the TANGO--CC.
-They collected data using the TANGO--CC in a sample of *N* = `r sample_table[sample_table$Community == "Total",]$Total` children between 2.5 to 11 years of age.
+We used the data set from @bohn2024universal for psychometric evaluation of the TANGO--CC.
+The data set contains a sample of *N* = `r sample_table[sample_table$Community == "Total",]$Total` children, aged 2.5 to 11 years.
 Participants came from 17 communities on five continents, in rural and urban settings, with varying degrees of market integration and technology exposure.
-@bohn2024universal carried out 19 trials (1 training 1, 2 training 2, and 16 test trials, of which the first of each type had audio instructions).
+@bohn2024universal carried out 19 trials (1 training 1, 2 training 2, and 16 test trials, of which the first of each type had audio instructions) on a touchscreen device.
 Faces, backgrounds, and languages were chosen by researchers and assistants with experience in the specific community.
-For further details on the communities and data collection procedures, see the supplements of @bohn2024universal.
+For further details on the communities, participant information, and data collection procedures, see the supplements of @bohn2024universal.
 
@@
 
-(ref:figlab2) **Measurement of the TANGO--CC by community.** (A) Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type.
-Imprecision is defined as the distance between the participant's touch and the balloon's center in units of balloon width.
+(ref:figlab3) **Variability measured by the TANGO--CC.** Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type.
+Imprecision is defined as the distance between the participant's click and the balloon's center in units of balloon width.
 For a depiction of each trial's procedure, see Figure \@ref(fig:fig1).
-(B) Internal consistency estimates by community, following three different approaches.
-In the odd-even split, the size of points reflects the sample size in each community.
-In the stratified approach with and without age correction, density curves show the posterior distributions of the GLMM.
 
-```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
-knitr::include_graphics("../figures/TANGO-CC-results.png")
+```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
+knitr::include_graphics("../figures/tango-cc-variability.png")
 ```
@@
 First, we inspected the mean and standard deviations by community and compared performance in each trial type (training 1, training 2, test trials).
-Performance was defined as the absolute click distance between the target center and the click x coordinate (measured in balloon widths).
-Across communities, children performed best in training 1 (mean = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 1",]$mean_click`, sd = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 1",]$sd_click`), followed by training 2 (mean = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 2",]$mean_click`, sd = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 2",]$sd_click`) and test trials (mean = `r descr_trialtypes[descr_trialtypes$trialtype== "Test",]$mean_click`, sd = `r descr_trialtypes[descr_trialtypes$trialtype== "Test",]$sd_click`; see Figure \@ref(fig:fig2)A).
+Performance was defined as the absolute distance between the target center and the x coordinate of the participant's click (measured in balloon widths).
+Across communities, children performed best in training 1 (mean = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 1",]$mean_click`, sd = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 1",]$sd_click`), followed by training 2 (mean = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 2",]$mean_click`, sd = `r descr_trialtypes[descr_trialtypes$trialtype== "Training 2",]$sd_click`) and test trials (mean = `r descr_trialtypes[descr_trialtypes$trialtype== "Test",]$mean_click`, sd = `r descr_trialtypes[descr_trialtypes$trialtype== "Test",]$sd_click`; see Figure \@ref(fig:fig3)).
 
-To formally estimate the effect of trial type on performance in the TANGO--CC, we fit a generalized linear mixed model (GLMM) predicting the task performance by trial type (reference category: test trials).
+To formally estimate the effect of trial type on performance in the TANGO--CC, we fitted a generalized linear mixed model (GLMM) predicting the task performance by trial type (reference category: test trials).
 All analyses were run in `r R.version$version.string` [@rcoreteam2024language].
@@
 Our GLMM analysis supported the visual inspection of the data: the fixed-effect estimates for training 1 ($\beta$ = `r fixef(mtrialtypes)["trialtypeTraining1", "Estimate"]`; 95% CrI [`r fixef(mtrialtypes)["trialtypeTraining1", "Q2.5"]`; `r fixef(mtrialtypes)["trialtypeTraining1", "Q97.5"]`]) and training 2 ($\beta$ = `r fixef(mtrialtypes)["trialtypeTraining2", "Estimate"]`; 95% CrI [`r fixef(mtrialtypes)["trialtypeTraining2", "Q2.5"]`; `r fixef(mtrialtypes)["trialtypeTraining2", "Q97.5"]`]) were negative and reliably different from zero.
-Please note that the TANGO--CC measures imprecision in gaze following.
-Therefore, a negative sign shows that children showed less imprecision (i.e., were more precise) in the training trials than in the test trials.
+[^1]
 This effect was found across all communities (random effects of trial type within community: minimum estimate for training 1 = `r max(trialtypes_est$Training1)`; 95%CrI [`r trialtypes_est$Training1_q25[which.max(trialtypes_est$Training1)]`; `r trialtypes_est$Training1_q975[which.max(trialtypes_est$Training1)]`]; minimum estimate for training 2 = `r max(trialtypes_est$Training2)`; 95%CrI [`r trialtypes_est$Training2_q25[which.max(trialtypes_est$Training2)]`; `r trialtypes_est$Training2_q975[which.max(trialtypes_est$Training2)]`]).
-The almost perfect performance in training trials indicated that children understood the task and were able to locate the balloon.
+The almost perfect performance in training trials indicated that children understood the task and were able to correctly indicate the location of the balloon when its path was (mostly) visible.
 In test trials, children's imprecision was higher, indicating that the task was more challenging.
-All communities showed substantial individual variation and overlapped in their imprecision levels (see Figure \@ref(fig:fig2)A).
+All communities showed substantial individual variation and overlapped in their imprecision levels (see Figure \@ref(fig:fig3)).
+
+[^1]: Please note that the TANGO--CC measures imprecision in gaze following.
+Therefore, a negative sign indicates that children showed less imprecision (i.e., were more precise) in the training trials than in the test trials.
 
 To identify the sources of variation, we computed intraclass correlations (ICC).
-The variation of children within communities was substantially larger than the variation between the communities.
+The variation of children's imprecision within communities was substantially larger than the variation between the communities.
 The mean within-community variance was `r mean(var_df$within_community_var)`, ranging from `r min(var_df$within_community_var)` (in Pune, India) to `r max(var_df$within_community_var)` (in Chimfunshi, Zambia).
@@
 The ICC, representing the proportion of between-community variance relative to the total variance (sum of within- and between-community variance), was `r var_df$ICC_b[1]`.
-This indicates that only `r var_df$ICC_b[1] * 100`% of the total variability in the data can be attributed to differences between communities, while the remaining `r (1 - var_df$ICC_b[1]) * 100`% are attributed to differences within communities [@kusano2024mismeasure].
+This indicated that only `r var_df$ICC_b[1] * 100`% of the total variability in the data could be attributed to differences between communities, while the remaining `r (1 - var_df$ICC_b[1]) * 100`% were attributed to differences within communities [@kusano2024mismeasure].
 
 ## Reliability
+
+(ref:figlab4) **Reliability of the TANGO--CC by community.** Internal consistency estimates by community, following three different approaches.
+In the odd-even split, the size of points reflects the sample size in each community.
+In the stratified approach with and without age correction, density curves show the posterior distributions of the GLMM.
+
+```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
+knitr::include_graphics("../figures/tango-cc-reli.png")
+```
 
@@
 Second, using the function `by_split` from the `splithalfr` package [@pronk2022methods], data was stratified by target centrality (capturing trial difficulty), and a Pearson correlation was calculated between the matched halves.
-Third, a data set was generated with stratified test halves by target centrality.
-Then, we followed the Generalized Linear Mixed Model (GLMM) approach introduced by @rouder2019psychometrics.
+Third, a data set was generated with stratified test halves by target centrality and we applied the Generalized Linear Mixed Model (GLMM) approach introduced by @rouder2019psychometrics.
 A GLMM was fitted with the mean imprecision as the outcome, age as the predictor, and test half and participant id as random effects (model notation: `imprecision ~ age + (0 + half | subjid)`).
@@
 By incorporating age as a fixed effect, the correlation between the two person-specific estimates represents the age-independent estimate for internal consistency.
-This eliminates the chance that a good internal consistency estimate results from general cognitive development rather than task-specific inter-individual differences.
+This removes the possibility that a good internal consistency estimate results from general cognitive development rather than task-specific inter-individual differences.
 Because the process of generating stratified data sets is partly random, the model was fitted 50 times for each community.
@@
 
-The results are shown in Figure \@ref(fig:fig2)C. 
+The results are shown in Figure \@ref(fig:fig4). 
 Across communities, internal consistency estimates ranged from `r min(int_con$odd_even)` to `r max(int_con$odd_even)` for the odd-even split, `r min(int_con$stratified)` to `r max(int_con$stratified)` for the stratified internal consistency, and `r int_con_wo_uk$min` to `r max(int_con$stratified_agecorrected)` for the age-corrected approach (Plymouth, UK, being an outlier with `r int_con$stratified_agecorrected[int_con$community == "Plymouth (UK)"]`).
-Following Cohen's suggestions [@cohen1988statistical; @cohen1992power], these correlations constitute large effects (*r* > .50), and indicate good internal consistency.[^1] 
+Following Cohen's suggestions [@cohen1988statistical; @cohen1992power], these correlations constitute large effects (*r* > .50), and indicate good internal consistency.[^2] 
 The results are comparable to the internal consistency estimates found in the original TANGO study [@prein2023tango], and also resemble reliability estimates of classical false belief tasks [@hughes2000good].
 
-[^1]: Note that for scale reliability and Cronbach's $\alpha$, values of .7 to .8 have been suggested to be acceptable [@kline1999handbook; @field2012discovering].
+[^2]: Note that for scale reliability and Cronbach's $\alpha$, values of .7 to .8 have been suggested to be acceptable [@kline1999handbook; @field2012discovering].
 However, @kline1999handbook suggested that values below .7 could be realistic for psychological constructs due to their variable nature.
@@
 In an exploratory analysis, we found that communities with larger individual variation showed higher internal consistency estimates (Pearson's *r* = `r sd_int_cor$r`, 95%CI [`r sd_int_cor$lower`; `r sd_int_cor$upper`]).
-Please note that this could be influenced by outliers and that the sample size here (*N* = 17 communities) is too small to make substantial claims.
+This suggests that the less variation a task can capture within a community, the lower the reliability.
+However, please note that this correlation could be influenced by outliers and that the sample size here (*N* = 17 communities) is too small to make substantial claims.
 
@@
 The TANGO--CC measures imprecision in gaze following across individuals, ages, and communities.
-The task was developed in two phases.
-First, the task's underlying functionality was designed in one community.
-Next, we adapted the superficial features of the task to be used in 17 diverse communities and assessed the task's psychometric properties.
-Children’s imprecision in gaze following highly overlapped between communities: children performed better in the training than the test trials, and within-community variation greatly exceeded between-community variation.
-The task showed satisfactory to high reliability across all communities.
-Therefore, we believe the TANGO--CC is a promising task to capture individual differences in social-cognitive development in diverse communities.
-Its design process lays out a much-needed pragmatic approach to conducting cross-cultural individual differences research.
+Children’s imprecision in gaze following showed highly similar result patterns across communities: children performed better in the training than the test trials, and within-community variation greatly exceeded between-community variation.
+Furthermore, the task showed satisfactory to high reliability across all communities.
+Therefore, the TANGO--CC is a suitable task to capture individual differences in social-cognitive development in diverse communities.
 
-A similar approach to task development was taken by @mehta2011validation.
-The researchers (1) selected social cognition measures that have been established in WEIRD settings, (2) adapted the agent's names, appearance, backgrounds, and languages to the local context, and (3) assessed the task's validity and internal consistency in the new setting.
-Participants were adults with and without schizophrenia from India. Theory of Mind tasks included Sally-Anne, Smarties, Ice cream van and Missing cookies stories.
-For this specific context, the authors' approach yielded a successful adaptation of social cognition measures for the tested Indian (Hindi/Kannada) communities.
+The TANGO--CC's design process lays out a much-needed pragmatic approach to studying community-level and individual-level differences across cultures: 
+While we performed a detailed psychometric evaluation of the task in a German setting, we collaborated with local researchers for the cross-cultural stimulus development and selection.
+Importantly, we re-assessed the TANGO--CC's psychometric properties in a large and diverse data set from @bohn2024universal, including children from 17 diverse communities in rural and urban settings with varying degrees of market integration and technology exposure.
+While we cannot generalize our findings to all communities worldwide, we found that the TANGO-CC captured reliable individual variation in all communities studied by @bohn2024universal.
+We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful for other researchers. 
+We recommend that researchers consider generalizability concerns and cross-cultural applications of their tasks and collaborate with local researchers at early stages of task development [@torrens2023einfluss].
+Using the TANGO--CC (or any other task) in a new community requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
 
 @bourdage2023evaluation pointed out a major challenge with adapting social cognition tasks to diverse communities: the number of world cultures is vast, and communities are constantly changing.
-Therefore, a promising approach might be to provide tasks with a modular system where components can be exchanged according to the local context.
-In the case of the TANGO--CC, the task can not only be adapted to different languages, cartoon faces, and backgrounds (see Figure \@ref(fig:fig1)) but also updated with new stimuli.
-Unlike studies that present sequential, hand-painted pictures that are difficult to adapt [@mehta2011validation], the TANGO--CC uses SVGs that can be easily exchanged.
+Therefore, a promising approach might be to provide tasks with a modular system where components can be modified (*i.e.*, building block structure).
+In the case of the TANGO--CC, the task cannot only be adapted to different languages, cartoon faces, and backgrounds (see Figure \@ref(fig:fig2)) but also updated with new stimuli.
+Unlike studies that present sequential, hand-painted pictures that are difficult to adapt [@mehta2011validation], the TANGO--CC uses SVGs (Scalable Vector Graphics) that can be easily exchanged.
 
-The biggest strength of the TANGO--CC is its flexibility.
-The task is presented as a web app that can also run offline to enable remote data collection.
-Minimal language demands and an engaging, playful design increase the task's usability.
-Together with a short task duration, this reduces drop-out rates and enables efficient data collection with large sample sizes.
-The TANGO--CC follows a standardized procedure and uses a continuous, objective outcome measure (leaving no room for rater errors).
-An online manual with the most frequently asked questions is available at <https://ccp-odc.eva.mpg.de/tango-cc/manual.html>.
-Additional customization can be achieved by adding new stimuli to the open-source code available on GitHub (<https://github.com/ccp-eva/tango-cc>).
+Compared to one of the most commonly used social cognition measure -- the change-of-location false belief task [@wimmer1983beliefs; @baron-cohen1985does] -- the TANGO--CC has several advantages: a continuous outcome measure which can capture individual differences, a short task duration that allows for more trials per child, stimuli that can be easily adapted, and known psychometric properties across 17 communities.
+The task is presented as a web app that enables efficient data collection with large sample sizes, while it can also be used to collect data offline in locations without reliable internet connection.
+The TANGO--CC follows a standardized procedure, which leaves no room for rater errors and greatly simplifies online training of research assistants.
+Furthermore, minimal language demands and an engaging, playful design increase the task's usability and reduce non-completion rates.
 
-For years, researchers have called for more diverse sampling and culturally valid measures of cognitive development [e.g., @mehta2011validation; @nielsen2017persistent; @matsumoto2006new].
-As @hajduk2020how put it, "using large samples and multisite approaches will align with efforts to improve reproducibility and will clarify both the type and extent of cultural influences on social cognition" (p.
-463).
-The TANGO--CC takes a valuable step in this direction by sharing the task and its source code with other researchers.
-@bohn2024universal showed that data collection with the TANGO--CC was feasible in 17 diverse communities in rural and urban settings with varying degrees of market integration and technology exposure.
-While we cannot generalize our findings to all communities worldwide, we found that it captured reliable individual variation in the 17 communities studied by @bohn2024universal.
-Using the TANGO--CC in a new community nevertheless requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
-We hope that the TANGO--CC will facilitate future cross-cultural studies to assess social-cognitive development in a wide range of communities.
+The TANGO--CC is a screen-based task. 
+@bohn2024universal have shown that children with no prior touchscreen exposure were less precise in the TANGO--CC than children with prior experience.
+However, individual differences were also found in communities with 100% touchscreen exposure, showing that this factor alone could not explain children's performance in the task [@bohn2024universal].
+Notably, even though the touchscreen experience caused absolute differences in task performance, all communities showed the same processing signature. 
+A recent computational cognitive model described gaze following as a process of estimating pupil angles and the corresponding gaze vectors [@prein2024variation].
+@bohn2024universal found clear support for this model in every community studied, suggesting that children all over the world process gaze in a similar way.
+Nevertheless, the mode of stimulus presentation needs to be kept in mind when administering the TANGO--CC, especially in communities with little technology exposure.
+Additional touchscreen training (e.g., more trials of training 1) might prove helpful in these cases.
 
-A valid question is whether the TANGO--CC measures the same construct across different groups.
-This so-called measurement invariance is often seen as a requirement for a "fair" cross-cultural comparison and relies on minimizing group differences while individual differences are magnified.
+@schilbach2013secondperson pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions.
+First evidence suggests that the TANGO--CC indeed taps into social cognition as utilized in real life: @prein2024variation found that children's perspective-taking abilities in a personal social interaction was linked to performance in the TANGO, but less so to a matched, non-social vector following task.
+However, this study exclusively relied on a German sample and future research should investigate whether the relationship between the TANGO--CC and perspective-taking abilities holds across communities.
+
+We have reported reliability estimates for each community by calculating internal consistency.
+Ideally, we would have additionally evaluated the task's test-retest reliability in each community and checked for relationships with theoretically related constructs to assess validity.
+Unfortunately, this might not always be feasible in large-scale cross-cultural studies due to organizational and financial constraints.
+An example of assessing the TANGO's predictive validity is a study conducted in Leipzig, Germany, which used the TANGO to predict children's receptive vocabulary 6 months later [@prein2023tango].
+Future cross-cultural studies could investigate the TANGO--CC's predictive validity and its relationship to other social-cognitive abilities (e.g., Theory of Mind, language development) in diverse communities.
+
+Measurement invariance (*i.e.*, measuring the same construct across different communities) is often seen as a requirement for a “fair” cross-cultural comparison: it is important that any group differences are not the result of the task unintentionally tapping into different underlying constructs.
 As @kusano2024mismeasure put it: "The research challenge is to achieve a balance between ensuring methodological “fairness” at the individual level while also recognizing and capturing genuine sociocultural variability" (p.
@@
 We argue that the TANGO--CC measures a fundamental social-cognitive ability that is likely similar across communities.
-@bohn2024universal have shown that children with no prior touchscreen exposure were less precise in the TANGO--CC than children with prior experience.
-However, individual differences were also found in communities with 100% touch screen exposure, showing that this factor alone could not explain children's performance in the task [@bohn2024universal].
-Notably, even though the touchscreen experience caused absolute differences in task performance, all communities showed the same processing signature.
-A recent computational cognitive model described gaze following as a process of estimating pupil angles and the corresponding gaze vectors [@prein2024variation].
-The model predicted that all individuals use the same process to locate an attentional focus but differ in their uncertainty around the estimated pupil angles, which results in less precision.
-@bohn2024universal found clear support for this model in every community they studied, suggesting that children all over the world process gaze in a similar way.
-In this manuscript, we could also show that internal consistency was high across all communities, meaning that the task captured individual differences in a similar way.
-Consequently, the TANGO--CC seems to measure systematic individual differences across diverse communities.
-
 @selcuk2023development pointed out that researchers should study both within- and between-culture variability in the development of social cognition since sometimes within-culture differences exceed between-culture differences.
@@
 
-# Limitations
-
-The TANGO--CC and its psychometric properties need to be considered against some limitations.
-Reliability for each community was assessed by calculating the internal consistency.
-Ideally, we would have additionally assessed the task's retest reliability in each community and checked for relationships with theoretically related constructs to assess validity.
-
-@schilbach2013secondperson pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions.
-Of course, the TANGO--CC does not depict real-life social interaction, and future research should investigate how task performance relates to the real world.
-Suggestive evidence comes from a study by @prein2024variation, who found that children's performance in the TANGO was linked to children's visual perspective-taking abilities in real-life social interaction.
-The mode of stimulus presentation surely needs to be kept in mind when administering the TANGO--CC, especially in communities with little technology exposure.
-Additional touch screen training (e.g., more trials of training 1) might prove helpful in these cases.
+For years, researchers have called for more diverse sampling and culturally valid measures of cognitive development [e.g., @mehta2011validation; @nielsen2017persistent; @matsumoto2006new].
+As @hajduk2020how said, "using large samples and multisite approaches will align with efforts to improve reproducibility [replicability] and will clarify both the type and extent of cultural influences on social cognition" (p.
+463).
+Similarly, @elson2023psychological have called for standardized, psychometrically evaluated measures that can be re-used by other researchers in order to "build a cumulative evidence base in psychology" (p.
+2).
+This underlines how efforts to improve the replicability can be combined with the goal of increasing the generalisability of psychological research [@li2024developmental; @syed2021reproducibility].
+@li2024developmental have argued that replicable and generalisable results rely on stimulus sets with slight variations, more diverse samples, and data collection at a greater scale, which are all steps the TANGO--CC has taken.
+Openly sharing the TANGO--CC's materials will allow other researchers to (hopefully) replicate the results and deepen our cumulative understanding of social-cognitive development across diverse communities.
 
@@
 
-The TANGO--CC is a promising task to capture individual differences in social-cognitive development across diverse communities.
-The task was developed in two phases: (1) implementing the task’s underlying functionality and estimating detailed psychometrics in one community, and (2) expanding the stimulus pool to accommodate diverse communities worldwide.
-The task’s flexibility, minimal language demands, and engaging design make it a valuable task for cross-cultural research.
-The task showed satisfactory to high reliability (internal consistency) in a large dataset including 17 diverse communities.
-We hope that the TANGO--CC – and its pragmatic construction process – will inspire future cross-cultural studies to assess cognitive development in a wide range of communities.
+The TANGO--CC captures individual differences in social-cognitive development across diverse communities.
+The task’s customizability, minimal language demands, and its efficient data collection method make it a valuable tool for cross-cultural research.
+The task showed satisfactory to high reliability (internal consistency) in a large data set including 17 diverse communities on five continents.
+We hope that the TANGO--CC – and its pragmatic construction process – will provide a roadmap for future cross-cultural studies on cognitive development.
 

### 2024-06-12 paper/manuscript.tex
incorporate co-author feedback

@@
 \usepackage{csquotes}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{unicode-math}
 \usepackage{setspace}
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology\\\textsuperscript{3} Budongo Conservation Field Station\\\textsuperscript{4} School of Psychology, University of Auckland\\\textsuperscript{5} Université Marien Ngouabi\\\textsuperscript{6} Department of Psychology, Stanford University\\\textsuperscript{7} School of Psychology, University of Plymouth\\\textsuperscript{8} Department of Psychology, Koç University\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia\\\textsuperscript{11} Department of Psychology, University of York\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences\\\textsuperscript{13} Department of Psychology, Developmental Psychology, Uppsala University\\\textsuperscript{+} joint last author}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg, Germany\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany\\\textsuperscript{3} Budongo Conservation Field Station, Uganda\\\textsuperscript{4} School of Psychology, University of Auckland, New Zealand\\\textsuperscript{5} Université Marien Ngouabi, Republic of the Congo\\\textsuperscript{6} Department of Psychology, Stanford University, USA\\\textsuperscript{7} School of Psychology, University of Plymouth, UK\\\textsuperscript{8} Department of Psychology, Koç University, Türkiye\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia, Namibia\\\textsuperscript{11} Department of Psychology, University of York, UK\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China\\\textsuperscript{13} Department of Psychology, Developmental Psychology, Uppsala University, Sweden\\\textsuperscript{+} joint last author}
 
 \abstract{%
-Cross-cultural studies are crucial for investigating the universality and robustness of cognitive developmental processes.
-Yet, suitable methods to measure variability in cognition across languages and communities are lacking.
-This paper describes the TANGO--CC (Task for Assessing Individual Differences in Gaze Understanding -- Cross-Cultural), a gaze following task designed to measure basic social cognition across individuals, ages, and communities.
-The TANGO--CC was developed and psychometrically assessed in one setting and subsequently adapted for cross-cultural data collection.
+Cross-cultural studies are crucial for investigating cultural variability and universality of cognitive developmental processes.
+However, cross-cultural assessment tools in cognition across languages and communities are limited.
+This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (Task for Assessing iNdividual Differences in Gaze understanding Open -- Cross-Cultural or TANGO--CC).
+The TANGO--CC was developed and psychometrically assessed in one cultural setting and, with the input of local collaborators, adapted for cross-cultural data collection.
 Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community.
-The TANGO--CC captured individual differences and showed good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities.
+The TANGO--CC captures individual- and community-level variation and shows good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities.
 Within-community variation outweighed between-community variation.
 We provide an open-source website for researchers to customize and use the task.
-The TANGO--CC represents a valuable contribution to assessing basic social cognition in diverse communities, establishing a roadmap for researching cross-cultural individual differences.
+The TANGO--CC can be used to assess basic social cognition in diverse communities and provides a roadmap for researching community-level and individual-level differences across cultures.
 }
@@
 
-For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) communities (Henrich et al., 2010; Lillard, 1998).
-Despite numerous calls for change, the subject pools reported in high-impact journals still lack diversity (Gutchess \& Rajaram, 2023; Nielsen et al., 2017).
-This lack of representation hinders progress in theory building: inferences about the universal and variable aspects of the human cognitive system cannot be drawn from data collected in single communities (Krys et al., 2024).
-
-One reason for the lack of diversity in psychological studies is the scarcity of suitable methods to collect comparable psychological data in different communities (Bourdage et al., 2023).
-This shortage of suitable measures is even more prevalent in developmental psychology.
-In this paper, we describe the construction and psychometric evaluation of a measure of basic social cognition (gaze following) in children as a concrete example for how to overcome this problem.
-
-Studies investigating variation between communities and/or individuals need to ensure that the captured variation is systematic and not just random noise: measures need to be reliable and valid.
-This, of course, applies to all fields of psychology.
-Given the topic of this paper, we will focus on measures of social cognition for children.
-Studies on social cognition based on US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020).
-This picture further deteriorates when we look at cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020; Waschl \& Chen, 2022).
-Thus, it is already challenging to find reliable and valid tasks that can capture individual differences within one community, let alone tasks that do so across different communities.
-
-Adapting tasks to diverse communities and re-assessing their validity and reliability might be especially important in the social-cognitive domain.
-If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, the tasks need to represent different communities.
-Indeed, task performance can be diminished when stimuli are not adjusted (Peña, 2007).
+For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on convenience samples from the Global North (Arnett, 2008; Henrich et al., 2010; Lillard, 1998).
+Despite numerous calls for change, the samples reported in major psychology journals still lack diversity (Apicella et al., 2020; Gutchess \& Rajaram, 2023; Thalmayer et al., 2021).
+This hinders progress in theory building and testing: we cannot draw inferences about universal and variable aspects of the human cognitive system from data collected exclusively in one single communities (Krys et al., 2024).
+While this sampling bias is often discussed within adult psychology, it is equally relevant for developmental psychology (Nielsen et al., 2017).
+Early experiences shape the way children think about and interact with the world and an ontogenetic perspective is needed to explore the foundational aspects of human behavioral diversity (Amir \& McAuliffe, 2020; Broesch et al., 2023; Liebal \& Haun, 2018; Torréns et al., 2023).
+
+There are numerous challenges with collecting cross-cultural, developmental data (Amir \& McAuliffe, 2020; Broesch et al., 2023).
+Cross-cultural studies need reliable and valid measures to systematically capture variation between communities and/or individuals.
+However, studies on social cognition with US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020), and the picture further deteriorates when we look at cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020; Waschl \& Chen, 2022).
+Thus, it is already challenging to find reliable and valid tasks that have measurement sensitivity to detect individual differences within one community, let alone tasks that do so across different communities.
+In this paper, we describe the construction and psychometric evaluation of a cross-cultural measure of basic social cognition (gaze following) in children as a concrete example for how to address this problem.
+
+Adapting tasks to diverse communities and assessing their validity and reliability might be especially important in the social-cognitive domain.
+Social cognition refers to how an individual processes information in social situations which allows them to understand and predict others' behavior (Adolphs, 1999; Decety, 2020; Frith \& Frith, 2007; Zeigler-Hill et al., 2015).
+If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, then tasks themselves should be tuned to the features of specific communities.
+Indeed, task performance can be diminished when stimuli do not reflect characteristics of the participants' communities (Peña, 2007).
 For example, Elfenbein and Ambady (2002) found better emotion recognition for members of the same national, ethnic, or regional group.
 Selcuk et al. (2023) concluded that children often attribute mental states more accurately and more frequently to individuals from the same community.
-This underlines the importance of adapting tasks to each specific cultural context.
-
-Broadly speaking, there are two different approaches that researchers can take to collect cross-cultural data.
-One approach would be to translate the psychological construct into an individually designed study for each community (termed ``assembly''; He and Vijver (2012), Waschl and Chen (2022)).
-While this approach is most flexible and sensitive to cultural differences, it might be most feasible for studying up to a handful of communities as it becomes too demanding and time-consuming.
-Most importantly, this approach assumes that the measured underlying concept is the same, while absolute task scores are not comparable across the communities.
-Another approach would be to use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of culturally inappropriate stimuli (termed ``adoption'' and ``adaptation'', respectively; He and Vijver (2012), Waschl and Chen (2022)).
-This approach is less sensitive to each community's unique characteristics but allows for a direct comparison of the data across communities.
-Examples following this approach include Callaghan et al.
-(2011), Taumoepeau et al.
-(2019), Hughes et al.
-(2018), Hughes et al.
-(2014), Fujita et al.
-(2022), Mehta et al.
-(2011), Stengelin et al.
-(2020), and Chasiotis et al.
-(2006).
-The present paper aims to describe the development and psychometric properties of a standardized task that can be adapted to diverse communities.
-
-The task presented here focuses on gaze following, that is, the ability to identify the attentional focus of another agent.
+
+There exists a continuum of approaches that researchers can take to collect cross-cultural data, and the decision for a specific method partly depends on whether researchers aim to increasing the \emph{depth} (culture specificity) or \emph{breadth} (standardization across multiple communities) of our psychological knowledge (Amir \& McAuliffe, 2020).
+At one extreme, researchers translate the psychological construct into an individually designed study for each community (termed ``assembly''; He and Vijver (2012), Waschl and Chen (2022)).
+While this approach allows greater flexibility and sensitivity to cultural differences, it might not be feasible for studying a multitude of communities as it becomes too demanding and time-consuming.
+Due to its specificity, observations are limited to each community and absolute task scores might not be comparable across communities.
+A study following this approach is Wefers et al. (2023) who investigated how cultural variations in parenting styles modulated infants' responses to disruptions in social interactions.
+While studies in the Global North often apply the Still-Face Paradigm to assess infants' reactions to unresponsive partners, Wefers et al.
+(2023) reasoned that this paradigm might not capture infants' everyday interaction routines in communities with proximal (\emph{i.e.,} emphasis on body stimulation) parenting styles.
+By developing the novel No-Touch Paradigm, they found that indeed infants' responses to unresponsive partners were modulated by the cultural context in which they grew up: Kichwa infants from rural Ecuador showed stronger reactions to unresponsive partners in the No-Touch Paradigm compared to the Still-Face Paradigm, while reactions of urban German infants differed less in both paradigms.
+
+At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed ``adoption'' and ``adaptation'', respectively Waschl \& Chen (2022)).
+This approach is less sensitive to each community's unique characteristics but renders quantitative comparisons of data more feasible.
+An example following this approach is the Multilingual Assessment Instrument for Narratives {[}MAIN; Gagarina et al. (2012){]}, which assesses narrative abilities in mono- and multilingual children.
+Extensive piloting and adaptation of MAIN materials ensured that the instrument is culturally appropriate, robust and suitable for cross-linguistic comparisons (Gagarina et al., 2012), and new and revised language versions are continuously added to the MAIN database (Gagarina \& Lindgren, 2020).
+
+The present paper aims to describe the development and psychometric properties of a standardized social cognition task that can be adapted to diverse communities.
+Our task focuses on one of the most fundamental social-cognitive abilities: gaze following, that is, the ability to identify the attentional focus of another agent.
 Gaze following develops early in infancy (Del Bianco et al., 2019; Tang et al., 2024) and contributes to social learning, communication, and collaboration (Bohn \& Köymen, 2018; Hernik \& Broesch, 2019; Shepherd, 2010; Tomasello et al., 2007).
-While gaze following is one of the most fundamental social-cognitive abilities, studies focusing on cultural variations are rare.
-The few existing results are mixed on whether gaze following is influenced by cultural factors or not (Callaghan et al., 2011; Hernik \& Broesch, 2019).
-
-The task presented here builds upon the TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open) by Prein et al. (2023).
-The TANGO measures participants' imprecision in locating an agent's attentional focus.
-It has been shown to reliably capture individual differences in a German child sample and an English-speaking remote adult sample.
-The task was sensitive to developmental changes and linked to children's receptive vocabulary.
-Furthermore, an exploratory analysis showed that children performed equally well in a task version with animal faces compared to cartoon human faces (Prein et al., 2024).
-This suggests that superficial variations in the stimulus design do not influence children's performance in the task.
-
-This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that can be -- and has been -- adapted to several languages and communities.
+While the question how social-environmental and cultural factors impact gaze following was recently posed as one of the big open questions in gaze following research (Astor \& Gredebäck, 2022), studies focusing on cultural variations of gaze following are rare.
+Callaghan et al.
+(2011) investigated gaze following behind barriers in 12- and 17-month-olds from rural Canada (n = 35), Peru (n = 38) and India (n = 65).
+In their setup, an agent sat next to a wall or container and looked at a toy behind this barrier (experimental condition) or a sticker in front of it (control condition).
+The researchers then assessed whether and in which conditions the children crawled towards/around the barriers to follow the agent's gaze.
+While the absolute crawling rates differed across communities, children in all three communities crawled more often to gain visual access when the agent looked at an object behind the barrier compared to in front of it.
+Hernik and Broesch (2019) studied 22 infants between 5 to 7 months of age from Vanuatu and used an eye-tracking procedure displaying a local actor looking at one of two objects.
+Even though face-to-face interactions are less common in interactions between caregivers and children in Vanuatu than in Western communities, the result patterns of gaze following in Ni-Vanuatu infants resembled those of their Western counterparts: infants from Vanuatu followed the agent's gaze to the target object only when preceded by infant-directed, and not adult-directed, speech.
+While these two studies point towards a potential cross-cultural stability of gaze following,
+the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings.
+
+The task presented here aims to tackle these issues and builds upon a previously established gaze-following task called `TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by Prein et al.
+(2023).
+The TANGO measures how precisely participants locate an agent's attentional focus.
+It reliably measured individual differences in a German child sample and an English-speaking remote adult sample (Prein et al., 2023).
+As we cannot claim a task's generalizability and reliability based on mono-cultural samples, we need to assess the TANGO's psychometric properties in a larger cross-cultural sample.
+This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 different communities on five continents (Bohn et al., 2024).
 We describe the task's development and provide a tutorial for the open-source website (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).
-We assess its cross-cultural applicability based on data from a large cross-cultural sample of 2.5- to 11-year-olds from 17 different urban/rural communities across the world and discuss the task's psychometrics.
-The task and all its adaptations have been initially designed for a paper by Bohn et al. (2024), and we re-use the data set in this paper.
 
@@
 
-In a perfect world, developing a cross-cultural task would include international collaboration and diverse samples from the beginning, already during study design, piloting and item selection.
-As this seems hardly feasible, we present a pragmatic approach.
-The TANGO-CC was first implemented in one context, in our case Leipzig, Germany (Prein et al., 2023).
-Here, the task's reliability and validity were assessed in detail.
-Even though this does not guarantee that the task will be valid and reliable in another context, it substantially increases the likelihood.
-Second, we reassessed the TANGO--CC's measurement quality (i.e., variability and reliability) across diverse communities by analyzing the data from Bohn et al.
-(2024), who used the task to collect data in 17 communities.
-Therefore, our procedure maintains a balance between a detailed analysis of the task's psychometric properties and a swift and feasible task adaptation.
-In the following, we describe the different steps in further detail.
-We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful for other researchers.
-
-In the first step, the task's underlying structure was designed.
-The TANGO--CC measures the precision with which participants locate an agent's attentional focus.
-The participant's task is to locate a target by following the agent's gaze (see Figure \ref{fig:fig1}).
-Precision was measured in a continuous way as the distance between the participant's click on the screen (\emph{i.e.}, where the participant thinks the target is) and the target's real position.
-The task's core functionality is to animate the agent's eyes so that they follow the target's movement.
-This basic structure was then embedded in the task's superficial appearance (e.g., background scene) and audio instructions.
-Once this structure was implemented, adaptations of the task were greatly simplified.
-For example, we can change the background scene, the faces of the agent, and the target without changing how and what the task measures.
-
-This basic version of the TANGO was psychometrically evaluated in a prototypical WEIRD sample (German child sample; English-speaking remote adult sample) and was found to be highly reliable and valid (Prein et al., 2023).
-While participants got more and more precise in locating the attentional focus of the agent the older they were, individuals differed across all age groups and showed no floor- or ceiling effects.
-Performance in the TANGO was linked to children's receptive vocabulary and weakly related to factors of children's daily social environment.
-In another study, Prein et al. (2024) proposed a computational cognitive model that described gaze following as a social form of vector following.
-Gaze following, as measured by the TANGO, was related to children's non-social vector following and visual perspective-taking abilities.
-These connections to related constructs indicate the task's validity in the tested WEIRD setting.
-
-To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces that were judged by researchers and research assistants from each target community to be representative of the local population (see Figure \ref{fig:fig1}).
-Similarly, different backgrounds were created that roughly represented a typical accommodation in each community.
-Audio instructions were translated into the corresponding local language.
+The TANGO-CC was implemented in Leipzig, Germany, and thoroughly assessed in terms of reliability and validity (Prein et al., 2023).
+During this process, the cross-cultural adaptation of the task was prepared within a team of cross-cultural psychologists and cognitive scientists.
+In this paper, we assess the TANGO--CC's measurement quality (i.e., variability and reliability) across 17 diverse communities by analyzing the data set from Bohn et al. (2024).
+In the following, we describe the different steps in detail.
+
+The TANGO--CC is a screen-based task that measures the imprecision with which participants locate a balloon by following an agent's gaze (see Figure \ref{fig:fig1}).
+Participants click or touch the location on the screen where they believe the balloon to be.
+Precision is measured as the distance between the participant's click on the screen and the balloon's real position.
+
+During the task development, we decided to implement the task's main functionality independently of the task's appearance.
+We programmed a function that calculates the x and y coordinates of where the agent's pupil and iris should move to follow the balloon, given the eyes' and balloon's original positions and measures.
+As the measures of the eyes and balloon are read out dynamically from the image on screen, stimuli can be easily adapted and exchanged.
+No coordination values for animation are hard-coded into the task's source code.
+After having programmed this ``backbone'' functionality of the task (\emph{i.e.}, animate the eyes so that they follow the balloon), we added the task's audio instructions and superficial appearance (e.g., background scene, hedge, more agent faces).
+
+This basic version of the TANGO was psychometrically evaluated in a German child sample and an English-speaking remote adult sample and was found to be highly reliable and valid (Prein et al., 2023).
+While children became more precise in locating the attentional focus of the agent with age, individuals differed across all age groups and showed no floor- or ceiling effects.
+In the Leipzig sample, performance in the TANGO was weakly related to factors of children's daily social environment and could predict children's receptive vocabulary 6 months later.
+In a computational cognitive model, Prein et al.
+(2024) described gaze following as form of social vector following and empirically found that performance in the TANGO was related to children's non-social vector following and visual perspective-taking abilities.
+These connections to related constructs indicate the task's convergent validity in the German child sample.
+
+To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces and background scenes with the feedback from local researchers and research assistants.
+The stimulus pool was adjusted and expanded until the researchers and research assistants from each target community judged the selected stimuli to be representative of the local population and typical accommodation (see Figure \ref{fig:fig2}).
+Audio instructions were translated from English into the corresponding local language(s).
 By back-translating these instructions, we ensured the original meaning did not change.
-Sometimes, specific words were linguistically slightly modified, although functionally equivalent (e.g., ``bush'' instead of ``hedge''), to ensure that all participants understood the instructions.
+Sometimes, specific words were slightly modified in the target language (e.g., ``bush'' instead of ``hedge'') to ensure that all participants understood the instructions well.
+Based on these adaptations, the TANGO--CC could be applied in 17 communities and 13 different languages (Bohn et al., 2024).
 In the following, we describe how researchers can use and customize the TANGO--CC in more detail.
@@
 
-We quickly recap the TANGO's (Prein et al., 2023) most characteristic features: Participants are asked to locate a balloon with the help of a gaze cue.
-The task consists of three different trial types (see Figure \ref{fig:fig1}).
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/tango-cc-procedure}
+
+}
+
+\caption{\textbf{Screenshots of the trials.} In training 1, an agent looks at a balloon that falls to the ground, and participants have to respond by clicking/touching the balloon.
+In training 2, the balloon falls behind the hedge while its flight is still visible.
+Participants respond by clicking the hedge where they think the balloon is.
+In test trials, the balloon's movement and final position are covered by a hedge, and participants respond by clicking the hedge.
+In the task, all movements are smoothly animated (no still pictures).
+Yellow frames indicate the time point when participants respond (only illustrative, not shown during the task).}\label{fig:fig1}
+\end{figure}
+
+The task consists of three different trial types: training 1, training 2, and test trials (see Figure \ref{fig:fig1}).
 In every trial, participants see an agent (boy or girl) looking out of a house with a balloon (red, blue, green, or yellow) in front of them.
-The balloon falls down to the ground, while the eyes of the agent follow the movement of the balloon in a way that their centers always align.
+The balloon falls down to the ground. The eyes of the agent follow the movement of the balloon in a way that the balloon center and the pupil center always align.
 Depending on the trial type, participants have different visual access to the balloon's position.
-In training 1, participants see the full trajectory of the balloon and directly have to touch the balloon itself.
+In training 1, participants see the full trajectory of the balloon and directly have to click the balloon itself.
 In training 2, participants see most of the balloon's movement, but a hedge covers the final location.
@@
 
-The outcome variable is the distance between the participant's touch and the balloon's center.
-Trials can be completed quickly and efficiently so that children can easily complete 15 trials within 10 minutes.
-This drastically reduces drop-out rates.
-By using essentially self-explanatory animations, language demands are kept to a minimum.
-No differential feedback is given to keep trials comparable and avoid learning effects.
+The outcome variable is the distance between the participant's click and the balloon's center.
+Trials can be completed quickly and efficiently so that children can complete 15 trials within 10 minutes, and few children fail to complete the task.
+By using self-explanatory animations, language demands are kept to a minimum.
+The task uses simple audio instructions, which makes the task accessible to children from different age groups, and no reading skills are needed.
+There is no feedback during the task to prevent learning effects across trials.
 
@@
 All agents, balloon colors, and bins appear equally often and are not repeated in more than two consecutive trials.
-If the total number of trials is not divisible by the number of unique elements, additional elements are randomly selected to make up for the remainder.
+If the total number of trials is not divisible by the number of unique elements, some elements (\emph{i.e.,} some agents, balloon colors, bins) are randomly repeated to make up for the remainder.
 
@@
 
-The TANGO--CC can be accessed via the following link: (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).
-In the first step, researchers can select the language for audio instructions, currently available for 13 different languages and even more dialects (see Table 1).
-All written instructions are presented in English because they are not directed to the participant but to the research assistant who guides the participant through the task.
-The task can either be started with the default settings or further customized.
+When reseachers visit the TANGO--CC's website
+(\url{https://ccp-odc.eva.mpg.de/tango-cc/}), they can select the language for audio instructions which are currently available for 13 different languages and five more dialects (see Table 1).
+To add a new language, researchers have two options:
+(1) for using their own audio instructions in the offline version of the task, researchers can download the task, exchange the audio instructions in the dist folder (in the folder sounds \textgreater{} custom) and select ``Custom'' in the language drop down menu.
+For detailed instructions, see the TANGO--CC's manual (\url{https://ccp-odc.eva.mpg.de/tango-cc/manual.html}).
+(2) For adding a new language in the online version of the task, researchers can contact the first author of this paper.
+Please note that this option requires new audio recordings by the interested reseachers, which will then be openly available for all users of the task.
+All written instructions in the task are solely for the research assistant to help them guide participants through the task; these instructions are solely available in English.
+The task can either be started with the default settings or further customized by adapting the numbers of trials, agents, and background scenes.
 The default settings use the version applied in Bohn et al. (2024) based on the selected language.
 
-If researchers choose to customize the task (see Figure \ref{fig:fig1}), the number of trials can be chosen for each trial type.
-As the trial types build up on each other, each trial type is necessary to understand the structure of the task and needs to be completed before the next trial type starts.
-Therefore, no trial type can be skipped.
+If researchers choose to customize the task (see Figure \ref{fig:fig2}), they can adjust the number of trials for each trial type, but not their sequence.
+Specifically, trial types build on each other and participants need to complete each trial type (without skipping any) to understand the structure of the task.
 The minimum number of trials per type is 1; the maximum is 100.
-One out of four different backgrounds can be selected.
-Finally, there are 50 diverse human faces (50\% female, 50\% male) from which researchers can choose.
-No constraint exists on how many faces are allowed (min 1, max 50).
-Once all the settings are adjusted, the customized task is compiled.
+Furthermore, researchers can customize backgrounds by selecting one of four different backgrounds.
+Finally, researchers can choose from 50 diverse cartoon-like human faces (50\% female, 50\% male) and freely select how many different faces to include (min 1, max 50).
+Once all the settings are selected, the customized task is compiled.
+To save the selected settings, researchers can bookmark the URL to easily access the customized task.
 
 In the last step, researchers can enter an alphanumeric participant identifier (1 - 8 characters) and enable a webcam recording of the participant, if needed.
-To save the selected settings, researchers can bookmark the URL so that the customized task can be easily accessed, and only the participant ID and choice of webcam recording need to be entered again.
-The task can then be started.
-
-The source code of the task is available on GitHub (\url{https://github.com/ccp-eva/tango-cc}).
-By directly editing the \texttt{HTML} and \texttt{JavaScript} code, researchers gain even more flexibility in adjusting the task to their needs.
+A webcam recording might prove especially helpful for unsupervised online data collection to ensure that the participant is alone during the task and no help is provided.
+The participant identifier and webcam choice has to be provided every time the task is run.
+
+The source code of the task is openly available on GitHub (\url{https://github.com/ccp-eva/tango-cc}).
+By directly editing the \texttt{HTML} and \texttt{JavaScript} code, researchers can further modify the task as needed.
+
+We created a public OSF page (\url{https://doi.org/10.17605/OSF.IO/P2EGU}) where we plan to collect data sets that used the TANGO-CC.
+Researchers who have collected data using the TANGO--CC can share their data with the community by contacting the first author of this paper or visiting this OSF repository.
 
@@
 
-\caption{\label{tab:langtab}Languages available for the audio instructions in the TANGO--CC}
+\caption{\label{tab:langtab}Current language options available for the audio instructions in the TANGO--CC}
 
@@
 German & Indo-European & Germany\\
-Hai||om & Khoesan & Namibia\\
-Khewdam & Khoesan & Namibia\\
+(≠Akhoe) Hai||om & Khoe-Kwadi & Namibia\\
+Khwedam & Khoe-Kwadi & Namibia\\
 Lingala & Bantu & Rep. Congo\\
@@
 Shona & Bantu & Zimbabwe\\
-Spanish & Indo-European & Argentina / Mexico\\
-Swahili & Bantu & Uganda\\
+Spanish & Indo-European & Argentina (Rioplatense Spanish) / Mexico (Mexiquense Spanish)\\
+Kiswahili & Bantu & Uganda\\
 Turkish & Turkic & Türkiye\\
@@
 \bottomrule
+\addlinespace
 \end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} In those cases where more than one speaker's country of origin is listed, the audio instructions were recorded multiple times by different speakers.
+For example, the English instructions are available in five different versions.}
+\end{tablenotes}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../figures/TANGO-CC-procedure}
+{\centering \includegraphics[width=1\linewidth]{../figures/tango-cc-screenshot}
 
@@
 
-\caption{\textbf{Customizable components of the TANGO--CC.} Researchers can select the language of the audio instructions, the number of trials per trial type, the background, and the agent's face.
-Screenshots of the trials show the proceeding events: In training 1, an agent looks at a balloon that falls to the ground, and participants have to respond by touching the balloon.
-In training 2, the balloon falls behind the hedge while its flight is still visible.
-Participants respond by touching the hedge where they think the balloon is.
-In test trials, the balloon's movement and final position are covered by a hedge, and participants respond by touching the hedge.
-In the task, all movements are smoothly animated (no still pictures).
-Yellow frames indicate the time point when participants respond (only illustrative, not shown during the task).}\label{fig:fig1}
+\caption{\textbf{Customizable components of the TANGO--CC.} Researchers can select the language of the audio instructions (see Table 1), the number of trials per trial type, the background, and the agent's face.}\label{fig:fig2}
 \end{figure}
@@
 The task was implemented in \texttt{JavaScript}, \texttt{HTML}, and \texttt{CSS} and is presented as a web app.
-It can be accessed on any web browser and does not require prior installation.
-The online version of the task has been proven convenient for unsupervised data collection (for example, using participant recruitment services like \emph{Prolific}; see Prein et al.
-(2023)) and sharing the task internationally.
-Importantly, the web app implementation does not necessarily need a working WIFI connection: An offline, local version of the task can be quickly set up for devices that support Node.js (\url{https://nodejs.org/en}).
-This is an especially useful feature for researchers working in remote areas with limited internet access.
-
-The stimuli are embedded as Scalable Vector Graphics (SVG).
-The setup allows for an easy adaptation of task elements and ensures that picture quality, aspect ratio, and relative object positioning are constant.
-The task is programmed so that responses are only registered when the participant touches the relevant part of the screen (i.e., in test trials, the hedge).
+It can be accessed on any modern web browser on any device (e.g., computer or tablet) and does not require prior installation (please note that configurations of browsers and JavaScript may change in the future).
+Participant's responses can be recorded on a touchscreen or with a mouse or track pad.
+The online version of the task can be used for unsupervised data collection (for example, using online platforms like \emph{Prolific}; see Prein et al.
+(2023)).
+The task can be shared easily internationally by providing the URL.
+Importantly, the web app implementation does not require a working WIFI connection: An offline version of the task can be downloaded and quickly set up for devices that support Node.js (\url{https://nodejs.org/en}).
+This is an especially useful feature for researchers working in locations with limited internet access.
+
+The stimuli are embedded as Scalable Vector Graphics (SVG; an image format that stores image elements via mathematical formulas based on points and lines on a grid).
+SVGs ensure that the picture quality, aspect ratio, and relative object positioning are constant.
+Furthermore, stimuli are added as individual components to the image scene which allows for an easy adaptation of task's elements (in contrast to other image formats that consist of only one combined layer that would need entire replacement).
+The task is programmed so that responses are only registered when the participant clicks the relevant part of the screen (i.e., in test trials, when they click the hedge).
 Furthermore, clicks are only registered after the voice recordings stop playing.
@@
 The file will be stored in the device's downloads folder and is named after the following pattern: ``tangoCC-participantID-YYYY-MM-DD\_hh\_mm\_ss''.
+To modify the storage location on the device, researchers can change the designated downloads folder in the browser settings.
 
@@
 
-We used the data set from Bohn et al. (2024) for the psychometric evaluation of the TANGO--CC.
-They collected data using the TANGO--CC in a sample of \emph{N} = 1377 children between 2.5 to 11 years of age.
+We used the data set from Bohn et al. (2024) for psychometric evaluation of the TANGO--CC.
+The data set contains a sample of \emph{N} = 1377 children, aged 2.5 to 11 years.
 Participants came from 17 communities on five continents, in rural and urban settings, with varying degrees of market integration and technology exposure.
-Bohn et al. (2024) carried out 19 trials (1 training 1, 2 training 2, and 16 test trials, of which the first of each type had audio instructions).
+Bohn et al. (2024) carried out 19 trials (1 training 1, 2 training 2, and 16 test trials, of which the first of each type had audio instructions) on a touchscreen device.
 Faces, backgrounds, and languages were chosen by researchers and assistants with experience in the specific community.
-For further details on the communities and data collection procedures, see the supplements of Bohn et al. (2024).
+For further details on the communities, participant information, and data collection procedures, see the supplements of Bohn et al. (2024).
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../figures/TANGO-CC-results}
+{\centering \includegraphics[width=1\linewidth]{../figures/tango-cc-variability}
 
@@
 
-\caption{\textbf{Measurement of the TANGO--CC by community.} (A) Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type.
-Imprecision is defined as the distance between the participant's touch and the balloon's center in units of balloon width.
-For a depiction of each trial's procedure, see Figure \ref{fig:fig1}.
-(B) Internal consistency estimates by community, following three different approaches.
-In the odd-even split, the size of points reflects the sample size in each community.
-In the stratified approach with and without age correction, density curves show the posterior distributions of the GLMM.}\label{fig:fig2}
+\caption{\textbf{Variability measured by the TANGO--CC.} Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type.
+Imprecision is defined as the distance between the participant's click and the balloon's center in units of balloon width.
+For a depiction of each trial's procedure, see Figure \ref{fig:fig1}.}\label{fig:fig3}
 \end{figure}
@@
 First, we inspected the mean and standard deviations by community and compared performance in each trial type (training 1, training 2, test trials).
-Performance was defined as the absolute click distance between the target center and the click x coordinate (measured in balloon widths).
-Across communities, children performed best in training 1 (mean = 0.19, sd = 0.63), followed by training 2 (mean = 0.79, sd = 1.44) and test trials (mean = 2.21, sd = 2.03; see Figure \ref{fig:fig2}A).
-
-To formally estimate the effect of trial type on performance in the TANGO--CC, we fit a generalized linear mixed model (GLMM) predicting the task performance by trial type (reference category: test trials).
+Performance was defined as the absolute distance between the target center and the x coordinate of the participant's click (measured in balloon widths).
+Across communities, children performed best in training 1 (mean = 0.19, sd = 0.63), followed by training 2 (mean = 0.79, sd = 1.44) and test trials (mean = 2.21, sd = 2.03; see Figure \ref{fig:fig3}).
+
+To formally estimate the effect of trial type on performance in the TANGO--CC, we fitted a generalized linear mixed model (GLMM) predicting the task performance by trial type (reference category: test trials).
 All analyses were run in R version 4.4.0 (2024-04-24) (R Core Team, 2024).
@@
 Our GLMM analysis supported the visual inspection of the data: the fixed-effect estimates for training 1 (\(\beta\) = -3.26; 95\% CrI {[}-3.41; -3.10{]}) and training 2 (\(\beta\) = -1.47; 95\% CrI {[}-1.58; -1.35{]}) were negative and reliably different from zero.
-Please note that the TANGO--CC measures imprecision in gaze following.
-Therefore, a negative sign shows that children showed less imprecision (i.e., were more precise) in the training trials than in the test trials.
+\footnote{Please note that the TANGO--CC measures imprecision in gaze following.
+  Therefore, a negative sign indicates that children showed less imprecision (i.e., were more precise) in the training trials than in the test trials.}
 This effect was found across all communities (random effects of trial type within community: minimum estimate for training 1 = -2.87; 95\%CrI {[}-3.11; -2.60{]}; minimum estimate for training 2 = -1.27; 95\%CrI {[}-1.51; -0.98{]}).
-The almost perfect performance in training trials indicated that children understood the task and were able to locate the balloon.
+The almost perfect performance in training trials indicated that children understood the task and were able to correctly indicate the location of the balloon when its path was (mostly) visible.
 In test trials, children's imprecision was higher, indicating that the task was more challenging.
-All communities showed substantial individual variation and overlapped in their imprecision levels (see Figure \ref{fig:fig2}A).
+All communities showed substantial individual variation and overlapped in their imprecision levels (see Figure \ref{fig:fig3}).
 
 To identify the sources of variation, we computed intraclass correlations (ICC).
-The variation of children within communities was substantially larger than the variation between the communities.
+The variation of children's imprecision within communities was substantially larger than the variation between the communities.
 The mean within-community variance was 1.28, ranging from 0.24 (in Pune, India) to 3.46 (in Chimfunshi, Zambia).
@@
 The ICC, representing the proportion of between-community variance relative to the total variance (sum of within- and between-community variance), was 0.02.
-This indicates that only 2\% of the total variability in the data can be attributed to differences between communities, while the remaining 98\% are attributed to differences within communities (Kusano et al., 2024).
+This indicated that only 2\% of the total variability in the data could be attributed to differences between communities, while the remaining 98\% were attributed to differences within communities (Kusano et al., 2024).
 
 \subsection{Reliability}\label{reliability}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/tango-cc-reli}
+
+}
+
+\caption{\textbf{Reliability of the TANGO--CC by community.} Internal consistency estimates by community, following three different approaches.
+In the odd-even split, the size of points reflects the sample size in each community.
+In the stratified approach with and without age correction, density curves show the posterior distributions of the GLMM.}\label{fig:fig4}
+\end{figure}
 
@@
 Second, using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2022), data was stratified by target centrality (capturing trial difficulty), and a Pearson correlation was calculated between the matched halves.
-Third, a data set was generated with stratified test halves by target centrality.
-Then, we followed the Generalized Linear Mixed Model (GLMM) approach introduced by Rouder and Haaf (2019).
+Third, a data set was generated with stratified test halves by target centrality and we applied the Generalized Linear Mixed Model (GLMM) approach introduced by Rouder and Haaf (2019).
 A GLMM was fitted with the mean imprecision as the outcome, age as the predictor, and test half and participant id as random effects (model notation: \texttt{imprecision\ \textasciitilde{}\ age\ +\ (0\ +\ half\ \textbar{}\ subjid)}).
@@
 
-The results are shown in Figure \ref{fig:fig2}C.
+The results are shown in Figure \ref{fig:fig4}.
 Across communities, internal consistency estimates ranged from 0.51 to 0.80 for the odd-even split, 0.62 to 0.89 for the stratified internal consistency, and 0.62 to 0.87 for the age-corrected approach (Plymouth, UK, being an outlier with 0.28).
@@
 In an exploratory analysis, we found that communities with larger individual variation showed higher internal consistency estimates (Pearson's \emph{r} = 0.46, 95\%CI {[}-0.03; 0.77{]}).
-Please note that this could be influenced by outliers and that the sample size here (\emph{N} = 17 communities) is too small to make substantial claims.
+This suggests that the less variation a task can capture within a community, the lower the reliability.
+However, please note that this correlation could be influenced by outliers and that the sample size here (\emph{N} = 17 communities) is too small to make substantial claims.
 
@@
 The TANGO--CC measures imprecision in gaze following across individuals, ages, and communities.
-The task was developed in two phases.
-First, the task's underlying functionality was designed in one community.
-Next, we adapted the superficial features of the task to be used in 17 diverse communities and assessed the task's psychometric properties.
-Children's imprecision in gaze following highly overlapped between communities: children performed better in the training than the test trials, and within-community variation greatly exceeded between-community variation.
-The task showed satisfactory to high reliability across all communities.
-Therefore, we believe the TANGO--CC is a promising task to capture individual differences in social-cognitive development in diverse communities.
-Its design process lays out a much-needed pragmatic approach to conducting cross-cultural individual differences research.
-
-A similar approach to task development was taken by Mehta et al. (2011).
-The researchers (1) selected social cognition measures that have been established in WEIRD settings, (2) adapted the agent's names, appearance, backgrounds, and languages to the local context, and (3) assessed the task's validity and internal consistency in the new setting.
-Participants were adults with and without schizophrenia from India. Theory of Mind tasks included Sally-Anne, Smarties, Ice cream van and Missing cookies stories.
-For this specific context, the authors' approach yielded a successful adaptation of social cognition measures for the tested Indian (Hindi/Kannada) communities.
+Children's imprecision in gaze following showed highly similar result patterns across communities: children performed better in the training than the test trials, and within-community variation greatly exceeded between-community variation.
+Furthermore, the task showed satisfactory to high reliability across all communities.
+Therefore, the TANGO--CC is a suitable task to capture individual differences in social-cognitive development in diverse communities.
+
+The TANGO--CC's design process lays out a much-needed pragmatic approach to studying community-level and individual-level differences across cultures:
+While we performed a detailed psychometric evaluation of the task in a German setting, we collaborated with local researchers for the cross-cultural stimulus development and selection.
+Importantly, we re-assessed the TANGO--CC's psychometric properties in a large and diverse sample of children.
+The data set by Bohn et al.
+(2024) showed that data collection with the TANGO--CC was feasible in 17 diverse communities in rural and urban settings with varying degrees of market integration and technology exposure.
+While we cannot generalize our findings to all communities worldwide, we found that the TANGO-CC captured reliable individual variation in all communities studied by Bohn et al. (2024).
+We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful for other researchers.
+Using the TANGO--CC (or any other task) in a new community requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
+We recommend that researchers consider generalizability concerns and cross-cultural applications of their tasks and collaborate with local researchers at early stages of task development (Torréns et al., 2023).
 
 Bourdage et al. (2023) pointed out a major challenge with adapting social cognition tasks to diverse communities: the number of world cultures is vast, and communities are constantly changing.
-Therefore, a promising approach might be to provide tasks with a modular system where components can be exchanged according to the local context.
-In the case of the TANGO--CC, the task can not only be adapted to different languages, cartoon faces, and backgrounds (see Figure \ref{fig:fig1}) but also updated with new stimuli.
-Unlike studies that present sequential, hand-painted pictures that are difficult to adapt (Mehta et al., 2011), the TANGO--CC uses SVGs that can be easily exchanged.
-
-The biggest strength of the TANGO--CC is its flexibility.
-The task is presented as a web app that can also run offline to enable remote data collection.
-Minimal language demands and an engaging, playful design increase the task's usability.
-Together with a short task duration, this reduces drop-out rates and enables efficient data collection with large sample sizes.
-The TANGO--CC follows a standardized procedure and uses a continuous, objective outcome measure (leaving no room for rater errors).
-An online manual with the most frequently asked questions is available at \url{https://ccp-odc.eva.mpg.de/tango-cc/manual.html}.
-Additional customization can be achieved by adding new stimuli to the open-source code available on GitHub (\url{https://github.com/ccp-eva/tango-cc}).
-
-For years, researchers have called for more diverse sampling and culturally valid measures of cognitive development (Matsumoto \& Yoo, 2006; e.g., Mehta et al., 2011; Nielsen et al., 2017).
-As Hajdúk et al.
-(2020) put it, ``using large samples and multisite approaches will align with efforts to improve reproducibility and will clarify both the type and extent of cultural influences on social cognition'' (p.~463).
-The TANGO--CC takes a valuable step in this direction by sharing the task and its source code with other researchers.
-Bohn et al. (2024) showed that data collection with the TANGO--CC was feasible in 17 diverse communities in rural and urban settings with varying degrees of market integration and technology exposure.
-While we cannot generalize our findings to all communities worldwide, we found that it captured reliable individual variation in the 17 communities studied by Bohn et al. (2024).
-Using the TANGO--CC in a new community nevertheless requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
-We hope that the TANGO--CC will facilitate future cross-cultural studies to assess social-cognitive development in a wide range of communities.
-
-A valid question is whether the TANGO--CC measures the same construct across different groups.
-This so-called measurement invariance is often seen as a requirement for a ``fair'' cross-cultural comparison and relies on minimizing group differences while individual differences are magnified.
+Therefore, a promising approach might be to provide tasks with a modular system where components can be modified (\emph{i.e.}, building block structure).
+In the case of the TANGO--CC, the task cannot only be adapted to different languages, cartoon faces, and backgrounds (see Figure \ref{fig:fig2}) but also updated with new stimuli.
+Unlike studies that present sequential, hand-painted pictures that are difficult to adapt (Mehta et al., 2011), the TANGO--CC uses SVGs (Scalable Vector Graphics) that can be easily exchanged.
+
+Compared to one of the most commonly used social cognition measure -- the change-of-location false belief task (Baron-Cohen et al., 1985; Wimmer \& Perner, 1983) -- the TANGO--CC has several advantages: a continuous outcome measure which can capture individual differences, a short task duration that allows for more trials per child, stimuli that can be easily adapted, and known psychometric properties across 17 communities.
+The task is presented as a web app that enables efficient data collection with large sample sizes, while it can also be used to collect data offline in locations without reliable internet connection.
+The TANGO--CC follows a standardized procedure, which leaves no room for rater errors and greatly simplifies online training of research assistants.
+Furthermore, minimal language demands and an engaging, playful design increase the task's usability and reduce non-completion rates.
+
+The TANGO--CC is a screen-based task.
+Bohn et al. (2024) have shown that children with no prior touchscreen exposure were less precise in the TANGO--CC than children with prior experience.
+However, individual differences were also found in communities with 100\% touchscreen exposure, showing that this factor alone could not explain children's performance in the task (Bohn et al., 2024).
+Notably, even though the touchscreen experience caused absolute differences in task performance, all communities showed the same processing signature.
+A recent computational cognitive model described gaze following as a process of estimating pupil angles and the corresponding gaze vectors (Prein et al., 2024).
+Bohn et al. (2024) found clear support for this model in every community studied, suggesting that children all over the world process gaze in a similar way.
+Nevertheless, the mode of stimulus presentation needs to be kept in mind when administering the TANGO--CC, especially in communities with little technology exposure.
+Additional touchscreen training (e.g., more trials of training 1) might prove helpful in these cases.
+
+Schilbach et al. (2013) pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions.
+First evidence suggests that the TANGO--CC indeed taps into social cognition as utilized in real life: Prein et al.
+(2024) found that children's perspective-taking abilities in a personal social interaction was linked to performance in the TANGO, but less so to a matched, non-social vector following task.
+However, this study exclusively relied on a German sample and future research should investigate whether the relationship between the TANGO--CC and perspective-taking abilities holds across communities.
+
+We have reported reliability estimates for each community by calculating internal consistency.
+Ideally, we would have additionally evaluated the task's test-retest reliability in each community and checked for relationships with theoretically related constructs to assess validity.
+Unfortunately, this might not always be feasible in large-scale cross-cultural studies due to organizational and financial constraints.
+An example of assessing the TANGO's predictive validity is a study conducted in Leipzig, Germany, which used the TANGO to predict children's receptive vocabulary 6 months later (Prein et al., 2023).
+Future cross-cultural studies could investigate the TANGO--CC's predictive validity and its relationship to other social-cognitive abilities (e.g., Theory of Mind, language development) in diverse communities.
+
+Measurement invariance (\emph{i.e.}, measuring the same construct across different communities) is often seen as a requirement for a ``fair'' cross-cultural comparison: it is important that any group differences are not the result of the task unintentionally tapping into different underlying constructs.
 As Kusano et al.
@@
 We argue that the TANGO--CC measures a fundamental social-cognitive ability that is likely similar across communities.
-Bohn et al. (2024) have shown that children with no prior touchscreen exposure were less precise in the TANGO--CC than children with prior experience.
-However, individual differences were also found in communities with 100\% touch screen exposure, showing that this factor alone could not explain children's performance in the task (Bohn et al., 2024).
-Notably, even though the touchscreen experience caused absolute differences in task performance, all communities showed the same processing signature.
-A recent computational cognitive model described gaze following as a process of estimating pupil angles and the corresponding gaze vectors (Prein et al., 2024).
-The model predicted that all individuals use the same process to locate an attentional focus but differ in their uncertainty around the estimated pupil angles, which results in less precision.
-Bohn et al. (2024) found clear support for this model in every community they studied, suggesting that children all over the world process gaze in a similar way.
-In this manuscript, we could also show that internal consistency was high across all communities, meaning that the task captured individual differences in a similar way.
-Consequently, the TANGO--CC seems to measure systematic individual differences across diverse communities.
-
 Selcuk et al.
@@
 
-\section{Limitations}\label{limitations}
-
-The TANGO--CC and its psychometric properties need to be considered against some limitations.
-Reliability for each community was assessed by calculating the internal consistency.
-Ideally, we would have additionally assessed the task's retest reliability in each community and checked for relationships with theoretically related constructs to assess validity.
-
-Schilbach et al. (2013) pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions.
-Of course, the TANGO--CC does not depict real-life social interaction, and future research should investigate how task performance relates to the real world.
-Suggestive evidence comes from a study by Prein et al.
-(2024), who found that children's performance in the TANGO was linked to children's visual perspective-taking abilities in real-life social interaction.
-The mode of stimulus presentation surely needs to be kept in mind when administering the TANGO--CC, especially in communities with little technology exposure.
-Additional touch screen training (e.g., more trials of training 1) might prove helpful in these cases.
+For years, researchers have called for more diverse sampling and culturally valid measures of cognitive development (Matsumoto \& Yoo, 2006; e.g., Mehta et al., 2011; Nielsen et al., 2017).
+As Hajdúk et al.
+(2020) said, ``using large samples and multisite approaches will align with efforts to improve reproducibility {[}replicability{]} and will clarify both the type and extent of cultural influences on social cognition'' (p.~463).
+Similarly, Elson et al.
+(2023) have called for standardized, psychometrically evaluated measures that can be re-used by other researchers in order to ``build a cumulative evidence base in psychology'' (p.~2).
+This underlines how efforts to improve the replicability can be combined with the goal of increasing the generalisability of psychological research (Li et al., 2024; Syed, 2021).
+Li et al.
+(2024) have argued that replicable and generalisable results rely on stimulus sets with slight variations, more diverse samples, and data collection at a greater scale, which are all steps the TANGO--CC has taken.
+Openly sharing the TANGO--CC's materials will allow other researchers to (hopefully) replicate the results and deepen our cumulative understanding of social-cognitive development across diverse communities.
 
@@
 
-The TANGO--CC is a promising task to capture individual differences in social-cognitive development across diverse communities.
-The task was developed in two phases: (1) implementing the task's underlying functionality and estimating detailed psychometrics in one community, and (2) expanding the stimulus pool to accommodate diverse communities worldwide.
-The task's flexibility, minimal language demands, and engaging design make it a valuable task for cross-cultural research.
-The task showed satisfactory to high reliability (internal consistency) in a large dataset including 17 diverse communities.
-We hope that the TANGO--CC -- and its pragmatic construction process -- will inspire future cross-cultural studies to assess cognitive development in a wide range of communities.
+The TANGO--CC captures individual differences in social-cognitive development across diverse communities.
+The task's customizability, minimal language demands, and its efficient data collection method make it a valuable task for cross-cultural research.
+The task showed satisfactory to high reliability (internal consistency) in a large data set including 17 diverse communities on five continents.
+We hope that the TANGO--CC -- and its pragmatic construction process -- will provide a roadmap for future cross-cultural studies on cognitive development.
 
@@
 \begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-adolphs1999social}
+Adolphs, R. (1999). Social cognition and the human brain. \emph{Trends in Cognitive Sciences}, \emph{3}(12), 469--479. \url{https://doi.org/10.1016/S1364-6613(99)01399-6}
+
+\bibitem[\citeproctext]{ref-amir2020crosscultural}
+Amir, D., \& McAuliffe, K.
+(2020).
+Cross-cultural, developmental psychology: Integrating approaches and key insights.
+\emph{Evolution and Human Behavior}, \emph{41}(5), 430--444.
+\url{https://doi.org/10.1016/j.evolhumbehav.2020.06.006}
+
+\bibitem[\citeproctext]{ref-apicella2020weird}
+Apicella, C., Norenzayan, A., \& Henrich, J.
+(2020).
+Beyond {WEIRD}: {A} review of the last decade and a look ahead to the global laboratory of the future.
+\emph{Evolution and Human Behavior}, \emph{41}(5), 319--329.
+\url{https://doi.org/10.1016/j.evolhumbehav.2020.07.015}
+
+\bibitem[\citeproctext]{ref-arnett2008neglecteda}
+Arnett, J.
+J.
+(2008).
+The neglected 95\%: {Why American} psychology needs to become less {American}.
+\emph{American Psychologist}, \emph{63}(7), 602--614.
+\url{https://doi.org/10.1037/0003-066X.63.7.602}
+
+\bibitem[\citeproctext]{ref-astor2022gaze}
+Astor, K., \& Gredebäck, G.
+(2022).
+Gaze following in infancy: {Five} big questions that the field should answer.
+In \emph{Advances in {Child Development} and {Behavior}} (p.
+S0065240722000192).
+Elsevier.
+\url{https://doi.org/10.1016/bs.acdb.2022.04.003}
+
+\bibitem[\citeproctext]{ref-baron-cohen1985does}
+Baron-Cohen, S., Leslie, A. M., \& Frith, U. (1985). Does the autistic child have a "theory of mind" ? \emph{Cognition}, \emph{21}, 37--46. \url{https://doi.org/10.1016/0010-0277(85)90022-8}
+
 \bibitem[\citeproctext]{ref-beaudoin2020systematic}
@@
 \emph{A universal of human social cognition: {Children} from 17 communities process gaze in similar ways}.
-OSF.
+PsyArXiv.
 \url{https://doi.org/10.31234/osf.io/z3ahv}
@@
 
+\bibitem[\citeproctext]{ref-broesch2023roadmap}
+Broesch, T., Lew-Levy, S., Kärtner, J., Kanngiesser, P., \& Kline, M.
+(2023).
+A roadmap to doing culturally grounded developmental science.
+\emph{Review of Philosophy and Psychology}, \emph{14}(2), 587--609.
+\url{https://doi.org/10.1007/s13164-022-00636-y}
+
 \bibitem[\citeproctext]{ref-burkner2017brms}
@@
 
-\bibitem[\citeproctext]{ref-chasiotis2006theory}
-Chasiotis, A., Kiessling, F., Hofer, J., \& Campos, D.
-(2006).
-Theory of mind and inhibitory control in three cultures: {Conflict} inhibition predicts false belief understanding in {Germany}, {Costa Rica} and {Cameroon}.
-\emph{International Journal of Behavioral Development}, \emph{30}(3), 249--260.
-\url{https://doi.org/10.1177/0165025406066759}
-
 \bibitem[\citeproctext]{ref-cohen1988statistical}
@@
 Cohen, J. (1992). A power primer. \emph{Psychological Bulletin}, \emph{112}(1), 155--159. \url{https://doi.org/10.1037/0033-2909.112.1.155}
+
+\bibitem[\citeproctext]{ref-decety2020social}
+Decety, J. (Ed.). (2020). \emph{The social brain: {A} developmental perspective} (pp. xii, 426). The MIT Press. \url{https://doi.org/10.7551/mitpress/11970.001.0001}
 
@@
 
+\bibitem[\citeproctext]{ref-elson2023psychological}
+Elson, M., Hussey, I., Alsalti, T., \& Arslan, R.
+C.
+(2023).
+Psychological measures aren't toothbrushes.
+\emph{Communications Psychology}, \emph{1}(1), 1--4.
+\url{https://doi.org/10.1038/s44271-023-00026-9}
+
 \bibitem[\citeproctext]{ref-field2012discovering}
@@
 
-\bibitem[\citeproctext]{ref-fujita2022theory}
-Fujita, N., Devine, R.
-T., \& Hughes, C.
-(2022).
-Theory of mind and executive function in early childhood: {A} cross-cultural investigation.
-\emph{Cognitive Development}, \emph{61}, 101150.
-\url{https://doi.org/10.1016/j.cogdev.2021.101150}
+\bibitem[\citeproctext]{ref-frith2007social}
+Frith, C. D., \& Frith, U. (2007). Social {Cognition} in {Humans}. \emph{Current Biology}, \emph{17}(16), R724--R732. \url{https://doi.org/10.1016/j.cub.2007.05.068}
+
+\bibitem[\citeproctext]{ref-gagarina2012main}
+Gagarina, N., Klop, D., Kunnari, S., Tantele, K., Välimaa, T., Balčiūnienė, I., Bohnacker, U., \& Walters, J.
+(2012).
+\emph{{MAIN}: {Multilingual Assessment Instrument} for {Narratives}}.
+Zentrum f{ü}r Allgemeine Sprachwissenschaft.
+
+\bibitem[\citeproctext]{ref-gagarina2020new}
+Gagarina, N., \& Lindgren, J.
+(2020).
+New language versions of {MAIN}: {Multilingual Assessment Instrument} for {Narratives} -- {Revised}.
+\emph{ZAS Papers in Linguistics}, \emph{64}, 274.
+\url{https://doi.org/10.21248/zaspil.64.2020.543}
 
@@
 
-\bibitem[\citeproctext]{ref-hughes2014lost}
-Hughes, C., Devine, R.
-T., Ensor, R., Koyasu, M., Mizokawa, A., \& Lecce, S.
-(2014).
-Lost in {Translation}?
-{Comparing British}, {Japanese}, and {Italian Children}'s {Theory-of-Mind Performance}.
-\emph{Child Development Research}, \emph{2014}, e893492.
-\url{https://doi.org/10.1155/2014/893492}
-
-\bibitem[\citeproctext]{ref-hughes2018does}
-Hughes, C., Devine, R.
-T., \& Wang, Z.
-(2018).
-Does {Parental Mind-Mindedness Account} for {Cross-Cultural Differences} in {Preschoolers}' {Theory} of {Mind}?
-\emph{Child Development}, \emph{89}(4), 1296--1310.
-\url{https://doi.org/10.1111/cdev.12746}
-
 \bibitem[\citeproctext]{ref-kline1999handbook}
@@
 \url{https://doi.org/10.31234/osf.io/9qe2k}
+
+\bibitem[\citeproctext]{ref-li2024developmental}
+Li, W., Germine, L.
+T., Mehr, S.
+A., Srinivasan, M., \& Hartshorne, J.
+(2024).
+Developmental psychologists should adopt citizen science to improve generalization and reproducibility.
+\emph{Infant and Child Development}, \emph{33}(1), e2348.
+\url{https://doi.org/10.1002/icd.2348}
+
+\bibitem[\citeproctext]{ref-liebal2018crosscultural}
+Liebal, K., \& Haun, D.
+B.
+M.
+(2018).
+Why {Cross-Cultural Psychology Is Incomplete Without Comparative} and {Developmental Perspectives}.
+\emph{Journal of Cross-Cultural Psychology}, \emph{49}(5), 751--763.
+\url{https://doi.org/10.1177/0022022117738085}
 
@@
 {TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults.
-\emph{Behavior Research Methods}.
+\emph{Behavior Research Methods}, \emph{56}(3), 2469--2485.
 \url{https://doi.org/10.3758/s13428-023-02159-5}
@@
 
-\bibitem[\citeproctext]{ref-stengelin2020cultural}
-Stengelin, R., Hepach, R., \& Haun, D.
-B.
-M.
-(2020).
-Cultural variation in young children's social motivation for peer collaboration and its relation to the ontogeny of {Theory} of {Mind}.
-\emph{PLOS ONE}, \emph{15}(11), e0242071.
-\url{https://doi.org/10.1371/journal.pone.0242071}
+\bibitem[\citeproctext]{ref-syed2021reproducibility}
+Syed, M. (2021). \emph{Reproducibility, {Diversity}, and the {Crisis} of {Inference} in {Psychology}}. OSF. \url{https://doi.org/10.31234/osf.io/89buj}
 
@@
 
-\bibitem[\citeproctext]{ref-taumoepeau2019crosscultural}
-Taumoepeau, M., Sadeghi, S., \& Nobilo, A.
-(2019).
-Cross-cultural differences in children's theory of mind in {Iran} and {New Zealand}: {The} role of caregiver mental state talk.
-\emph{Cognitive Development}, \emph{51}, 32--45.
-\url{https://doi.org/10.1016/j.cogdev.2019.05.004}
+\bibitem[\citeproctext]{ref-thalmayer2021neglecteda}
+Thalmayer, A.
+G., Toscanelli, C., \& Arnett, J.
+J.
+(2021).
+The neglected 95\% revisited: {Is American} psychology becoming less {American}?
+\emph{American Psychologist}, \emph{76}(1), 116--129.
+\url{https://doi.org/10.1037/amp0000622}
 
@@
 \url{https://doi.org/10.1016/j.jhevol.2006.10.001}
+
+\bibitem[\citeproctext]{ref-torrens2023einfluss}
+Torréns, M.
+G., Wefers, H., \& Kärtner, J.
+(2023).
+Der {Einfluss} von {Kultur} auf die {Entwicklung} in den ersten drei {Lebensjahren}.
+\emph{Zeitschrift f{ü}r Entwicklungspsychologie Und P{ä}dagogische Psychologie}, \emph{55}(1), 14--18.
+\url{https://doi.org/10.1026/0049-8637/a000271}
 
@@
 
+\bibitem[\citeproctext]{ref-wefers2023universality}
+Wefers, H., Schuhmacher, N., Chacón, L.
+H., \& Kärtner, J.
+(2023).
+Universality without uniformity -- infants' reactions to unresponsive partners in urban {Germany} and rural {Ecuador}.
+\emph{Memory \& Cognition}, \emph{51}(3), 807--823.
+\url{https://doi.org/10.3758/s13421-022-01318-x}
+
+\bibitem[\citeproctext]{ref-wimmer1983beliefs}
+Wimmer, H., \& Perner, J.
+(1983).
+Beliefs about beliefs: {Representation} and constraining function of wrong beliefs in young children's understanding of deception.
+\emph{Cognition}, \emph{13}(1), 103--128.
+\url{https://doi.org/10.1016/0010-0277(83)90004-5}
+
+\bibitem[\citeproctext]{ref-zeigler-hill2015how}
+Zeigler-Hill, V., Welling, L.
+L., \& Shackelford, T.
+K.
+(2015).
+How can an understanding of evolutionary psychology contribute to social psychology?
+In \emph{Evolutionary perspectives on social psychology} (pp.
+3--12).
+Springer, Cham.
+
 \end{CSLReferences}

### 2024-06-12 stats/analysis.Rmd
incorporate co-author feedback

@@
 saveRDS(training_trials_plot, "../saves/training_trials_plot.rds")
+
+ggsave("../figures/tango-cc-variability.png", width = 15, height = 11, scale = 0.7, bg = "white")
 ```
@@
 
+```{r}
+library(ggplot2)
+library(ggridges)
+
+# Create example data
+data <- data.frame(
+  x = rnorm(1000),
+  y = as.factor(rep(1:10, each = 100))
+)
+
+# Plot using geom_density_ridges
+ggplot(data, aes(x = x, y = y)) +
+  geom_density_ridges()
+
+```
+
 ```{r combine_plot}
-# odd_even_plot <- readRDS("../saves/odd_even_plot.rds")
-# stratified_plot <- readRDS("../saves/stratified_plot.rds")
-# stratified_agecorrected_plot <- readRDS("../saves/stratified_agecorrected_plot.rds")
-# training_trials_plot <- readRDS("../saves/training_trials_plot.rds")
+odd_even_plot <- readRDS("../saves/odd_even_plot.rds")
+stratified_plot <- readRDS("../saves/stratified_plot.rds")
+stratified_agecorrected_plot <- readRDS("../saves/stratified_agecorrected_plot.rds")
+training_trials_plot <- readRDS("../saves/training_trials_plot.rds")
 
@@
   widths = c(1.7, 1.2, 1.2), 
-  nrow = 1,
-  labels = c("B", "C", "", "") 
+  nrow = 1
 )
 
-ggarrange(
-  training_trials_plot,
-  top_row,
-  nrow = 2,
-  heights = c(3, 1.5),
-  labels = c("A", "") 
-)
+ggsave("../figures/tango-cc-reli.png", width = 12, height = 6, scale = 0.8, bg = "white")
 
-ggsave("../figures/tango-cc-results.png", width = 12, height = 11, scale = 0.9, bg = "white")
+# top_row <- ggarrange(
+#   odd_even_plot,
+#   stratified_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
+#   stratified_agecorrected_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
+#   widths = c(1.7, 1.2, 1.2), 
+#   nrow = 1,
+#   labels = c("B", "C", "", "") 
+# )
+# 
+# ggarrange(
+#   training_trials_plot,
+#   top_row,
+#   nrow = 2,
+#   heights = c(3, 1.5),
+#   labels = c("A", "") 
+# )
+# 
+# ggsave("../figures/tango-cc-results.png", width = 12, height = 5, scale = 0.7, bg = "white")
 ```

### 2024-06-12 supplements/supplements.Rmd
incorporate co-author feedback

---
title: "Supplements for the manuscript 'Measuring variation in gaze following across communities, ages, and individuals — a showcase of the TANGO-CC'"
shorttitle: "supplements"

author: 
  - name : "Julia Christin Prein"
  - name : "Florian M. Bednarski"
  - name : "Ardain Dzabatou"
  - name : "Michael C. Frank"
  - name : "Annette M. E. Henderson"
  - name : "Josefine Kalbitz"
  - name : "Patricia Kanngiesse"
  - name : "Dilara Keşşafoğlu"
  - name : "Bahar Köymen"
  - name : "Maira V. Manrique-Hernandez"
  - name : "Shirley Magazi"
  - name : "Lizbeth Mújica-Manrique"
  - name : "Julia Ohlendorf"
  - name : "Damilola Olaoba"
  - name : "Wesley R. Pieter"
  - name : "Sarah Pope-Caldwell"
  - name : "Umay Sen"
  - name : "Katie Slocombe"
  - name : "Robert Z. Sparks"
  - name : "Roman Stengelin"
  - name : "Jahnavi Sunderarajan"
  - name : "Kirsten Sutherland"
  - name : "Florence Tusiime"
  - name : "Wilson Vieira"
  - name : "Zhen Zhang"
  - name : "Yufei Zong"
  - name : "Daniel B. M. Haun"
  - name : "Manuel Bohn"

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
classoption       : "man"
header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{unicode-math}
  - \usepackage{setspace}
  - \usepackage{libertine}
  - \captionsetup[figure]{font={stretch=1}}
  - \renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
  - \renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}

    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            :   
  papaja::apa6_pdf:
    latex_engine: xelatex
    keep_tex: true
editor_options    : 
  markdown: 
    wrap: sentence
bibliography      : "../../references.bib"
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```

```{r setup, include = FALSE}
library("papaja")
library("tidyverse")
library("ggpubr")
library("kableExtra")
library("brms")
theme_set(theme_classic())
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Voice-over script 
The TANGO--CC was designed for a cross-cultural study by @bohn2024universal. For further information on the sample and further methodological choices, see their supplementary material ().

Here, we repeat the voice over script as it was presented in @bohn2024universal. The first trial of each trial type played audio descriptions of the presented events, and the voice-over script in English was as follows:

## Welcome (before the start of the task)

Hello! Great that you’re here. We’ll now play a balloon game. Can you see the children in the picture over there? We want to play together with the children using the balloon. We’ll now talk you through exactly what will happen.

## Training 1

Look, a girl/boy is standing in the window. And can you see the balloon over there? The balloon always falls down and lands on the ground. And you have to find it! The girl/boy helps you and always looks at the balloon.

[balloon falls down]

Where is the balloon? Touch the balloon!

## Training 2

Perfect, that was great! Now, we’ll continue playing. Can you see the girl/boy and the balloon again? The balloon will fall down again. This time, it will fall behind a hedge. And you have to find it! The girl/boy helps you and looks at the balloon.

[balloon falls down]

Where is the balloon? On the hedge, touch where the balloon is.

## Test

Nice, good job! Now, we’ll continue playing. There is the balloon, the girl/boy and the hedge. The hedge is growing a bit now.

The balloon is behind the hedge now. You can’t see it - but the girl/boy can! The balloon falls to the ground and you have to find it. Remember - the girl/boy always looks at the balloon!

## Goodbye (after the last test trial)

The children are super happy after playing. Thanks a lot for your help! See you soon and goodbye!

# Default settings

When researchers use the default settings of the TANGO-CC, the following settings are applied based on the selected language. Visit this website https://ccp-odc.eva.mpg.de/tango-cc/customize.html and hover over the agent faces to view their IDs.

-  Bemba (Zambia): background 01, agents f01-f02-f03-f04-m01-m02-m03-m04
-  Chinese (China): background 01, agents f18-f19-f20-f21-m18-m19-m20-m21
-  English (India): background 01, agents f22-f23-f24-f25-m22-m23-m24-m25
-  English (New Zealand): background 01, agents f05-f06-f11-f15-m05-m06-m11-m15
-  English (Nigeria): background 01, agents f01-f02-f03-f04-m01-m02-m03-m04
-  English (UK): background 01, agents f05-f07-f08-f10-m03-m06-m09-m11
-  English (USA): background 01, agents f01-f05-f06-f09-m05-m06-m08-m09
-  German (Germany): background 01, agents f05-f07-f08-f10-m03-m06-m09-m11
-  Hai||kom (Namibia): background 01, agents f01-f02-f03-f04-m01-m02-m03-m04
-  Khwedam (Namibia): background 01, agents f01-f02-f03-f04-m01-m02-m03-m04
-  Lingala (Rep. Congo): background 02, agents f01-f02-f03-f04-m01-m02-m03-m04
-  Marathi (India): background 01, agents f22-f23-f24-f25-m22-m23-m24-m25
-  Shona (Zimbabwe): background 01, agents f01-f02-f03-f04-m01-m02-m03-m04
-  Spanish (Argentina): background 01, agents f05-f07-f09-f21-m05-m07-m13-m18
-  Spanish (Mexico): background 01, agents f05-f12-f15-f16-m13-m14-m15-m17
-  Kiswahili (Uganda): background 02, agents f01-f02-f03-f04-m01-m02-m03-m04
-  Turkish (Türkiye): background 01, agents f05-f09-f18-f21-m05-m09-m18-m21
-  Yaka (Rep. Congo): background 02, agents f01-f02-f03-f04-m01-m02-m03-m04

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```

### 2024-06-12 supplements/supplements.tex
incorporate co-author feedback

--- 2024-05-15 paper/manuscript.tex
@@
 {}{\PatchFailed}
-\keywords{cross-cultural psychology, social cognition, gaze following, individual differences, reliability\newline\indent Word count: 5457}
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{unicode-math}
 \usepackage{setspace}
@@
 \captionsetup[figure]{font={stretch=1}}
+\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
+\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
 \makeatletter
@@
 \hypersetup{
-  pdftitle={Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC},
-  pdfauthor={Julia Christin Prein (ORCID: 0000-0002-3154-6167)1,2, Florian M.
-Bednarski (ORCID: 0000-0003-4384-4791)4, Ardain Dzabatou5, Michael C.
-Frank (ORCID: 0000-0002-7551-4378)6, Annette M.
+  pdftitle={Supplements for the manuscript `Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO-CC'},
+  pdfauthor={Julia Christin Prein, Florian M.
+Bednarski, Ardain Dzabatou, Michael C.
+Frank, Annette M.
 E.
-Henderson (ORCID: 0000-0003-4384-4791)4, Josefine Kalbitz2, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)7, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)8, Bahar Köymen (ORCID: 0000-0001-5126-8240)9, Maira V.
-Manrique-Hernandez2, Shirley Magazi (ORCID: 0009-0006-0479-9800)10, Lizbeth Mújica-Manrique2, Julia Ohlendorf2, Damilola Olaoba2, Wesley R.
-Pieters (ORCID:0000-0002-6152-249X)10, Sarah Pope-Caldwell2, Umay Sen (ORCID: 0000-0001-9488-0851)13, Katie Slocombe (ORCID: 0000-0002-7310-1887)11, Robert Z.
-Sparks (ORCID: 0000-0001-7545-0522)6, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,10, Jahnavi Sunderarajan2, Kirsten Sutherland2, Florence Tusiime3, Wilson Vieira (ORCID: 0009-0001-9400-6328)2, Zhen Zhang (ORCID: 0000-0001-9300-0920)12, Yufei Zong (ORCID: 0009-0000-5012-0244)12, Daniel B.
+Henderson, Josefine Kalbitz, Patricia Kanngiesse, Dilara Keşşafoğlu, Bahar Köymen, Maira V.
+Manrique-Hernandez, Shirley Magazi, Lizbeth Mújica-Manrique, Julia Ohlendorf, Damilola Olaoba, Wesley R.
+Pieter, Sarah Pope-Caldwell, Umay Sen, Katie Slocombe, Robert Z.
+Sparks, Roman Stengelin, Jahnavi Sunderarajan, Kirsten Sutherland, Florence Tusiime, Wilson Vieira, Zhen Zhang, Yufei Zong, Daniel B.
 M.
-Haun (ORCID: 0000-0002-3262-645X)2,+, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)1,2,+},
+Haun, \& Manuel Bohn},
   pdflang={en-EN},
-  pdfkeywords={cross-cultural psychology, social cognition, gaze following, individual differences, reliability},
   hidelinks,
@@
 
-\title{Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC}
-\author{Julia Christin Prein (ORCID: 0000-0002-3154-6167)\textsuperscript{1,2}, Florian M.
-Bednarski (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Ardain Dzabatou\textsuperscript{5}, Michael C.
-Frank (ORCID: 0000-0002-7551-4378)\textsuperscript{6}, Annette M.
+\title{Supplements for the manuscript `Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO-CC'}
+\author{Julia Christin Prein\textsuperscript{}, Florian M.
+Bednarski\textsuperscript{}, Ardain Dzabatou\textsuperscript{}, Michael C.
+Frank\textsuperscript{}, Annette M.
 E.
-Henderson (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Josefine Kalbitz\textsuperscript{2}, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)\textsuperscript{7}, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)\textsuperscript{8}, Bahar Köymen (ORCID: 0000-0001-5126-8240)\textsuperscript{9}, Maira V.
-Manrique-Hernandez\textsuperscript{2}, Shirley Magazi (ORCID: 0009-0006-0479-9800)\textsuperscript{10}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R.
-Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{10}, Sarah Pope-Caldwell\textsuperscript{2}, Umay Sen (ORCID: 0000-0001-9488-0851)\textsuperscript{13}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{11}, Robert Z.
-Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{6}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,10}, Jahnavi Sunderarajan\textsuperscript{2}, Kirsten Sutherland\textsuperscript{2}, Florence Tusiime\textsuperscript{3}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{12}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{12}, Daniel B.
+Henderson\textsuperscript{}, Josefine Kalbitz\textsuperscript{}, Patricia Kanngiesse\textsuperscript{}, Dilara Keşşafoğlu\textsuperscript{}, Bahar Köymen\textsuperscript{}, Maira V.
+Manrique-Hernandez\textsuperscript{}, Shirley Magazi\textsuperscript{}, Lizbeth Mújica-Manrique\textsuperscript{}, Julia Ohlendorf\textsuperscript{}, Damilola Olaoba\textsuperscript{}, Wesley R.
+Pieter\textsuperscript{}, Sarah Pope-Caldwell\textsuperscript{}, Umay Sen\textsuperscript{}, Katie Slocombe\textsuperscript{}, Robert Z.
+Sparks\textsuperscript{}, Roman Stengelin\textsuperscript{}, Jahnavi Sunderarajan\textsuperscript{}, Kirsten Sutherland\textsuperscript{}, Florence Tusiime\textsuperscript{}, Wilson Vieira\textsuperscript{}, Zhen Zhang\textsuperscript{}, Yufei Zong\textsuperscript{}, Daniel B.
 M.
-Haun (ORCID: 0000-0002-3262-645X)\textsuperscript{2,+}, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)\textsuperscript{1,2,+}}
+Haun\textsuperscript{}, \& Manuel Bohn\textsuperscript{}}
 \date{}
 
-\shorttitle{measuring gaze following across communities}
+\shorttitle{supplements}
 
-\authornote{
-
-The authors made the following contributions.
-Julia Christin Prein (ORCID: 0000-0002-3154-6167): Conceptualization, Methodology, Software, Formal Analysis, Resources, Writing - Original Draft Preparation, Writing - Review \& Editing; Florian M.
-Bednarski (ORCID: 0000-0003-4384-4791): Resources, Writing - Review \& Editing; Ardain Dzabatou: Resources, Writing - Review \& Editing; Michael C.
-Frank (ORCID: 0000-0002-7551-4378): Resources, Writing - Review \& Editing; Annette M.
-E.
-Henderson (ORCID: 0000-0003-4384-4791): Resources, Writing - Review \& Editing; Josefine Kalbitz: Resources, Writing - Review \& Editing; Patricia Kanngiesser (ORCID:0000-0003-1068-3725): Resources, Writing - Review \& Editing; Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733): Resources, Writing - Review \& Editing; Bahar Köymen (ORCID: 0000-0001-5126-8240): Resources, Writing - Review \& Editing; Maira V.
-Manrique-Hernandez: Resources, Writing - Review \& Editing; Shirley Magazi (ORCID: 0009-0006-0479-9800): Resources, Writing - Review \& Editing; Lizbeth Mújica-Manrique: Resources, Writing - Review \& Editing; Julia Ohlendorf: Resources, Writing - Review \& Editing; Damilola Olaoba: Resources, Writing - Review \& Editing; Wesley R.
-Pieters (ORCID:0000-0002-6152-249X): Resources, Writing - Review \& Editing; Sarah Pope-Caldwell: Resources, Writing - Review \& Editing; Umay Sen (ORCID: 0000-0001-9488-0851): Resources, Writing - Review \& Editing; Katie Slocombe (ORCID: 0000-0002-7310-1887): Resources, Writing - Review \& Editing; Robert Z.
-Sparks (ORCID: 0000-0001-7545-0522): Resources, Writing - Review \& Editing; Roman Stengelin (ORCID: 0000-0003-2212-4613): Resources, Writing - Review \& Editing; Jahnavi Sunderarajan: Resources, Writing - Review \& Editing; Kirsten Sutherland: Resources, Writing - Review \& Editing; Florence Tusiime: Resources, Writing - Review \& Editing; Wilson Vieira (ORCID: 0009-0001-9400-6328): Resources, Writing - Review \& Editing; Zhen Zhang (ORCID: 0000-0001-9300-0920): Resources, Writing - Review \& Editing; Yufei Zong (ORCID: 0009-0000-5012-0244): Resources, Writing - Review \& Editing; Daniel B.
-M.
-Haun (ORCID: 0000-0002-3262-645X): Funding acquisition, Writing - Review \& Editing; Manuel Bohn (ORCID: 0000-0001-6006-1348): Conceptualization, Methodology, Writing - Review \& Editing.
-
-Correspondence concerning this article should be addressed to Julia Christin Prein (ORCID: 0000-0002-3154-6167), Universitätsallee 1, 21335 Lüneburg, Germany.
-E-mail: \href{mailto:julia.prein@leuphana.de}{\nolinkurl{julia.prein@leuphana.de}}
-
-}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology\\\textsuperscript{3} Budongo Conservation Field Station\\\textsuperscript{4} School of Psychology, University of Auckland\\\textsuperscript{5} Université Marien Ngouabi\\\textsuperscript{6} Department of Psychology, Stanford University\\\textsuperscript{7} School of Psychology, University of Plymouth\\\textsuperscript{8} Department of Psychology, Koç University\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia\\\textsuperscript{11} Department of Psychology, University of York\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences\\\textsuperscript{13} Department of Psychology, Developmental Psychology, Uppsala University\\\textsuperscript{+} joint last author}
-
-\abstract{%
-Cross-cultural studies are crucial for investigating the universality and robustness of cognitive developmental processes.
-Yet, suitable methods to measure variability in cognition across languages and communities are lacking.
-This paper describes the TANGO--CC (Task for Assessing Individual Differences in Gaze Understanding -- Cross-Cultural), a gaze following task designed to measure basic social cognition across individuals, ages, and communities.
-The TANGO--CC was developed and psychometrically assessed in one setting and subsequently adapted for cross-cultural data collection.
-Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community.
-The TANGO--CC captured individual differences and showed good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities.
-Within-community variation outweighed between-community variation.
-We provide an open-source website for researchers to customize and use the task.
-The TANGO--CC represents a valuable contribution to assessing basic social cognition in diverse communities, establishing a roadmap for researching cross-cultural individual differences.
-}
+\affiliation{\phantom{0}}
 
@@
 
-\section{Introduction}\label{introduction}
+\section{Voice-over script}\label{voice-over-script}
 
-For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) communities (Henrich et al., 2010; Lillard, 1998).
-Despite numerous calls for change, the subject pools reported in high-impact journals still lack diversity (Gutchess \& Rajaram, 2023; Nielsen et al., 2017).
-This lack of representation hinders progress in theory building: inferences about the universal and variable aspects of the human cognitive system cannot be drawn from data collected in single communities (Krys et al., 2024).
+The TANGO--CC was designed for a cross-cultural study by Bohn et al. (2024). For further information on the sample and further methodological choices, see their supplementary material ().
 
-One reason for the lack of diversity in psychological studies is the scarcity of suitable methods to collect comparable psychological data in different communities (Bourdage et al., 2023).
-This shortage of suitable measures is even more prevalent in developmental psychology.
-In this paper, we describe the construction and psychometric evaluation of a measure of basic social cognition (gaze following) in children as a concrete example for how to overcome this problem.
+Here, we repeat the voice over script as it was presented in Bohn et al.
+(2024).
+The first trial of each trial type played audio descriptions of the presented events, and the voice-over script in English was as follows:
 
-Studies investigating variation between communities and/or individuals need to ensure that the captured variation is systematic and not just random noise: measures need to be reliable and valid.
-This, of course, applies to all fields of psychology.
-Given the topic of this paper, we will focus on measures of social cognition for children.
-Studies on social cognition based on US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020).
-This picture further deteriorates when we look at cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020; Waschl \& Chen, 2022).
-Thus, it is already challenging to find reliable and valid tasks that can capture individual differences within one community, let alone tasks that do so across different communities.
+\subsection{Welcome (before the start of the task)}\label{welcome-before-the-start-of-the-task}
 
-Adapting tasks to diverse communities and re-assessing their validity and reliability might be especially important in the social-cognitive domain.
-If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, the tasks need to represent different communities.
-Indeed, task performance can be diminished when stimuli are not adjusted (Peña, 2007).
-For example, Elfenbein and Ambady (2002) found better emotion recognition for members of the same national, ethnic, or regional group.
-Selcuk et al. (2023) concluded that children often attribute mental states more accurately and more frequently to individuals from the same community.
-This underlines the importance of adapting tasks to each specific cultural context.
+Hello!
+Great that you're here.
+We'll now play a balloon game.
+Can you see the children in the picture over there?
+We want to play together with the children using the balloon.
+We'll now talk you through exactly what will happen.
 
-Broadly speaking, there are two different approaches that researchers can take to collect cross-cultural data.
-One approach would be to translate the psychological construct into an individually designed study for each community (termed ``assembly''; He and Vijver (2012), Waschl and Chen (2022)).
-While this approach is most flexible and sensitive to cultural differences, it might be most feasible for studying up to a handful of communities as it becomes too demanding and time-consuming.
-Most importantly, this approach assumes that the measured underlying concept is the same, while absolute task scores are not comparable across the communities.
-Another approach would be to use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of culturally inappropriate stimuli (termed ``adoption'' and ``adaptation'', respectively; He and Vijver (2012), Waschl and Chen (2022)).
-This approach is less sensitive to each community's unique characteristics but allows for a direct comparison of the data across communities.
-Examples following this approach include Callaghan et al.
-(2011), Taumoepeau et al.
-(2019), Hughes et al.
-(2018), Hughes et al.
-(2014), Fujita et al.
-(2022), Mehta et al.
-(2011), Stengelin et al.
-(2020), and Chasiotis et al.
-(2006).
-The present paper aims to describe the development and psychometric properties of a standardized task that can be adapted to diverse communities.
+\subsection{Training 1}\label{training-1}
 
-The task presented here focuses on gaze following, that is, the ability to identify the attentional focus of another agent.
-Gaze following develops early in infancy (Del Bianco et al., 2019; Tang et al., 2024) and contributes to social learning, communication, and collaboration (Bohn \& Köymen, 2018; Hernik \& Broesch, 2019; Shepherd, 2010; Tomasello et al., 2007).
-While gaze following is one of the most fundamental social-cognitive abilities, studies focusing on cultural variations are rare.
-The few existing results are mixed on whether gaze following is influenced by cultural factors or not (Callaghan et al., 2011; Hernik \& Broesch, 2019).
+Look, a girl/boy is standing in the window.
+And can you see the balloon over there?
+The balloon always falls down and lands on the ground.
+And you have to find it!
+The girl/boy helps you and always looks at the balloon.
 
-The task presented here builds upon the TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open) by Prein et al. (2023).
-The TANGO measures participants' imprecision in locating an agent's attentional focus.
-It has been shown to reliably capture individual differences in a German child sample and an English-speaking remote adult sample.
-The task was sensitive to developmental changes and linked to children's receptive vocabulary.
-Furthermore, an exploratory analysis showed that children performed equally well in a task version with animal faces compared to cartoon human faces (Prein et al., 2024).
-This suggests that superficial variations in the stimulus design do not influence children's performance in the task.
+{[}balloon falls down{]}
 
-This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that can be -- and has been -- adapted to several languages and communities.
-We describe the task's development and provide a tutorial for the open-source website (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).
-We assess its cross-cultural applicability based on data from a large cross-cultural sample of 2.5- to 11-year-olds from 17 different urban/rural communities across the world and discuss the task's psychometrics.
-The task and all its adaptations have been initially designed for a paper by Bohn et al. (2024), and we re-use the data set in this paper.
+Where is the balloon? Touch the balloon!
 
-\section{Task development}\label{task-development}
+\subsection{Training 2}\label{training-2}
 
-\subsection{Approach}\label{approach}
+Perfect, that was great!
+Now, we'll continue playing.
+Can you see the girl/boy and the balloon again?
+The balloon will fall down again.
+This time, it will fall behind a hedge.
+And you have to find it!
+The girl/boy helps you and looks at the balloon.
 
-In a perfect world, developing a cross-cultural task would include international collaboration and diverse samples from the beginning, already during study design, piloting and item selection.
-As this seems hardly feasible, we present a pragmatic approach.
-The TANGO-CC was first implemented in one context, in our case Leipzig, Germany (Prein et al., 2023).
-Here, the task's reliability and validity were assessed in detail.
-Even though this does not guarantee that the task will be valid and reliable in another context, it substantially increases the likelihood.
-Second, we reassessed the TANGO--CC's measurement quality (i.e., variability and reliability) across diverse communities by analyzing the data from Bohn et al.
-(2024), who used the task to collect data in 17 communities.
-Therefore, our procedure maintains a balance between a detailed analysis of the task's psychometric properties and a swift and feasible task adaptation.
-In the following, we describe the different steps in further detail.
-We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful for other researchers.
+{[}balloon falls down{]}
 
-In the first step, the task's underlying structure was designed.
-The TANGO--CC measures the precision with which participants locate an agent's attentional focus.
-The participant's task is to locate a target by following the agent's gaze (see Figure \ref{fig:fig1}).
-Precision was measured in a continuous way as the distance between the participant's click on the screen (\emph{i.e.}, where the participant thinks the target is) and the target's real position.
-The task's core functionality is to animate the agent's eyes so that they follow the target's movement.
-This basic structure was then embedded in the task's superficial appearance (e.g., background scene) and audio instructions.
-Once this structure was implemented, adaptations of the task were greatly simplified.
-For example, we can change the background scene, the faces of the agent, and the target without changing how and what the task measures.
+Where is the balloon? On the hedge, touch where the balloon is.
 
-This basic version of the TANGO was psychometrically evaluated in a prototypical WEIRD sample (German child sample; English-speaking remote adult sample) and was found to be highly reliable and valid (Prein et al., 2023).
-While participants got more and more precise in locating the attentional focus of the agent the older they were, individuals differed across all age groups and showed no floor- or ceiling effects.
-Performance in the TANGO was linked to children's receptive vocabulary and weakly related to factors of children's daily social environment.
-In another study, Prein et al. (2024) proposed a computational cognitive model that described gaze following as a social form of vector following.
-Gaze following, as measured by the TANGO, was related to children's non-social vector following and visual perspective-taking abilities.
-These connections to related constructs indicate the task's validity in the tested WEIRD setting.
+\subsection{Test}\label{test}
 
-To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces that were judged by researchers and research assistants from each target community to be representative of the local population (see Figure \ref{fig:fig1}).
-Similarly, different backgrounds were created that roughly represented a typical accommodation in each community.
-Audio instructions were translated into the corresponding local language.
-By back-translating these instructions, we ensured the original meaning did not change.
-Sometimes, specific words were linguistically slightly modified, although functionally equivalent (e.g., ``bush'' instead of ``hedge''), to ensure that all participants understood the instructions.
-In the following, we describe how researchers can use and customize the TANGO--CC in more detail.
+Nice, good job! Now, we'll continue playing. There is the balloon, the girl/boy and the hedge. The hedge is growing a bit now.
 
-\subsection{Features of the TANGO--CC}\label{features-of-the-tangocc}
+The balloon is behind the hedge now. You can't see it - but the girl/boy can! The balloon falls to the ground and you have to find it. Remember - the girl/boy always looks at the balloon!
 
-\subsubsection{Trials}\label{trials}
+\subsection{Goodbye (after the last test trial)}\label{goodbye-after-the-last-test-trial}
 
-We quickly recap the TANGO's (Prein et al., 2023) most characteristic features: Participants are asked to locate a balloon with the help of a gaze cue.
-The task consists of three different trial types (see Figure \ref{fig:fig1}).
-In every trial, participants see an agent (boy or girl) looking out of a house with a balloon (red, blue, green, or yellow) in front of them.
-The balloon falls down to the ground, while the eyes of the agent follow the movement of the balloon in a way that their centers always align.
-Depending on the trial type, participants have different visual access to the balloon's position.
-In training 1, participants see the full trajectory of the balloon and directly have to touch the balloon itself.
-In training 2, participants see most of the balloon's movement, but a hedge covers the final location.
-In test trials, a hedge grows at the beginning of the trial and participants see neither the movement nor the final position of the balloon.
-The first trial of each type contains an audio description of the presented events (see supplements of Bohn et al. (2024)).
-Notably, the instructions explicitly state that the agent is looking at the balloon.
+The children are super happy after playing. Thanks a lot for your help! See you soon and goodbye!
 
-The outcome variable is the distance between the participant's touch and the balloon's center.
-Trials can be completed quickly and efficiently so that children can easily complete 15 trials within 10 minutes.
-This drastically reduces drop-out rates.
-By using essentially self-explanatory animations, language demands are kept to a minimum.
-No differential feedback is given to keep trials comparable and avoid learning effects.
+\section{Default settings}\label{default-settings}
 
-\subsubsection{Randomization}\label{randomization}
+When researchers use the default settings of the TANGO-CC, the following settings are applied based on the selected language.
+Visit this website \url{https://ccp-odc.eva.mpg.de/tango-cc/customize.html} and hover over the agent faces to view their IDs.
 
-The order of the agents, balloon colors (red, yellow, green, blue), and balloon positions are each randomized independently.
-For the balloon positions, the entire width of the screen (1920 in ``SVG units'') is divided into ten bins.
-Exact coordinates (value between 0 far left and 1920 far right) within each bin are then randomly generated.
-The number of repetitions for each agent, balloon color, and balloon bin is calculated based on the total number of trials and the number of unique agents, balloon colors, and bins, respectively.
-All agents, balloon colors, and bins appear equally often and are not repeated in more than two consecutive trials.
-If the total number of trials is not divisible by the number of unique elements, additional elements are randomly selected to make up for the remainder.
-
-\subsubsection{Cross-cultural customization}\label{cross-cultural-customization}
-
-The TANGO--CC can be accessed via the following link: (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).
-In the first step, researchers can select the language for audio instructions, currently available for 13 different languages and even more dialects (see Table 1).
-All written instructions are presented in English because they are not directed to the participant but to the research assistant who guides the participant through the task.
-The task can either be started with the default settings or further customized.
-The default settings use the version applied in Bohn et al. (2024) based on the selected language.
-
-If researchers choose to customize the task (see Figure \ref{fig:fig1}), the number of trials can be chosen for each trial type.
-As the trial types build up on each other, each trial type is necessary to understand the structure of the task and needs to be completed before the next trial type starts.
-Therefore, no trial type can be skipped.
-The minimum number of trials per type is 1; the maximum is 100.
-One out of four different backgrounds can be selected.
-Finally, there are 50 diverse human faces (50\% female, 50\% male) from which researchers can choose.
-No constraint exists on how many faces are allowed (min 1, max 50).
-Once all the settings are adjusted, the customized task is compiled.
-
-In the last step, researchers can enter an alphanumeric participant identifier (1 - 8 characters) and enable a webcam recording of the participant, if needed.
-To save the selected settings, researchers can bookmark the URL so that the customized task can be easily accessed, and only the participant ID and choice of webcam recording need to be entered again.
-The task can then be started.
-
-The source code of the task is available on GitHub (\url{https://github.com/ccp-eva/tango-cc}).
-By directly editing the \texttt{HTML} and \texttt{JavaScript} code, researchers gain even more flexibility in adjusting the task to their needs.
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:langtab}Languages available for the audio instructions in the TANGO--CC}
-
-\begin{tabular}{lll}
-\toprule
-Languages & \multicolumn{1}{c}{Language family} & \multicolumn{1}{c}{Speaker's country of origin}\\
-\midrule
-Bemba & Bantu & Zambia\\
-Chinese & Sino-Tibetan & China\\
-English & Indo-European & USA / UK / India / Nigeria / New Zealand\\
-German & Indo-European & Germany\\
-Hai||om & Khoesan & Namibia\\
-Khewdam & Khoesan & Namibia\\
-Lingala & Bantu & Rep. Congo\\
-Marathi & Indo-European & India\\
-Shona & Bantu & Zimbabwe\\
-Spanish & Indo-European & Argentina / Mexico\\
-Swahili & Bantu & Uganda\\
-Turkish & Turkic & Türkiye\\
-Yaka & Bantu & Rep. Congo\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/TANGO-CC-procedure}
-
-}
-
-\caption{\textbf{Customizable components of the TANGO--CC.} Researchers can select the language of the audio instructions, the number of trials per trial type, the background, and the agent's face.
-Screenshots of the trials show the proceeding events: In training 1, an agent looks at a balloon that falls to the ground, and participants have to respond by touching the balloon.
-In training 2, the balloon falls behind the hedge while its flight is still visible.
-Participants respond by touching the hedge where they think the balloon is.
-In test trials, the balloon's movement and final position are covered by a hedge, and participants respond by touching the hedge.
-In the task, all movements are smoothly animated (no still pictures).
-Yellow frames indicate the time point when participants respond (only illustrative, not shown during the task).}\label{fig:fig1}
-\end{figure}
-
-\subsubsection{Task implementation}\label{task-implementation}
-
-The task was implemented in \texttt{JavaScript}, \texttt{HTML}, and \texttt{CSS} and is presented as a web app.
-It can be accessed on any web browser and does not require prior installation.
-The online version of the task has been proven convenient for unsupervised data collection (for example, using participant recruitment services like \emph{Prolific}; see Prein et al.
-(2023)) and sharing the task internationally.
-Importantly, the web app implementation does not necessarily need a working WIFI connection: An offline, local version of the task can be quickly set up for devices that support Node.js (\url{https://nodejs.org/en}).
-This is an especially useful feature for researchers working in remote areas with limited internet access.
-
-The stimuli are embedded as Scalable Vector Graphics (SVG).
-The setup allows for an easy adaptation of task elements and ensures that picture quality, aspect ratio, and relative object positioning are constant.
-The task is programmed so that responses are only registered when the participant touches the relevant part of the screen (i.e., in test trials, the hedge).
-Furthermore, clicks are only registered after the voice recordings stop playing.
-An audio reminder is played again if no click is registered within 5 seconds.
-
-The website does not use cookies, nor does it upload any data to servers; that is, the data is only stored locally on the device.
-The output of the task is a CSV file (and WEBM file if a webcam recording was selected) that contains the participants' responses and can be easily imported into statistical software for further analysis.
-The file will be stored in the device's downloads folder and is named after the following pattern: ``tangoCC-participantID-YYYY-MM-DD\_hh\_mm\_ss''.
-
-\section{Psychometric evaluation}\label{psychometric-evaluation}
-
-\subsection{Data set}\label{data-set}
-
-We used the data set from Bohn et al. (2024) for the psychometric evaluation of the TANGO--CC.
-They collected data using the TANGO--CC in a sample of \emph{N} = 1377 children between 2.5 to 11 years of age.
-Participants came from 17 communities on five continents, in rural and urban settings, with varying degrees of market integration and technology exposure.
-Bohn et al. (2024) carried out 19 trials (1 training 1, 2 training 2, and 16 test trials, of which the first of each type had audio instructions).
-Faces, backgrounds, and languages were chosen by researchers and assistants with experience in the specific community.
-For further details on the communities and data collection procedures, see the supplements of Bohn et al. (2024).
-
-\subsection{Individual differences}\label{individual-differences}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/TANGO-CC-results}
-
-}
-
-\caption{\textbf{Measurement of the TANGO--CC by community.} (A) Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type.
-Imprecision is defined as the distance between the participant's touch and the balloon's center in units of balloon width.
-For a depiction of each trial's procedure, see Figure \ref{fig:fig1}.
-(B) Internal consistency estimates by community, following three different approaches.
-In the odd-even split, the size of points reflects the sample size in each community.
-In the stratified approach with and without age correction, density curves show the posterior distributions of the GLMM.}\label{fig:fig2}
-\end{figure}
-
-First, we inspected the mean and standard deviations by community and compared performance in each trial type (training 1, training 2, test trials).
-Performance was defined as the absolute click distance between the target center and the click x coordinate (measured in balloon widths).
-Across communities, children performed best in training 1 (mean = 0.19, sd = 0.63), followed by training 2 (mean = 0.79, sd = 1.44) and test trials (mean = 2.21, sd = 2.03; see Figure \ref{fig:fig2}A).
-
-To formally estimate the effect of trial type on performance in the TANGO--CC, we fit a generalized linear mixed model (GLMM) predicting the task performance by trial type (reference category: test trials).
-All analyses were run in R version 4.4.0 (2024-04-24) (R Core Team, 2024).
-GLMMs were fitted with default priors using the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017, 2018).
-The model included random effects for trial type by community (model notation in \texttt{R:\ imprecision\ \textasciitilde{}\ trialtype\ +\ (trialtype\ \textbar{}\ community)}), and imprecision was modeled by a \texttt{lognormal} distribution.
-We inspected the posterior distribution (mean and 95\% Credible Interval (CrI)) for the trial type estimates.
-
-Our GLMM analysis supported the visual inspection of the data: the fixed-effect estimates for training 1 (\(\beta\) = -3.26; 95\% CrI {[}-3.41; -3.10{]}) and training 2 (\(\beta\) = -1.47; 95\% CrI {[}-1.58; -1.35{]}) were negative and reliably different from zero.
-Please note that the TANGO--CC measures imprecision in gaze following.
-Therefore, a negative sign shows that children showed less imprecision (i.e., were more precise) in the training trials than in the test trials.
-This effect was found across all communities (random effects of trial type within community: minimum estimate for training 1 = -2.87; 95\%CrI {[}-3.11; -2.60{]}; minimum estimate for training 2 = -1.27; 95\%CrI {[}-1.51; -0.98{]}).
-The almost perfect performance in training trials indicated that children understood the task and were able to locate the balloon.
-In test trials, children's imprecision was higher, indicating that the task was more challenging.
-All communities showed substantial individual variation and overlapped in their imprecision levels (see Figure \ref{fig:fig2}A).
-
-To identify the sources of variation, we computed intraclass correlations (ICC).
-The variation of children within communities was substantially larger than the variation between the communities.
-The mean within-community variance was 1.28, ranging from 0.24 (in Pune, India) to 3.46 (in Chimfunshi, Zambia).
-Between-community variance was 0.34.
-The ICC, representing the proportion of between-community variance relative to the total variance (sum of within- and between-community variance), was 0.02.
-This indicates that only 2\% of the total variability in the data can be attributed to differences between communities, while the remaining 98\% are attributed to differences within communities (Kusano et al., 2024).
-
-\subsection{Reliability}\label{reliability}
-
-To assess reliability, we estimated internal consistency in each community in three different ways.
-First, data of each participant was split into odd and even trials and a Pearson correlation was calculated between the aggregated scores of the two halves.
-Second, using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2022), data was stratified by target centrality (capturing trial difficulty), and a Pearson correlation was calculated between the matched halves.
-Third, a data set was generated with stratified test halves by target centrality.
-Then, we followed the Generalized Linear Mixed Model (GLMM) approach introduced by Rouder and Haaf (2019).
-A GLMM was fitted with the mean imprecision as the outcome, age as the predictor, and test half and participant id as random effects (model notation: \texttt{imprecision\ \textasciitilde{}\ age\ +\ (0\ +\ half\ \textbar{}\ subjid)}).
-The model estimates correlations between participant-specific estimates for each test half.
-The hierarchical shrinkage of the model enables accurate person-specific estimates.
-By incorporating age as a fixed effect, the correlation between the two person-specific estimates represents the age-independent estimate for internal consistency.
-This eliminates the chance that a good internal consistency estimate results from general cognitive development rather than task-specific inter-individual differences.
-Because the process of generating stratified data sets is partly random, the model was fitted 50 times for each community.
-The posterior estimate of the correlation between the two person-specific estimates was taken as the age-independent estimate for internal consistency.
-
-The results are shown in Figure \ref{fig:fig2}C.
-Across communities, internal consistency estimates ranged from 0.51 to 0.80 for the odd-even split, 0.62 to 0.89 for the stratified internal consistency, and 0.62 to 0.87 for the age-corrected approach (Plymouth, UK, being an outlier with 0.28).
-Following Cohen's suggestions (Cohen, 1988, 1992), these correlations constitute large effects (\emph{r} \textgreater{} .50), and indicate good internal consistency.\footnote{Note that for scale reliability and Cronbach's \(\alpha\), values of .7 to .8 have been suggested to be acceptable (Field et al., 2012; Kline, 1999).
-However, Kline (1999) suggested that values below .7 could be realistic for psychological constructs due to their variable nature.}
-The results are comparable to the internal consistency estimates found in the original TANGO study (Prein et al., 2023), and also resemble reliability estimates of classical false belief tasks (Hughes et al., 2000).
-
-In an exploratory analysis, we found that communities with larger individual variation showed higher internal consistency estimates (Pearson's \emph{r} = 0.46, 95\%CI {[}-0.03; 0.77{]}).
-Please note that this could be influenced by outliers and that the sample size here (\emph{N} = 17 communities) is too small to make substantial claims.
-
-\section{Discussion}\label{discussion}
-
-The TANGO--CC measures imprecision in gaze following across individuals, ages, and communities.
-The task was developed in two phases.
-First, the task's underlying functionality was designed in one community.
-Next, we adapted the superficial features of the task to be used in 17 diverse communities and assessed the task's psychometric properties.
-Children's imprecision in gaze following highly overlapped between communities: children performed better in the training than the test trials, and within-community variation greatly exceeded between-community variation.
-The task showed satisfactory to high reliability across all communities.
-Therefore, we believe the TANGO--CC is a promising task to capture individual differences in social-cognitive development in diverse communities.
-Its design process lays out a much-needed pragmatic approach to conducting cross-cultural individual differences research.
-
-A similar approach to task development was taken by Mehta et al. (2011).
-The researchers (1) selected social cognition measures that have been established in WEIRD settings, (2) adapted the agent's names, appearance, backgrounds, and languages to the local context, and (3) assessed the task's validity and internal consistency in the new setting.
-Participants were adults with and without schizophrenia from India. Theory of Mind tasks included Sally-Anne, Smarties, Ice cream van and Missing cookies stories.
-For this specific context, the authors' approach yielded a successful adaptation of social cognition measures for the tested Indian (Hindi/Kannada) communities.
-
-Bourdage et al. (2023) pointed out a major challenge with adapting social cognition tasks to diverse communities: the number of world cultures is vast, and communities are constantly changing.
-Therefore, a promising approach might be to provide tasks with a modular system where components can be exchanged according to the local context.
-In the case of the TANGO--CC, the task can not only be adapted to different languages, cartoon faces, and backgrounds (see Figure \ref{fig:fig1}) but also updated with new stimuli.
-Unlike studies that present sequential, hand-painted pictures that are difficult to adapt (Mehta et al., 2011), the TANGO--CC uses SVGs that can be easily exchanged.
-
-The biggest strength of the TANGO--CC is its flexibility.
-The task is presented as a web app that can also run offline to enable remote data collection.
-Minimal language demands and an engaging, playful design increase the task's usability.
-Together with a short task duration, this reduces drop-out rates and enables efficient data collection with large sample sizes.
-The TANGO--CC follows a standardized procedure and uses a continuous, objective outcome measure (leaving no room for rater errors).
-An online manual with the most frequently asked questions is available at \url{https://ccp-odc.eva.mpg.de/tango-cc/manual.html}.
-Additional customization can be achieved by adding new stimuli to the open-source code available on GitHub (\url{https://github.com/ccp-eva/tango-cc}).
-
-For years, researchers have called for more diverse sampling and culturally valid measures of cognitive development (Matsumoto \& Yoo, 2006; e.g., Mehta et al., 2011; Nielsen et al., 2017).
-As Hajdúk et al.
-(2020) put it, ``using large samples and multisite approaches will align with efforts to improve reproducibility and will clarify both the type and extent of cultural influences on social cognition'' (p.~463).
-The TANGO--CC takes a valuable step in this direction by sharing the task and its source code with other researchers.
-Bohn et al. (2024) showed that data collection with the TANGO--CC was feasible in 17 diverse communities in rural and urban settings with varying degrees of market integration and technology exposure.
-While we cannot generalize our findings to all communities worldwide, we found that it captured reliable individual variation in the 17 communities studied by Bohn et al. (2024).
-Using the TANGO--CC in a new community nevertheless requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
-We hope that the TANGO--CC will facilitate future cross-cultural studies to assess social-cognitive development in a wide range of communities.
-
-A valid question is whether the TANGO--CC measures the same construct across different groups.
-This so-called measurement invariance is often seen as a requirement for a ``fair'' cross-cultural comparison and relies on minimizing group differences while individual differences are magnified.
-As Kusano et al.
-(2024) put it: ``The research challenge is to achieve a balance between ensuring methodological ``fairness'' at the individual level while also recognizing and capturing genuine sociocultural variability'' (p.~34).
-We argue that the TANGO--CC measures a fundamental social-cognitive ability that is likely similar across communities.
-Bohn et al. (2024) have shown that children with no prior touchscreen exposure were less precise in the TANGO--CC than children with prior experience.
-However, individual differences were also found in communities with 100\% touch screen exposure, showing that this factor alone could not explain children's performance in the task (Bohn et al., 2024).
-Notably, even though the touchscreen experience caused absolute differences in task performance, all communities showed the same processing signature.
-A recent computational cognitive model described gaze following as a process of estimating pupil angles and the corresponding gaze vectors (Prein et al., 2024).
-The model predicted that all individuals use the same process to locate an attentional focus but differ in their uncertainty around the estimated pupil angles, which results in less precision.
-Bohn et al. (2024) found clear support for this model in every community they studied, suggesting that children all over the world process gaze in a similar way.
-In this manuscript, we could also show that internal consistency was high across all communities, meaning that the task captured individual differences in a similar way.
-Consequently, the TANGO--CC seems to measure systematic individual differences across diverse communities.
-
-Selcuk et al.
-(2023) pointed out that researchers should study both within- and between-culture variability in the development of social cognition since sometimes within-culture differences exceed between-culture differences.
-Indeed, we found that within-group variability was greater than between-group variability.
-While we believe that the TANGO--CC can be used to compare mean differences across communities, we would recommend using it to study individual differences within communities.
-
-\section{Limitations}\label{limitations}
-
-The TANGO--CC and its psychometric properties need to be considered against some limitations.
-Reliability for each community was assessed by calculating the internal consistency.
-Ideally, we would have additionally assessed the task's retest reliability in each community and checked for relationships with theoretically related constructs to assess validity.
-
-Schilbach et al. (2013) pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions.
-Of course, the TANGO--CC does not depict real-life social interaction, and future research should investigate how task performance relates to the real world.
-Suggestive evidence comes from a study by Prein et al.
-(2024), who found that children's performance in the TANGO was linked to children's visual perspective-taking abilities in real-life social interaction.
-The mode of stimulus presentation surely needs to be kept in mind when administering the TANGO--CC, especially in communities with little technology exposure.
-Additional touch screen training (e.g., more trials of training 1) might prove helpful in these cases.
-
-\section{Conclusion}\label{conclusion}
-
-The TANGO--CC is a promising task to capture individual differences in social-cognitive development across diverse communities.
-The task was developed in two phases: (1) implementing the task's underlying functionality and estimating detailed psychometrics in one community, and (2) expanding the stimulus pool to accommodate diverse communities worldwide.
-The task's flexibility, minimal language demands, and engaging design make it a valuable task for cross-cultural research.
-The task showed satisfactory to high reliability (internal consistency) in a large dataset including 17 diverse communities.
-We hope that the TANGO--CC -- and its pragmatic construction process -- will inspire future cross-cultural studies to assess cognitive development in a wide range of communities.
-
-\newpage
+\begin{itemize}
+\tightlist
+\item
+  Bemba (Zambia): background 01, agents f01-f02-f03-f04-m01-m02-m03-m04
+\item
+  Chinese (China): background 01, agents f18-f19-f20-f21-m18-m19-m20-m21
+\item
+  English (India): background 01, agents f22-f23-f24-f25-m22-m23-m24-m25
+\item
+  English (New Zealand): background 01, agents f05-f06-f11-f15-m05-m06-m11-m15
+\item
+  English (Nigeria): background 01, agents f01-f02-f03-f04-m01-m02-m03-m04
+\item
+  English (UK): background 01, agents f05-f07-f08-f10-m03-m06-m09-m11
+\item
+  English (USA): background 01, agents f01-f05-f06-f09-m05-m06-m08-m09
+\item
+  German (Germany): background 01, agents f05-f07-f08-f10-m03-m06-m09-m11
+\item
+  Hai\textbar\textbar kom (Namibia): background 01, agents f01-f02-f03-f04-m01-m02-m03-m04
+\item
+  Khwedam (Namibia): background 01, agents f01-f02-f03-f04-m01-m02-m03-m04
+\item
+  Lingala (Rep.~Congo): background 02, agents f01-f02-f03-f04-m01-m02-m03-m04
+\item
+  Marathi (India): background 01, agents f22-f23-f24-f25-m22-m23-m24-m25
+\item
+  Shona (Zimbabwe): background 01, agents f01-f02-f03-f04-m01-m02-m03-m04
+\item
+  Spanish (Argentina): background 01, agents f05-f07-f09-f21-m05-m07-m13-m18
+\item
+  Spanish (Mexico): background 01, agents f05-f12-f15-f16-m13-m14-m15-m17
+\item
+  Kiswahili (Uganda): background 02, agents f01-f02-f03-f04-m01-m02-m03-m04
+\item
+  Turkish (Türkiye): background 01, agents f05-f09-f18-f21-m05-m09-m18-m21
+\item
+  Yaka (Rep.~Congo): background 02, agents f01-f02-f03-f04-m01-m02-m03-m04
+\end{itemize}
 
@@
 \begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-beaudoin2020systematic}
-Beaudoin, C., Leblanc, É., Gagner, C., \& Beauchamp, M.
-H.
-(2020).
-Systematic {Review} and {Inventory} of {Theory} of {Mind Measures} for {Young Children}.
-\emph{Frontiers in Psychology}, \emph{10}, 2905.
-\url{https://doi.org/10.3389/fpsyg.2019.02905}
-
-\bibitem[\citeproctext]{ref-bohn2018common}
-Bohn, M., \& Köymen, B. (2018). Common {Ground} and {Development}. \emph{Child Development Perspectives}, \emph{12}(2), 104--108. \url{https://doi.org/10.1111/cdep.12269}
-
 \bibitem[\citeproctext]{ref-bohn2024universal}
@@
 \emph{A universal of human social cognition: {Children} from 17 communities process gaze in similar ways}.
-OSF.
+PsyArXiv.
 \url{https://doi.org/10.31234/osf.io/z3ahv}
-
-\bibitem[\citeproctext]{ref-bourdage2023evaluation}
-Bourdage, R., Narme, P., Neeskens, R., Papma, J., \& Franzen, S.
-(2023).
-An {Evaluation} of {Cross-Cultural Adaptations} of {Social Cognition Testing}: {A Systematic Review}.
-\emph{Neuropsychology Review}.
-\url{https://doi.org/10.1007/s11065-023-09616-0}
-
-\bibitem[\citeproctext]{ref-burkner2017brms}
-Bürkner, P.-C. (2017). Brms: {An R Package} for {Bayesian Multilevel Models Using Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
-
-\bibitem[\citeproctext]{ref-burkner2018advanced}
-Bürkner, P.-C. (2018). Advanced {Bayesian Multilevel Modeling} with the {R Package} brms. \emph{The R Journal}, \emph{10}(1), 395. \url{https://doi.org/10.32614/RJ-2018-017}
-
-\bibitem[\citeproctext]{ref-callaghan2011early}
-Callaghan, T., Moll, H., Rakoczy, H., Warneken, F., Liszkowski, U., Behne, T., \& Tomasello, M.
-(2011).
-Early social cognition in three cultural contexts.
-\emph{Monographs of the Society for Research in Child Development}, \emph{76}(2), vii--viii, 1--142.
-\url{https://doi.org/10.1111/j.1540-5834.2011.00603.x}
-
-\bibitem[\citeproctext]{ref-chasiotis2006theory}
-Chasiotis, A., Kiessling, F., Hofer, J., \& Campos, D.
-(2006).
-Theory of mind and inhibitory control in three cultures: {Conflict} inhibition predicts false belief understanding in {Germany}, {Costa Rica} and {Cameroon}.
-\emph{International Journal of Behavioral Development}, \emph{30}(3), 249--260.
-\url{https://doi.org/10.1177/0165025406066759}
-
-\bibitem[\citeproctext]{ref-cohen1988statistical}
-Cohen, J. (1988). \emph{Statistical power analysis for the behavioral sciences} (2nd ed). L. Erlbaum Associates.
-
-\bibitem[\citeproctext]{ref-cohen1992power}
-Cohen, J. (1992). A power primer. \emph{Psychological Bulletin}, \emph{112}(1), 155--159. \url{https://doi.org/10.1037/0033-2909.112.1.155}
-
-\bibitem[\citeproctext]{ref-delbianco2019developmental}
-Del Bianco, T., Falck-Ytter, T., Thorup, E., \& Gredebäck, G.
-(2019).
-The {Developmental Origins} of {Gaze-Following} in {Human Infants}.
-\emph{Infancy}, \emph{24}(3), 433--454.
-\url{https://doi.org/10.1111/infa.12276}
-
-\bibitem[\citeproctext]{ref-elfenbein2002universality}
-Elfenbein, H.
-A., \& Ambady, N.
-(2002).
-On the universality and cultural specificity of emotion recognition: {A} meta-analysis.
-\emph{Psychological Bulletin}, \emph{128}(2), 203--235.
-\url{https://doi.org/10.1037/0033-2909.128.2.203}
-
-\bibitem[\citeproctext]{ref-field2012discovering}
-Field, A., Miles, J., \& Field, Z. (2012). \emph{Discovering statistics using {R}}. Sage.
-
-\bibitem[\citeproctext]{ref-fujita2022theory}
-Fujita, N., Devine, R.
-T., \& Hughes, C.
-(2022).
-Theory of mind and executive function in early childhood: {A} cross-cultural investigation.
-\emph{Cognitive Development}, \emph{61}, 101150.
-\url{https://doi.org/10.1016/j.cogdev.2021.101150}
-
-\bibitem[\citeproctext]{ref-gutchess2023considerationa}
-Gutchess, A., \& Rajaram, S.
-(2023).
-Consideration of culture in cognition: {How} we can enrich methodology and theory.
-\emph{Psychonomic Bulletin \& Review}, \emph{30}(3), 914--931.
-\url{https://doi.org/10.3758/s13423-022-02227-5}
-
-\bibitem[\citeproctext]{ref-hajduk2020how}
-Hajdúk, M., Achim, A.
-M., Brunet -- Gouet, E., Mehta, U.
-M., \& Pinkham, A.
-E.
-(2020).
-How to move forward in social cognition research?
-{Put} it into an international perspective.
-\emph{Schizophrenia Research}, \emph{215}, 463--464.
-\url{https://doi.org/10.1016/j.schres.2019.10.001}
-
-\bibitem[\citeproctext]{ref-he2012bias}
-He, J., \& Vijver, F. van de. (2012). Bias and {Equivalence} in {Cross-Cultural Research}. \emph{Online Readings in Psychology and Culture}, \emph{2}(2). \url{https://doi.org/10.9707/2307-0919.1111}
-
-\bibitem[\citeproctext]{ref-henrich2010weirdesta}
-Henrich, J., Heine, S.
-J., \& Norenzayan, A.
-(2010).
-The weirdest people in the world?
-\emph{The Behavioral and Brain Sciences}, \emph{33}(2-3), 61-83; discussion 83-135.
-\url{https://doi.org/10.1017/S0140525X0999152X}
-
-\bibitem[\citeproctext]{ref-hernik2019infant}
-Hernik, M., \& Broesch, T.
-(2019).
-Infant gaze following depends on communicative signals: {An} eye-tracking study of 5- to 7-month-olds in {Vanuatu}.
-\emph{Developmental Science}, \emph{22}(4), e12779.
-\url{https://doi.org/10.1111/desc.12779}
-
-\bibitem[\citeproctext]{ref-hughes2000good}
-Hughes, C., Adlam, A., Happé, F., Jackson, J., Taylor, A., \& Caspi, A.
-(2000).
-Good {Test}-{Retest Reliability} for {Standard} and {Advanced False}-{Belief Tasks} across a {Wide Range} of {Abilities}.
-\emph{Journal of Child Psychology and Psychiatry}, \emph{41}(4), 483--490.
-\url{https://doi.org/10.1111/1469-7610.00633}
-
-\bibitem[\citeproctext]{ref-hughes2014lost}
-Hughes, C., Devine, R.
-T., Ensor, R., Koyasu, M., Mizokawa, A., \& Lecce, S.
-(2014).
-Lost in {Translation}?
-{Comparing British}, {Japanese}, and {Italian Children}'s {Theory-of-Mind Performance}.
-\emph{Child Development Research}, \emph{2014}, e893492.
-\url{https://doi.org/10.1155/2014/893492}
-
-\bibitem[\citeproctext]{ref-hughes2018does}
-Hughes, C., Devine, R.
-T., \& Wang, Z.
-(2018).
-Does {Parental Mind-Mindedness Account} for {Cross-Cultural Differences} in {Preschoolers}' {Theory} of {Mind}?
-\emph{Child Development}, \emph{89}(4), 1296--1310.
-\url{https://doi.org/10.1111/cdev.12746}
-
-\bibitem[\citeproctext]{ref-kline1999handbook}
-Kline, P. (1999). \emph{The {Handbook} of {Psychological Testing}} (2nd ed.). Routledge.
-
-\bibitem[\citeproctext]{ref-krys2024weirda}
-Krys, K., De Almeida, I., Wasiel, A., \& Vignoles, V.
-L.
-(2024).
-{WEIRD}--{Confucian} comparisons: {Ongoing} cultural biases in psychology's evidence base and some recommendations for improving global representation.
-\emph{American Psychologist}.
-\url{https://doi.org/10.1037/amp0001298}
-
-\bibitem[\citeproctext]{ref-kusano2024mismeasure}
-Kusano, K., Napier, J., \& Jost, J.
-(2024).
-\emph{The {Mismeasure} of {Culture}: {When Measurement Invariance Requirements Hinder Cross-Cultural Research} in {Psychology}}.
-OSF.
-\url{https://doi.org/10.31234/osf.io/9qe2k}
-
-\bibitem[\citeproctext]{ref-lillard1998ethnopsychologies}
-Lillard, A. (1998). Ethnopsychologies: {Cultural} variations in theories of mind. \emph{Psychological Bulletin}, \emph{123}(1), 3--32. \url{https://doi.org/10.1037/0033-2909.123.1.3}
-
-\bibitem[\citeproctext]{ref-matsumoto2006new}
-Matsumoto, D., \& Yoo, S.
-H.
-(2006).
-Toward a {New Generation} of {Cross-Cultural Research}.
-\emph{Perspectives on Psychological Science}, \emph{1}(3), 234--250.
-\url{https://doi.org/10.1111/j.1745-6916.2006.00014.x}
-
-\bibitem[\citeproctext]{ref-mehta2011validation}
-Mehta, U.
-M., Thirthalli, J., Naveen Kumar, C., Mahadevaiah, M., Rao, K., Subbakrishna, D.
-K., Gangadhar, B.
-N., \& Keshavan, M.
-S.
-(2011).
-Validation of {Social Cognition Rating Tools} in {Indian Setting} ({SOCRATIS}): {A} new test-battery to assess social cognition.
-\emph{Asian Journal of Psychiatry}, \emph{4}(3), 203--209.
-\url{https://doi.org/10.1016/j.ajp.2011.05.014}
-
-\bibitem[\citeproctext]{ref-nielsen2017persistent}
-Nielsen, M., Haun, D., Kärtner, J., \& Legare, C.
-H.
-(2017).
-The persistent sampling bias in developmental psychology: {A} call to action.
-\emph{Journal of Experimental Child Psychology}, \emph{162}, 31--38.
-\url{https://doi.org/10.1016/j.jecp.2017.04.017}
-
-\bibitem[\citeproctext]{ref-pena2007lost}
-Peña, E. D. (2007). Lost in {Translation}: {Methodological Considerations} in {Cross-Cultural Research}. \emph{Child Development}, \emph{78}(4), 1255--1264. \url{https://www.jstor.org/stable/4620701}
-
-\bibitem[\citeproctext]{ref-prein2023tango}
-Prein, J.
-C., Kalinke, S., Haun, D.
-B.
-M., \& Bohn, M.
-(2023).
-{TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults.
-\emph{Behavior Research Methods}.
-\url{https://doi.org/10.3758/s13428-023-02159-5}
-
-\bibitem[\citeproctext]{ref-prein2024variation}
-Prein, J.
-C., Maurits, L., Werwach, A., Haun, D.
-B.
-M., \& Bohn, M.
-(2024).
-\emph{Variation in gaze following across the life span: {A} process-level perspective}.
-PsyArXiv.
-\url{https://doi.org/10.31234/osf.io/dy73a}
-
-\bibitem[\citeproctext]{ref-pronk2022methods}
-Pronk, T., Molenaar, D., Wiers, R.
-W., \& Murre, J.
-(2022).
-Methods to split cognitive task data for estimating split-half reliability: {A} comprehensive review and systematic assessment.
-\emph{Psychonomic Bulletin \& Review}, \emph{29}(1), 44--54.
-\url{https://doi.org/10.3758/s13423-021-01948-3}
-
-\bibitem[\citeproctext]{ref-rcoreteam2024language}
-R Core Team. (2024). \emph{R: {A} language and environment for statistical computing} {[}Manual{]}. R Foundation for Statistical Computing.
-
-\bibitem[\citeproctext]{ref-rouder2019psychometrics}
-Rouder, J.
-N., \& Haaf, J.
-M.
-(2019).
-A psychometrics of individual differences in experimental tasks.
-\emph{Psychonomic Bulletin \& Review}, \emph{26}(2), 452--467.
-\url{https://doi.org/10.3758/s13423-018-1558-y}
-
-\bibitem[\citeproctext]{ref-schilbach2013secondperson}
-Schilbach, L., Timmermans, B., Reddy, V., Costall, A., Bente, G., Schlicht, T., \& Vogeley, K.
-(2013).
-Toward a second-person neuroscience.
-\emph{The Behavioral and Brain Sciences}, \emph{36}(4), 393--414.
-\url{https://doi.org/10.1017/S0140525X12000660}
-
-\bibitem[\citeproctext]{ref-selcuk2023development}
-Selcuk, B., Gonultas, S., \& Ekerim-Akbulut, M.
-(2023).
-Development and use of theory of mind in social and cultural context.
-\emph{Child Development Perspectives}, \emph{17}(1), 39--45.
-\url{https://doi.org/10.1111/cdep.12473}
-
-\bibitem[\citeproctext]{ref-shepherd2010following}
-Shepherd, S.
-(2010).
-Following {Gaze}: {Gaze-Following Behavior} as a {Window} into {Social Cognition}.
-\emph{Frontiers in Integrative Neuroscience}, \emph{4}(5).
-\url{https://doi.org/10.3389/fnint.2010.00005}
-
-\bibitem[\citeproctext]{ref-stengelin2020cultural}
-Stengelin, R., Hepach, R., \& Haun, D.
-B.
-M.
-(2020).
-Cultural variation in young children's social motivation for peer collaboration and its relation to the ontogeny of {Theory} of {Mind}.
-\emph{PLOS ONE}, \emph{15}(11), e0242071.
-\url{https://doi.org/10.1371/journal.pone.0242071}
-
-\bibitem[\citeproctext]{ref-tang2024slow}
-Tang, Y., Gonzalez, M.
-R., \& Deák, G.
-O.
-(2024).
-The slow emergence of gaze- and point-following: {A} longitudinal study of infants from 4 to 12 months.
-\emph{Developmental Science}, \emph{27}(3), e13457.
-\url{https://doi.org/10.1111/desc.13457}
-
-\bibitem[\citeproctext]{ref-taumoepeau2019crosscultural}
-Taumoepeau, M., Sadeghi, S., \& Nobilo, A.
-(2019).
-Cross-cultural differences in children's theory of mind in {Iran} and {New Zealand}: {The} role of caregiver mental state talk.
-\emph{Cognitive Development}, \emph{51}, 32--45.
-\url{https://doi.org/10.1016/j.cogdev.2019.05.004}
-
-\bibitem[\citeproctext]{ref-tomasello2007reliance}
-Tomasello, M., Hare, B., Lehmann, H., \& Call, J.
-(2007).
-Reliance on head versus eyes in the gaze following of great apes and human infants: The cooperative eye hypothesis.
-\emph{Journal of Human Evolution}, \emph{52}(3), 314--320.
-\url{https://doi.org/10.1016/j.jhevol.2006.10.001}
-
-\bibitem[\citeproctext]{ref-waschl2022crosscultural}
-Waschl, N., \& Chen, M.
-(2022).
-Cross-{Cultural Considerations} for {Adapting Valid Psychoeducational Assessments}.
-In O.
-S.
-Tan, K.
-K.
-Poon, B.
-A.
-O'Brien, \& A.
-Rifkin-Graboi (Eds.), \emph{Early {Childhood Development} and {Education} in {Singapore}} (pp.
-113--140).
-Springer.
-\url{https://doi.org/10.1007/978-981-16-7405-1_7}
 

### 2024-06-19 paper/manuscript.Rmd
upload preprint

@@
       - "Conceptualization"
+      - "Formal Analysis"
       - "Methodology"
+      - "Project administration"
+      - "Resources"
       - "Software"
-      - "Formal Analysis"
-      - "Resources"
+      - "Visualization"
       - "Writing - Original Draft Preparation"
@@
   - name          : "Florian M. Bednarski (ORCID: 0000-0003-4384-4791)"
-    affiliation   : "4"
+    affiliation   : "3"
     role:
+      - "Methodology"
       - "Resources"
@@
   - name          : "Ardain Dzabatou"
-    affiliation   : "5"
+    affiliation   : "4"
     role:
+      - "Methodology"
       - "Resources"
@@
   - name          : "Michael C. Frank (ORCID: 0000-0002-7551-4378)"
-    affiliation   : "6"
+    affiliation   : "5"
     role:
+      - "Methodology"
       - "Resources"
@@
   - name          : "Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)"
-    affiliation   : "4"
+    affiliation   : "3"
     role:
+      - "Methodology"
       - "Resources"
@@
     role:
+      - "Methodology"
       - "Resources"
@@
   - name          : "Patricia Kanngiesser (ORCID:0000-0003-1068-3725)"
-    affiliation   : "7"
+    affiliation   : "6"
     role:
+      - "Methodology"
       - "Resources"
@@
   - name          : "Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)"
-    affiliation   : "8"
+    affiliation   : "7"
     role:
+      - "Methodology"
       - "Resources"
@@
   - name          : "Bahar Köymen (ORCID: 0000-0001-5126-8240)"
-    affiliation   : "9"
+    affiliation   : "8"
     role:
+      - "Methodology"
       - "Resources"
@@
   - name          : "Shirley Magazi (ORCID: 0009-0006-0479-9800)"
-    affiliation   : "10"
+    affiliation   : "9"
     role:
+      - "Methodology"
       - "Resources"
@@
   - name          : "Wesley R. Pieters (ORCID:0000-0002-6152-249X)"
-    affiliation   : "10"
+    affiliation   : "9"
     role:
+      - "Methodology"
       - "Resources"
@@
   - name          : "Umay Sen (ORCID: 0000-0001-9488-0851)"
-    affiliation   : "13"
+    affiliation   : "10"
     role:
+      - "Methodology"
       - "Resources"
@@
   - name          : "Robert Z. Sparks (ORCID: 0000-0001-7545-0522)"
-    affiliation   : "6"
+    affiliation   : "5"
     role:
+      - "Methodology"
       - "Resources"
@@
   - name          : "Roman Stengelin (ORCID: 0000-0003-2212-4613)"
-    affiliation   : "2,10"
+    affiliation   : "2,9"
     role:
+      - "Conceptualization"
+      - "Methodology"
       - "Resources"
@@
   - name          : "Florence Tusiime"
-    affiliation   : "3"
+    affiliation   : "12"
     role:
+      - "Methodology"
       - "Resources"
@@
   - name          : "Zhen Zhang (ORCID: 0000-0001-9300-0920)"
-    affiliation   : "12"
+    affiliation   : "13"
     role:
+      - "Methodology"
       - "Resources"
@@
   - name          : "Yufei Zong (ORCID: 0009-0000-5012-0244)"
-    affiliation   : "12"
+    affiliation   : "13"
     role:
+      - "Methodology"
       - "Resources"
@@
     role:
+      - "Conceptualization"
       - "Funding acquisition"
+      - "Methodology"
       - "Writing - Review & Editing" 
@@
       - "Conceptualization"
+      - "Funding acquisition"
       - "Methodology"
+      - "Project administration"
+      - "Supervision"
       - "Writing - Review & Editing"
@@
   - id            : "3"
-    institution   : "Budongo Conservation Field Station, Uganda"
+    institution   : "School of Psychology, University of Auckland, New Zealand"
   - id            : "4"
-    institution   : "School of Psychology, University of Auckland, New Zealand"
+    institution   : "Université Marien Ngouabi, Republic of the Congo"
   - id            : "5"
-    institution   : "Université Marien Ngouabi, Republic of the Congo"
+    institution   : "Department of Psychology, Stanford University, USA"
   - id            : "6"
-    institution   : "Department of Psychology, Stanford University, USA"
+    institution   : "School of Psychology, University of Plymouth, UK"
   - id            : "7"
-    institution   : "School of Psychology, University of Plymouth, UK"
+    institution   : "Department of Psychology, Koç University, Türkiye"
   - id            : "8"
-    institution   : "Department of Psychology, Koç University, Türkiye"
+    institution   : "Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK"
   - id            : "9"
-    institution   : "Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK"
+    institution   : "Department of Psychology and Social Work, University of Namibia, Namibia"
   - id            : "10"
-    institution   : "Department of Psychology and Social Work, University of Namibia, Namibia"
+    institution   : "Department of Psychology, Developmental Psychology, Uppsala University, Sweden"
   - id            : "11"
@@
   - id            : "12"
+    institution   : "Budongo Conservation Field Station, Uganda"
+  - id            : "13"
     institution   : "CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China"
-  - id            : "13"
-    institution   : "Department of Psychology, Developmental Psychology, Uppsala University, Sweden"
   - id            : "+"
@@
 abstract: | 
-            Cross-cultural studies are crucial for investigating cultural variability and universality of cognitive developmental processes.
+            Cross-cultural studies are crucial for investigating the cultural variability and universality of cognitive developmental processes.
 However, cross-cultural assessment tools in cognition across languages and communities are limited.
-This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (Task for Assessing iNdividual Differences in Gaze understanding Open -- Cross-Cultural or TANGO--CC).
-The TANGO--CC was developed and psychometrically assessed in one cultural setting and, with the input of local collaborators, adapted for cross-cultural data collection.
+This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (TANGO--CC).
+The task was developed and psychometrically assessed in one cultural setting and, with input of local collaborators, adapted for cross-cultural data collection.
 Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community.
@@
 Within-community variation outweighed between-community variation.
-We provide an open-source website for researchers to customize and use the task.
+We provide an open-source website for researchers to customize and use the task (https://ccp-odc.eva.mpg.de/tango-cc).
 The TANGO--CC can be used to assess basic social cognition in diverse communities and provides a roadmap for researching community-level and individual-level differences across cultures.
@@
 keywords          : "cross-cultural psychology, social cognition, gaze following, individual differences, reliability"
-wordcount         : "5457"
+wordcount         : "XXX"
 floatsintext      : yes
@@
 ```{r setup, include = FALSE}
+# for pdf output: 
+# output            :   
+#   papaja::apa6_pdf:
+#     latex_engine: xelatex
+#     keep_tex: true
+
 library("tidyverse")
@@
 Despite numerous calls for change, the samples reported in major psychology journals still lack diversity [@gutchess2023considerationa; @thalmayer2021neglecteda; @apicella2020weird].
-This hinders progress in theory building and testing: we cannot draw inferences about universal and variable aspects of the human cognitive system from data collected exclusively in one single communities [@krys2024weirda].
-While this sampling bias is often discussed within adult psychology, it is equally relevant for developmental psychology [@nielsen2017persistent]. 
+This hinders progress in theory building and testing: we cannot draw inferences about universal and variable aspects of the human cognitive system from data collected exclusively in one single community [@krys2024weirda].
+While this sampling bias is often discussed within adult psychology, it is equally relevant to developmental psychology [@nielsen2017persistent]. 
 Early experiences shape the way children think about and interact with the world and an ontogenetic perspective is needed to explore the foundational aspects of human behavioral diversity [@torrens2023einfluss; @amir2020crosscultural; @broesch2023roadmap; @liebal2018crosscultural].
@@
 There are numerous challenges with collecting cross-cultural, developmental data [@amir2020crosscultural; @broesch2023roadmap].
-Cross-cultural studies need reliable and valid measures to systematically capture variation between communities and/or individuals.
-However, studies on social cognition with US-American and European samples rarely report psychometric information [for a review, see @beaudoin2020systematic], and the picture further deteriorates when we look at cross-cultural social cognition tasks [@hajduk2020how; @bourdage2023evaluation; @waschl2022crosscultural].
-Thus, it is already challenging to find reliable and valid tasks that have measurement sensitivity to detect individual differences within one community, let alone tasks that do so across different communities.
-In this paper, we describe the construction and psychometric evaluation of a cross-cultural measure of basic social cognition (gaze following) in children as a concrete example for how to address this problem.
+Cross-cultural studies need reliable and valid measures to capture variation between communities and/or individuals systematically.
+Even though this applies to all areas of cognitive development, we focus on social cognition in this paper.
 
-Adapting tasks to diverse communities and assessing their validity and reliability might be especially important in the social-cognitive domain.
 Social cognition refers to how an individual processes information in social situations which allows them to understand and predict others' behavior [@decety2020social; @zeigler-hill2015how; @adolphs1999social; @frith2007social].
 If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, then tasks themselves should be tuned to the features of specific communities.
-Indeed, task performance can be diminished when stimuli do not reflect characteristics of the participants' communities [@pena2007lost].
+Indeed, task performance can be diminished when stimuli do not reflect the characteristics of the participants' communities [@pena2007lost].
 For example, @elfenbein2002universality found better emotion recognition for members of the same national, ethnic, or regional group.
@@
 
-There exists a continuum of approaches that researchers can take to collect cross-cultural data, and the decision for a specific method partly depends on whether researchers aim to increasing the *depth* (culture specificity) or *breadth* (standardization across multiple communities) of our psychological knowledge [@amir2020crosscultural].
-At one extreme, researchers translate the psychological construct into an individually designed study for each community (termed "assembly"; @he2012bias, @waschl2022crosscultural).
-While this approach allows greater flexibility and sensitivity to cultural differences, it might not be feasible for studying a multitude of communities as it becomes too demanding and time-consuming.
-Due to its specificity, observations are limited to each community and absolute task scores might not be comparable across communities.
+From a psychometric perspective, the situation looks dire.
+Studies on social cognition with US-American and European samples rarely report psychometric information [for a review, see @beaudoin2020systematic], and the picture further deteriorates when we look at cross-cultural social cognition tasks [@hajduk2020how; @bourdage2023evaluation; @waschl2022crosscultural].
+Thus, it is already challenging to find reliable and valid tasks that have measurement sensitivity to detect individual differences within one community, let alone tasks that do so across different communities.
+In this paper, we describe the construction and psychometric evaluation of a cross-cultural measure of basic social cognition (gaze following) in children as a concrete example of how to address this problem.
+
+The approaches that researchers can take to collect cross-cultural data lie on a continuum: the decision for a specific method partly depends on whether researchers aim to increase the *depth* (culture specificity) or *breadth* (standardization across multiple communities) of their work [@amir2020crosscultural].
+At one extreme, researchers translate the psychological construct into a separate design or task for each community (termed "assembly"; @he2012bias, @waschl2022crosscultural).
+While this approach allows greater flexibility and sensitivity to cultural differences, it might not be feasible to study a multitude of communities as it becomes too demanding and time-consuming.
+Furthermore, the results are limited to each community and absolute task scores might not be comparable across communities.
 A study following this approach is @wefers2023universality who investigated how cultural variations in parenting styles modulated infants' responses to disruptions in social interactions. 
@@
 
-At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed "adoption" and "adaptation", respectively [@he2012bias, @waschl2022crosscultural]).
+At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed "adoption" and "adaptation", respectively; [@he2012bias, @waschl2022crosscultural]).
 This approach is less sensitive to each community's unique characteristics but renders quantitative comparisons of data more feasible.
-An example following this approach is the Multilingual Assessment Instrument for Narratives [MAIN; @gagarina2012main], which assesses narrative abilities in mono- and multilingual children. 
-Extensive piloting and adaptation of MAIN materials ensured that the instrument is culturally appropriate, robust and suitable for cross-linguistic comparisons [@gagarina2012main], and new and revised language versions are continuously added to the MAIN database [@gagarina2020new].
+An example following this approach is the Multilingual Assessment Instrument for Narratives (MAIN; [@gagarina2012main]), which assesses narrative abilities in mono- and multilingual children. 
+Extensive piloting and adaptation of MAIN materials ensured that the instrument is culturally appropriate, robust, and suitable for cross-linguistic comparisons [@gagarina2012main], and new and revised language versions are continuously added to the MAIN database [@gagarina2020new].
 
-The present paper aims to describe the development and psychometric properties of a standardized social cognition task that can be adapted to diverse communities.
-Our task focuses on one of the most fundamental social-cognitive abilities: gaze following, that is, the ability to identify the attentional focus of another agent.
+The present paper aims to describe the development and psychometric properties of a social cognition task that can be adapted to diverse communities.
+On the continuum described above, our task lies more toward standardized approaches but allows for some customization of the stimuli to each local community.
+The task focuses on one of the most fundamental social-cognitive abilities: gaze following, that is, the ability to identify the attentional focus of another agent.
 Gaze following develops early in infancy [@delbianco2019developmental; @tang2024slow] and contributes to social learning, communication, and collaboration [@shepherd2010following; @tomasello2007reliance; @bohn2018common; @hernik2019infant].
-While the question how social-environmental and cultural factors impact gaze following was recently posed as one of the big open questions in gaze following research [@astor2022gaze], studies focusing on cultural variations of gaze following are rare.
-@callaghan2011early investigated gaze following behind barriers in 12- and 17-month-olds from rural Canada (n = 35), Peru (n = 38) and India (n = 65).
-In their setup, an agent sat next to a wall or container and looked at a toy behind this barrier (experimental condition) or a sticker in front of it (control condition).
-The researchers then assessed whether and in which conditions the children crawled towards/around the barriers to follow the agent's gaze.
-While the absolute crawling rates differed across communities, children in all three communities crawled more often to gain visual access when the agent looked at an object behind the barrier compared to in front of it.
+While the question of how social-environmental and cultural factors impact gaze following was recently posed as one of the big open questions in gaze following research [@astor2022gaze], studies focusing on cultural variations of gaze following are rare.
+@callaghan2011early investigated gaze following behind barriers in 12- and 17-month-olds from rural Canada (n = 35), Peru (n = 38), and India (n = 65). 
+In their setup, an agent looked at a toy behind (experimental condition) or a sticker in front of (control condition) a barrier, and children's crawling toward the barrier to follow the agent's gaze was assessed.
+While the absolute crawling rates differed across communities, children in all three communities crawled more often to gain visual access when the agent looked at an object behind the barrier than in front of it.
 @hernik2019infant studied 22 infants between 5 to 7 months of age from Vanuatu and used an eye-tracking procedure displaying a local actor looking at one of two objects.
-Even though face-to-face interactions are less common in interactions between caregivers and children in Vanuatu than in Western communities, the result patterns of gaze following in Ni-Vanuatu infants resembled those of their Western counterparts: infants from Vanuatu followed the agent's gaze to the target object only when preceded by infant-directed, and not adult-directed, speech.
-While these two studies point towards a potential cross-cultural stability of gaze following, 
-the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings.
+Even though face-to-face interactions are less common in parent-child interactions in Vanuatu than in Western communities, the result patterns of gaze following in Ni-Vanuatu infants resembled those of their Western counterparts: infants from Vanuatu followed the agent's gaze to the target object only when preceded by infant-directed, and not adult-directed, speech.
+While these two studies point towards potential cross-cultural stability of gaze following, the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings and – more importantly – does not allow for studying individual-differences.
+A more comprehensive cross-cultural study on gaze following was recently conducted by @bohn2024universal.
+The researchers tested the universality of gaze following by studying 17 different communities on five continents and found evidence for a similar processing mechanism across communities.
 
-The task presented here aims to tackle these issues and builds upon a previously established gaze-following task called 'TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by @prein2023tango.
+The task presented in this manuscript was developed for the study by @bohn2024universal and is based on a previously established gaze-following task called 'TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by @prein2023tango.
 The TANGO measures how precisely participants locate an agent's attentional focus.
 It reliably measured individual differences in a German child sample and an English-speaking remote adult sample [@prein2023tango].
-As we cannot claim a task's generalizability and reliability based on mono-cultural samples, we need to assess the TANGO's psychometric properties in a larger cross-cultural sample. 
-This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 different communities on five continents [@bohn2024universal].
+However, we cannot claim the task's generalizability and reliability based on a mono-cultural sample. 
+This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 diverse communities [@bohn2024universal].
 We describe the task's development and provide a tutorial for the open-source website (<https://ccp-odc.eva.mpg.de/tango-cc/>).
@@
 The TANGO-CC was implemented in Leipzig, Germany, and thoroughly assessed in terms of reliability and validity [@prein2023tango].
-During this process, the cross-cultural adaptation of the task was prepared within a team of cross-cultural psychologists and cognitive scientists. 
-In this paper, we assess the TANGO--CC's measurement quality (i.e., variability and reliability) across 17 diverse communities by analyzing the data set from @bohn2024universal.
+During this process, the cross-cultural adaptation of the task was prepared by a team of cross-cultural psychologists and cognitive scientists. 
+In this paper, we assess the TANGO--CC's measurement quality (*i.e.,* variability and reliability) across 17 diverse communities by analyzing the data set from @bohn2024universal.
 In the following, we describe the different steps in detail.
@@
 We programmed a function that calculates the x and y coordinates of where the agent's pupil and iris should move to follow the balloon, given the eyes' and balloon's original positions and measures. 
-As the measures of the eyes and balloon are read out dynamically from the image on screen, stimuli can be easily adapted and exchanged.
-No coordination values for animation are hard-coded into the task's source code.
-After having programmed this "backbone" functionality of the task (*i.e.*, animate the eyes so that they follow the balloon), we added the task's audio instructions and superficial appearance (e.g., background scene, hedge, more agent faces).
+As the measures of the eyes and balloon are read out dynamically from the image on screen, stimuli can be easily adapted and exchanged (*i.e.*, no coordination values for animation are hard-coded into the task's source code).
+After having programmed this "backbone" functionality of the task (*i.e.*, animate the eyes so that they follow the balloon), we added the task's audio instructions and superficial appearance (e.g., background scene, hedge, agent faces).
 
 This basic version of the TANGO was psychometrically evaluated in a German child sample and an English-speaking remote adult sample and was found to be highly reliable and valid [@prein2023tango].
-While children became more precise in locating the attentional focus of the agent with age, individuals differed across all age groups and showed no floor- or ceiling effects.
+While children became more precise in locating the agent's attentional focus with age, individuals differed across all age groups and showed no floor- or ceiling effects.
 In the Leipzig sample, performance in the TANGO was weakly related to factors of children's daily social environment and could predict children's receptive vocabulary 6 months later.
-In a computational cognitive model, @prein2024variation described gaze following as form of social vector following and empirically found that performance in the TANGO was related to children's non-social vector following and visual perspective-taking abilities.
+In a computational cognitive model, @prein2024variation described gaze following as a form of social vector following and empirically found that performance in the TANGO was related to children's non-social vector following and visual perspective-taking abilities.
 These connections to related constructs indicate the task's convergent validity in the German child sample.
 
-To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces and background scenes with the feedback from local researchers and research assistants. 
+To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces and background scenes with input from local researchers and research assistants. 
 The stimulus pool was adjusted and expanded until the researchers and research assistants from each target community judged the selected stimuli to be representative of the local population and typical accommodation (see Figure \@ref(fig:fig2)).
-Audio instructions were translated from English into the corresponding local language(s).
+Audio instructions were translated from English or German into the corresponding local language(s).
 By back-translating these instructions, we ensured the original meaning did not change.
@@
 In test trials, a hedge grows at the beginning of the trial and participants see neither the movement nor the final position of the balloon.
-The first trial of each type contains an audio description of the presented events (see supplements of @bohn2024universal).
+The first trial of each type contains an audio description of the presented events (see Supplements).
 Notably, the instructions explicitly state that the agent is looking at the balloon.
@@
 By using self-explanatory animations, language demands are kept to a minimum.
-The task uses simple audio instructions, which makes the task accessible to children from different age groups, and no reading skills are needed. 
+The task uses simple audio instructions, which makes the task accessible to children from different age groups, and no reading skills are required. 
 There is no feedback during the task to prevent learning effects across trials.
@@
 For the balloon positions, the entire width of the screen (1920 in "SVG units") is divided into ten bins.
-Exact coordinates (value between 0 far left and 1920 far right) within each bin are then randomly generated.
+Exact coordinates (value between 0 for the far left and 1920 for the far right) within each bin are then randomly generated.
 The number of repetitions for each agent, balloon color, and balloon bin is calculated based on the total number of trials and the number of unique agents, balloon colors, and bins, respectively.
@@
 
-When reseachers visit the TANGO--CC's website 
+When researchers visit the TANGO--CC's website 
 (<https://ccp-odc.eva.mpg.de/tango-cc/>), they can select the language for audio instructions which are currently available for 13 different languages and five more dialects (see Table 1). 
 To add a new language, researchers have two options: 
-(1) for using their own audio instructions in the offline version of the task, researchers can download the task, exchange the audio instructions in the dist folder (in the folder sounds > custom) and select "Custom" in the language drop down menu.
+(1) for using their own audio instructions in the offline version of the task, researchers can download the task, exchange the audio instructions in the dist folder (in the folder sounds > custom) and select "Custom" in the language drop-down menu.
 For detailed instructions, see the TANGO--CC's manual (<https://ccp-odc.eva.mpg.de/tango-cc/manual.html>). 
 (2) For adding a new language in the online version of the task, researchers can contact the first author of this paper.
-Please note that this option requires new audio recordings by the interested reseachers, which will then be openly available for all users of the task.
+Please note that this option requires new audio recordings by the interested researchers, which will then be openly available for all users of the task.
 All written instructions in the task are solely for the research assistant to help them guide participants through the task; these instructions are solely available in English. 
-The task can either be started with the default settings or further customized by adapting the numbers of trials, agents, and background scenes.
-The default settings use the version applied in @bohn2024universal based on the selected language.
+The task can either be started with the default settings or further customized by adapting the number of trials, agents, and background scenes.
+The default settings use the version applied in @bohn2024universal based on the selected language (see Supplements).
 
@@
 A webcam recording might prove especially helpful for unsupervised online data collection to ensure that the participant is alone during the task and no help is provided.
-The participant identifier and webcam choice has to be provided every time the task is run.
+The participant identifier and webcam choice have to be provided every time the task is run.
 
@@
 
-We created a public OSF page (https://doi.org/10.17605/OSF.IO/P2EGU) where we plan to collect data sets that used the TANGO-CC.
-Researchers who have collected data using the TANGO--CC can share their data with the community by contacting the first author of this paper or visiting this OSF repository.
+We created a public OSF page (https://doi.org/10.17605/OSF.IO/P2EGU) on which we plan to collect data sets that used the TANGO-CC.
+Researchers who have collected data using the TANGO--CC can share their data with the community by contacting the first author of this paper or visiting the OSF repository.
 
@@
               "Marathi",
-              "Shona",
+              "Shona *",
               "Spanish",
@@
   caption = "Current language options available for the audio instructions in the TANGO--CC", 
-  note = "In those cases where more than one speaker's country of origin is listed, the audio instructions were recorded multiple times by different speakers.
-For example, the English instructions are available in five different versions."
+  note = "In cases where more than one speaker's country of origin is listed, the audio instructions were recorded multiple times by different speakers.
+For example, the English instructions are available in five different versions.
+* Please note that audio instructions are available in Shona but no data of this version is included in the present data set."
 )
@@
 
-(ref:figlab2) **Customizable components of the TANGO--CC.** Researchers can select the language of the audio instructions (see Table 1), the number of trials per trial type, the background, and the agent's face.
+(ref:figlab2) **Screenshot of the customizable components of the TANGO--CC.** Researchers can select the language of the audio instructions (see Table 1), the number of trials per trial type, the background, and the agent's face.
 
@@
 The task was implemented in `JavaScript`, `HTML`, and `CSS` and is presented as a web app.
-It can be accessed on any modern web browser on any device (e.g., computer or tablet) and does not require prior installation (please note that configurations of browsers and JavaScript may change in the future).
-Participant's responses can be recorded on a touchscreen or with a mouse or track pad.
+It can be accessed on any modern web browser on any device (e.g., computer or tablet) and does not require prior installation (though please note that configurations of browsers and JavaScript may change in the future).
+Participant's responses can be recorded on a touchscreen or with a mouse or trackpad.
 The online version of the task can be used for unsupervised data collection (for example, using online platforms like *Prolific*; see @prein2023tango).
@@
 SVGs ensure that the picture quality, aspect ratio, and relative object positioning are constant. 
-Furthermore, stimuli are added as individual components to the image scene which allows for an easy adaptation of task's elements (in contrast to other image formats that consist of only one combined layer that would need entire replacement).
-The task is programmed so that responses are only registered when the participant clicks the relevant part of the screen (i.e., in test trials, when they click the hedge).
+Furthermore, stimuli are added as individual components to the image scene which allows for an easy adaptation of the task's elements (in contrast to other image formats that consist of only one combined layer that would need entire replacement).
+The task is programmed so that responses are only registered when the participant clicks the relevant part of the screen (*i.e.,* in test trials, when they click the hedge).
 Furthermore, clicks are only registered after the voice recordings stop playing.
@@
 The file will be stored in the device's downloads folder and is named after the following pattern: "tangoCC-participantID-YYYY-MM-DD_hh_mm_ss".
-To modify the storage location on the device, researchers can change the designated downloads folder in the browser settings.
+To modify the storage location on the device, researchers can change the designated downloads folder in their browser settings.
 
@@
 
-We used the data set from @bohn2024universal for psychometric evaluation of the TANGO--CC.
+We used the data set from @bohn2024universal for the psychometric evaluation of the TANGO--CC.
 The data set contains a sample of *N* = `r sample_table[sample_table$Community == "Total",]$Total` children, aged 2.5 to 11 years.
@@
 
+All analyses and the data set can be accessed on GitHub (https://github.com/ccp-eva/tango-cc-methods/).
 First, we inspected the mean and standard deviations by community and compared performance in each trial type (training 1, training 2, test trials).
@@
 
-Our GLMM analysis supported the visual inspection of the data: the fixed-effect estimates for training 1 ($\beta$ = `r fixef(mtrialtypes)["trialtypeTraining1", "Estimate"]`; 95% CrI [`r fixef(mtrialtypes)["trialtypeTraining1", "Q2.5"]`; `r fixef(mtrialtypes)["trialtypeTraining1", "Q97.5"]`]) and training 2 ($\beta$ = `r fixef(mtrialtypes)["trialtypeTraining2", "Estimate"]`; 95% CrI [`r fixef(mtrialtypes)["trialtypeTraining2", "Q2.5"]`; `r fixef(mtrialtypes)["trialtypeTraining2", "Q97.5"]`]) were negative and reliably different from zero.
-[^1]
+Our GLMM analysis supported the visual inspection of the data: the fixed-effect estimates for training 1 ($\beta$ = `r fixef(mtrialtypes)["trialtypeTraining1", "Estimate"]`; 95% CrI [`r fixef(mtrialtypes)["trialtypeTraining1", "Q2.5"]`; `r fixef(mtrialtypes)["trialtypeTraining1", "Q97.5"]`]) and training 2 ($\beta$ = `r fixef(mtrialtypes)["trialtypeTraining2", "Estimate"]`; 95% CrI [`r fixef(mtrialtypes)["trialtypeTraining2", "Q2.5"]`; `r fixef(mtrialtypes)["trialtypeTraining2", "Q97.5"]`]) were negative and reliably different from zero.[^1]
 This effect was found across all communities (random effects of trial type within community: minimum estimate for training 1 = `r max(trialtypes_est$Training1)`; 95%CrI [`r trialtypes_est$Training1_q25[which.max(trialtypes_est$Training1)]`; `r trialtypes_est$Training1_q975[which.max(trialtypes_est$Training1)]`]; minimum estimate for training 2 = `r max(trialtypes_est$Training2)`; 95%CrI [`r trialtypes_est$Training2_q25[which.max(trialtypes_est$Training2)]`; `r trialtypes_est$Training2_q975[which.max(trialtypes_est$Training2)]`]).
@@
 [^1]: Please note that the TANGO--CC measures imprecision in gaze following.
-Therefore, a negative sign indicates that children showed less imprecision (i.e., were more precise) in the training trials than in the test trials.
+Therefore, a negative sign indicates that children showed less imprecision (*i.e.,* were more precise) in the training trials than in the test trials.
 
 To identify the sources of variation, we computed intraclass correlations (ICC).
-The variation of children's imprecision within communities was substantially larger than the variation between the communities.
+The variation in children's imprecision within communities was substantially larger than the variation between the communities.
 The mean within-community variance was `r mean(var_df$within_community_var)`, ranging from `r min(var_df$within_community_var)` (in Pune, India) to `r max(var_df$within_community_var)` (in Chimfunshi, Zambia).
@@
 Second, using the function `by_split` from the `splithalfr` package [@pronk2022methods], data was stratified by target centrality (capturing trial difficulty), and a Pearson correlation was calculated between the matched halves.
-Third, a data set was generated with stratified test halves by target centrality and we applied the Generalized Linear Mixed Model (GLMM) approach introduced by @rouder2019psychometrics.
+Third, a data set was generated with stratified test halves by target centrality and we applied the GLMM approach introduced by @rouder2019psychometrics.
 A GLMM was fitted with the mean imprecision as the outcome, age as the predictor, and test half and participant id as random effects (model notation: `imprecision ~ age + (0 + half | subjid)`).
@@
 While we performed a detailed psychometric evaluation of the task in a German setting, we collaborated with local researchers for the cross-cultural stimulus development and selection.
-Importantly, we re-assessed the TANGO--CC's psychometric properties in a large and diverse data set from @bohn2024universal, including children from 17 diverse communities in rural and urban settings with varying degrees of market integration and technology exposure.
-While we cannot generalize our findings to all communities worldwide, we found that the TANGO-CC captured reliable individual variation in all communities studied by @bohn2024universal.
-We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful for other researchers. 
-We recommend that researchers consider generalizability concerns and cross-cultural applications of their tasks and collaborate with local researchers at early stages of task development [@torrens2023einfluss].
+Importantly, we re-assessed the TANGO--CC's psychometric properties in a large and diverse data set.
+While we cannot generalize our findings to all communities worldwide, we found that the TANGO-CC captured reliable individual variation in all 17 communities studied by @bohn2024universal.
+We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful to other researchers. 
+We recommend that researchers consider generalizability concerns and cross-cultural applications of their tasks and collaborate with local researchers at the early stages of task development [@torrens2023einfluss].
 Using the TANGO--CC (or any other task) in a new community requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
@@
 
-Compared to one of the most commonly used social cognition measure -- the change-of-location false belief task [@wimmer1983beliefs; @baron-cohen1985does] -- the TANGO--CC has several advantages: a continuous outcome measure which can capture individual differences, a short task duration that allows for more trials per child, stimuli that can be easily adapted, and known psychometric properties across 17 communities.
-The task is presented as a web app that enables efficient data collection with large sample sizes, while it can also be used to collect data offline in locations without reliable internet connection.
+Compared to one of the most commonly used social cognition measures -- the change-of-location false belief task [@wimmer1983beliefs; @baron-cohen1985does] -- the TANGO--CC has several advantages: a continuous outcome measure that can capture individual differences from three years to adulthood, a short task duration that allows for more trials per child, stimuli that can be easily adapted, and known psychometric properties across 17 communities.
+The task is presented as a web app that enables efficient data collection with large sample sizes, while it can also be used to collect data offline in locations without a reliable internet connection.
 The TANGO--CC follows a standardized procedure, which leaves no room for rater errors and greatly simplifies online training of research assistants.
@@
 @schilbach2013secondperson pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions.
-First evidence suggests that the TANGO--CC indeed taps into social cognition as utilized in real life: @prein2024variation found that children's perspective-taking abilities in a personal social interaction was linked to performance in the TANGO, but less so to a matched, non-social vector following task.
+First evidence suggests that the TANGO--CC indeed taps into social cognition as utilized in real life: @prein2024variation found that children's perspective-taking abilities in a personal social interaction were linked to performance in the TANGO, but less so to a matched, non-social vector following task.
 However, this study exclusively relied on a German sample and future research should investigate whether the relationship between the TANGO--CC and perspective-taking abilities holds across communities.
@@
 2).
-This underlines how efforts to improve the replicability can be combined with the goal of increasing the generalisability of psychological research [@li2024developmental; @syed2021reproducibility].
-@li2024developmental have argued that replicable and generalisable results rely on stimulus sets with slight variations, more diverse samples, and data collection at a greater scale, which are all steps the TANGO--CC has taken.
+This underlines how efforts to improve replicability can be combined with the goal of increasing the generalisability of psychological research findings [@li2024developmental; @syed2021reproducibility].
+@li2024developmental have argued that replicable and generalizable results rely on stimulus sets with slight variations, more diverse samples, and data collection at a greater scale, which are indeed all steps the TANGO--CC has taken.
 Openly sharing the TANGO--CC's materials will allow other researchers to (hopefully) replicate the results and deepen our cumulative understanding of social-cognitive development across diverse communities.

### 2024-06-19 paper/manuscript.tex
upload preprint

@@
 {}{\PatchFailed}
-\keywords{cross-cultural psychology, social cognition, gaze following, individual differences, reliability\newline\indent Word count: 5457}
+\keywords{cross-cultural psychology, social cognition, gaze following, individual differences, reliability\newline\indent Word count: XXX}
 \usepackage{lineno}
@@
   pdfauthor={Julia Christin Prein (ORCID: 0000-0002-3154-6167)1,2, Florian M.
-Bednarski (ORCID: 0000-0003-4384-4791)4, Ardain Dzabatou5, Michael C.
-Frank (ORCID: 0000-0002-7551-4378)6, Annette M.
+Bednarski (ORCID: 0000-0003-4384-4791)3, Ardain Dzabatou4, Michael C.
+Frank (ORCID: 0000-0002-7551-4378)5, Annette M.
 E.
-Henderson (ORCID: 0000-0003-4384-4791)4, Josefine Kalbitz2, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)7, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)8, Bahar Köymen (ORCID: 0000-0001-5126-8240)9, Maira V.
-Manrique-Hernandez2, Shirley Magazi (ORCID: 0009-0006-0479-9800)10, Lizbeth Mújica-Manrique2, Julia Ohlendorf2, Damilola Olaoba2, Wesley R.
-Pieters (ORCID:0000-0002-6152-249X)10, Sarah Pope-Caldwell2, Umay Sen (ORCID: 0000-0001-9488-0851)13, Katie Slocombe (ORCID: 0000-0002-7310-1887)11, Robert Z.
-Sparks (ORCID: 0000-0001-7545-0522)6, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,10, Jahnavi Sunderarajan2, Kirsten Sutherland2, Florence Tusiime3, Wilson Vieira (ORCID: 0009-0001-9400-6328)2, Zhen Zhang (ORCID: 0000-0001-9300-0920)12, Yufei Zong (ORCID: 0009-0000-5012-0244)12, Daniel B.
+Henderson (ORCID: 0000-0003-4384-4791)3, Josefine Kalbitz2, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)6, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)7, Bahar Köymen (ORCID: 0000-0001-5126-8240)8, Maira V.
+Manrique-Hernandez2, Shirley Magazi (ORCID: 0009-0006-0479-9800)9, Lizbeth Mújica-Manrique2, Julia Ohlendorf2, Damilola Olaoba2, Wesley R.
+Pieters (ORCID:0000-0002-6152-249X)9, Sarah Pope-Caldwell2, Umay Sen (ORCID: 0000-0001-9488-0851)10, Katie Slocombe (ORCID: 0000-0002-7310-1887)11, Robert Z.
+Sparks (ORCID: 0000-0001-7545-0522)5, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,9, Jahnavi Sunderarajan2, Kirsten Sutherland2, Florence Tusiime12, Wilson Vieira (ORCID: 0009-0001-9400-6328)2, Zhen Zhang (ORCID: 0000-0001-9300-0920)13, Yufei Zong (ORCID: 0009-0000-5012-0244)13, Daniel B.
 M.
@@
 \author{Julia Christin Prein (ORCID: 0000-0002-3154-6167)\textsuperscript{1,2}, Florian M.
-Bednarski (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Ardain Dzabatou\textsuperscript{5}, Michael C.
-Frank (ORCID: 0000-0002-7551-4378)\textsuperscript{6}, Annette M.
+Bednarski (ORCID: 0000-0003-4384-4791)\textsuperscript{3}, Ardain Dzabatou\textsuperscript{4}, Michael C.
+Frank (ORCID: 0000-0002-7551-4378)\textsuperscript{5}, Annette M.
 E.
-Henderson (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Josefine Kalbitz\textsuperscript{2}, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)\textsuperscript{7}, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)\textsuperscript{8}, Bahar Köymen (ORCID: 0000-0001-5126-8240)\textsuperscript{9}, Maira V.
-Manrique-Hernandez\textsuperscript{2}, Shirley Magazi (ORCID: 0009-0006-0479-9800)\textsuperscript{10}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R.
-Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{10}, Sarah Pope-Caldwell\textsuperscript{2}, Umay Sen (ORCID: 0000-0001-9488-0851)\textsuperscript{13}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{11}, Robert Z.
-Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{6}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,10}, Jahnavi Sunderarajan\textsuperscript{2}, Kirsten Sutherland\textsuperscript{2}, Florence Tusiime\textsuperscript{3}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{12}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{12}, Daniel B.
+Henderson (ORCID: 0000-0003-4384-4791)\textsuperscript{3}, Josefine Kalbitz\textsuperscript{2}, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)\textsuperscript{6}, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)\textsuperscript{7}, Bahar Köymen (ORCID: 0000-0001-5126-8240)\textsuperscript{8}, Maira V.
+Manrique-Hernandez\textsuperscript{2}, Shirley Magazi (ORCID: 0009-0006-0479-9800)\textsuperscript{9}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R.
+Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{9}, Sarah Pope-Caldwell\textsuperscript{2}, Umay Sen (ORCID: 0000-0001-9488-0851)\textsuperscript{10}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{11}, Robert Z.
+Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{5}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,9}, Jahnavi Sunderarajan\textsuperscript{2}, Kirsten Sutherland\textsuperscript{2}, Florence Tusiime\textsuperscript{12}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{13}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{13}, Daniel B.
 M.
@@
 The authors made the following contributions.
-Julia Christin Prein (ORCID: 0000-0002-3154-6167): Conceptualization, Methodology, Software, Formal Analysis, Resources, Writing - Original Draft Preparation, Writing - Review \& Editing; Florian M.
-Bednarski (ORCID: 0000-0003-4384-4791): Resources, Writing - Review \& Editing; Ardain Dzabatou: Resources, Writing - Review \& Editing; Michael C.
-Frank (ORCID: 0000-0002-7551-4378): Resources, Writing - Review \& Editing; Annette M.
+Julia Christin Prein (ORCID: 0000-0002-3154-6167): Conceptualization, Formal Analysis, Methodology, Project administration, Resources, Software, Visualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Florian M.
+Bednarski (ORCID: 0000-0003-4384-4791): Methodology, Resources, Writing - Review \& Editing; Ardain Dzabatou: Methodology, Resources, Writing - Review \& Editing; Michael C.
+Frank (ORCID: 0000-0002-7551-4378): Methodology, Resources, Writing - Review \& Editing; Annette M.
 E.
-Henderson (ORCID: 0000-0003-4384-4791): Resources, Writing - Review \& Editing; Josefine Kalbitz: Resources, Writing - Review \& Editing; Patricia Kanngiesser (ORCID:0000-0003-1068-3725): Resources, Writing - Review \& Editing; Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733): Resources, Writing - Review \& Editing; Bahar Köymen (ORCID: 0000-0001-5126-8240): Resources, Writing - Review \& Editing; Maira V.
-Manrique-Hernandez: Resources, Writing - Review \& Editing; Shirley Magazi (ORCID: 0009-0006-0479-9800): Resources, Writing - Review \& Editing; Lizbeth Mújica-Manrique: Resources, Writing - Review \& Editing; Julia Ohlendorf: Resources, Writing - Review \& Editing; Damilola Olaoba: Resources, Writing - Review \& Editing; Wesley R.
-Pieters (ORCID:0000-0002-6152-249X): Resources, Writing - Review \& Editing; Sarah Pope-Caldwell: Resources, Writing - Review \& Editing; Umay Sen (ORCID: 0000-0001-9488-0851): Resources, Writing - Review \& Editing; Katie Slocombe (ORCID: 0000-0002-7310-1887): Resources, Writing - Review \& Editing; Robert Z.
-Sparks (ORCID: 0000-0001-7545-0522): Resources, Writing - Review \& Editing; Roman Stengelin (ORCID: 0000-0003-2212-4613): Resources, Writing - Review \& Editing; Jahnavi Sunderarajan: Resources, Writing - Review \& Editing; Kirsten Sutherland: Resources, Writing - Review \& Editing; Florence Tusiime: Resources, Writing - Review \& Editing; Wilson Vieira (ORCID: 0009-0001-9400-6328): Resources, Writing - Review \& Editing; Zhen Zhang (ORCID: 0000-0001-9300-0920): Resources, Writing - Review \& Editing; Yufei Zong (ORCID: 0009-0000-5012-0244): Resources, Writing - Review \& Editing; Daniel B.
+Henderson (ORCID: 0000-0003-4384-4791): Methodology, Resources, Writing - Review \& Editing; Josefine Kalbitz: Methodology, Resources, Writing - Review \& Editing; Patricia Kanngiesser (ORCID:0000-0003-1068-3725): Methodology, Resources, Writing - Review \& Editing; Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733): Methodology, Resources, Writing - Review \& Editing; Bahar Köymen (ORCID: 0000-0001-5126-8240): Methodology, Resources, Writing - Review \& Editing; Maira V.
+Manrique-Hernandez: Methodology, Resources, Writing - Review \& Editing; Shirley Magazi (ORCID: 0009-0006-0479-9800): Methodology, Resources, Writing - Review \& Editing; Lizbeth Mújica-Manrique: Methodology, Resources, Writing - Review \& Editing; Julia Ohlendorf: Methodology, Resources, Writing - Review \& Editing; Damilola Olaoba: Methodology, Resources, Writing - Review \& Editing; Wesley R.
+Pieters (ORCID:0000-0002-6152-249X): Methodology, Resources, Writing - Review \& Editing; Sarah Pope-Caldwell: Methodology, Resources, Writing - Review \& Editing; Umay Sen (ORCID: 0000-0001-9488-0851): Methodology, Resources, Writing - Review \& Editing; Katie Slocombe (ORCID: 0000-0002-7310-1887): Methodology, Resources, Writing - Review \& Editing; Robert Z.
+Sparks (ORCID: 0000-0001-7545-0522): Methodology, Resources, Writing - Review \& Editing; Roman Stengelin (ORCID: 0000-0003-2212-4613): Conceptualization, Methodology, Resources, Writing - Review \& Editing; Jahnavi Sunderarajan: Methodology, Resources, Writing - Review \& Editing; Kirsten Sutherland: Methodology, Resources, Writing - Review \& Editing; Florence Tusiime: Methodology, Resources, Writing - Review \& Editing; Wilson Vieira (ORCID: 0009-0001-9400-6328): Methodology, Resources, Writing - Review \& Editing; Zhen Zhang (ORCID: 0000-0001-9300-0920): Methodology, Resources, Writing - Review \& Editing; Yufei Zong (ORCID: 0009-0000-5012-0244): Methodology, Resources, Writing - Review \& Editing; Daniel B.
 M.
-Haun (ORCID: 0000-0002-3262-645X): Funding acquisition, Writing - Review \& Editing; Manuel Bohn (ORCID: 0000-0001-6006-1348): Conceptualization, Methodology, Writing - Review \& Editing.
+Haun (ORCID: 0000-0002-3262-645X): Conceptualization, Funding acquisition, Methodology, Writing - Review \& Editing; Manuel Bohn (ORCID: 0000-0001-6006-1348): Conceptualization, Funding acquisition, Methodology, Project administration, Supervision, Writing - Review \& Editing.
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg, Germany\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany\\\textsuperscript{3} Budongo Conservation Field Station, Uganda\\\textsuperscript{4} School of Psychology, University of Auckland, New Zealand\\\textsuperscript{5} Université Marien Ngouabi, Republic of the Congo\\\textsuperscript{6} Department of Psychology, Stanford University, USA\\\textsuperscript{7} School of Psychology, University of Plymouth, UK\\\textsuperscript{8} Department of Psychology, Koç University, Türkiye\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia, Namibia\\\textsuperscript{11} Department of Psychology, University of York, UK\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China\\\textsuperscript{13} Department of Psychology, Developmental Psychology, Uppsala University, Sweden\\\textsuperscript{+} joint last author}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg, Germany\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany\\\textsuperscript{3} School of Psychology, University of Auckland, New Zealand\\\textsuperscript{4} Université Marien Ngouabi, Republic of the Congo\\\textsuperscript{5} Department of Psychology, Stanford University, USA\\\textsuperscript{6} School of Psychology, University of Plymouth, UK\\\textsuperscript{7} Department of Psychology, Koç University, Türkiye\\\textsuperscript{8} Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK\\\textsuperscript{9} Department of Psychology and Social Work, University of Namibia, Namibia\\\textsuperscript{10} Department of Psychology, Developmental Psychology, Uppsala University, Sweden\\\textsuperscript{11} Department of Psychology, University of York, UK\\\textsuperscript{12} Budongo Conservation Field Station, Uganda\\\textsuperscript{13} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China\\\textsuperscript{+} joint last author}
 
 \abstract{%
-Cross-cultural studies are crucial for investigating cultural variability and universality of cognitive developmental processes.
+Cross-cultural studies are crucial for investigating the cultural variability and universality of cognitive developmental processes.
 However, cross-cultural assessment tools in cognition across languages and communities are limited.
-This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (Task for Assessing iNdividual Differences in Gaze understanding Open -- Cross-Cultural or TANGO--CC).
-The TANGO--CC was developed and psychometrically assessed in one cultural setting and, with the input of local collaborators, adapted for cross-cultural data collection.
+This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (TANGO--CC).
+The task was developed and psychometrically assessed in one cultural setting and, with input of local collaborators, adapted for cross-cultural data collection.
 Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community.
@@
 Within-community variation outweighed between-community variation.
-We provide an open-source website for researchers to customize and use the task.
+We provide an open-source website for researchers to customize and use the task (\url{https://ccp-odc.eva.mpg.de/tango-cc}).
 The TANGO--CC can be used to assess basic social cognition in diverse communities and provides a roadmap for researching community-level and individual-level differences across cultures.
@@
 Despite numerous calls for change, the samples reported in major psychology journals still lack diversity (Apicella et al., 2020; Gutchess \& Rajaram, 2023; Thalmayer et al., 2021).
-This hinders progress in theory building and testing: we cannot draw inferences about universal and variable aspects of the human cognitive system from data collected exclusively in one single communities (Krys et al., 2024).
-While this sampling bias is often discussed within adult psychology, it is equally relevant for developmental psychology (Nielsen et al., 2017).
+This hinders progress in theory building and testing: we cannot draw inferences about universal and variable aspects of the human cognitive system from data collected exclusively in one single community (Krys et al., 2024).
+While this sampling bias is often discussed within adult psychology, it is equally relevant to developmental psychology (Nielsen et al., 2017).
 Early experiences shape the way children think about and interact with the world and an ontogenetic perspective is needed to explore the foundational aspects of human behavioral diversity (Amir \& McAuliffe, 2020; Broesch et al., 2023; Liebal \& Haun, 2018; Torréns et al., 2023).
@@
 There are numerous challenges with collecting cross-cultural, developmental data (Amir \& McAuliffe, 2020; Broesch et al., 2023).
-Cross-cultural studies need reliable and valid measures to systematically capture variation between communities and/or individuals.
-However, studies on social cognition with US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020), and the picture further deteriorates when we look at cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020; Waschl \& Chen, 2022).
-Thus, it is already challenging to find reliable and valid tasks that have measurement sensitivity to detect individual differences within one community, let alone tasks that do so across different communities.
-In this paper, we describe the construction and psychometric evaluation of a cross-cultural measure of basic social cognition (gaze following) in children as a concrete example for how to address this problem.
-
-Adapting tasks to diverse communities and assessing their validity and reliability might be especially important in the social-cognitive domain.
+Cross-cultural studies need reliable and valid measures to capture variation between communities and/or individuals systematically.
+Even though this applies to all areas of cognitive development, we focus on social cognition in this paper.
+
 Social cognition refers to how an individual processes information in social situations which allows them to understand and predict others' behavior (Adolphs, 1999; Decety, 2020; Frith \& Frith, 2007; Zeigler-Hill et al., 2015).
 If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, then tasks themselves should be tuned to the features of specific communities.
-Indeed, task performance can be diminished when stimuli do not reflect characteristics of the participants' communities (Peña, 2007).
+Indeed, task performance can be diminished when stimuli do not reflect the characteristics of the participants' communities (Peña, 2007).
 For example, Elfenbein and Ambady (2002) found better emotion recognition for members of the same national, ethnic, or regional group.
@@
 
-There exists a continuum of approaches that researchers can take to collect cross-cultural data, and the decision for a specific method partly depends on whether researchers aim to increasing the \emph{depth} (culture specificity) or \emph{breadth} (standardization across multiple communities) of our psychological knowledge (Amir \& McAuliffe, 2020).
-At one extreme, researchers translate the psychological construct into an individually designed study for each community (termed ``assembly''; He and Vijver (2012), Waschl and Chen (2022)).
-While this approach allows greater flexibility and sensitivity to cultural differences, it might not be feasible for studying a multitude of communities as it becomes too demanding and time-consuming.
-Due to its specificity, observations are limited to each community and absolute task scores might not be comparable across communities.
+From a psychometric perspective, the situation looks dire.
+Studies on social cognition with US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020), and the picture further deteriorates when we look at cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020; Waschl \& Chen, 2022).
+Thus, it is already challenging to find reliable and valid tasks that have measurement sensitivity to detect individual differences within one community, let alone tasks that do so across different communities.
+In this paper, we describe the construction and psychometric evaluation of a cross-cultural measure of basic social cognition (gaze following) in children as a concrete example of how to address this problem.
+
+The approaches that researchers can take to collect cross-cultural data lie on a continuum: the decision for a specific method partly depends on whether researchers aim to increase the \emph{depth} (culture specificity) or \emph{breadth} (standardization across multiple communities) of their work (Amir \& McAuliffe, 2020).
+At one extreme, researchers translate the psychological construct into a separate design or task for each community (termed ``assembly''; He and Vijver (2012), Waschl and Chen (2022)).
+While this approach allows greater flexibility and sensitivity to cultural differences, it might not be feasible to study a multitude of communities as it becomes too demanding and time-consuming.
+Furthermore, the results are limited to each community and absolute task scores might not be comparable across communities.
 A study following this approach is Wefers et al. (2023) who investigated how cultural variations in parenting styles modulated infants' responses to disruptions in social interactions.
@@
 
-At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed ``adoption'' and ``adaptation'', respectively Waschl \& Chen (2022)).
+At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed ``adoption'' and ``adaptation'', respectively; Waschl \& Chen (2022)).
 This approach is less sensitive to each community's unique characteristics but renders quantitative comparisons of data more feasible.
-An example following this approach is the Multilingual Assessment Instrument for Narratives {[}MAIN; Gagarina et al. (2012){]}, which assesses narrative abilities in mono- and multilingual children.
-Extensive piloting and adaptation of MAIN materials ensured that the instrument is culturally appropriate, robust and suitable for cross-linguistic comparisons (Gagarina et al., 2012), and new and revised language versions are continuously added to the MAIN database (Gagarina \& Lindgren, 2020).
-
-The present paper aims to describe the development and psychometric properties of a standardized social cognition task that can be adapted to diverse communities.
-Our task focuses on one of the most fundamental social-cognitive abilities: gaze following, that is, the ability to identify the attentional focus of another agent.
+An example following this approach is the Multilingual Assessment Instrument for Narratives (MAIN; (Gagarina et al., 2012)), which assesses narrative abilities in mono- and multilingual children.
+Extensive piloting and adaptation of MAIN materials ensured that the instrument is culturally appropriate, robust, and suitable for cross-linguistic comparisons (Gagarina et al., 2012), and new and revised language versions are continuously added to the MAIN database (Gagarina \& Lindgren, 2020).
+
+The present paper aims to describe the development and psychometric properties of a social cognition task that can be adapted to diverse communities.
+On the continuum described above, our task lies more toward standardized approaches but allows for some customization of the stimuli to each local community.
+The task focuses on one of the most fundamental social-cognitive abilities: gaze following, that is, the ability to identify the attentional focus of another agent.
 Gaze following develops early in infancy (Del Bianco et al., 2019; Tang et al., 2024) and contributes to social learning, communication, and collaboration (Bohn \& Köymen, 2018; Hernik \& Broesch, 2019; Shepherd, 2010; Tomasello et al., 2007).
-While the question how social-environmental and cultural factors impact gaze following was recently posed as one of the big open questions in gaze following research (Astor \& Gredebäck, 2022), studies focusing on cultural variations of gaze following are rare.
-Callaghan et al.
-(2011) investigated gaze following behind barriers in 12- and 17-month-olds from rural Canada (n = 35), Peru (n = 38) and India (n = 65).
-In their setup, an agent sat next to a wall or container and looked at a toy behind this barrier (experimental condition) or a sticker in front of it (control condition).
-The researchers then assessed whether and in which conditions the children crawled towards/around the barriers to follow the agent's gaze.
-While the absolute crawling rates differed across communities, children in all three communities crawled more often to gain visual access when the agent looked at an object behind the barrier compared to in front of it.
+While the question of how social-environmental and cultural factors impact gaze following was recently posed as one of the big open questions in gaze following research (Astor \& Gredebäck, 2022), studies focusing on cultural variations of gaze following are rare.
+Callaghan et al. (2011) investigated gaze following behind barriers in 12- and 17-month-olds from rural Canada (n = 35), Peru (n = 38), and India (n = 65).
+In their setup, an agent looked at a toy behind (experimental condition) or a sticker in front of (control condition) a barrier, and children's crawling toward the barrier to follow the agent's gaze was assessed.
+While the absolute crawling rates differed across communities, children in all three communities crawled more often to gain visual access when the agent looked at an object behind the barrier than in front of it.
 Hernik and Broesch (2019) studied 22 infants between 5 to 7 months of age from Vanuatu and used an eye-tracking procedure displaying a local actor looking at one of two objects.
-Even though face-to-face interactions are less common in interactions between caregivers and children in Vanuatu than in Western communities, the result patterns of gaze following in Ni-Vanuatu infants resembled those of their Western counterparts: infants from Vanuatu followed the agent's gaze to the target object only when preceded by infant-directed, and not adult-directed, speech.
-While these two studies point towards a potential cross-cultural stability of gaze following,
-the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings.
-
-The task presented here aims to tackle these issues and builds upon a previously established gaze-following task called `TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by Prein et al.
+Even though face-to-face interactions are less common in parent-child interactions in Vanuatu than in Western communities, the result patterns of gaze following in Ni-Vanuatu infants resembled those of their Western counterparts: infants from Vanuatu followed the agent's gaze to the target object only when preceded by infant-directed, and not adult-directed, speech.
+While these two studies point towards potential cross-cultural stability of gaze following, the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings and -- more importantly -- does not allow for studying individual-differences.
+A more comprehensive cross-cultural study on gaze following was recently conducted by Bohn et al.
+(2024).
+The researchers tested the universality of gaze following by studying 17 different communities on five continents and found evidence for a similar processing mechanism across communities.
+
+The task presented in this manuscript was developed for the study by Bohn et al.
+(2024) and is based on a previously established gaze-following task called `TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by Prein et al.
 (2023).
@@
 It reliably measured individual differences in a German child sample and an English-speaking remote adult sample (Prein et al., 2023).
-As we cannot claim a task's generalizability and reliability based on mono-cultural samples, we need to assess the TANGO's psychometric properties in a larger cross-cultural sample.
-This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 different communities on five continents (Bohn et al., 2024).
+However, we cannot claim the task's generalizability and reliability based on a mono-cultural sample.
+This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 diverse communities (Bohn et al., 2024).
 We describe the task's development and provide a tutorial for the open-source website (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).
@@
 The TANGO-CC was implemented in Leipzig, Germany, and thoroughly assessed in terms of reliability and validity (Prein et al., 2023).
-During this process, the cross-cultural adaptation of the task was prepared within a team of cross-cultural psychologists and cognitive scientists.
-In this paper, we assess the TANGO--CC's measurement quality (i.e., variability and reliability) across 17 diverse communities by analyzing the data set from Bohn et al. (2024).
+During this process, the cross-cultural adaptation of the task was prepared by a team of cross-cultural psychologists and cognitive scientists.
+In this paper, we assess the TANGO--CC's measurement quality (\emph{i.e.,} variability and reliability) across 17 diverse communities by analyzing the data set from Bohn et al. (2024).
 In the following, we describe the different steps in detail.
@@
 We programmed a function that calculates the x and y coordinates of where the agent's pupil and iris should move to follow the balloon, given the eyes' and balloon's original positions and measures.
-As the measures of the eyes and balloon are read out dynamically from the image on screen, stimuli can be easily adapted and exchanged.
-No coordination values for animation are hard-coded into the task's source code.
-After having programmed this ``backbone'' functionality of the task (\emph{i.e.}, animate the eyes so that they follow the balloon), we added the task's audio instructions and superficial appearance (e.g., background scene, hedge, more agent faces).
+As the measures of the eyes and balloon are read out dynamically from the image on screen, stimuli can be easily adapted and exchanged (\emph{i.e.}, no coordination values for animation are hard-coded into the task's source code).
+After having programmed this ``backbone'' functionality of the task (\emph{i.e.}, animate the eyes so that they follow the balloon), we added the task's audio instructions and superficial appearance (e.g., background scene, hedge, agent faces).
 
 This basic version of the TANGO was psychometrically evaluated in a German child sample and an English-speaking remote adult sample and was found to be highly reliable and valid (Prein et al., 2023).
-While children became more precise in locating the attentional focus of the agent with age, individuals differed across all age groups and showed no floor- or ceiling effects.
+While children became more precise in locating the agent's attentional focus with age, individuals differed across all age groups and showed no floor- or ceiling effects.
 In the Leipzig sample, performance in the TANGO was weakly related to factors of children's daily social environment and could predict children's receptive vocabulary 6 months later.
 In a computational cognitive model, Prein et al.
-(2024) described gaze following as form of social vector following and empirically found that performance in the TANGO was related to children's non-social vector following and visual perspective-taking abilities.
+(2024) described gaze following as a form of social vector following and empirically found that performance in the TANGO was related to children's non-social vector following and visual perspective-taking abilities.
 These connections to related constructs indicate the task's convergent validity in the German child sample.
 
-To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces and background scenes with the feedback from local researchers and research assistants.
+To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces and background scenes with input from local researchers and research assistants.
 The stimulus pool was adjusted and expanded until the researchers and research assistants from each target community judged the selected stimuli to be representative of the local population and typical accommodation (see Figure \ref{fig:fig2}).
-Audio instructions were translated from English into the corresponding local language(s).
+Audio instructions were translated from English or German into the corresponding local language(s).
 By back-translating these instructions, we ensured the original meaning did not change.
@@
 In test trials, a hedge grows at the beginning of the trial and participants see neither the movement nor the final position of the balloon.
-The first trial of each type contains an audio description of the presented events (see supplements of Bohn et al. (2024)).
+The first trial of each type contains an audio description of the presented events (see Supplements).
 Notably, the instructions explicitly state that the agent is looking at the balloon.
@@
 By using self-explanatory animations, language demands are kept to a minimum.
-The task uses simple audio instructions, which makes the task accessible to children from different age groups, and no reading skills are needed.
+The task uses simple audio instructions, which makes the task accessible to children from different age groups, and no reading skills are required.
 There is no feedback during the task to prevent learning effects across trials.
@@
 For the balloon positions, the entire width of the screen (1920 in ``SVG units'') is divided into ten bins.
-Exact coordinates (value between 0 far left and 1920 far right) within each bin are then randomly generated.
+Exact coordinates (value between 0 for the far left and 1920 for the far right) within each bin are then randomly generated.
 The number of repetitions for each agent, balloon color, and balloon bin is calculated based on the total number of trials and the number of unique agents, balloon colors, and bins, respectively.
@@
 
-When reseachers visit the TANGO--CC's website
+When researchers visit the TANGO--CC's website
 (\url{https://ccp-odc.eva.mpg.de/tango-cc/}), they can select the language for audio instructions which are currently available for 13 different languages and five more dialects (see Table 1).
 To add a new language, researchers have two options:
-(1) for using their own audio instructions in the offline version of the task, researchers can download the task, exchange the audio instructions in the dist folder (in the folder sounds \textgreater{} custom) and select ``Custom'' in the language drop down menu.
+(1) for using their own audio instructions in the offline version of the task, researchers can download the task, exchange the audio instructions in the dist folder (in the folder sounds \textgreater{} custom) and select ``Custom'' in the language drop-down menu.
 For detailed instructions, see the TANGO--CC's manual (\url{https://ccp-odc.eva.mpg.de/tango-cc/manual.html}).
 (2) For adding a new language in the online version of the task, researchers can contact the first author of this paper.
-Please note that this option requires new audio recordings by the interested reseachers, which will then be openly available for all users of the task.
+Please note that this option requires new audio recordings by the interested researchers, which will then be openly available for all users of the task.
 All written instructions in the task are solely for the research assistant to help them guide participants through the task; these instructions are solely available in English.
-The task can either be started with the default settings or further customized by adapting the numbers of trials, agents, and background scenes.
-The default settings use the version applied in Bohn et al. (2024) based on the selected language.
+The task can either be started with the default settings or further customized by adapting the number of trials, agents, and background scenes.
+The default settings use the version applied in Bohn et al. (2024) based on the selected language (see Supplements).
 
@@
 
-We created a public OSF page (\url{https://doi.org/10.17605/OSF.IO/P2EGU}) where we plan to collect data sets that used the TANGO-CC.
-Researchers who have collected data using the TANGO--CC can share their data with the community by contacting the first author of this paper or visiting this OSF repository.
+We created a public OSF page (\url{https://doi.org/10.17605/OSF.IO/P2EGU}) on which we plan to collect data sets that used the TANGO-CC.
+Researchers who have collected data using the TANGO--CC can share their data with the community by contacting the first author of this paper or visiting the OSF repository.
 
@@
 Marathi & Indo-European & India\\
-Shona & Bantu & Zimbabwe\\
+Shona * & Bantu & Zimbabwe\\
 Spanish & Indo-European & Argentina (Rioplatense Spanish) / Mexico (Mexiquense Spanish)\\
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} In those cases where more than one speaker's country of origin is listed, the audio instructions were recorded multiple times by different speakers.
-For example, the English instructions are available in five different versions.}
+\normalsize{\textit{Note.} In cases where more than one speaker's country of origin is listed, the audio instructions were recorded multiple times by different speakers.
+For example, the English instructions are available in five different versions.
+* Please note that audio instructions are available in Shona but no data of this version is included in the present data set.}
 \end{tablenotes}
@@
 
-\caption{\textbf{Customizable components of the TANGO--CC.} Researchers can select the language of the audio instructions (see Table 1), the number of trials per trial type, the background, and the agent's face.}\label{fig:fig2}
+\caption{\textbf{Screenshot of the customizable components of the TANGO--CC.} Researchers can select the language of the audio instructions (see Table 1), the number of trials per trial type, the background, and the agent's face.}\label{fig:fig2}
 \end{figure}
@@
 The task was implemented in \texttt{JavaScript}, \texttt{HTML}, and \texttt{CSS} and is presented as a web app.
-It can be accessed on any modern web browser on any device (e.g., computer or tablet) and does not require prior installation (please note that configurations of browsers and JavaScript may change in the future).
-Participant's responses can be recorded on a touchscreen or with a mouse or track pad.
+It can be accessed on any modern web browser on any device (e.g., computer or tablet) and does not require prior installation (though please note that configurations of browsers and JavaScript may change in the future).
+Participant's responses can be recorded on a touchscreen or with a mouse or trackpad.
 The online version of the task can be used for unsupervised data collection (for example, using online platforms like \emph{Prolific}; see Prein et al.
@@
 SVGs ensure that the picture quality, aspect ratio, and relative object positioning are constant.
-Furthermore, stimuli are added as individual components to the image scene which allows for an easy adaptation of task's elements (in contrast to other image formats that consist of only one combined layer that would need entire replacement).
-The task is programmed so that responses are only registered when the participant clicks the relevant part of the screen (i.e., in test trials, when they click the hedge).
+Furthermore, stimuli are added as individual components to the image scene which allows for an easy adaptation of the task's elements (in contrast to other image formats that consist of only one combined layer that would need entire replacement).
+The task is programmed so that responses are only registered when the participant clicks the relevant part of the screen (\emph{i.e.,} in test trials, when they click the hedge).
 Furthermore, clicks are only registered after the voice recordings stop playing.
@@
 The file will be stored in the device's downloads folder and is named after the following pattern: ``tangoCC-participantID-YYYY-MM-DD\_hh\_mm\_ss''.
-To modify the storage location on the device, researchers can change the designated downloads folder in the browser settings.
+To modify the storage location on the device, researchers can change the designated downloads folder in their browser settings.
 
@@
 
-We used the data set from Bohn et al. (2024) for psychometric evaluation of the TANGO--CC.
+We used the data set from Bohn et al. (2024) for the psychometric evaluation of the TANGO--CC.
 The data set contains a sample of \emph{N} = 1377 children, aged 2.5 to 11 years.
@@
 
+All analyses and the data set can be accessed on GitHub (\url{https://github.com/ccp-eva/tango-cc-methods/}).
 First, we inspected the mean and standard deviations by community and compared performance in each trial type (training 1, training 2, test trials).
@@
 
-Our GLMM analysis supported the visual inspection of the data: the fixed-effect estimates for training 1 (\(\beta\) = -3.26; 95\% CrI {[}-3.41; -3.10{]}) and training 2 (\(\beta\) = -1.47; 95\% CrI {[}-1.58; -1.35{]}) were negative and reliably different from zero.
-\footnote{Please note that the TANGO--CC measures imprecision in gaze following.
-  Therefore, a negative sign indicates that children showed less imprecision (i.e., were more precise) in the training trials than in the test trials.}
+Our GLMM analysis supported the visual inspection of the data: the fixed-effect estimates for training 1 (\(\beta\) = -3.26; 95\% CrI {[}-3.41; -3.10{]}) and training 2 (\(\beta\) = -1.47; 95\% CrI {[}-1.58; -1.35{]}) were negative and reliably different from zero.\footnote{Please note that the TANGO--CC measures imprecision in gaze following.
+  Therefore, a negative sign indicates that children showed less imprecision (\emph{i.e.,} were more precise) in the training trials than in the test trials.}
 This effect was found across all communities (random effects of trial type within community: minimum estimate for training 1 = -2.87; 95\%CrI {[}-3.11; -2.60{]}; minimum estimate for training 2 = -1.27; 95\%CrI {[}-1.51; -0.98{]}).
@@
 To identify the sources of variation, we computed intraclass correlations (ICC).
-The variation of children's imprecision within communities was substantially larger than the variation between the communities.
+The variation in children's imprecision within communities was substantially larger than the variation between the communities.
 The mean within-community variance was 1.28, ranging from 0.24 (in Pune, India) to 3.46 (in Chimfunshi, Zambia).
@@
 Second, using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2022), data was stratified by target centrality (capturing trial difficulty), and a Pearson correlation was calculated between the matched halves.
-Third, a data set was generated with stratified test halves by target centrality and we applied the Generalized Linear Mixed Model (GLMM) approach introduced by Rouder and Haaf (2019).
+Third, a data set was generated with stratified test halves by target centrality and we applied the GLMM approach introduced by Rouder and Haaf (2019).
 A GLMM was fitted with the mean imprecision as the outcome, age as the predictor, and test half and participant id as random effects (model notation: \texttt{imprecision\ \textasciitilde{}\ age\ +\ (0\ +\ half\ \textbar{}\ subjid)}).
@@
 While we performed a detailed psychometric evaluation of the task in a German setting, we collaborated with local researchers for the cross-cultural stimulus development and selection.
-Importantly, we re-assessed the TANGO--CC's psychometric properties in a large and diverse sample of children.
-The data set by Bohn et al.
-(2024) showed that data collection with the TANGO--CC was feasible in 17 diverse communities in rural and urban settings with varying degrees of market integration and technology exposure.
-While we cannot generalize our findings to all communities worldwide, we found that the TANGO-CC captured reliable individual variation in all communities studied by Bohn et al. (2024).
-We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful for other researchers.
+Importantly, we re-assessed the TANGO--CC's psychometric properties in a large and diverse data set.
+While we cannot generalize our findings to all communities worldwide, we found that the TANGO-CC captured reliable individual variation in all 17 communities studied by Bohn et al. (2024).
+We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful to other researchers.
+We recommend that researchers consider generalizability concerns and cross-cultural applications of their tasks and collaborate with local researchers at the early stages of task development (Torréns et al., 2023).
 Using the TANGO--CC (or any other task) in a new community requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
-We recommend that researchers consider generalizability concerns and cross-cultural applications of their tasks and collaborate with local researchers at early stages of task development (Torréns et al., 2023).
 
@@
 
-Compared to one of the most commonly used social cognition measure -- the change-of-location false belief task (Baron-Cohen et al., 1985; Wimmer \& Perner, 1983) -- the TANGO--CC has several advantages: a continuous outcome measure which can capture individual differences, a short task duration that allows for more trials per child, stimuli that can be easily adapted, and known psychometric properties across 17 communities.
-The task is presented as a web app that enables efficient data collection with large sample sizes, while it can also be used to collect data offline in locations without reliable internet connection.
+Compared to one of the most commonly used social cognition measures -- the change-of-location false belief task (Baron-Cohen et al., 1985; Wimmer \& Perner, 1983) -- the TANGO--CC has several advantages: a continuous outcome measure that can capture individual differences from three years to adulthood, a short task duration that allows for more trials per child, stimuli that can be easily adapted, and known psychometric properties across 17 communities.
+The task is presented as a web app that enables efficient data collection with large sample sizes, while it can also be used to collect data offline in locations without a reliable internet connection.
 The TANGO--CC follows a standardized procedure, which leaves no room for rater errors and greatly simplifies online training of research assistants.
@@
 First evidence suggests that the TANGO--CC indeed taps into social cognition as utilized in real life: Prein et al.
-(2024) found that children's perspective-taking abilities in a personal social interaction was linked to performance in the TANGO, but less so to a matched, non-social vector following task.
+(2024) found that children's perspective-taking abilities in a personal social interaction were linked to performance in the TANGO, but less so to a matched, non-social vector following task.
 However, this study exclusively relied on a German sample and future research should investigate whether the relationship between the TANGO--CC and perspective-taking abilities holds across communities.
@@
 (2023) have called for standardized, psychometrically evaluated measures that can be re-used by other researchers in order to ``build a cumulative evidence base in psychology'' (p.~2).
-This underlines how efforts to improve the replicability can be combined with the goal of increasing the generalisability of psychological research (Li et al., 2024; Syed, 2021).
+This underlines how efforts to improve replicability can be combined with the goal of increasing the generalisability of psychological research findings (Li et al., 2024; Syed, 2021).
 Li et al.
-(2024) have argued that replicable and generalisable results rely on stimulus sets with slight variations, more diverse samples, and data collection at a greater scale, which are all steps the TANGO--CC has taken.
+(2024) have argued that replicable and generalizable results rely on stimulus sets with slight variations, more diverse samples, and data collection at a greater scale, which are indeed all steps the TANGO--CC has taken.
 Openly sharing the TANGO--CC's materials will allow other researchers to (hopefully) replicate the results and deepen our cumulative understanding of social-cognitive development across diverse communities.
@@
 The TANGO--CC captures individual differences in social-cognitive development across diverse communities.
-The task's customizability, minimal language demands, and its efficient data collection method make it a valuable task for cross-cultural research.
+The task's customizability, minimal language demands, and its efficient data collection method make it a valuable tool for cross-cultural research.
 The task showed satisfactory to high reliability (internal consistency) in a large data set including 17 diverse communities on five continents.

### 2024-09-23 paper/manuscript.Rmd
revisions 1

@@
 ---
-title: "Measuring variation in gaze following across communities, ages, and individuals — a showcase of the TANGO--CC"
+title: "Measuring variation in gaze following across communities, ages, and individuals — a showcase of the TANGO-CC"
 shorttitle: "measuring gaze following across communities"
@@
   - name          : "Sarah Pope-Caldwell"
-    affiliation   : "2"
+    affiliation   : "2,10"
     role:
@@
   - name          : "Umay Sen (ORCID: 0000-0001-9488-0851)"
-    affiliation   : "10"
+    affiliation   : "11"
     role:
@@
   - name          : "Katie Slocombe (ORCID: 0000-0002-7310-1887)"
-    affiliation   : "11"
+    affiliation   : "12"
     role:
@@
   - name          : "Florence Tusiime"
-    affiliation   : "12"
+    affiliation   : "13"
     role:
@@
   - name          : "Zhen Zhang (ORCID: 0000-0001-9300-0920)"
-    affiliation   : "13"
+    affiliation   : "14"
     role:
@@
   - name          : "Yufei Zong (ORCID: 0009-0000-5012-0244)"
-    affiliation   : "13"
+    affiliation   : "14"
     role:
@@
   - id            : "10"
+    institution   : "Department of Psychology, Georgia State University, USA"
+  - id            : "11"
     institution   : "Department of Psychology, Developmental Psychology, Uppsala University, Sweden"
-  - id            : "11"
+  - id            : "12"
     institution   : "Department of Psychology, University of York, UK"
-  - id            : "12"
+  - id            : "13"
     institution   : "Budongo Conservation Field Station, Uganda"
-  - id            : "13"
+  - id            : "14"
     institution   : "CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China"
@@
 However, cross-cultural assessment tools in cognition across languages and communities are limited.
-This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (TANGO--CC).
+This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (TANGO-CC).
 The task was developed and psychometrically assessed in one cultural setting and, with input of local collaborators, adapted for cross-cultural data collection.
 Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community.
-The TANGO--CC captures individual- and community-level variation and shows good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities.
+The TANGO-CC captures individual- and community-level variation and shows good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities.
 Within-community variation outweighed between-community variation.
 We provide an open-source website for researchers to customize and use the task (https://ccp-odc.eva.mpg.de/tango-cc).
-The TANGO--CC can be used to assess basic social cognition in diverse communities and provides a roadmap for researching community-level and individual-level differences across cultures.
+The TANGO-CC can be used to assess basic social cognition in diverse communities and provides a roadmap for researching community-level and individual-level differences across cultures.
 
@@
 A study following this approach is @wefers2023universality who investigated how cultural variations in parenting styles modulated infants' responses to disruptions in social interactions. 
-While studies in the Global North often apply the Still-Face Paradigm to assess infants' reactions to unresponsive partners, @wefers2023universality reasoned that this paradigm might not capture infants' everyday interaction routines in communities with proximal (*i.e.,* emphasis on body stimulation) parenting styles.
+While studies in the Global North often apply the Still-Face Paradigm to assess infants' reactions to unresponsive partners, @wefers2023universality reasoned that this paradigm might not capture infants' everyday interaction routines in communities with proximal (i.e., emphasis on body stimulation) parenting styles.
 By developing the novel No-Touch Paradigm, they found that indeed infants' responses to unresponsive partners were modulated by the cultural context in which they grew up: Kichwa infants from rural Ecuador showed stronger reactions to unresponsive partners in the No-Touch Paradigm compared to the Still-Face Paradigm, while reactions of urban German infants differed less in both paradigms.
 
-At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed "adoption" and "adaptation", respectively; [@he2012bias, @waschl2022crosscultural]).
+At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed "adoption" and "adaptation", respectively; @he2012bias, @waschl2022crosscultural).
 This approach is less sensitive to each community's unique characteristics but renders quantitative comparisons of data more feasible.
-An example following this approach is the Multilingual Assessment Instrument for Narratives (MAIN; [@gagarina2012main]), which assesses narrative abilities in mono- and multilingual children. 
+An example following this approach is the Multilingual Assessment Instrument for Narratives (MAIN; @gagarina2012main), which assesses narrative abilities in mono- and multilingual children. 
 Extensive piloting and adaptation of MAIN materials ensured that the instrument is culturally appropriate, robust, and suitable for cross-linguistic comparisons [@gagarina2012main], and new and revised language versions are continuously added to the MAIN database [@gagarina2020new].
@@
 Gaze following develops early in infancy [@delbianco2019developmental; @tang2024slow] and contributes to social learning, communication, and collaboration [@shepherd2010following; @tomasello2007reliance; @bohn2018common; @hernik2019infant].
-While the question of how social-environmental and cultural factors impact gaze following was recently posed as one of the big open questions in gaze following research [@astor2022gaze], studies focusing on cultural variations of gaze following are rare.
+Identifying the attentional focus of a conversational partner facilitates language development [@brooks2015connecting; @carpenter1998social; @mundy2007individual], as children might use gaze to identify the referent of a new word [@brooks2005development].
+
+One of the main open questions is the impact of social-environmental and cultural factors on gaze following [@astor2022gaze], but studies on variation in gaze following across communities are rare. 
+Recently, @brooks2020enhanced found that Deaf infants show increased gaze following compared to hearing infants, underlining the importance of visual-communicative signals for Deaf children. 
 @callaghan2011early investigated gaze following behind barriers in 12- and 17-month-olds from rural Canada (n = 35), Peru (n = 38), and India (n = 65). 
@@
 Even though face-to-face interactions are less common in parent-child interactions in Vanuatu than in Western communities, the result patterns of gaze following in Ni-Vanuatu infants resembled those of their Western counterparts: infants from Vanuatu followed the agent's gaze to the target object only when preceded by infant-directed, and not adult-directed, speech.
-While these two studies point towards potential cross-cultural stability of gaze following, the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings and – more importantly – does not allow for studying individual-differences.
+@astor2022maternal analyzed the effects of maternal postpartum depression on gaze following in 9-month-olds from Bhutan and Sweden.
+While infants showed similar gaze following rates in both countries, maternal postpartum depression was associated with reduced gaze following only in the Swedish sample.
+Beyond gaze following, some studies conducted in the Global South have investigated opportunities for mutual eye gaze and factors influencing joint attention [see @akhtar2008privileging]. 
+For example, Kaluli infants in Papua New Guinea are often carried facing away from their mothers so infants and caregivers share mutual gaze less frequently [@ochs1984language].
+@childers2007jointa studied Ngas-speaking infants in Nigeria and found no effect of the caregivers’ carrying style (usually on the back) on children’s joint attention tendencies.
+
+While these studies point towards potential cross-cultural stability of gaze following, the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings and – more importantly – does not allow for studying individual-differences.
 A more comprehensive cross-cultural study on gaze following was recently conducted by @bohn2024universal.
@@
 
-The task presented in this manuscript was developed for the study by @bohn2024universal and is based on a previously established gaze-following task called 'TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by @prein2023tango.
+The task presented in this manuscript was developed for the study by @bohn2024universal and is based on a previously established gaze-following task called 'TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by @prein2024tango.
 The TANGO measures how precisely participants locate an agent's attentional focus.
-It reliably measured individual differences in a German child sample and an English-speaking remote adult sample [@prein2023tango].
+It reliably measured individual differences in a German child sample and an English-speaking remote adult sample [@prein2024tango].
 However, we cannot claim the task's generalizability and reliability based on a mono-cultural sample. 
-This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 diverse communities [@bohn2024universal].
+This paper showcases the TANGO-CC (TANGO - Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 diverse communities [@bohn2024universal].
 We describe the task's development and provide a tutorial for the open-source website (<https://ccp-odc.eva.mpg.de/tango-cc/>).
@@
 
-The TANGO-CC was implemented in Leipzig, Germany, and thoroughly assessed in terms of reliability and validity [@prein2023tango].
+The TANGO-CC was implemented in Leipzig, Germany, and thoroughly assessed in terms of reliability and validity [@prein2024tango].
 During this process, the cross-cultural adaptation of the task was prepared by a team of cross-cultural psychologists and cognitive scientists. 
-In this paper, we assess the TANGO--CC's measurement quality (*i.e.,* variability and reliability) across 17 diverse communities by analyzing the data set from @bohn2024universal.
+In this paper, we assess the TANGO-CC's measurement quality (i.e., variability and reliability) across 17 diverse communities by analyzing the data set from @bohn2024universal.
 In the following, we describe the different steps in detail.
 
-The TANGO--CC is a screen-based task that measures the imprecision with which participants locate a balloon by following an agent’s gaze (see Figure \@ref(fig:fig1)). 
+The TANGO-CC is a screen-based, interactive picture book with cartoon-like line drawings (see Figure \@ref(fig:fig1)).
+Previous gaze studies have successfully implemented tasks with (schematic) line drawings for both children and adults [e.g., @anderson1997preschoolers; @doherty2009rapid; @doherty1999new; @kingstone2000reflexive; @lee1998children].
+The TANGO-CC measures the imprecision with which participants locate a balloon by following an agent’s gaze. 
 Participants click or touch the location on the screen where they believe the balloon to be.
@@
 We programmed a function that calculates the x and y coordinates of where the agent's pupil and iris should move to follow the balloon, given the eyes' and balloon's original positions and measures. 
-As the measures of the eyes and balloon are read out dynamically from the image on screen, stimuli can be easily adapted and exchanged (*i.e.*, no coordination values for animation are hard-coded into the task's source code).
-After having programmed this "backbone" functionality of the task (*i.e.*, animate the eyes so that they follow the balloon), we added the task's audio instructions and superficial appearance (e.g., background scene, hedge, agent faces).
+As the measures of the eyes and balloon are read out dynamically from the image on screen, stimuli can be easily adapted and exchanged (i.e., no coordination values for animation are hard-coded into the task's source code).
+After having programmed this "backbone" functionality of the task (i.e., animate the eyes so that they follow the balloon), we added the task's audio instructions and superficial appearance (e.g., background scene, hedge, agent faces).
 
-This basic version of the TANGO was psychometrically evaluated in a German child sample and an English-speaking remote adult sample and was found to be highly reliable and valid [@prein2023tango].
+This basic version of the TANGO was psychometrically evaluated in a German child sample and an English-speaking remote adult sample and was found to be highly reliable and valid [@prein2024tango].
 While children became more precise in locating the agent's attentional focus with age, individuals differed across all age groups and showed no floor- or ceiling effects.
@@
 Sometimes, specific words were slightly modified in the target language (e.g., "bush" instead of "hedge") to ensure that all participants understood the instructions well. 
-Based on these adaptations, the TANGO--CC could be applied in 17 communities and 13 different languages [@bohn2024universal].
-In the following, we describe how researchers can use and customize the TANGO--CC in more detail.
+Based on these adaptations, the TANGO-CC could be applied in 17 communities and 13 different languages [@bohn2024universal].
+In the following, we describe how researchers can use and customize the TANGO-CC in more detail.
 
-## Features of the TANGO--CC
+## Features of the TANGO-CC
 
@@
 The balloon falls down to the ground. The eyes of the agent follow the movement of the balloon in a way that the balloon center and the pupil center always align.
-Depending on the trial type, participants have different visual access to the balloon's position.
+Depending on the trial type, participants' visual access to the balloon's position varies.
+This experimental design builds on existing gaze following paradigms that have used barriers or obstacles [e.g., @butler2000infant; @dunphy-lelii2004infants; @franco2001toddlers; @moll200412].
 In training 1, participants see the full trajectory of the balloon and directly have to click the balloon itself.
@@
 In test trials, a hedge grows at the beginning of the trial and participants see neither the movement nor the final position of the balloon.
+
 The first trial of each type contains an audio description of the presented events (see Supplements).
 Notably, the instructions explicitly state that the agent is looking at the balloon.
+This ensures all participants understand the purpose of the task, and minimizes learning effects (increasing comparability between earlier and later trials; avoiding that participants notice the gaze cue only after e.g.
+half of the trials).
+The TANGO-CC measures *how precisely* participants use the gaze cue, rather than *if* they notice it in the first place.
 
@@
 All agents, balloon colors, and bins appear equally often and are not repeated in more than two consecutive trials.
-If the total number of trials is not divisible by the number of unique elements, some elements (*i.e.,* some agents, balloon colors, bins) are randomly repeated to make up for the remainder.
+If the total number of trials is not divisible by the number of unique elements, some elements (i.e., some agents, balloon colors, bins) are randomly repeated to make up for the remainder.
 
@@
 
-When researchers visit the TANGO--CC's website 
+When researchers visit the TANGO-CC's website 
 (<https://ccp-odc.eva.mpg.de/tango-cc/>), they can select the language for audio instructions which are currently available for 13 different languages and five more dialects (see Table 1). 
@@
 (1) for using their own audio instructions in the offline version of the task, researchers can download the task, exchange the audio instructions in the dist folder (in the folder sounds > custom) and select "Custom" in the language drop-down menu.
-For detailed instructions, see the TANGO--CC's manual (<https://ccp-odc.eva.mpg.de/tango-cc/manual.html>). 
+For detailed instructions, see the TANGO-CC's manual (<https://ccp-odc.eva.mpg.de/tango-cc/manual.html>). 
 (2) For adding a new language in the online version of the task, researchers can contact the first author of this paper.
@@
 By directly editing the `HTML` and `JavaScript` code, researchers can further modify the task as needed. 
+To ensure the accessibility of the TANGO–CC long-term, we have additionally stored the source code on Zenodo (https://zenodo.org/doi/10.5281/zenodo.13643836).
 
 We created a public OSF page (https://doi.org/10.17605/OSF.IO/P2EGU) on which we plan to collect data sets that used the TANGO-CC.
-Researchers who have collected data using the TANGO--CC can share their data with the community by contacting the first author of this paper or visiting the OSF repository.
+Researchers who have collected data using the TANGO-CC can share their data with the community by contacting the first author of this paper or visiting the OSF repository.
 
@@
   lang,
-  caption = "Current language options available for the audio instructions in the TANGO--CC", 
+  caption = "Current language options available for the audio instructions in the TANGO-CC", 
   note = "In cases where more than one speaker's country of origin is listed, the audio instructions were recorded multiple times by different speakers.
@@
 
-(ref:figlab2) **Screenshot of the customizable components of the TANGO--CC.** Researchers can select the language of the audio instructions (see Table 1), the number of trials per trial type, the background, and the agent's face.
+(ref:figlab2) **Screenshot of the customizable components of the TANGO-CC.** Researchers can select the language of the audio instructions (see Table 1), the number of trials per trial type, the background, and the agent's face.
 
@@
 Participant's responses can be recorded on a touchscreen or with a mouse or trackpad.
-The online version of the task can be used for unsupervised data collection (for example, using online platforms like *Prolific*; see @prein2023tango).
+The online version of the task can be used for unsupervised data collection (for example, using online platforms like *Prolific*; see @prein2024tango).
 The task can be shared easily internationally by providing the URL.
@@
 
-The stimuli are embedded as Scalable Vector Graphics (SVG; an image format that stores image elements via mathematical formulas based on points and lines on a grid).
+The stimuli are embedded as Scalable Vector Graphics (SVG; an XML format that describes elements in mathematical formulas based on points and lines on a grid).
 SVGs ensure that the picture quality, aspect ratio, and relative object positioning are constant. 
 Furthermore, stimuli are added as individual components to the image scene which allows for an easy adaptation of the task's elements (in contrast to other image formats that consist of only one combined layer that would need entire replacement).
-The task is programmed so that responses are only registered when the participant clicks the relevant part of the screen (*i.e.,* in test trials, when they click the hedge).
+The task is programmed so that responses are only registered when the participant clicks the relevant part of the screen (i.e., in test trials, when they click the hedge).
 Furthermore, clicks are only registered after the voice recordings stop playing.
@@
 
-We used the data set from @bohn2024universal for the psychometric evaluation of the TANGO--CC.
-The data set contains a sample of *N* = `r sample_table[sample_table$Community == "Total",]$Total` children, aged 2.5 to 11 years.
+We used the data set from @bohn2024universal for the psychometric evaluation of the TANGO-CC.
+The data set contains a sample of *N* = `r sample_table[sample_table$Community == "Total",]$Total` children, aged 2.5 to 11 years (see supplements).
 Participants came from 17 communities on five continents, in rural and urban settings, with varying degrees of market integration and technology exposure.
@@
 
-(ref:figlab3) **Variability measured by the TANGO--CC.** Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type.
+(ref:figlab3) **Variability measured by the TANGO-CC.** Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type.
 Imprecision is defined as the distance between the participant's click and the balloon's center in units of balloon width.
@@
 
-To formally estimate the effect of trial type on performance in the TANGO--CC, we fitted a generalized linear mixed model (GLMM) predicting the task performance by trial type (reference category: test trials).
+To formally estimate the effect of trial type on performance in the TANGO-CC, we fitted a generalized linear mixed model (GLMM) predicting the task performance by trial type (reference category: test trials).
 All analyses were run in `r R.version$version.string` [@rcoreteam2024language].
@@
 
-[^1]: Please note that the TANGO--CC measures imprecision in gaze following.
-Therefore, a negative sign indicates that children showed less imprecision (*i.e.,* were more precise) in the training trials than in the test trials.
+[^1]: Please note that the TANGO-CC measures imprecision in gaze following.
+Therefore, a negative sign indicates that children showed less imprecision (i.e., were more precise) in the training trials than in the test trials.
 
@@
 
-(ref:figlab4) **Reliability of the TANGO--CC by community.** Internal consistency estimates by community, following three different approaches.
+(ref:figlab4) **Reliability of the TANGO-CC by community.** Internal consistency estimates by community, following three different approaches.
 In the odd-even split, the size of points reflects the sample size in each community.
@@
 First, data of each participant was split into odd and even trials and a Pearson correlation was calculated between the aggregated scores of the two halves.
-Second, using the function `by_split` from the `splithalfr` package [@pronk2022methods], data was stratified by target centrality (capturing trial difficulty), and a Pearson correlation was calculated between the matched halves.
+Second, using the function `by_split` from the `splithalfr` package [@pronk2022methods], data was stratified by target centrality, and a Pearson correlation was calculated between the matched halves.
+Target centrality measured how closely the target landed to the center of the screen (i.e., distance from the balloon center to the screen center), which served as a proxy for trial difficulty and was previously found to be a relevant component in predicting participants’ performance in a cognitive model [@prein2024variation].
 Third, a data set was generated with stratified test halves by target centrality and we applied the GLMM approach introduced by @rouder2019psychometrics.
@@
 Following Cohen's suggestions [@cohen1988statistical; @cohen1992power], these correlations constitute large effects (*r* > .50), and indicate good internal consistency.[^2] 
-The results are comparable to the internal consistency estimates found in the original TANGO study [@prein2023tango], and also resemble reliability estimates of classical false belief tasks [@hughes2000good].
+The results are comparable to the internal consistency estimates found in the original TANGO study [@prein2024tango], and also resemble reliability estimates of classical false belief tasks [@hughes2000good].
 
@@
 
-The TANGO--CC measures imprecision in gaze following across individuals, ages, and communities.
+The TANGO-CC measures imprecision in gaze following across individuals, ages, and communities.
 Children’s imprecision in gaze following showed highly similar result patterns across communities: children performed better in the training than the test trials, and within-community variation greatly exceeded between-community variation.
 Furthermore, the task showed satisfactory to high reliability across all communities.
-Therefore, the TANGO--CC is a suitable task to capture individual differences in social-cognitive development in diverse communities.
+Therefore, the TANGO-CC is a suitable task to capture individual differences in social-cognitive development in diverse communities.
 
-The TANGO--CC's design process lays out a much-needed pragmatic approach to studying community-level and individual-level differences across cultures: 
+The TANGO-CC's design process lays out a much-needed pragmatic approach to studying community-level and individual-level differences across cultures: 
 While we performed a detailed psychometric evaluation of the task in a German setting, we collaborated with local researchers for the cross-cultural stimulus development and selection.
-Importantly, we re-assessed the TANGO--CC's psychometric properties in a large and diverse data set.
+Importantly, we re-assessed the TANGO-CC's psychometric properties in a large and diverse data set.
 While we cannot generalize our findings to all communities worldwide, we found that the TANGO-CC captured reliable individual variation in all 17 communities studied by @bohn2024universal.
-We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful to other researchers. 
+We hope that not just the TANGO-CC but also our pragmatic approach to constructing it will be helpful to other researchers. 
 We recommend that researchers consider generalizability concerns and cross-cultural applications of their tasks and collaborate with local researchers at the early stages of task development [@torrens2023einfluss].
-Using the TANGO--CC (or any other task) in a new community requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
+Using the TANGO-CC (or any other task) in a new community requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
 
 @bourdage2023evaluation pointed out a major challenge with adapting social cognition tasks to diverse communities: the number of world cultures is vast, and communities are constantly changing.
-Therefore, a promising approach might be to provide tasks with a modular system where components can be modified (*i.e.*, building block structure).
-In the case of the TANGO--CC, the task cannot only be adapted to different languages, cartoon faces, and backgrounds (see Figure \@ref(fig:fig2)) but also updated with new stimuli.
-Unlike studies that present sequential, hand-painted pictures that are difficult to adapt [@mehta2011validation], the TANGO--CC uses SVGs (Scalable Vector Graphics) that can be easily exchanged.
+Therefore, a promising approach might be to provide tasks with a modular system where components can be modified (i.e., building block structure).
+In the case of the TANGO-CC, the task cannot only be adapted to different languages, cartoon faces, and backgrounds (see Figure \@ref(fig:fig2)) but also updated with new stimuli.
+Unlike studies that present sequential, hand-painted pictures that are difficult to adapt [@mehta2011validation], the TANGO-CC uses SVGs (Scalable Vector Graphics) that can be easily exchanged.
 
-Compared to one of the most commonly used social cognition measures -- the change-of-location false belief task [@wimmer1983beliefs; @baron-cohen1985does] -- the TANGO--CC has several advantages: a continuous outcome measure that can capture individual differences from three years to adulthood, a short task duration that allows for more trials per child, stimuli that can be easily adapted, and known psychometric properties across 17 communities.
+Compared to one of the most commonly used social cognition measures -- the change-of-location false belief task [@wimmer1983beliefs; @baron-cohen1985does] -- the TANGO-CC has several advantages: a continuous outcome measure that can capture individual differences from three years to adulthood, a short task duration that allows for more trials per child, stimuli that can be easily adapted, and known psychometric properties across 17 communities.
 The task is presented as a web app that enables efficient data collection with large sample sizes, while it can also be used to collect data offline in locations without a reliable internet connection.
-The TANGO--CC follows a standardized procedure, which leaves no room for rater errors and greatly simplifies online training of research assistants.
+The TANGO-CC follows a standardized procedure, which prevents rater errors and greatly simplifies online training of research assistants.
 Furthermore, minimal language demands and an engaging, playful design increase the task's usability and reduce non-completion rates.
 
-The TANGO--CC is a screen-based task. 
-@bohn2024universal have shown that children with no prior touchscreen exposure were less precise in the TANGO--CC than children with prior experience.
-However, individual differences were also found in communities with 100% touchscreen exposure, showing that this factor alone could not explain children's performance in the task [@bohn2024universal].
-Notably, even though the touchscreen experience caused absolute differences in task performance, all communities showed the same processing signature. 
-A recent computational cognitive model described gaze following as a process of estimating pupil angles and the corresponding gaze vectors [@prein2024variation].
+The TANGO-CC will be a useful asset for exploring a range of research questions.
+First, the TANGO-CC could be applied to assessing relationships between gaze following and other (social-) cognitive constructs.
+Examples include the relationship between gaze following and Theory of Mind [@prein2024variation] or eye gaze in sharing behaviors and Dictator games [@kelsey2018earlya; @manesi2016eyes; @nettle2013watching; @wu2018shea].
+Second, the TANGO-CC could be used to examine the influence of environmental factors on gaze following.
+Environmental factors of interest could include household size [@bohn2024understanding] or maternal postpartum depression [@astor2022maternal].
+Third, scores in the TANGO-CC could predict performance in other tasks at later time points.
+This would be helpful for assessing predictive validity of gaze following, for example for language comprehension [@prein2024tango].
+Fourth, the TANGO-CC could be applied to measure children’s gaze following development longitudinally, potentially combined with interim interventions.
+The task is suitable for children, teenagers, and adults alike and is sensitive to individual differences throughout the lifespan (established in a German sample; @prein2024tango).
+
+The TANGO-CC is a screen-based task. 
+@bohn2024universal have shown that children with no prior touchscreen exposure were less precise in the TANGO-CC than children with prior experience.
+Therefore, the mode of stimulus presentation needs to be kept in mind when administering the TANGO-CC, especially in communities with little technology exposure.
+Additional touchscreen training (e.g., more trials of training 1) might prove helpful in these cases.
+If researchers are interested in controlling for an effect of stimulus presentation, we recommend gathering information on touchscreen exposure.
+
+Interestingly, individual differences were also present in communities with 100% touchscreen exposure, showing that this factor alone could not explain children's performance in the task [@bohn2024universal].
+Even though the touchscreen experience caused absolute differences in task performance, all communities showed the same processing signature: Children were more precise in trials in which the agent looked to a more central position (i.e., higher target centrality) compared to a position to the far left or right of the screen.
+A computational cognitive model predicted this processing signature and described gaze following as a process of estimating pupil angles and the corresponding gaze vectors [@prein2024variation].
 @bohn2024universal found clear support for this model in every community studied, suggesting that children all over the world process gaze in a similar way.
-Nevertheless, the mode of stimulus presentation needs to be kept in mind when administering the TANGO--CC, especially in communities with little technology exposure.
-Additional touchscreen training (e.g., more trials of training 1) might prove helpful in these cases.
+Alternative theories on gaze following exist, but have not been cross-culturally validated to date. 
+@doherty2015developmentally proposed two separate gaze processing systems based on luminance versus geometric cues. 
+Other theoretical accounts assign a central role to reinforcement learning [@corkum1998origins; @ishikawa2020learning; @silverstein2021infants; @triesch2006gaze] or self-other equivalence (“like me”, @meltzoff2007me, @meltzoff2005imitation).
 
 @schilbach2013secondperson pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions.
-First evidence suggests that the TANGO--CC indeed taps into social cognition as utilized in real life: @prein2024variation found that children's perspective-taking abilities in a personal social interaction were linked to performance in the TANGO, but less so to a matched, non-social vector following task.
-However, this study exclusively relied on a German sample and future research should investigate whether the relationship between the TANGO--CC and perspective-taking abilities holds across communities.
+First evidence suggests that the TANGO-CC indeed taps into social cognition as utilized in real life: @prein2024variation found that children's perspective-taking abilities in a personal social interaction were linked to performance in the TANGO, but less so to a matched, non-social vector following task.
+However, this study exclusively relied on a German sample and future research should investigate whether the relationship between the TANGO-CC and perspective-taking abilities holds across communities.
 
@@
 Unfortunately, this might not always be feasible in large-scale cross-cultural studies due to organizational and financial constraints.
-An example of assessing the TANGO's predictive validity is a study conducted in Leipzig, Germany, which used the TANGO to predict children's receptive vocabulary 6 months later [@prein2023tango].
-Future cross-cultural studies could investigate the TANGO--CC's predictive validity and its relationship to other social-cognitive abilities (e.g., Theory of Mind, language development) in diverse communities.
+An example of assessing the TANGO's predictive validity is a study conducted in Leipzig, Germany, which used the TANGO to predict children's receptive vocabulary 6 months later [@prein2024tango].
+Future cross-cultural studies could investigate the TANGO-CC's predictive validity and its relationship to other social-cognitive abilities (e.g., Theory of Mind, language development) in diverse communities.
 
-Measurement invariance (*i.e.*, measuring the same construct across different communities) is often seen as a requirement for a “fair” cross-cultural comparison: it is important that any group differences are not the result of the task unintentionally tapping into different underlying constructs.
+Measurement invariance (i.e., measuring the same construct across different communities) is often seen as a requirement for a “fair” cross-cultural comparison: it is important that any group differences are not the result of the task unintentionally tapping into different underlying constructs.
 As @kusano2024mismeasure put it: "The research challenge is to achieve a balance between ensuring methodological “fairness” at the individual level while also recognizing and capturing genuine sociocultural variability" (p.
 34).
-We argue that the TANGO--CC measures a fundamental social-cognitive ability that is likely similar across communities.
+We argue that the TANGO-CC measures a fundamental social-cognitive ability that is likely similar across communities.
 @selcuk2023development pointed out that researchers should study both within- and between-culture variability in the development of social cognition since sometimes within-culture differences exceed between-culture differences.
 Indeed, we found that within-group variability was greater than between-group variability.
-While we believe that the TANGO--CC can be used to compare mean differences across communities, we would recommend using it to study individual differences within communities.
+While we believe that the TANGO-CC can be used to compare mean differences across communities, we would recommend using it to study individual differences within communities.
 
@@
 This underlines how efforts to improve replicability can be combined with the goal of increasing the generalisability of psychological research findings [@li2024developmental; @syed2021reproducibility].
-@li2024developmental have argued that replicable and generalizable results rely on stimulus sets with slight variations, more diverse samples, and data collection at a greater scale, which are indeed all steps the TANGO--CC has taken.
-Openly sharing the TANGO--CC's materials will allow other researchers to (hopefully) replicate the results and deepen our cumulative understanding of social-cognitive development across diverse communities.
+@li2024developmental have argued that replicable and generalizable results rely on stimulus sets with slight variations, more diverse samples, and data collection at a greater scale, which are indeed all steps the TANGO-CC has taken.
+Openly sharing the TANGO-CC's materials will allow other researchers to (hopefully) replicate the results and deepen our cumulative understanding of social-cognitive development across diverse communities.
 
@@
 
-The TANGO--CC captures individual differences in social-cognitive development across diverse communities.
+The TANGO-CC captures individual differences in social-cognitive development across diverse communities.
 The task’s customizability, minimal language demands, and its efficient data collection method make it a valuable tool for cross-cultural research.
 The task showed satisfactory to high reliability (internal consistency) in a large data set including 17 diverse communities on five continents.
-We hope that the TANGO--CC – and its pragmatic construction process – will provide a roadmap for future cross-cultural studies on cognitive development.
+We hope that the TANGO-CC – and its pragmatic construction process – will provide a roadmap for future cross-cultural studies on cognitive development.
 

### 2024-09-23 paper/manuscript.tex
revisions 1

@@
 \hypersetup{
-  pdftitle={Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC},
+  pdftitle={Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO-CC},
   pdfauthor={Julia Christin Prein (ORCID: 0000-0002-3154-6167)1,2, Florian M.
@@
 Manrique-Hernandez2, Shirley Magazi (ORCID: 0009-0006-0479-9800)9, Lizbeth Mújica-Manrique2, Julia Ohlendorf2, Damilola Olaoba2, Wesley R.
-Pieters (ORCID:0000-0002-6152-249X)9, Sarah Pope-Caldwell2, Umay Sen (ORCID: 0000-0001-9488-0851)10, Katie Slocombe (ORCID: 0000-0002-7310-1887)11, Robert Z.
-Sparks (ORCID: 0000-0001-7545-0522)5, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,9, Jahnavi Sunderarajan2, Kirsten Sutherland2, Florence Tusiime12, Wilson Vieira (ORCID: 0009-0001-9400-6328)2, Zhen Zhang (ORCID: 0000-0001-9300-0920)13, Yufei Zong (ORCID: 0009-0000-5012-0244)13, Daniel B.
+Pieters (ORCID:0000-0002-6152-249X)9, Sarah Pope-Caldwell2,10, Umay Sen (ORCID: 0000-0001-9488-0851)11, Katie Slocombe (ORCID: 0000-0002-7310-1887)12, Robert Z.
+Sparks (ORCID: 0000-0001-7545-0522)5, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,9, Jahnavi Sunderarajan2, Kirsten Sutherland2, Florence Tusiime13, Wilson Vieira (ORCID: 0009-0001-9400-6328)2, Zhen Zhang (ORCID: 0000-0001-9300-0920)14, Yufei Zong (ORCID: 0009-0000-5012-0244)14, Daniel B.
 M.
@@
 
-\title{Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC}
+\title{Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO-CC}
 \author{Julia Christin Prein (ORCID: 0000-0002-3154-6167)\textsuperscript{1,2}, Florian M.
@@
 Manrique-Hernandez\textsuperscript{2}, Shirley Magazi (ORCID: 0009-0006-0479-9800)\textsuperscript{9}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R.
-Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{9}, Sarah Pope-Caldwell\textsuperscript{2}, Umay Sen (ORCID: 0000-0001-9488-0851)\textsuperscript{10}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{11}, Robert Z.
-Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{5}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,9}, Jahnavi Sunderarajan\textsuperscript{2}, Kirsten Sutherland\textsuperscript{2}, Florence Tusiime\textsuperscript{12}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{13}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{13}, Daniel B.
+Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{9}, Sarah Pope-Caldwell\textsuperscript{2,10}, Umay Sen (ORCID: 0000-0001-9488-0851)\textsuperscript{11}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{12}, Robert Z.
+Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{5}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,9}, Jahnavi Sunderarajan\textsuperscript{2}, Kirsten Sutherland\textsuperscript{2}, Florence Tusiime\textsuperscript{13}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{14}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{14}, Daniel B.
 M.
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg, Germany\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany\\\textsuperscript{3} School of Psychology, University of Auckland, New Zealand\\\textsuperscript{4} Université Marien Ngouabi, Republic of the Congo\\\textsuperscript{5} Department of Psychology, Stanford University, USA\\\textsuperscript{6} School of Psychology, University of Plymouth, UK\\\textsuperscript{7} Department of Psychology, Koç University, Türkiye\\\textsuperscript{8} Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK\\\textsuperscript{9} Department of Psychology and Social Work, University of Namibia, Namibia\\\textsuperscript{10} Department of Psychology, Developmental Psychology, Uppsala University, Sweden\\\textsuperscript{11} Department of Psychology, University of York, UK\\\textsuperscript{12} Budongo Conservation Field Station, Uganda\\\textsuperscript{13} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China\\\textsuperscript{+} joint last author}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg, Germany\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany\\\textsuperscript{3} School of Psychology, University of Auckland, New Zealand\\\textsuperscript{4} Université Marien Ngouabi, Republic of the Congo\\\textsuperscript{5} Department of Psychology, Stanford University, USA\\\textsuperscript{6} School of Psychology, University of Plymouth, UK\\\textsuperscript{7} Department of Psychology, Koç University, Türkiye\\\textsuperscript{8} Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK\\\textsuperscript{9} Department of Psychology and Social Work, University of Namibia, Namibia\\\textsuperscript{10} Department of Psychology, Georgia State University, USA\\\textsuperscript{11} Department of Psychology, Developmental Psychology, Uppsala University, Sweden\\\textsuperscript{12} Department of Psychology, University of York, UK\\\textsuperscript{13} Budongo Conservation Field Station, Uganda\\\textsuperscript{14} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China\\\textsuperscript{+} joint last author}
 
@@
 However, cross-cultural assessment tools in cognition across languages and communities are limited.
-This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (TANGO--CC).
+This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (TANGO-CC).
 The task was developed and psychometrically assessed in one cultural setting and, with input of local collaborators, adapted for cross-cultural data collection.
 Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community.
-The TANGO--CC captures individual- and community-level variation and shows good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities.
+The TANGO-CC captures individual- and community-level variation and shows good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities.
 Within-community variation outweighed between-community variation.
 We provide an open-source website for researchers to customize and use the task (\url{https://ccp-odc.eva.mpg.de/tango-cc}).
-The TANGO--CC can be used to assess basic social cognition in diverse communities and provides a roadmap for researching community-level and individual-level differences across cultures.
+The TANGO-CC can be used to assess basic social cognition in diverse communities and provides a roadmap for researching community-level and individual-level differences across cultures.
 }
@@
 While studies in the Global North often apply the Still-Face Paradigm to assess infants' reactions to unresponsive partners, Wefers et al.
-(2023) reasoned that this paradigm might not capture infants' everyday interaction routines in communities with proximal (\emph{i.e.,} emphasis on body stimulation) parenting styles.
+(2023) reasoned that this paradigm might not capture infants' everyday interaction routines in communities with proximal (i.e., emphasis on body stimulation) parenting styles.
 By developing the novel No-Touch Paradigm, they found that indeed infants' responses to unresponsive partners were modulated by the cultural context in which they grew up: Kichwa infants from rural Ecuador showed stronger reactions to unresponsive partners in the No-Touch Paradigm compared to the Still-Face Paradigm, while reactions of urban German infants differed less in both paradigms.
 
-At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed ``adoption'' and ``adaptation'', respectively; Waschl \& Chen (2022)).
+At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed ``adoption'' and ``adaptation'', respectively; He and Vijver (2012), Waschl and Chen (2022)).
 This approach is less sensitive to each community's unique characteristics but renders quantitative comparisons of data more feasible.
-An example following this approach is the Multilingual Assessment Instrument for Narratives (MAIN; (Gagarina et al., 2012)), which assesses narrative abilities in mono- and multilingual children.
+An example following this approach is the Multilingual Assessment Instrument for Narratives (MAIN; Gagarina et al. (2012)), which assesses narrative abilities in mono- and multilingual children.
 Extensive piloting and adaptation of MAIN materials ensured that the instrument is culturally appropriate, robust, and suitable for cross-linguistic comparisons (Gagarina et al., 2012), and new and revised language versions are continuously added to the MAIN database (Gagarina \& Lindgren, 2020).
@@
 Gaze following develops early in infancy (Del Bianco et al., 2019; Tang et al., 2024) and contributes to social learning, communication, and collaboration (Bohn \& Köymen, 2018; Hernik \& Broesch, 2019; Shepherd, 2010; Tomasello et al., 2007).
-While the question of how social-environmental and cultural factors impact gaze following was recently posed as one of the big open questions in gaze following research (Astor \& Gredebäck, 2022), studies focusing on cultural variations of gaze following are rare.
+Identifying the attentional focus of a conversational partner facilitates language development (Brooks \& Meltzoff, 2015; Carpenter et al., 1998; Mundy et al., 2007), as children might use gaze to identify the referent of a new word (Brooks \& Meltzoff, 2005).
+
+One of the main open questions is the impact of social-environmental and cultural factors on gaze following (Astor \& Gredebäck, 2022), but studies on variation in gaze following across communities are rare.
+Recently, Brooks et al. (2020) found that Deaf infants show increased gaze following compared to hearing infants, underlining the importance of visual-communicative signals for Deaf children.
 Callaghan et al. (2011) investigated gaze following behind barriers in 12- and 17-month-olds from rural Canada (n = 35), Peru (n = 38), and India (n = 65).
@@
 Even though face-to-face interactions are less common in parent-child interactions in Vanuatu than in Western communities, the result patterns of gaze following in Ni-Vanuatu infants resembled those of their Western counterparts: infants from Vanuatu followed the agent's gaze to the target object only when preceded by infant-directed, and not adult-directed, speech.
-While these two studies point towards potential cross-cultural stability of gaze following, the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings and -- more importantly -- does not allow for studying individual-differences.
-A more comprehensive cross-cultural study on gaze following was recently conducted by Bohn et al.
+Astor et al.
+(2022) analyzed the effects of maternal postpartum depression on gaze following in 9-month-olds from Bhutan and Sweden.
+While infants showed similar gaze following rates in both countries, maternal postpartum depression was associated with reduced gaze following only in the Swedish sample.
+Beyond gaze following, some studies conducted in the Global South have investigated opportunities for mutual eye gaze and factors influencing joint attention (see Akhtar \& Gernsbacher, 2008).
+For example, Kaluli infants in Papua New Guinea are often carried facing away from their mothers so infants and caregivers share mutual gaze less frequently (Ochs \& Schieffelin, 1984).
+Childers et al.
+(2007) studied Ngas-speaking infants in Nigeria and found no effect of the caregivers' carrying style (usually on the back) on children's joint attention tendencies.
+
+While these studies point towards potential cross-cultural stability of gaze following, the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings and -- more importantly -- does not allow for studying individual-differences.
+A more comprehensive cross-cultural study on gaze following was recently conducted by Bohn, Prein, et al.
 (2024).
@@
 
-The task presented in this manuscript was developed for the study by Bohn et al.
-(2024) and is based on a previously established gaze-following task called `TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by Prein et al.
-(2023).
+The task presented in this manuscript was developed for the study by Bohn, Prein, et al.
+(2024) and is based on a previously established gaze-following task called `TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by Prein, Kalinke, et al.
+(2024).
 The TANGO measures how precisely participants locate an agent's attentional focus.
-It reliably measured individual differences in a German child sample and an English-speaking remote adult sample (Prein et al., 2023).
+It reliably measured individual differences in a German child sample and an English-speaking remote adult sample (Prein, Kalinke, et al., 2024).
 However, we cannot claim the task's generalizability and reliability based on a mono-cultural sample.
-This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 diverse communities (Bohn et al., 2024).
+This paper showcases the TANGO-CC (TANGO - Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 diverse communities (Bohn, Prein, et al., 2024).
 We describe the task's development and provide a tutorial for the open-source website (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).
@@
 
-The TANGO-CC was implemented in Leipzig, Germany, and thoroughly assessed in terms of reliability and validity (Prein et al., 2023).
+The TANGO-CC was implemented in Leipzig, Germany, and thoroughly assessed in terms of reliability and validity (Prein, Kalinke, et al., 2024).
 During this process, the cross-cultural adaptation of the task was prepared by a team of cross-cultural psychologists and cognitive scientists.
-In this paper, we assess the TANGO--CC's measurement quality (\emph{i.e.,} variability and reliability) across 17 diverse communities by analyzing the data set from Bohn et al. (2024).
+In this paper, we assess the TANGO-CC's measurement quality (i.e., variability and reliability) across 17 diverse communities by analyzing the data set from Bohn, Prein, et al. (2024).
 In the following, we describe the different steps in detail.
 
-The TANGO--CC is a screen-based task that measures the imprecision with which participants locate a balloon by following an agent's gaze (see Figure \ref{fig:fig1}).
+The TANGO-CC is a screen-based, interactive picture book with cartoon-like line drawings (see Figure \ref{fig:fig1}).
+Previous gaze studies have successfully implemented tasks with (schematic) line drawings for both children and adults (e.g., Anderson \& Doherty, 1997; Doherty et al., 2009; Doherty \& Anderson, 1999; Kingstone et al., 2000; Lee et al., 1998).
+The TANGO-CC measures the imprecision with which participants locate a balloon by following an agent's gaze.
 Participants click or touch the location on the screen where they believe the balloon to be.
@@
 We programmed a function that calculates the x and y coordinates of where the agent's pupil and iris should move to follow the balloon, given the eyes' and balloon's original positions and measures.
-As the measures of the eyes and balloon are read out dynamically from the image on screen, stimuli can be easily adapted and exchanged (\emph{i.e.}, no coordination values for animation are hard-coded into the task's source code).
-After having programmed this ``backbone'' functionality of the task (\emph{i.e.}, animate the eyes so that they follow the balloon), we added the task's audio instructions and superficial appearance (e.g., background scene, hedge, agent faces).
-
-This basic version of the TANGO was psychometrically evaluated in a German child sample and an English-speaking remote adult sample and was found to be highly reliable and valid (Prein et al., 2023).
+As the measures of the eyes and balloon are read out dynamically from the image on screen, stimuli can be easily adapted and exchanged (i.e., no coordination values for animation are hard-coded into the task's source code).
+After having programmed this ``backbone'' functionality of the task (i.e., animate the eyes so that they follow the balloon), we added the task's audio instructions and superficial appearance (e.g., background scene, hedge, agent faces).
+
+This basic version of the TANGO was psychometrically evaluated in a German child sample and an English-speaking remote adult sample and was found to be highly reliable and valid (Prein, Kalinke, et al., 2024).
 While children became more precise in locating the agent's attentional focus with age, individuals differed across all age groups and showed no floor- or ceiling effects.
 In the Leipzig sample, performance in the TANGO was weakly related to factors of children's daily social environment and could predict children's receptive vocabulary 6 months later.
-In a computational cognitive model, Prein et al.
+In a computational cognitive model, Prein, Maurits, et al.
 (2024) described gaze following as a form of social vector following and empirically found that performance in the TANGO was related to children's non-social vector following and visual perspective-taking abilities.
@@
 Sometimes, specific words were slightly modified in the target language (e.g., ``bush'' instead of ``hedge'') to ensure that all participants understood the instructions well.
-Based on these adaptations, the TANGO--CC could be applied in 17 communities and 13 different languages (Bohn et al., 2024).
-In the following, we describe how researchers can use and customize the TANGO--CC in more detail.
-
-\subsection{Features of the TANGO--CC}\label{features-of-the-tangocc}
+Based on these adaptations, the TANGO-CC could be applied in 17 communities and 13 different languages (Bohn, Prein, et al., 2024).
+In the following, we describe how researchers can use and customize the TANGO-CC in more detail.
+
+\subsection{Features of the TANGO-CC}\label{features-of-the-tango-cc}
 
@@
 The balloon falls down to the ground. The eyes of the agent follow the movement of the balloon in a way that the balloon center and the pupil center always align.
-Depending on the trial type, participants have different visual access to the balloon's position.
+Depending on the trial type, participants' visual access to the balloon's position varies.
+This experimental design builds on existing gaze following paradigms that have used barriers or obstacles (e.g., Butler et al., 2000; Dunphy-Lelii \& Wellman, 2004; Franco \& Gagliano, 2001; Moll \& Tomasello, 2004).
 In training 1, participants see the full trajectory of the balloon and directly have to click the balloon itself.
@@
 In test trials, a hedge grows at the beginning of the trial and participants see neither the movement nor the final position of the balloon.
+
 The first trial of each type contains an audio description of the presented events (see Supplements).
 Notably, the instructions explicitly state that the agent is looking at the balloon.
+This ensures all participants understand the purpose of the task, and minimizes learning effects (increasing comparability between earlier and later trials; avoiding that participants notice the gaze cue only after e.g.~half of the trials).
+The TANGO-CC measures \emph{how precisely} participants use the gaze cue, rather than \emph{if} they notice it in the first place.
 
@@
 All agents, balloon colors, and bins appear equally often and are not repeated in more than two consecutive trials.
-If the total number of trials is not divisible by the number of unique elements, some elements (\emph{i.e.,} some agents, balloon colors, bins) are randomly repeated to make up for the remainder.
+If the total number of trials is not divisible by the number of unique elements, some elements (i.e., some agents, balloon colors, bins) are randomly repeated to make up for the remainder.
 
@@
 
-When researchers visit the TANGO--CC's website
+When researchers visit the TANGO-CC's website
 (\url{https://ccp-odc.eva.mpg.de/tango-cc/}), they can select the language for audio instructions which are currently available for 13 different languages and five more dialects (see Table 1).
@@
 (1) for using their own audio instructions in the offline version of the task, researchers can download the task, exchange the audio instructions in the dist folder (in the folder sounds \textgreater{} custom) and select ``Custom'' in the language drop-down menu.
-For detailed instructions, see the TANGO--CC's manual (\url{https://ccp-odc.eva.mpg.de/tango-cc/manual.html}).
+For detailed instructions, see the TANGO-CC's manual (\url{https://ccp-odc.eva.mpg.de/tango-cc/manual.html}).
 (2) For adding a new language in the online version of the task, researchers can contact the first author of this paper.
@@
 The task can either be started with the default settings or further customized by adapting the number of trials, agents, and background scenes.
-The default settings use the version applied in Bohn et al. (2024) based on the selected language (see Supplements).
+The default settings use the version applied in Bohn, Prein, et al. (2024) based on the selected language (see Supplements).
 
@@
 By directly editing the \texttt{HTML} and \texttt{JavaScript} code, researchers can further modify the task as needed.
+To ensure the accessibility of the TANGO--CC long-term, we have additionally stored the source code on Zenodo (\url{https://zenodo.org/doi/10.5281/zenodo.13643836}).
 
 We created a public OSF page (\url{https://doi.org/10.17605/OSF.IO/P2EGU}) on which we plan to collect data sets that used the TANGO-CC.
-Researchers who have collected data using the TANGO--CC can share their data with the community by contacting the first author of this paper or visiting the OSF repository.
+Researchers who have collected data using the TANGO-CC can share their data with the community by contacting the first author of this paper or visiting the OSF repository.
 
@@
 
-\caption{\label{tab:langtab}Current language options available for the audio instructions in the TANGO--CC}
+\caption{\label{tab:langtab}Current language options available for the audio instructions in the TANGO-CC}
 
@@
 
-\caption{\textbf{Screenshot of the customizable components of the TANGO--CC.} Researchers can select the language of the audio instructions (see Table 1), the number of trials per trial type, the background, and the agent's face.}\label{fig:fig2}
+\caption{\textbf{Screenshot of the customizable components of the TANGO-CC.} Researchers can select the language of the audio instructions (see Table 1), the number of trials per trial type, the background, and the agent's face.}\label{fig:fig2}
 \end{figure}
@@
 Participant's responses can be recorded on a touchscreen or with a mouse or trackpad.
-The online version of the task can be used for unsupervised data collection (for example, using online platforms like \emph{Prolific}; see Prein et al.
-(2023)).
+The online version of the task can be used for unsupervised data collection (for example, using online platforms like \emph{Prolific}; see Prein, Kalinke, et al.
+(2024)).
 The task can be shared easily internationally by providing the URL.
@@
 
-The stimuli are embedded as Scalable Vector Graphics (SVG; an image format that stores image elements via mathematical formulas based on points and lines on a grid).
+The stimuli are embedded as Scalable Vector Graphics (SVG; an XML format that describes elements in mathematical formulas based on points and lines on a grid).
 SVGs ensure that the picture quality, aspect ratio, and relative object positioning are constant.
 Furthermore, stimuli are added as individual components to the image scene which allows for an easy adaptation of the task's elements (in contrast to other image formats that consist of only one combined layer that would need entire replacement).
-The task is programmed so that responses are only registered when the participant clicks the relevant part of the screen (\emph{i.e.,} in test trials, when they click the hedge).
+The task is programmed so that responses are only registered when the participant clicks the relevant part of the screen (i.e., in test trials, when they click the hedge).
 Furthermore, clicks are only registered after the voice recordings stop playing.
@@
 
-We used the data set from Bohn et al. (2024) for the psychometric evaluation of the TANGO--CC.
-The data set contains a sample of \emph{N} = 1377 children, aged 2.5 to 11 years.
+We used the data set from Bohn, Prein, et al. (2024) for the psychometric evaluation of the TANGO-CC.
+The data set contains a sample of \emph{N} = 1377 children, aged 2.5 to 11 years (see supplements).
 Participants came from 17 communities on five continents, in rural and urban settings, with varying degrees of market integration and technology exposure.
-Bohn et al. (2024) carried out 19 trials (1 training 1, 2 training 2, and 16 test trials, of which the first of each type had audio instructions) on a touchscreen device.
+Bohn, Prein, et al. (2024) carried out 19 trials (1 training 1, 2 training 2, and 16 test trials, of which the first of each type had audio instructions) on a touchscreen device.
 Faces, backgrounds, and languages were chosen by researchers and assistants with experience in the specific community.
-For further details on the communities, participant information, and data collection procedures, see the supplements of Bohn et al. (2024).
+For further details on the communities, participant information, and data collection procedures, see the supplements of Bohn, Prein, et al. (2024).
 
@@
 
-\caption{\textbf{Variability measured by the TANGO--CC.} Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type.
+\caption{\textbf{Variability measured by the TANGO-CC.} Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type.
 Imprecision is defined as the distance between the participant's click and the balloon's center in units of balloon width.
@@
 
-To formally estimate the effect of trial type on performance in the TANGO--CC, we fitted a generalized linear mixed model (GLMM) predicting the task performance by trial type (reference category: test trials).
-All analyses were run in R version 4.4.0 (2024-04-24) (R Core Team, 2024).
+To formally estimate the effect of trial type on performance in the TANGO-CC, we fitted a generalized linear mixed model (GLMM) predicting the task performance by trial type (reference category: test trials).
+All analyses were run in R version 4.4.1 (2024-06-14) (R Core Team, 2024).
 GLMMs were fitted with default priors using the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017, 2018).
@@
 
-Our GLMM analysis supported the visual inspection of the data: the fixed-effect estimates for training 1 (\(\beta\) = -3.26; 95\% CrI {[}-3.41; -3.10{]}) and training 2 (\(\beta\) = -1.47; 95\% CrI {[}-1.58; -1.35{]}) were negative and reliably different from zero.\footnote{Please note that the TANGO--CC measures imprecision in gaze following.
-  Therefore, a negative sign indicates that children showed less imprecision (\emph{i.e.,} were more precise) in the training trials than in the test trials.}
+Our GLMM analysis supported the visual inspection of the data: the fixed-effect estimates for training 1 (\(\beta\) = -3.26; 95\% CrI {[}-3.41; -3.10{]}) and training 2 (\(\beta\) = -1.47; 95\% CrI {[}-1.58; -1.35{]}) were negative and reliably different from zero.\footnote{Please note that the TANGO-CC measures imprecision in gaze following.
+  Therefore, a negative sign indicates that children showed less imprecision (i.e., were more precise) in the training trials than in the test trials.}
 This effect was found across all communities (random effects of trial type within community: minimum estimate for training 1 = -2.87; 95\%CrI {[}-3.11; -2.60{]}; minimum estimate for training 2 = -1.27; 95\%CrI {[}-1.51; -0.98{]}).
@@
 
-\caption{\textbf{Reliability of the TANGO--CC by community.} Internal consistency estimates by community, following three different approaches.
+\caption{\textbf{Reliability of the TANGO-CC by community.} Internal consistency estimates by community, following three different approaches.
 In the odd-even split, the size of points reflects the sample size in each community.
@@
 First, data of each participant was split into odd and even trials and a Pearson correlation was calculated between the aggregated scores of the two halves.
-Second, using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2022), data was stratified by target centrality (capturing trial difficulty), and a Pearson correlation was calculated between the matched halves.
+Second, using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2022), data was stratified by target centrality, and a Pearson correlation was calculated between the matched halves.
+Target centrality measured how closely the target landed to the center of the screen (i.e., distance from the balloon center to the screen center), which served as a proxy for trial difficulty and was previously found to be a relevant component in predicting participants' performance in a cognitive model (Prein, Maurits, et al., 2024).
 Third, a data set was generated with stratified test halves by target centrality and we applied the GLMM approach introduced by Rouder and Haaf (2019).
@@
 However, Kline (1999) suggested that values below .7 could be realistic for psychological constructs due to their variable nature.}
-The results are comparable to the internal consistency estimates found in the original TANGO study (Prein et al., 2023), and also resemble reliability estimates of classical false belief tasks (Hughes et al., 2000).
+The results are comparable to the internal consistency estimates found in the original TANGO study (Prein, Kalinke, et al., 2024), and also resemble reliability estimates of classical false belief tasks (Hughes et al., 2000).
 
@@
 
-The TANGO--CC measures imprecision in gaze following across individuals, ages, and communities.
+The TANGO-CC measures imprecision in gaze following across individuals, ages, and communities.
 Children's imprecision in gaze following showed highly similar result patterns across communities: children performed better in the training than the test trials, and within-community variation greatly exceeded between-community variation.
 Furthermore, the task showed satisfactory to high reliability across all communities.
-Therefore, the TANGO--CC is a suitable task to capture individual differences in social-cognitive development in diverse communities.
-
-The TANGO--CC's design process lays out a much-needed pragmatic approach to studying community-level and individual-level differences across cultures:
+Therefore, the TANGO-CC is a suitable task to capture individual differences in social-cognitive development in diverse communities.
+
+The TANGO-CC's design process lays out a much-needed pragmatic approach to studying community-level and individual-level differences across cultures:
 While we performed a detailed psychometric evaluation of the task in a German setting, we collaborated with local researchers for the cross-cultural stimulus development and selection.
-Importantly, we re-assessed the TANGO--CC's psychometric properties in a large and diverse data set.
-While we cannot generalize our findings to all communities worldwide, we found that the TANGO-CC captured reliable individual variation in all 17 communities studied by Bohn et al. (2024).
-We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful to other researchers.
+Importantly, we re-assessed the TANGO-CC's psychometric properties in a large and diverse data set.
+While we cannot generalize our findings to all communities worldwide, we found that the TANGO-CC captured reliable individual variation in all 17 communities studied by Bohn, Prein, et al. (2024).
+We hope that not just the TANGO-CC but also our pragmatic approach to constructing it will be helpful to other researchers.
 We recommend that researchers consider generalizability concerns and cross-cultural applications of their tasks and collaborate with local researchers at the early stages of task development (Torréns et al., 2023).
-Using the TANGO--CC (or any other task) in a new community requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
+Using the TANGO-CC (or any other task) in a new community requires sensitivity to the specific context, piloting, and, most importantly, the involvement of researchers or research assistants from the specific community.
 
 Bourdage et al. (2023) pointed out a major challenge with adapting social cognition tasks to diverse communities: the number of world cultures is vast, and communities are constantly changing.
-Therefore, a promising approach might be to provide tasks with a modular system where components can be modified (\emph{i.e.}, building block structure).
-In the case of the TANGO--CC, the task cannot only be adapted to different languages, cartoon faces, and backgrounds (see Figure \ref{fig:fig2}) but also updated with new stimuli.
-Unlike studies that present sequential, hand-painted pictures that are difficult to adapt (Mehta et al., 2011), the TANGO--CC uses SVGs (Scalable Vector Graphics) that can be easily exchanged.
-
-Compared to one of the most commonly used social cognition measures -- the change-of-location false belief task (Baron-Cohen et al., 1985; Wimmer \& Perner, 1983) -- the TANGO--CC has several advantages: a continuous outcome measure that can capture individual differences from three years to adulthood, a short task duration that allows for more trials per child, stimuli that can be easily adapted, and known psychometric properties across 17 communities.
+Therefore, a promising approach might be to provide tasks with a modular system where components can be modified (i.e., building block structure).
+In the case of the TANGO-CC, the task cannot only be adapted to different languages, cartoon faces, and backgrounds (see Figure \ref{fig:fig2}) but also updated with new stimuli.
+Unlike studies that present sequential, hand-painted pictures that are difficult to adapt (Mehta et al., 2011), the TANGO-CC uses SVGs (Scalable Vector Graphics) that can be easily exchanged.
+
+Compared to one of the most commonly used social cognition measures -- the change-of-location false belief task (Baron-Cohen et al., 1985; Wimmer \& Perner, 1983) -- the TANGO-CC has several advantages: a continuous outcome measure that can capture individual differences from three years to adulthood, a short task duration that allows for more trials per child, stimuli that can be easily adapted, and known psychometric properties across 17 communities.
 The task is presented as a web app that enables efficient data collection with large sample sizes, while it can also be used to collect data offline in locations without a reliable internet connection.
-The TANGO--CC follows a standardized procedure, which leaves no room for rater errors and greatly simplifies online training of research assistants.
+The TANGO-CC follows a standardized procedure, which prevents rater errors and greatly simplifies online training of research assistants.
 Furthermore, minimal language demands and an engaging, playful design increase the task's usability and reduce non-completion rates.
 
-The TANGO--CC is a screen-based task.
-Bohn et al. (2024) have shown that children with no prior touchscreen exposure were less precise in the TANGO--CC than children with prior experience.
-However, individual differences were also found in communities with 100\% touchscreen exposure, showing that this factor alone could not explain children's performance in the task (Bohn et al., 2024).
-Notably, even though the touchscreen experience caused absolute differences in task performance, all communities showed the same processing signature.
-A recent computational cognitive model described gaze following as a process of estimating pupil angles and the corresponding gaze vectors (Prein et al., 2024).
-Bohn et al. (2024) found clear support for this model in every community studied, suggesting that children all over the world process gaze in a similar way.
-Nevertheless, the mode of stimulus presentation needs to be kept in mind when administering the TANGO--CC, especially in communities with little technology exposure.
+The TANGO-CC will be a useful asset for exploring a range of research questions.
+First, the TANGO-CC could be applied to assessing relationships between gaze following and other (social-) cognitive constructs.
+Examples include the relationship between gaze following and Theory of Mind (Prein, Maurits, et al., 2024) or eye gaze in sharing behaviors and Dictator games (Kelsey et al., 2018; Manesi et al., 2016; Nettle et al., 2013; Wu et al., 2018).
+Second, the TANGO-CC could be used to examine the influence of environmental factors on gaze following.
+Environmental factors of interest could include household size (Bohn, Fong, et al., 2024) or maternal postpartum depression (Astor et al., 2022).
+Third, scores in the TANGO-CC could predict performance in other tasks at later time points.
+This would be helpful for assessing predictive validity of gaze following, for example for language comprehension (Prein, Kalinke, et al., 2024).
+Fourth, the TANGO-CC could be applied to measure children's gaze following development longitudinally, potentially combined with interim interventions.
+The task is suitable for children, teenagers, and adults alike and is sensitive to individual differences throughout the lifespan (established in a German sample; Prein, Kalinke, et al.
+(2024)).
+
+The TANGO-CC is a screen-based task.
+Bohn, Prein, et al. (2024) have shown that children with no prior touchscreen exposure were less precise in the TANGO-CC than children with prior experience.
+Therefore, the mode of stimulus presentation needs to be kept in mind when administering the TANGO-CC, especially in communities with little technology exposure.
 Additional touchscreen training (e.g., more trials of training 1) might prove helpful in these cases.
+If researchers are interested in controlling for an effect of stimulus presentation, we recommend gathering information on touchscreen exposure.
+
+Interestingly, individual differences were also present in communities with 100\% touchscreen exposure, showing that this factor alone could not explain children's performance in the task (Bohn, Prein, et al., 2024).
+Even though the touchscreen experience caused absolute differences in task performance, all communities showed the same processing signature: Children were more precise in trials in which the agent looked to a more central position (i.e., higher target centrality) compared to a position to the far left or right of the screen.
+A computational cognitive model predicted this processing signature and described gaze following as a process of estimating pupil angles and the corresponding gaze vectors (Prein, Maurits, et al., 2024).
+Bohn, Prein, et al. (2024) found clear support for this model in every community studied, suggesting that children all over the world process gaze in a similar way.
+Alternative theories on gaze following exist, but have not been cross-culturally validated to date.
+Doherty et al. (2015) proposed two separate gaze processing systems based on luminance versus geometric cues.
+Other theoretical accounts assign a central role to reinforcement learning (Corkum \& Moore, 1998; Ishikawa et al., 2020; Silverstein et al., 2021; Triesch et al., 2006) or self-other equivalence (``like me'', Meltzoff (2007), Meltzoff (2005)).
 
 Schilbach et al. (2013) pointed out that witnessing social interactions as an observer undoubtedly differs from actively participating in social interactions.
-First evidence suggests that the TANGO--CC indeed taps into social cognition as utilized in real life: Prein et al.
+First evidence suggests that the TANGO-CC indeed taps into social cognition as utilized in real life: Prein, Maurits, et al.
 (2024) found that children's perspective-taking abilities in a personal social interaction were linked to performance in the TANGO, but less so to a matched, non-social vector following task.
-However, this study exclusively relied on a German sample and future research should investigate whether the relationship between the TANGO--CC and perspective-taking abilities holds across communities.
+However, this study exclusively relied on a German sample and future research should investigate whether the relationship between the TANGO-CC and perspective-taking abilities holds across communities.
 
@@
 Unfortunately, this might not always be feasible in large-scale cross-cultural studies due to organizational and financial constraints.
-An example of assessing the TANGO's predictive validity is a study conducted in Leipzig, Germany, which used the TANGO to predict children's receptive vocabulary 6 months later (Prein et al., 2023).
-Future cross-cultural studies could investigate the TANGO--CC's predictive validity and its relationship to other social-cognitive abilities (e.g., Theory of Mind, language development) in diverse communities.
-
-Measurement invariance (\emph{i.e.}, measuring the same construct across different communities) is often seen as a requirement for a ``fair'' cross-cultural comparison: it is important that any group differences are not the result of the task unintentionally tapping into different underlying constructs.
+An example of assessing the TANGO's predictive validity is a study conducted in Leipzig, Germany, which used the TANGO to predict children's receptive vocabulary 6 months later (Prein, Kalinke, et al., 2024).
+Future cross-cultural studies could investigate the TANGO-CC's predictive validity and its relationship to other social-cognitive abilities (e.g., Theory of Mind, language development) in diverse communities.
+
+Measurement invariance (i.e., measuring the same construct across different communities) is often seen as a requirement for a ``fair'' cross-cultural comparison: it is important that any group differences are not the result of the task unintentionally tapping into different underlying constructs.
 As Kusano et al.
 (2024) put it: ``The research challenge is to achieve a balance between ensuring methodological ``fairness'' at the individual level while also recognizing and capturing genuine sociocultural variability'' (p.~34).
-We argue that the TANGO--CC measures a fundamental social-cognitive ability that is likely similar across communities.
+We argue that the TANGO-CC measures a fundamental social-cognitive ability that is likely similar across communities.
 Selcuk et al.
@@
 Indeed, we found that within-group variability was greater than between-group variability.
-While we believe that the TANGO--CC can be used to compare mean differences across communities, we would recommend using it to study individual differences within communities.
+While we believe that the TANGO-CC can be used to compare mean differences across communities, we would recommend using it to study individual differences within communities.
 
@@
 Li et al.
-(2024) have argued that replicable and generalizable results rely on stimulus sets with slight variations, more diverse samples, and data collection at a greater scale, which are indeed all steps the TANGO--CC has taken.
-Openly sharing the TANGO--CC's materials will allow other researchers to (hopefully) replicate the results and deepen our cumulative understanding of social-cognitive development across diverse communities.
+(2024) have argued that replicable and generalizable results rely on stimulus sets with slight variations, more diverse samples, and data collection at a greater scale, which are indeed all steps the TANGO-CC has taken.
+Openly sharing the TANGO-CC's materials will allow other researchers to (hopefully) replicate the results and deepen our cumulative understanding of social-cognitive development across diverse communities.
 
@@
 
-The TANGO--CC captures individual differences in social-cognitive development across diverse communities.
+The TANGO-CC captures individual differences in social-cognitive development across diverse communities.
 The task's customizability, minimal language demands, and its efficient data collection method make it a valuable tool for cross-cultural research.
 The task showed satisfactory to high reliability (internal consistency) in a large data set including 17 diverse communities on five continents.
-We hope that the TANGO--CC -- and its pragmatic construction process -- will provide a roadmap for future cross-cultural studies on cognitive development.
+We hope that the TANGO-CC -- and its pragmatic construction process -- will provide a roadmap for future cross-cultural studies on cognitive development.
 
@@
 Adolphs, R. (1999). Social cognition and the human brain. \emph{Trends in Cognitive Sciences}, \emph{3}(12), 469--479. \url{https://doi.org/10.1016/S1364-6613(99)01399-6}
+
+\bibitem[\citeproctext]{ref-akhtar2008privileging}
+Akhtar, N., \& Gernsbacher, M.
+A.
+(2008).
+On {Privileging} the {Role} of {Gaze} in {Infant Social Cognition}.
+\emph{Child Development Perspectives}, \emph{2}(2), 59--65.
+\url{https://doi.org/10.1111/j.1750-8606.2008.00044.x}
 
@@
 \url{https://doi.org/10.1016/j.evolhumbehav.2020.06.006}
+
+\bibitem[\citeproctext]{ref-anderson1997preschoolers}
+Anderson, J.
+R., \& Doherty, M.
+J.
+(1997).
+Preschoolers' perception of other people's looking: {Photographs} and drawings.
+\emph{Perception}, \emph{26}(3), 333--343.
+\url{https://doi.org/10.1068/p260333}
 
@@
 Gaze following in infancy: {Five} big questions that the field should answer.
-In \emph{Advances in {Child Development} and {Behavior}} (p.
-S0065240722000192).
+In \emph{Advances in {Child Development} and {Behavior}} (Vol.
+63, pp.
+191--223).
 Elsevier.
 \url{https://doi.org/10.1016/bs.acdb.2022.04.003}
+
+\bibitem[\citeproctext]{ref-astor2022maternal}
+Astor, K., Lindskog, M., Juvrud, J., Wangchuk, Namgyel, S.
+C., Wangmo, T., Tshering, K., \& Gredebäck, G.
+(2022).
+Maternal postpartum depression impacts infants' joint attention differentially across cultures.
+\emph{Developmental Psychology}, \emph{58}(12), 2230--2238.
+\url{https://doi.org/10.1037/dev0001413}
 
@@
 \url{https://doi.org/10.3389/fpsyg.2019.02905}
+
+\bibitem[\citeproctext]{ref-bohn2024understanding}
+Bohn, M., Fong, F.
+T.
+K., Pope-Caldwell, S., Stengelin, R., \& Haun, D.
+B.
+M.
+(2024).
+Understanding cultural variation in cognition one child at a time.
+\emph{Nature Reviews Psychology}.
+\url{https://doi.org/10.1038/s44159-024-00351-8}
 
@@
 
+\bibitem[\citeproctext]{ref-brooks2005development}
+Brooks, R., \& Meltzoff, A.
+N.
+(2005).
+The development of gaze following and its relation to language.
+\emph{Developmental Science}, \emph{8}(6), 535--543.
+\url{https://doi.org/10.1111/j.1467-7687.2005.00445.x}
+
+\bibitem[\citeproctext]{ref-brooks2015connecting}
+Brooks, R., \& Meltzoff, A.
+N.
+(2015).
+Connecting the dots from infancy to childhood: {A} longitudinal study connecting gaze following, language, and explicit theory of mind.
+\emph{Journal of Experimental Child Psychology}, \emph{130}, 67--78.
+\url{https://doi.org/10.1016/j.jecp.2014.09.010}
+
+\bibitem[\citeproctext]{ref-brooks2020enhanced}
+Brooks, R., Singleton, J.
+L., \& Meltzoff, A.
+N.
+(2020).
+Enhanced gaze-following behavior in {Deaf} infants of {Deaf} parents.
+\emph{Developmental Science}, \emph{23}(2), e12900.
+\url{https://doi.org/10.1111/desc.12900}
+
 \bibitem[\citeproctext]{ref-burkner2017brms}
@@
 Bürkner, P.-C. (2018). Advanced {Bayesian Multilevel Modeling} with the {R Package} brms. \emph{The R Journal}, \emph{10}(1), 395. \url{https://doi.org/10.32614/RJ-2018-017}
+
+\bibitem[\citeproctext]{ref-butler2000infant}
+Butler, S.
+C., Caron, A.
+J., \& Brooks, R.
+(2000).
+Infant {Understanding} of the {Referential Nature} of {Looking}.
+\emph{Journal of Cognition and Development}, \emph{1}(4), 359--377.
+\url{https://doi.org/10.1207/S15327647JCD0104_01}
 
@@
 
+\bibitem[\citeproctext]{ref-carpenter1998social}
+Carpenter, M., Nagell, K., \& Tomasello, M.
+(1998).
+\href{https://www.ncbi.nlm.nih.gov/pubmed/9835078}{Social cognition, joint attention, and communicative competence from 9 to 15 months of age}.
+\emph{Monographs of the Society for Research in Child Development}, \emph{63}(4), i--vi, 1--143.
+
+\bibitem[\citeproctext]{ref-childers2007jointa}
+Childers, J.
+B., Vaughan, J., \& Burquest, D.
+A.
+(2007).
+Joint attention and word learning in {Ngas-speaking} toddlers in {Nigeria}.
+\emph{Journal of Child Language}, \emph{34}(2), 199--225.
+\url{https://doi.org/10.1017/S0305000906007835}
+
 \bibitem[\citeproctext]{ref-cohen1988statistical}
@@
 
+\bibitem[\citeproctext]{ref-corkum1998origins}
+Corkum, V., \& Moore, C. (1998). The origins of joint visual attention in infants. \emph{Developmental Psychology}, \emph{34}(1), 28--38. \url{https://doi.org/10.1037/0012-1649.34.1.28}
+
 \bibitem[\citeproctext]{ref-decety2020social}
-Decety, J. (Ed.). (2020). \emph{The social brain: {A} developmental perspective} (pp. xii, 426). The MIT Press. \url{https://doi.org/10.7551/mitpress/11970.001.0001}
+Decety, J. (Ed.). (2020). \emph{The social brain: {A} developmental perspective}. The MIT Press.
 
@@
 \url{https://doi.org/10.1111/infa.12276}
+
+\bibitem[\citeproctext]{ref-doherty1999new}
+Doherty, M.
+J., \& Anderson, J.
+R.
+(1999).
+A new look at gaze: {Preschool} children's understanding of eye-direction.
+\emph{Cognitive Development}, \emph{14}(4), 549--571.
+\url{https://doi.org/10.1016/s0885-2014(99)00019-2}
+
+\bibitem[\citeproctext]{ref-doherty2009rapid}
+Doherty, M.
+J., Anderson, J.
+R., \& Howieson, L.
+(2009).
+The rapid development of explicit gaze judgment ability at 3 years.
+\emph{Journal of Experimental Child Psychology}, \emph{104}(3), 296--312.
+\url{https://doi.org/10.1016/j.jecp.2009.06.004}
+
+\bibitem[\citeproctext]{ref-doherty2015developmentally}
+Doherty, M.
+J., McIntyre, A.
+H., \& Langton, S.
+R.
+H.
+(2015).
+Developmentally distinct gaze processing systems: {Luminance} versus geometric cues.
+\emph{Cognition}, \emph{137}, 72--80.
+\url{https://doi.org/10.1016/j.cognition.2015.01.001}
+
+\bibitem[\citeproctext]{ref-dunphy-lelii2004infants}
+Dunphy-Lelii, S., \& Wellman, H.
+M.
+(2004).
+Infants' understanding of occlusion of others' line-of-sight: {Implications} for an emerging theory of mind.
+\emph{European Journal of Developmental Psychology}, \emph{1}(1), 49--66.
+\url{https://doi.org/10.1080/17405620444000049}
 
@@
 Field, A., Miles, J., \& Field, Z. (2012). \emph{Discovering statistics using {R}}. Sage.
+
+\bibitem[\citeproctext]{ref-franco2001toddlers}
+Franco, F., \& Gagliano, A. (2001). Toddlers' pointing when joint attention is obstructed. \emph{First Language}, \emph{21}(63), 289--321. \url{https://doi.org/10.1177/014272370102106305}
 
@@
 The weirdest people in the world?
-\emph{The Behavioral and Brain Sciences}, \emph{33}(2-3), 61-83; discussion 83-135.
+\emph{The Behavioral and Brain Sciences}, \emph{33}(2-3), 61--135.
 \url{https://doi.org/10.1017/S0140525X0999152X}
@@
 Infant gaze following depends on communicative signals: {An} eye-tracking study of 5- to 7-month-olds in {Vanuatu}.
-\emph{Developmental Science}, \emph{22}(4), e12779.
+\emph{Developmental Science}, \emph{22}(4), 1--8.
 \url{https://doi.org/10.1111/desc.12779}
@@
 \url{https://doi.org/10.1111/1469-7610.00633}
+
+\bibitem[\citeproctext]{ref-ishikawa2020learning}
+Ishikawa, M., Senju, A., \& Itakura, S.
+(2020).
+Learning {Process} of {Gaze Following}: {Computational Modeling Based} on {Reinforcement Learning}.
+\emph{Frontiers in Psychology}, \emph{11}(213), 1--10.
+\url{https://doi.org/10.3389/fpsyg.2020.00213}
+
+\bibitem[\citeproctext]{ref-kelsey2018earlya}
+Kelsey, C., Grossmann, T., \& Vaish, A.
+(2018).
+Early {Reputation Management}: {Three-Year-Old Children Are More Generous Following Exposure} to {Eyes}.
+\emph{Frontiers in Psychology}, \emph{9}.
+\url{https://doi.org/10.3389/fpsyg.2018.00698}
+
+\bibitem[\citeproctext]{ref-kingstone2000reflexive}
+Kingstone, A., Friesen, C.
+K., \& Gazzaniga, M.
+S.
+(2000).
+Reflexive {Joint Attention Depends} on {Lateralized Cortical Connections}.
+\emph{Psychological Science}, \emph{11}(2), 159--166.
+\url{https://doi.org/10.1111/1467-9280.00232}
 
@@
 \url{https://doi.org/10.31234/osf.io/9qe2k}
+
+\bibitem[\citeproctext]{ref-lee1998children}
+Lee, K., Eskritt, M., Symons, L.
+A., \& Muir, D.
+(1998).
+Children's use of triadic eye gaze information for "mind reading".
+\emph{Developmental Psychology}, \emph{34}(3), 525--539.
+\url{https://doi.org/10.1037//0012-1649.34.3.525}
 
@@
 Lillard, A. (1998). Ethnopsychologies: {Cultural} variations in theories of mind. \emph{Psychological Bulletin}, \emph{123}(1), 3--32. \url{https://doi.org/10.1037/0033-2909.123.1.3}
+
+\bibitem[\citeproctext]{ref-manesi2016eyes}
+Manesi, Z., Van Lange, P.
+A.
+M., \& Pollet, T.
+V.
+(2016).
+Eyes {Wide Open}: {Only Eyes That Pay Attention Promote Prosocial Behavior}.
+\emph{Evolutionary Psychology}, \emph{14}(2), 1474704916640780.
+\url{https://doi.org/10.1177/1474704916640780}
 
@@
 
+\bibitem[\citeproctext]{ref-meltzoff2005imitation}
+Meltzoff, A.
+N.
+(2005).
+Imitation and {Other Minds}: {The} "{Like Me}" {Hypothesis}.
+In \emph{Perspectives on imitation: {From} neuroscience to social science: {Vol}.
+2: {Imitation}, human development, and culture} (pp.
+55--77).
+MIT Press.
+
+\bibitem[\citeproctext]{ref-meltzoff2007me}
+Meltzoff, A. N. (2007). {``{Like} me''}: A foundation for social cognition. \emph{Developmental Science}, \emph{10}(1), 126--134. \url{https://doi.org/10.1111/j.1467-7687.2007.00574.x}
+
+\bibitem[\citeproctext]{ref-moll200412}
+Moll, H., \& Tomasello, M.
+(2004).
+12- and 18-month-old infants follow gaze to spaces behind barriers.
+\emph{Developmental Science}, \emph{7}(1), F1--F9.
+\url{https://doi.org/10.1111/j.1467-7687.2004.00315.x}
+
+\bibitem[\citeproctext]{ref-mundy2007individual}
+Mundy, P., Block, J., Delgado, C., Pomares, Y., Van Hecke, A.
+V., \& Parlade, M.
+V.
+(2007).
+Individual differences and the development of joint attention in infancy.
+\emph{Child Development}, \emph{78}(3), 938--954.
+\url{https://doi.org/10.1111/j.1467-8624.2007.01042.x}
+
+\bibitem[\citeproctext]{ref-nettle2013watching}
+Nettle, D., Harper, Z., Kidson, A., Stone, R., Penton-Voak, I.
+S., \& Bateson, M.
+(2013).
+The watching eyes effect in the {Dictator Game}: It's not how much you give, it's being seen to give something.
+\emph{Evolution and Human Behavior}, \emph{34}(1), 35--40.
+\url{https://doi.org/10.1016/j.evolhumbehav.2012.08.004}
+
 \bibitem[\citeproctext]{ref-nielsen2017persistent}
@@
 
+\bibitem[\citeproctext]{ref-ochs1984language}
+Ochs, E., \& Schieffelin, B.
+B.
+(1984).
+Language acquisition and socialization: {Three} developmental stories and their implications.
+In R.
+A.
+Shweder \& R.
+A.
+LeVine (Eds.), \emph{Culture theory: {Essays} on mind, self, and emotion} (pp.
+276--320).
+Cambridge University Press.
+
 \bibitem[\citeproctext]{ref-pena2007lost}
@@
 
-\bibitem[\citeproctext]{ref-prein2023tango}
+\bibitem[\citeproctext]{ref-prein2024tango}
 Prein, J.
@@
 M., \& Bohn, M.
-(2023).
+(2024).
 {TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults.
@@
 (2024).
-\emph{Variation in gaze following across the life span: {A} process-level perspective}.
-PsyArXiv.
-\url{https://doi.org/10.31234/osf.io/dy73a}
+Variation in gaze following across the life span: {A} process-level perspective.
+\emph{Developmental Science}, Article e13546.
+\url{https://doi.org/10.1111/desc.13546}
 
@@
 
+\bibitem[\citeproctext]{ref-silverstein2021infants}
+Silverstein, P., Feng, J., Westermann, G., Parise, E., \& Twomey, K.
+E.
+(2021).
+Infants {Learn} to {Follow Gaze} in {Stages}: {Evidence Confirming} a {Robotic Prediction}.
+\emph{Open Mind}, \emph{5}, 174--188.
+\url{https://doi.org/10.1162/opmi_a_00049}
+
 \bibitem[\citeproctext]{ref-syed2021reproducibility}
@@
 \url{https://doi.org/10.1026/0049-8637/a000271}
+
+\bibitem[\citeproctext]{ref-triesch2006gaze}
+Triesch, J., Teuscher, C., Deák, G.
+O., \& Carlson, E.
+(2006).
+Gaze following: Why (not) learn it?
+\emph{Developmental Science}, \emph{9}(2), 125--147.
+\url{https://doi.org/10.1111/j.1467-7687.2006.00470.x}
 
@@
 
+\bibitem[\citeproctext]{ref-wu2018shea}
+Wu, Z., Chen, X., Gros-Louis, J., \& Su, Y.
+(2018).
+{``{She} is looking at me!
+{Shall I} share?''} {How Chinese} and {American} preschoolers respond to eye gaze during sharing.
+\emph{Social Development}, \emph{27}(2), 447--460.
+\url{https://doi.org/10.1111/sode.12278}
+
 \bibitem[\citeproctext]{ref-zeigler-hill2015how}

### 2024-09-23 supplements/supplements.Rmd
revisions 1

@@
 
+```{r}
+data <- read_csv("../data/data.csv") %>%
+  mutate(continent = ifelse(
+    community %in% c("leipzig", "plymouth"), "Europe",
+    ifelse(
+      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
+      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "Americas",
+             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
+    )
+  ))%>%
+  mutate(continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
+  mutate(community = recode(community,
+                            akure = "Akure (Nigeria)",
+                            leipzig = "Leipzig (Germany)",
+                            `hai||om` = "Hai||om (Namibia)",
+                            khwe = "Khwe (Namibia)",
+                            windhoek = "Windhoek (Namibia)",
+                            stanford = "Stanford (USA)",
+                            chimfunshi = "Chimfunshi (Zambia)",
+                            mexico = "Ocuilan (Mexico)",
+                            plymouth = "Plymouth (UK)",
+                            beijing = "Beijing (China)",
+                            india = "Pune (India)",
+                            buenos_aires = "Buenos Aires (Argentina)",
+                            auckland = "Auckland (New Zealand)",
+                            turkey = "Malatya (Türkiye)",
+                            bandongo = "Bandongo (Rep. Congo)",
+                            bayaka = "BaYaka (Rep. Congo)",
+                            uganda = "Nyabyeya (Uganda)"),
+      imprecision = abs(clickdistfromtargetcenterx)/160,
+      centrality = as.character(abs(5-targetposition)), 
+      age_group = floor(ageinyears)) %>% 
+  filter(trialtype == "test", voiceover == F) %>%
+  mutate(trialnr = as.numeric(factor(trialnr))) 
+```
+
+# Participants
+
+```{r demtable, echo=F}
+demtab <- data %>%
+  separate(community, into = c("community", "country"), sep = " \\(")%>%
+  mutate(country = str_remove(country, "\\("),
+         country = str_remove(country, "\\)"))%>%
+  distinct(subjid, .keep_all = T)%>%
+  group_by(community, country, continent)%>%
+  summarise(N = n_distinct(subjid), 
+            mean_age = mean(ageinyears),
+            min_age = min(ageinyears), 
+            max_age = max(ageinyears))%>%
+  mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
+  mutate(age = mean_age, 
+         range = paste(min_age, " - ", max_age)) %>%
+  select(-c(mean_age, min_age, max_age))%>%
+  arrange(community)
+
+kableExtra::kable(demtab,
+             col.names = c("Community", "Country", "Continent", "N", "Sex (male)", "Age (range)"),
+              caption = "Participant demographics.", 
+             format="latex", booktabs=TRUE
+             )
+```
+
 # Voice-over script 

### 2024-09-23 supplements/supplements.tex
revisions 1

@@
 
+\section{Participants}\label{participants}
+
+\begin{table}
+
+\caption{\label{tab:demtable}Participant demographics.}
+\centering
+\begin{tabular}[t]{llllll}
+\toprule
+Community & Country & Continent & N & Sex (male) & Age (range)\\
+\midrule
+Akure & Nigeria & Africa & 114 & 5.07 & 2.57  -  7.33\\
+Auckland & New Zealand & Oceania & 43 & 5.14 & 2.81  -  8.75\\
+BaYaka & Rep. Congo & Africa & 29 & 7.80 & 3.94  -  10.56\\
+Bandongo & Rep. Congo & Africa & 30 & 7.45 & 3.50  -  10.95\\
+Beijing & China & Asia & 123 & 5.47 & 2.69  -  8.48\\
+\addlinespace
+Buenos Aires & Argentina & Americas & 105 & 4.72 & 3.00  -  6.96\\
+Chimfunshi & Zambia & Africa & 22 & 5.98 & 2.88  -  8.00\\
+Hai||om & Namibia & Africa & 60 & 5.85 & 2.74  -  8.34\\
+Khwe & Namibia & Africa & 59 & 5.84 & 3.38  -  8.63\\
+Leipzig & Germany & Europe & 100 & 4.88 & 2.53  -  6.95\\
+\addlinespace
+Malatya & Türkiye & Asia & 85 & 5.02 & 2.75  -  7.12\\
+Nyabyeya & Uganda & Africa & 125 & 5.94 & 2.67  -  8.92\\
+Ocuilan & Mexico & Americas & 127 & 4.96 & 2.57  -  6.95\\
+Plymouth & UK & Europe & 70 & 6.02 & 2.38  -  8.94\\
+Pune & India & Asia & 148 & 6.14 & 3.06  -  8.83\\
+\addlinespace
+Stanford & USA & Americas & 98 & 4.99 & 2.52  -  7.90\\
+Windhoek & Namibia & Africa & 39 & 5.69 & 2.66  -  8.66\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \section{Voice-over script}\label{voice-over-script}

### 2024-11-26 paper/manuscript.Rmd
add README files for project and data explanation, add comments to analysis script, update figures for production

@@
   - name          : "Yufei Zong (ORCID: 0009-0000-5012-0244)"
-    affiliation   : "14"
+    affiliation   : "14,15"
     role:
@@
     institution   : "CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China"
+  - id            : "15"
+    institution   : "Department of Cognitive Sciences, University of California Irvine, USA"
   - id            : "+"
@@
 documentclass     : "apa7"
-output            : 
-  papaja::apa6_pdf:
-    latex_engine: xelatex
-    keep_tex: true
+output            : papaja::apa6_word
 editor_options    : 

### 2024-11-26 paper/manuscript.tex
add README files for project and data explanation, add comments to analysis script, update figures for production

@@
 Pieters (ORCID:0000-0002-6152-249X)9, Sarah Pope-Caldwell2,10, Umay Sen (ORCID: 0000-0001-9488-0851)11, Katie Slocombe (ORCID: 0000-0002-7310-1887)12, Robert Z.
-Sparks (ORCID: 0000-0001-7545-0522)5, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,9, Jahnavi Sunderarajan2, Kirsten Sutherland2, Florence Tusiime13, Wilson Vieira (ORCID: 0009-0001-9400-6328)2, Zhen Zhang (ORCID: 0000-0001-9300-0920)14, Yufei Zong (ORCID: 0009-0000-5012-0244)14, Daniel B.
+Sparks (ORCID: 0000-0001-7545-0522)5, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,9, Jahnavi Sunderarajan2, Kirsten Sutherland2, Florence Tusiime13, Wilson Vieira (ORCID: 0009-0001-9400-6328)2, Zhen Zhang (ORCID: 0000-0001-9300-0920)14, Yufei Zong (ORCID: 0009-0000-5012-0244)14,15, Daniel B.
 M.
@@
 Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{9}, Sarah Pope-Caldwell\textsuperscript{2,10}, Umay Sen (ORCID: 0000-0001-9488-0851)\textsuperscript{11}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{12}, Robert Z.
-Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{5}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,9}, Jahnavi Sunderarajan\textsuperscript{2}, Kirsten Sutherland\textsuperscript{2}, Florence Tusiime\textsuperscript{13}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{14}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{14}, Daniel B.
+Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{5}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,9}, Jahnavi Sunderarajan\textsuperscript{2}, Kirsten Sutherland\textsuperscript{2}, Florence Tusiime\textsuperscript{13}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{14}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{14,15}, Daniel B.
 M.
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg, Germany\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany\\\textsuperscript{3} School of Psychology, University of Auckland, New Zealand\\\textsuperscript{4} Université Marien Ngouabi, Republic of the Congo\\\textsuperscript{5} Department of Psychology, Stanford University, USA\\\textsuperscript{6} School of Psychology, University of Plymouth, UK\\\textsuperscript{7} Department of Psychology, Koç University, Türkiye\\\textsuperscript{8} Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK\\\textsuperscript{9} Department of Psychology and Social Work, University of Namibia, Namibia\\\textsuperscript{10} Department of Psychology, Georgia State University, USA\\\textsuperscript{11} Department of Psychology, Developmental Psychology, Uppsala University, Sweden\\\textsuperscript{12} Department of Psychology, University of York, UK\\\textsuperscript{13} Budongo Conservation Field Station, Uganda\\\textsuperscript{14} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China\\\textsuperscript{+} joint last author}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg, Germany\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany\\\textsuperscript{3} School of Psychology, University of Auckland, New Zealand\\\textsuperscript{4} Université Marien Ngouabi, Republic of the Congo\\\textsuperscript{5} Department of Psychology, Stanford University, USA\\\textsuperscript{6} School of Psychology, University of Plymouth, UK\\\textsuperscript{7} Department of Psychology, Koç University, Türkiye\\\textsuperscript{8} Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK\\\textsuperscript{9} Department of Psychology and Social Work, University of Namibia, Namibia\\\textsuperscript{10} Department of Psychology, Georgia State University, USA\\\textsuperscript{11} Department of Psychology, Developmental Psychology, Uppsala University, Sweden\\\textsuperscript{12} Department of Psychology, University of York, UK\\\textsuperscript{13} Budongo Conservation Field Station, Uganda\\\textsuperscript{14} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China\\\textsuperscript{15} Department of Cognitive Sciences, University of California Irvine, USA\\\textsuperscript{+} joint last author}
 
@@
 Variation in gaze following across the life span: {A} process-level perspective.
-\emph{Developmental Science}, Article e13546.
+\emph{Developmental Science}, \emph{27}(6), e13546.
 \url{https://doi.org/10.1111/desc.13546}

### 2024-11-26 stats/analysis.Rmd
revisions 1
add README files for project and data explanation, add comments to analysis script, update figures for production

@@
 author: "Julia Prein"
-date: "10/27/2023"
+date: "11/26/2024"
 output: pdf_document
@@
 ```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
+# Load packages
 library(tidyverse) # data handling etc.
@@
 ```{r load_data}
+# Read in data set 
 complete_data <- read_csv("../data/data.csv")
@@
 ```{r data_preparation}
+# Prepare data set, clean community names, create continent variable, calculate imprecision, centrality, age group
 # complete dataset, with all trials
@@
 
-# dataset with test trials only 
+# Filter data set for test trials without audio instructions
 data <- all_trials %>%
@@
 ```{r sample}
-# full sample, check for less than 4 test trials
+# Original sample, check for less than 4 test trials
 all_trials %>%
@@
 
-# exclude children with less than 4 test trials (1 training 1, 2 training 2, 1 test with audio instructions + 4 test trials = 8 min)
+# Filter: exclude children with less than 4 test trials (1 training 1, 2 training 2, 1 test with audio instructions + 4 test trials = 8 min)
 exclude <- all_trials %>%
@@
 ```{r samplesize_table}
-# sample size table
+# Create sample size table
 sample_table <- data %>%
@@
 ```{r trialtypes_model}
+# Model for variation in imprecision by trial type
+# First, prepare data
 mdata <- all_trials %>% 
@@
 
+# Run model
 mtrialtypes <- brm(imprecision ~ trialtype + (trialtype | community),
@@
 
+# Extract estimates
 # ranef(mtrialtypes)
@@
 ```{r model_draws}
+# Extract draws from model for plotting
+
 # newdata <- mdata %>% 
@@
 ```{r training_trials}
+# Plot for variation in imprecision by trial type
 # function to suppress labels
@@
 
+# prepare plot data
 descr_trialtypes <- all_trials %>% 
@@
 
+# plot
 training_trials_plot <- all_trials %>% 
@@
 
+ggsave("../figures/tango-cc-variability.pdf", width = 15, height = 11, scale = 0.7, bg = "white")
 ggsave("../figures/tango-cc-variability.png", width = 15, height = 11, scale = 0.7, bg = "white")
@@
 ```{r icc}
+# Calculate ICC, first prepare data
 within_person <- data %>%
@@
 ```{r odd_even_plot}
+# Calculate odd-even split
 int_con <- data %>%
@@
 
+# Plot
 odd_even_plot <- int_con %>% 
@@
 ```{r stratified_data}
+# Calculate stratified internal consistency
 fn_mean <- function(ds) {
@@
 
+# empty tibble to store results
 strat <- tibble()
 
+# loop over communities, 50 iterations, stratified by target position
 communities <- unique(data$community)
@@
 ```{r stratified_plot}
+# Plot stratified internal consistency
 stratified_plot <- strat %>%   
@@
 ```{r stratified_agecorrected_data}
-# estimate age-corrected reliability
+# Estimate age-corrected, stratified reliability
 # run model first for one community to use update()
@@
 
+# prepare data
 sdata <- bind_rows(
@@
 
+# run model
 strat_age_model <- brm(impr ~ age + (0 + half | subjid),
@@
 
+# empty tibble to store results
 strat_age <- tibble()
 
+# loop over communities, 50 iterations, stratified by target position
 for (j in c(1:50)) {
@@
 
+    # update model for each community
     com_mod <- update(strat_split_model,
@@
 
+    # extract correlation between testhalves for each community as reliability estimate 
     cor <- summary(com_mod)$random$subjid %>%
@@
 ```{r stratified_agecorrected_plot}
+# Plot stratified and age-corrected internal consistency
 stratified_agecorrected_plot <- strat_age %>% 
@@
 ```{r combine_data}
+# Combine internal consistency data
 int_con <- full_join(
@@
 
-```{r}
-library(ggplot2)
-library(ggridges)
-
-# Create example data
-data <- data.frame(
-  x = rnorm(1000),
-  y = as.factor(rep(1:10, each = 100))
-)
-
-# Plot using geom_density_ridges
-ggplot(data, aes(x = x, y = y)) +
-  geom_density_ridges()
-
-```
-
 ```{r combine_plot}
+# Combine plots and arrange for publication figure
 odd_even_plot <- readRDS("../saves/odd_even_plot.rds")
@@
 
+ggsave("../figures/tango-cc-reli.pdf", width = 12, height = 6, scale = 0.8, bg = "white")
 ggsave("../figures/tango-cc-reli.png", width = 12, height = 6, scale = 0.8, bg = "white")
@@
 ```{r sd_int_plot}
+# Calculate correlation between community SD and internal consistency
+# general trend: higher internal consistency estimates when larger individual variation
+
 # var_df <- readRDS("../saves/var_df.rds")
